### 2014-12-16 LaTeX/SMGs_summary2.tex
Initial commit
This repository contains software and data files needed to reproduce
the research that will be published in Bussmann et al. 2015.

\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{multirow}
%\usepackage{subfig}

%\input epsf.sty
%\topmargin   0.25in
\topmargin -.5cm \textheight 21cm

\oddsidemargin -.125cm

\textwidth 16cm

\newcommand{\ra}{\rangle}
\newcommand{\la}{\langle}
\newcommand{\T}{\widetilde \Phi_{CFT}}
\newcommand{\Cn}{{\cal C}_n}
\newcommand{\vp}{\varphi}

\newcommand{\B}{b'}
\newcommand{\C}{c'}
\newcommand{\bB}{\bar b'}
\newcommand{\bC}{\bar c'}
\newcommand{\Bu}{B_{\vec u}}
\newcommand{\VV}{{\cal V}}
\newcommand{\II}{{\cal I}}
\newcommand{\HH}{{\cal H}}
\newcommand{\MM}{{\cal M}}
\newcommand{\BB}{{\cal B}}
\newcommand{\CC}{{\cal C}}
\newcommand{\OO}{{\cal O}}
\newcommand{\QQ}{{\cal Q}}
\newcommand{\PP}{{\cal P}}
\newcommand{\EE}{{\cal E}}
\newcommand{\LL}{{\cal L}}
\newcommand{\SSS} {{\cal S}}
%\newcommand{\lll}{\langle\langle}
%\newcommand{\rrr}{\rangle\rangle}
\newcommand{\half}{{1\over 2}}
\newcommand{\wt}{\widetilde}
\newcommand{\wh}{\widehat}
\newcommand{\wc}{\check}
\newcommand{\wb}{\bar}
\newcommand{\RR}{{\cal R}}
\newcommand{\NN}{{\cal N}}
\newcommand{\TT}{{\cal T}}
\newcommand{\bet}{\beta'}
\newcommand{\gam}{\gamma'}
\newcommand{\WW}{{\cal W}}
\newcommand{\nl}{\hspace{-.65cm}}
\newcommand{\bd}{\begin{displaymath}}
\newcommand{\ed}{\end{displaymath}}
\newcommand{\ba}{\begin{eqnarray}}
\newcommand{\ea}{\end{eqnarray}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\ben}{\begin{eqnarray}}
\newcommand{\een}{\end{eqnarray}}
\newcommand{\refb}[1]{(\ref{#1})}
\newcommand{\p}{\partial}
\newcommand{\sectiono}[1]{\section{#1}}
\setcounter{equation}{0}
\renewcommand{\theequation}{\thesection.\arabic{equation}}

\def\sqr#1#2{{\vcenter{\vbox{\hrule height.#2pt
         \hbox{\vrule width.#2pt height#1pt \kern#1pt
            \vrule width.#2pt}
         \hrule height.#2pt}}}}
\def\square{\mathop{\mathchoice\sqr66\sqr66\sqr{3.75}4\sqr34\,}\nolimits}

\begin{document} 
\section{Methodology}
By comparing the statistic of the observed lensed galaxies to the theoretical
predictions one can constrain the intrinsic luminosity function. Here we make
use of the observed sub-mm galaxies  located between $z = 1$ and $z = 4$ with
the  redshift distribution of sources from Simpson et al. 2014 \cite{Simpson:2014lr}, $
dN/dz \propto \exp\left[-(\ln(z+1)-\ln(1+z_\mu))^2/2\sigma_z^2\right]/\left[(z+1)\sigma_z\sqrt{2\pi}\right]$, where $z_\mu = 2.6$, $\sigma_z = 0.2$ to constrain the intrinsic luminosity function. To this end, we test several theoretical models which include broken power law and Schechter luminosity functions with various parameters and test them against the data. Similar analysis appeared, e.g.  in  Lima et al. 2010a \cite{Lima:2010a}, Lima et al. 2010b \cite{Lima:2010b}, Wardlow et al. (2013) \cite{Wardlow:2013}, etc.

 In the following we first describe our way to model the foreground population, we then discuss the calculation of the lensing statistics, and, finally, we list our choices for the intrinsic luminosity functions.

\subsection{Magnification by an individual lens}

We begin by summarizing the properties of the lenses. We use two ways to model our halos: (1) as a single isothermal sphere (SIS), and (2) a NFW profile (Navarro et al. 1997).  The NFW profile describes the outskirts of halos better whereas the SIS profile is good in describing the inside of a halo since it yields the  observed flat rotational curves. Here we make use of the both profiles to create the total probability distribution function.

In general, the magnification can be calculated as follows 
\begin{equation}
\mu(\theta) = \frac{1}{(1-\kappa(\theta))^2-|\gamma(\theta)|^2},
\end{equation}
where  $\theta$ is the angular  coordinate in the lens plane, $\kappa$ is the convergence and $\gamma $ the shear, which depend on the properties of the lens and its distance from the source.

We start with the NFW halos. In this case the convergence and shear are given by 
\begin{equation}
\kappa_{NFW}(\theta) = \frac{M_{vir}fc_{200}^2}{2\pi r_{200}^2}\frac{F\left(c_{200}\theta/\theta_{200}\right)}{\Sigma_{cr}}~~~~\textrm{and}~~~~\gamma(\theta) = \frac{M_{vir}f c_{200}^2}{2\pi r_{200}^2}\frac{G\left(c_{200}\theta/\theta_{200}\right)}{\Sigma_{cr}},
\label{Eq:kappa}\end{equation}
with  the critical projected density is given by  
\begin{equation}
\Sigma_{cr} = \frac{1}{4\pi G(1+z)}\frac{D_A^s)}{D_A^l)D_A^{ls})},
\end{equation}
where $D_A^s$, $D_A^l$ and $D_A^{ls}$  are the angular diameter distance between the observer and the source,  the observer and the lens and the lens and the source respectively. In eq.  \ref{Eq:kappa}  F and G are two functions given by Takada and Jian 2003 \cite{Takada:2003}, for which we assumed a truncated NFW profile (truncated at $r_{vir}$).  $M_{vir}$ is the virial mass, $r_{200}$ is the comoving virial radius, $\theta_{200}$ is the angular size on the lens plane which corresponds to  $r_{200}$, $c_{200}$ is the concentration parameter of the dark matter halos calculated as in Diemer and Kravtsov (2014) \cite{Diemer:2014} and  $f = \left[\log(1+c_{200})-c_{200}/(1+c_{200})\right]^{-1}$.

The magnification of SIS can be written as  
\begin{equation}
\mu_{SIS}(\theta)= \left(1-\frac{\theta_E}{|\theta|}\right)^{-1},~~~~\textrm{with}~~~~\theta_E = 4\pi\frac{\sigma_V^2}{c^2}\frac{D_{A}(r_{ls})}{D_A(r_s)}.
\end{equation}
Here $\sigma_V^2$ is the velocity  dispersion which we take from a simulation by Evrard et al. (2008) \cite{Evrard:2008}. In this simulation the dependence of $\sigma_V^2$ on the halo mass and redshift is provided which allows us to apply our model to high and low redshift galaxies.

Next for each given source we need to sum up the contributions to the total magnification from different lenses. Here we generate abundances of halos at each redshift using the Sheth-Tormen (1999) \cite{Sheth:1999} formalism which gives the number of halos per unit volume in each mass bin.

\subsection{Lensing Statistics}

The magnification of a source galaxy by a foreground galaxy depends on the profile of the foreground galaxy, redshifts of the lens and of the source and the impact parameter.  To model the probability distribution of lensing the  procedure is as follows. We first model the differential probability distribution $P(\mu)$ for a particular pair of source which emits light at $z_s$ and lens of mass $M_l$ which deflects the the light ray at $z_l$ where we account for a wide range of impact parameters. We next sum over the distribution of redshift sources and the masses and the redshifts of the  lenses to get the total probability distribution function.

Next, we calculate the total probability for lensig with the magnification larger than some $\mu$, $P(>\mu)$ and the probability density for magnification $\mu$, $P(\mu) = -dP(>\mu)/d\mu$. In this we generally follow the approach taken in Lima et al. (2010a) \cite{Lima:2010a}.

It should be noted that neither SIS nor NFW profiles fully describe the observations with SIS being a better match at small distances from the halo center and NFW better describing the outskirts. To be closer to reality,  we smoothly glue the probability densities $P_{SIS}(\mu)$ and $P_{NFW}(\mu)$ so that the former dominates at large magnifications (small impact parameters) and the latter dominates at small  magnifications (large impact parameters). We make sure that the resulting probability density, $P_{tot}(\mu)$, is normalized to unity.

We further use this probability density to estimate the effect of lensing on the observed luminosity function. To this end we calculate the mean magnification at given observed flux and compare it to data  \begin{equation}
 <\mu>(S_{obs}) = \int_0^\infty \mu P(\mu|S_{obs})  d\mu,
 \end{equation}
where the probability for lesning with magnification $\mu$ given the observed flux \cite{Lima:2010b} is
\begin{equation}
P(\mu|S_{obs}) = \frac{1}{N}\frac{P(\mu)}{\mu}\frac{dn}{dS}\left(\frac{S_{obs}}{\mu}\right), ~~~\textrm{where}~~~N = \frac{dn_{obs}(S_{obs})}{dS_{obs}} = \int  \frac{P(\mu)}{\mu}\frac{dn}{dS}\left(\frac{S_{obs}}{\mu}\right)d\mu.
\end{equation} 
Here $ dn_{obs}(S_{obs})/dS_{obs}$ is the observed luminosity function and $dn/dS$ is the intrinsic one which we discuss in the next section.

In addition we calculate the expected fraction of the sources of observed flux $S_{obs}$ lensed with magnification greater than $\mu$
\begin{equation}
Fr = \frac{\int_\mu^\infty P(\mu|S_{obs})}{\int_0^\infty P(\mu|S_{obs})}.
\end{equation}

\subsection{Intrinsic luminosity function}

The effects of lensing are expected to be manifested at the bright-luminosity end of the luminosity function. Therefore it is natural to assume that the faint-luminosity end has undergone a negligible amount of lensing.  
We use the faint-luminosity number counts recently reported by Karim et al. (2013) to normalize our intrinsic luminosity functions.

We use two functional forms to fit the number counts: 
\begin{enumerate}
\item The Shechter function with 
\begin{equation}
\frac{dn}{dS} = \frac{n_\star}{S_\star}\left(\frac{S}{S_\star}\right)^{-\alpha}\exp\left(-S/S_\star\right)
\end{equation}
with the parameters $n_s = 424$ $mJ^{-1}deg^{-2}$, $S_\star = 8$ [mJy], $\alpha = 1.1$ (from Karim et al. 2013) and $n_s = 424$ $mJ^{-1}deg^{-2}$, $S_\star = 7$ [mJy], $\alpha = 1.9$ (steep).   
\item The broken power law 
\begin{equation}
\frac{dn}{dS} = N_s\left(\frac{S}{S_\star}\right)^{-\beta_1},~~~~\textrm{for}~~~~S<S_\star,
\end{equation} 
\begin{displaymath}
\frac{dn}{dS} = N_s\left(\frac{S}{S_\star}\right)^{-\beta_2},~~~~\textrm{for}~~~~S>S_\star,
\end{displaymath}
with the parameters $N_s = 25$ $mJ^{-2}deg^{-2}$, $S_\star = 8$ [mJy], $\beta_1 = 2$ and $\beta_2 = 18$. 
\end{enumerate}

\begin{thebibliography}{9}

{\footnotesize

\bibitem{Simpson:2014}
J. M. Simpson, et al.,
ApJ, 788 (2014) 125.

\bibitem{Lima:2010a}
M. Lima, B. Jain, M. Devlin, 
MNRAS, 406 (2010) 2352.

\bibitem{Lima:2010b}
M. Lima, B. Jain, M. Devlin,  J. Aguirre, 
ApJL, 717 (2010) 31.

\bibitem{Wardlow:2013}
J.L.~Wardlow, et al.,
ApJ 762 (2013).

\bibitem{Takada:2003}
M.~Takada, B. Jain,
MNRAS 344 (2003) 857.

\bibitem{Diemer:2014}
B.~Diemer, A. V. Kravtsov,
arXiv:1407.4730.

\bibitem{Evrard:2008}
A.~E. Evrard et al.,
ApJ 672 (2008) 122.

\bibitem{Sheth:1999}
R. K. Sheth, G. Tormen, 
 MNRAS  308 (1999) 119.
}
\end{thebibliography} 
\end{document}

### 2014-12-16 LaTeX/ms.tex
Initial commit
This repository contains software and data files needed to reproduce
the research that will be published in Bussmann et al. 2015.

%\documentclass[10pt,preprint]{aastex}
\documentclass[iop]{emulateapj}
%\usepackage{epsfig}
%\usepackage{changebar}
%\usepackage{natbib}
%\usepackage{lscape}

%\topmargin -0.0in
\def\boldsymbol{\bf}
\newcommand{\tnm}{\tablenotemark}
\newcommand{\tnt}{\tablenotetext}

\bibpunct{(}{)}{;}{a}{}{,}

\slugcomment{To be submitted to the ApJ}

\shorttitle{ALMA Imaging of {\it Herschel} DSFGs}
\shortauthors{Bussmann et al.}

%\usepackage{amsmath}
%\usepackage{amssymb}

%\long\def\symbolfootnote[#1]#2{\begingroup%
%\def\thefootnote{\fnsymbol{footnote}}\footnote[#1]{#2}\endgroup} 
%\long\def\symbolfootnote[#1]#2{\begingroup\def\thefootnote{\fnsymbol{footnote}}
%\footnote[#1]{#2}\endgroup}

\begin{document}

\title{HerMES: Spatially resolved ALMA Imaging of {\it
Herschel}$^{\dagger}$-selected Dusty Star-forming Galaxies}

%shortlensing:[hda fdb hf aih mk alapi ao dr jw]

%./authors_list hermes_authors_data_dr1_20121108.txt apj rsb dr fialkov hayward cowley almalens

\author{R.~S.~Bussmann\altaffilmark{1},
D.~Riechers\altaffilmark{1},
A.~Fialkov\altaffilmark{2},
C.~Hayward\altaffilmark{3,4},
W.~Cowley\altaffilmark{5},
J.~Bock\altaffilmark{6,7},
J.~Calanog\altaffilmark{8},
A.~Cooray\altaffilmark{8},
F.~De Bernardis\altaffilmark{8},
R.~Hopwood\altaffilmark{9},
M.~Jarvis\altaffilmark{10},
C.~Lacey\altaffilmark{5},
A.~Loeb\altaffilmark{4},
S.~J.~Oliver\altaffilmark{11},
I.~P{\'e}rez-Fournon\altaffilmark{12,13},
I.~G.~Roseboom\altaffilmark{11,14},
A.~J.~Smith\altaffilmark{11},
L.~Wang\altaffilmark{11},
J.~Wardlow\altaffilmark{15}}
\altaffiltext{1}{Department of Astronomy, Space Science Building, Cornell University, Ithaca, NY, 14853-6801}
\altaffiltext{2}{Departement de Physique, Ecole Normale Sup erieure, CNRS, 24 rue Lhomond, Paris, 75005 France}
\altaffiltext{3}{TAPIR 350-17, California Institute of Technology, 1200 E. California Boulevard, Pasadena, CA 91125}
\altaffiltext{4}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{5}{Institute for Computational Cosmology, Department of Physics, University of Durham, South Road, Durham, DH1 3LE, UK}
\altaffiltext{6}{California Institute of Technology, 1200 E. California Blvd., Pasadena, CA 91125}
\altaffiltext{7}{Jet Propulsion Laboratory, 4800 Oak Grove Drive, Pasadena, CA 91109}
\altaffiltext{8}{Dept. of Physics \& Astronomy, University of California, Irvine, CA 92697}
\altaffiltext{9}{Astrophysics Group, Imperial College London, Blackett Laboratory, Prince Consort Road, London SW7 2AZ, UK}
\altaffiltext{10}{Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Hertfordshire AL10 9AB, UK}
\altaffiltext{11}{Astronomy Centre, Dept. of Physics \& Astronomy, University of Sussex, Brighton BN1 9QH, UK}
\altaffiltext{12}{Instituto de Astrof{\'\i}sica de Canarias (IAC), E-38200 La Laguna, Tenerife, Spain}
\altaffiltext{13}{Departamento de Astrof{\'\i}sica, Universidad de La Laguna (ULL), E-38205 La Laguna, Tenerife, Spain}
\altaffiltext{14}{Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{15}{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 Copenhagen, Denmark}

%\newpage

\begin{abstract}

    The {\it Herschel} Multi-tiered Extragalactic Survey (HerMES) has identified
    large numbers of dusty star-forming galaxies (DSFGs) over a wide range in
    redshift.  A detailed understanding of these DSFGs is hampered by the poor
    spatial resolution of {\it Herschel}.  We present 870$\,\mu$m 0$\farcs$45
    imaging obtained in Cycle~0 with the Atacama Large Millimeter/submillimeter
    Array (ALMA) of a sample of 29 HerMES DSFGs.  We identify a total of 62
    sources down to the $5\sigma$ limit in our ALMA sample ($\sigma \approx
    0.2\,$mJy).  Optical or near-infrared imaging indicates that 36 of the ALMA
    sources experience a significant flux boost from gravitational lensing ($\mu
    > 1.1$), but only 6 are strongly lensed and show multiple images.  We
    introduce and make use of {\sc uvmcmcfit}, a general purpose and publicly
    available Markov Chain Monte Carlo visibility plane analysis tool to analyze
    the source properties.  Nearly 70\% of the {\it Herschel} sources break down
    into multiple ALMA counterparts, consistent with previous research
    indicating that the multiplicity rate is high in bright sources discovered
    in sub-mm or FIR surveys with poor spatial resolution.  The ALMA
    counterparts to our {\it Herschel} targets are located much closer to each
    other than ALMA counterparts to sources found in the LABOCA ECDFS
    Submillimeter Survey.  Hydrodynamical numerical simulations and
    semi-analytical models both underpredict the excess in number of sources
    with small separations from each other that is seen in our ALMA sample.
    Combined with our previous work on brighter {\it Herschel} sources, the lens
    models presented here constrain the shape of the intrinsic luminosity
    function for DSFGs to have a break around 8$\,$mJy with a very steep fall
    off at higher flux densities.  The high multiplicity rate and low projected
    separations between sources seen in our sample argue in favor of
    interactions and mergers driving the prodigious emission from the brightest
    DSFGs.

\end{abstract}

\keywords{galaxies: evolution --- galaxies: fundamental parameters --- 
galaxies: high-redshift}

%\newpage

\section{Introduction} \label{sec:intro}

Galaxies selected in blind surveys at far-infrared (FIR) or sub-millimieter
(sub-mm) wavelengths are generally known as dusty star-forming galaxies (DSFGs).
They are found primarily at $z \sim2$ \citep{2005ApJ...622..772C,
Bothwell:2013lr} \citep[but extend down to $z \sim 1$ and up to $z > 6$;
see][]{Messias:2014fk, Riechers:2013lr} and represent the most FIR-luminous
objects in existence during this epoch.   They are signposts of significant
over-densities \citep{Daddi:2009qy, Capak:2011qy} and likely represent the
formative stages of the most massive elliptical galaxies found in the local
Universe \citep[e.g.,][]{Ivison:2013fk, Fu:2013lr}.  Moreover, they constitute
an important component of the overall galaxy population at $z \sim 2$
\citep[e.g.,][]{2005ApJ...632..169L}, when the star-formation rate density in
the Universe peaked \citep[e.g.,][]{Lilly:1996uq, 1996MNRAS.283.1388M}.

Our collective understanding of DSFGs is currently taking a dramatic leap
forward thanks in large part to the advent of the {\it Herschel Space
Observatory} \citep[{\it Herschel};][]{Pilbratt:2010fk}.  This has resulted in a
revolution in the size and depth of blind surveys at FIR and sub-mm wavelengths.
In particular, the {\it Herschel} Multi-tiered Extragalactic Survey
\citep[HerMES;][]{Oliver:2012lr} and the {\it Herschel} Astrophysical Terahertz
Large Area Survey \citep[H-ATLAS;][]{2010PASP..122..499E} together have surveyed
$\approx 650\,$deg$^2$ at 250$\,\mu$m, 350$\,\mu$m, and 500$\,\mu$m to the
confusion limit of {\it Herschel} \citep[$\sigma \approx 6-7\,$mJy in each
band][]{Nguyen:2010fk}, plus an additional $\approx 350\,$deg$^2$ to a level
approximately double the confusion limit.  A similar effort has been undertaken
at longer wavelengths by the South Pole Telescope
\citep[SPT;][]{Carlstrom:2011qy} and the Atacama Cosmology Telescope
\citep{Swetz:2011qy}.

Theoretical expectations based on the redshift distribution and luminosity
function of DSFGs suggested that HerMES and H-ATLAS would be efficient tools for
discovering strongly lensed DSFGs \citep[e.g.,][]{1996MNRAS.283.1340B,
2007MNRAS.377.1557N}.  Submillimeter Array \citep[SMA;][]{Ho:2004lr} imaging at
870$\,\mu$m with sub-arcsecond resolution has confirmed this, with $\geq 85\%$
of the brightest sources found by {\it Herschel} ($S_{500} > 100\,$mJy) being
gravitationally lensed by an intevening galaxy or group of galaxies along the
line of sight \citep{Negrello:2010fk, Conley:2011lr, Riechers:2011uq,
Bussmann:2012lr, Wardlow:2013lr, Bussmann:2013lr}.  Sources discovered in SPT
surveys have also been shown to have a high probibility of being strongly lensed
\citep{Vieira:2013fk, Hezaveh:2013fk}.  However, statistical models
significantly over-predict the median magnification factor experienced by a {\it
Herschel} DSFG of a given $S_{500}$ \citep{Bussmann:2013lr}.  This could
indicate a deficiency in our understanding of the bright end of the intrinsic
DSFG luminosity function.

We here present Atacama Large Millimeter/submillimeter Array (ALMA) Cycle~0
imaging at 870$\,\mu$m of a sample of 29 HerMES DSFGs.
%Our targets were selected to be significantly fainter than those reported in
%\citet{Bussmann:2013lr}, so they include a larger number of unlensed or weakly
%lensed ($\mu_{870} < 2$) sources.  
Three aspects of our dataset make it unique.  First, the sample occupies a
distinct regime in flux density between the brightest {\it Herschel} DSFGs
(almost all of which are lensed) and much fainter DSFGs found in ground-based
surveys \citep[most of which are expected to be unlensed;
e.g.,][]{Hodge:2013qy}.  Second, the ALMA images are extremely sensitive
($\sigma \approx 0.2\,$mJy) and all 29 HerMES DSFGs are detected \citep[such is
not the case in previous similar studies with shallower imaging;
e.g.,][]{Smolcic:2012zl, Barger:2012yg, Hodge:2013qy}.  Third, the typical
angular resolutions are $0\farcs45$ and nearly all sources detected by ALMA are
spatially resolved.

We also obtained Gemini-South optical imaging to complement our existing array
of ancillary multi-wavelength imaging.  We use those data in this paper to
identify lensing galaxies which are typically early-types with little on-going
star-formation and therefore very weak sub-mm emission.

In Section~\ref{sec:obs}, we characterize our sample and present our ALMA and
Gemini-South imaging.  Section~\ref{sec:modelfits} presents model fitting
methodology and model fits to all ALMA sources (lensed and unlensed) using {\sc
uvmcmcfit}, a publicly available
\footnote{https://github.com/sbussmann/uvmcmcfit} modified version of the
visibility plane lens modeling software used in \citet{Bussmann:2012lr,
Bussmann:2013lr}.  Results on the effect of lensing on the observed properties
of the {\it Herschel} DSFGs in our sample as well as the multiplicity rate and
typical angular separation between sources after delensing the ALMA sources
appear in Section~\ref{sec:results}.  We scrutinize statistical predictions for
$\mu_{870}$ as a function of $S_{870}$ and discuss implications for the bright
end of the DSFG luminosity function in Section~\ref{sec:discuss}.  Finally, we
present our conclusions in Section~\ref{sec:conclusions}.

Throughout this paper, we assume a flat cosmology with
$H_0=$69~km~s$^{-1}$~Mpc$^{-1}$, $\Omega_{\rm m_0} = 0.29$
\citep{Hinshaw:2013ty}.

\section{Data}\label{sec:obs}

In this section, we describe the selection of our {\it Herschel} DSFG sample,
present our ALMA high-spatial resolution imaging of thermal dust emission, and
present Gemini-S optical imaging that we use to identify intervening galaxies
along the line of sight.

\subsection{Selection of DSFG Sample}\label{sec:select}

The starting point for the sample selection is source extraction and
photometry.  Sources are detected using the {\sc StarFinder} code
\citep{Diolaiti:2000qy} on the 250$\, \mu$m {\it Herschel} Spectral and
Photometric Imaging REceiver \citep[SPIRE;][]{2010A&A...518L...3G} images.
Photometry is obtained from the HerMES XID pipeline \citep{Roseboom:2010lk},
which allocates flux density based on the 250$\, \mu$m position priors from
{\sc StarFinder}.

Our sample includes 29 DSFGs drawn from five independent fields in HerMES
totaling $55\,$deg$^2$ that are accessible to ALMA and have SPIRE sensitivity
that reaches the confusion limit.  The sample is selected primarily on the
basis of $S_{500}$ and covers a range of $20 < S_{500}/{\rm (mJy)} \lesssim
100$.  Additional selection criteria based on the $S_{500}/S_{350}$ and
$S_{350}/S_{250}$ colors lead to the sample being split roughly evenly between
``blue'' (typically implying $z < 2$) and ``green'' ($z = 2-3.5$) SPIRE colors.
We caution that redshifts based strictly on SPIRE colors are uncertain due to
the degeneracy between dust temperature and redshift as well as the fact that
the multiplicity rate is high in our sample.  It is not clear that the colors
of each individual ALMA counterpart are the same as the summed colors seen by
{\it Herschel}.  Low redshift contaminants to our sample ($z < 0.1$) are
trivially removed by searching for spatially resolved counterparts in SDSS
imaging.  There is also a small contamination from blazars, which are
non-thermal emitters and are easily identified and excised from the sample
using data from the NVSS or the Very Large Array Faint Images of the Radio Sky
at Twenty-Centimeters survey \citep[FIRST;][]{Becker:1995fj}.

Figure~\ref{fig:sample} shows that the ALMA sample is set clearly apart from the
very bright {\it Herschel} DSFGs that are selected to have $S_{500} > 100 \,
$mJy and have been shown to be almost entirely lensed DSFGs
\citep{Negrello:2010fk, Wardlow:2013lr, Bussmann:2013lr}.  In contrast, the
sample in this paper should include a more diverse mix of lensed and unlensed
DSFGs.  On the other hand, this sample is selected from a survey with an area
that is 200 times larger than that of ALESS.  It is no surprise then, that the
median $S_{500}$ in our sample is $\sim3.5$ times brighter than the median
$S_{500}$ in ALESS.  Our ALMA sample opens a new window of discovery space on
the bright end of the DSFG luminosity function.

\begin{figure}[!tbp] 
%\epsscale{1.00} 
\includegraphics[width=\linewidth]{../Figures/spirecolflux.pdf}

\caption{ {\it Herschel}/SPIRE photometry of all galaxies in the H-ATLAS
phase~I catalog with S/N$ > 3$ at 250$\,\mu$m, 350$\,\mu$m, and 500$\,\mu$m
(grayscale).  The sample of HerMES sources in this paper are shown with green
squares (the ``ALMA sample'').  The very bright {\it Herschel} DSFGs from
\citet{Bussmann:2013lr} (the ``SMA sample'') are shown by red circles, and the
overall sample of candidate lensed {\it Herschel} DSFGs are highlighted by
yellow circles.  Lensed SMGs discovered by the SPT that have published lens
models are represented by cyan stars \citep{Hezaveh:2013fk}.  A magenta diamond
shows the location in this diagram of the stacked signal from ALESS DSFGs.
Representative error bars are shown in the lower left corner.  The ALMA sample
fills the gap in 500$\,\mu$m flux density space between SMA/SPT and ALESS
samples.} \label{fig:sample}

\end{figure}

In detail, two of the sources in the ALMA sample (HXMM01 and HXMM02) overlap
with the ``confirmed lensed'' sample in \citet{Wardlow:2013lr} as well as with
the SMA sample in \citet{Bussmann:2013lr}.  A further 8 appear in the
``Supplementary sample'' in \citet{Wardlow:2013lr}.  The remainder have
$S_{500} < 80\,$mJy and thus do not appear in \citet{Wardlow:2013lr}.

%Efforts are on-going to obtain a complete database of follow-up observations
%for our ALMA sample.  The present paper focuses on a
%subset of 30 candidates with superb existing follow-up observations (hereafter,
%we refer to this as the ``SMA subsample'').  These targets were initially
%selected on the basis of strong 1.2$\,$mm detections from the Max Planck
%Millimeter Bolometer (MAMBO) array \citep{Kreysa:1998uq} at the Institut de
%Radioastronomie Millim\'etrique (IRAM) 30$\,$m telescope (Dannerbauer et al. in
%prep.).  Subsequent follow-up efforts have now provided high-spatial resolution
%880$\, \mu$m imaging with the SMA, spectroscopic redshifts of the lensed SMGs
%obtained with GBT, CSO, CARMA, PdBI, and {\it Herschel} \citep[][Riechers et
%al., in prep.; Krips et al., in prep., George et al., in prep.]{Cox:2011fk,
%Harris:2012fr, Lupu:2012ly}, and spectroscopic redshifts to the lenses obtained
%with the MMT, Gemini-S, or WHT.  In addition, Keck-II Near InfraRed Camera 2
%(NIRC2) laser guide star adaptive optics (LGSAO) imaging has been obtained for
%nearly half of the candidate lensed SMG sample \citep[][Calanog et al., in
%prep.]{Wardlow:2013lr}.  These datasets provide the information needed to
%confirm the lensing hypothesis and begin analysis of the source and lens
%properties.

Table~\ref{tab:position} provides reference data for the ALMA sample, including
centroid positions measured from the ALMA 870$\, \mu$m imaging (see
section~\ref{sec:almaobs}).

\subsection{ALMA Observations}\label{sec:almaobs}

ALMA data were obtained during Cycle~0 over a period from 2012 June to 2012
December (Program 2011.0.00539.S; PI: D. Riechers).  The observations were
carried out in good 870$\,\mu$m weather conditions which resulted in typical
system temperatures of $T_{\rm sys} \sim 130\,$K and phase fluctuations of $\sim
10\,$deg.  Each target was observed until an rms noise level of $\sigma \approx
0.2\,$mJy was achieved.  This typically required 10 minutes of on-source
integration time.  For the observations targeting the CDFS, Elais-S, and COSMOS
fields, the weather was of sufficient quality to reach $\sigma \approx
0.14\,$mJy.  The number of antennas used varied from 15 to 25.  The antennas
were configured with baseline lengths of 20$\,$m to 400$\,$m, providing a
synthesized beamsize of $\approx 0\farcs45$ FWHM while ensuring that no flux was
resolved out by the interferometer.  When possible, track-sharing of multiple
targets in a single track was used to optimize the {\it uv} coverage.

The quasars J0403$-$360, J2258$-$279, B0851$+$202, and J2258$-$279 were used
for bandpass and pointing calibration.  The quasars J0403$-$360, J0106$-$405,
J0519$-$454, J1008$+$063, and J0217$+017$ were used for amplitude and phase
gain calibration.  The following solar system objects were used for absolute
flux calibration: Callisto (CDFS targets), Neptune (XMM targets), Titan (COSMOS
targets) and Uranus (ADFS and XMM targets).  For ElaisS1, no solar system
object was observed.  Instead, J2258$-$279 was used for absolute flux
calibration, with the flux fixed according to a measurement made two days prior
to the observations of ElaisS1.

All observations were conducted with the correlator in ``Frequency Domain
Mode'', providing a total usable bandwidth of 7.5$\,$GHz with spectral windows
centered on 335.995$\,$GHz, 337.995$\,$GHz, 345.995$\,$GHz, 347.996$\,$GHz.  We
searched for evidence of serendipitous spectral lines but found none (typical
sensitivity is $\sigma \approx 8\,$mJy$\,$beam$^{-1}$ in 15$\,$km$\,$sec$^{-1}$
bins).

We used the Common Astronomy Software Applications (CASA, version 4.2.1)
package to investigate the quality of the reduced data provided by the North
American ALMA Science Center (NAASC).  Overall, the quality of the processed
data from the NAASC was very high.  We achieved a significant improvement in
the case of the ADFS and XMM targets by excluding datasets with moderate
$T_{\rm sys}$ and poor phase fluctuations.  For a handful of targets with peak
signal-to-noise ratio (S/N) greater than 20, we obtained a $\approx 10\%$
improvement in S/N by using the CASA {\sc selfcal} task to improve the phase
gain corrections.  Finally, we updated the absolute flux calibration to use the
Butler-JPL-Horizons 2012 solar system models.

For imaging, we used the CASA {\sc Clean} task with Briggs weighting and robust
= $+$0.5 to achieve an optimal balance between sensitivity and spatial
resolution.  We selected the multi-frequency synthesis option to optimize {\it
uv} coverage.  We designed custom masks for each target in CASA to ensure that
only regions with high S/N were considered during the cleaning process.

Figure~\ref{fig:imaging} presents our ALMA images (colorscale) in comparison to
the {\it Herschel} SPIRE images (black-white contours) originally used to
select the targets and noted in each panel as either 250$\,\mu$m or
350$\,\mu$m.  Each panel is centered on the phase center of the ALMA
observations of that target and a white circle traces the FWHM of the primary
beam of an ALMA 12$\,$m antenna at 870$\,\mu$m.  A white dashed box represents
the region of each image that is shown in greater detail in
Figure~\ref{fig:uvmodels}.

In most targets, the peak of the SPIRE map is spatially coincident with the
location of the ALMA sources.  In one case where two ALMA sources are separated
by $\approx 10\arcsec$ (ADFS02), the elongation in the SPIRE 250$\,\mu$m map is
consistent with the angular separation of the two ALMA counterparts.
Otherwise, the SPIRE imaging is consistent with a single component located at
the centroid of the ALMA sources.  This result is not a surprise, given the
typical angular separation of the ALMA sources ($\lesssim 5\arcsec$) and the
FWHM of the SPIRE beam at 250$\,\mu$m (18.1$\arcsec$).

\subsection{Gemini-South Imaging}\label{sec:geminiobs}

Optical imaging observations using the Gemini Multi-Object Spectrograph-South
\citep[GMOS-S;][]{Hook:2004qy} were conducted in queue mode during the 2013B
semester as part of program GS-2013B-Q-77 (PI: R.~S.~Bussmann).  The goal of the
program is to use shallow $u$, $g$, $r$, $i$, and $z$ imaging to identify
structure at $z<1$ and determine which of the ALMA sources are affected by
gravitational lensing.  Nearly half of the ALMA sources lie in regions with
existing deep optical imaging thanks to the extensive HerMES multi-wavelength
dataset --- these were excluded from our Gemini-S program.  The remaining
targets are: ADFS01, ADFS02, ADFS03, ADFS04, ADFS05, ADFS06, ADFS07, ADFS\_M0,
ElaisS1, XMM02, XMM05, XMM101, XMM108, XMM109, and XMM115.  Each of these
targets were observed for a total of 9$\,$minutes of on-source integration time
in each of $u$, $g$, $r$, $i$, and $z$.  The observations were obtained during
dark time in with adequate seeing conditions (image quality $ = 85\% \approx
1.1\arcsec$.

The data were reduced using the standard {\sc IRAF} Gemini GMOS reduction
routines, following the standard GMOS-S reduction steps in the example taken
from the Gemini observatory webpage
\footnote{http://www.gemini.edu/sciops/data-and-results/processing-software/getting-started\#gmos}.

We used the Sloan Digital Sky Survey (SDSS) or the 2 Micron All Sky Survey
(2MASS) to align the Gemini-S images to a common astrometric frame of
reference.  This imposes an rms uncertainty in the absolute astrometry of
$0\farcs2$ and $0\farcs4$ for SDSS and 2MASS, respectively.  The
astrometrically calibrated Gemini-S images served as the basis for aligning
higher resolution, smaller field-of-view imaging from {\it HST} or Keck that
were originally presented in \citet{Calanog:2014lr}.

\input{table_positions}

\begin{figure*}[!tbp] 
    \begin{centering}
%\epsscale{1.00} 
%\includegraphics[width=\textwidth]{cutouts_dec17.png}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/ADFS01_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/ADFS02_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/ADFS03_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/ADFS04_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/ADFS05_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/ADFS06_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/ADFS07_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/ADFS_M0_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/CDFS_M0_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/CDFS_M1_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/ECDFS02_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/COS01_870_250.pdf}
\end{centering}

\caption{ ALMA 870$\mu$m images (color scale, units of mJy/beam) of HerMES
DSFGs.  Contours (black and white) trace 250$\,\mu$m emission from {\it
Herschel}.  The FWHM size of the ALMA synthesized beam is shown in the lower
left corner of each panel.  A solid white circle shows the FWHM size of the
primary beam.  Dashed squares identify the regions of each image that are shown
in greater detail in Figure~\ref{fig:uvmodels}.  \label{fig:imaging}}
\addtocounter{figure}{-1}

\end{figure*}

\begin{figure*}[!tbp] 
    \begin{centering}
%\epsscale{1.00} 
%\includegraphics[width=\textwidth]{cutouts_dec17.png}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/COS02_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/ElaisS1_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM01_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM02_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM03_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM04_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM05_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM06_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM16_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM101_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM102_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM108_870_250.pdf}
\end{centering}

\caption{ Continued.}
\addtocounter{figure}{-1}

\end{figure*}

\begin{figure*}[!tbp] 
    \begin{centering}
%\epsscale{1.00} 
%\includegraphics[width=\textwidth]{cutouts_dec17.png}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM109_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM110_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM115_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM119_870_250.pdf}
\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM124_870_250.pdf}
\end{centering}

\caption{ Continued.}
%\addtocounter{figure}{-1}

\end{figure*}

\section{Model Fits}\label{sec:modelfits}

\subsection{Model Fitting Methodology}\label{sec:modelfitsmeth}

An interferometer measures visibilities at discrete points in the {\it uv}
plane.  This is why pixel-to-pixel errors in the inverted and deconvolved
surface brightness map of an astronomical source are correlated.  The best way
to deal with this situation is to compare model and data visibilities rather
than surface brightness maps.  The methodology used in this paper is similar in
many aspects to that used in \citet{Bussmann:2012lr}, who presented the first
lens model derived from a visibility-plane analysis of interferometric imaging
of a strongly lensed DSFG discovered in wide-field submm surveys as well as
\citet{Bussmann:2013lr}, who extended this work to a statistically significant
sample of 30 objects.  It also bears some resemblence to the method used in
\citet{Hezaveh:2013fk}, who undertake lens modeling of interferometric data in
the visibility plane.  We summarize important information on the methodology
here, taking care to highlight where any differences occur between this work and
that of our previous efforts.

We created and made publicly available custom software, called {\sc uvmcmcfit},
that is capable of modeling all of the ALMA sources in this paper efficiently
and reliably.

Sources are assumed to be elliptical Gaussians that are parameterized by the
following six free parameters: the position of the source (relative to the
primary lens if a lens is present) ($\Delta \alpha_{\rm s}$ and $\Delta
\delta_{\rm s}$), the total intrinsic flux density ($S_{\rm in}$), the
effective radius intermediate axis length ($r_{\rm s} = \sqrt{a_{\rm s} b_{\rm
s}}$), the axial ratio ($q_{\rm s}$ =  $b_{\rm s}/a_{\rm s}$), and the position
angle ($\phi_{\rm s}$, degrees east of north).  The use of an elliptical
Gaussian represents a simplification from the S\'ersic profile
\citep{1968adga.book.....S}  that is justified based on the relatively weak
constraints on the S\'ersic index found in our previous work
\citep{Bussmann:2012lr, Bussmann:2013lr}.

When an intervening galaxy (or group of galaxies) is present along the line of
sight, {\sc uvmcmcfit} accounts for the deflection of light caused by this
structure using a simple ray-tracing routine that is adopted from a 
Python routine written by A.~Bolton
\footnote{http://www.physics.utah.edu/$\sim$bolton/python\_lens\_demo/}.  This
represents a significant difference from \citet{Bussmann:2012lr} and
\citet{Bussmann:2013lr}, where we used the publicly available {\sc Gravlens}
software \citep{Keeton:2001lr} to map emission from the source plane to
the image plane for a given lensing mass distribution.  {\sc Gravlens} has a
wide range of lens mass profiles as well as a sophisticated algorithm for
mapping source-plane emission to the image-plane, but it also comes with a
significant input/output penalty that makes parallel computing prohibitively
expensive.  The use of pure-Python code for tracing the deflection of light
rays is a critical component of making {\sc uvmcmcfit} computationally
feasible.

In {\sc uvmcmcfit}, lens mass profiles are represented by $N_{\rm lens}$
singular isothermal ellipsoid (SIE) profiles, where $N_{\rm lens}$ is the
number of lensing galaxies found from the best available optical or near-IR
imaging \citep[a multitude of evidence supports the SIE as a reasonable choice;
for a recent review, see][]{Treu:2010fk}.  Each SIE is fully described by the
following five free parameters: the position of the lens relative to the
arbitrarily chosen ``image center'' based on the ALMA 870$\,\mu$m emission and
any lensing galaxies seen in the optical or near-IR ($\Delta \alpha_{\rm lens}$
and $\Delta \delta_{\rm lens}$; these can be compared with the position of the
optical or near-IR counterpart relative to the ``image center'': $\Delta
\alpha_{\rm NIR}$ and $\Delta \delta_{\rm NIR}$), the mass of the lens
(parameterized in terms of the intermediate axis angular Einstein radius,
$\theta_{\rm E}$), the axial ratio of the lens ($q_{\rm lens} = b_{\rm lens} /
a_{\rm lens}$), and the position angle of the lens ($\phi_{\rm lens}$; degrees
east of north).  Unless otherwise stated, when optical or near-IR imaging
suggests the presence of additional lenses (see Figure~\ref{fig:uvmodels}), we
estimate centroids for each lens by-eye and fix the positions of the additional
lenses with respect to the primary lens.  Each additional lens thus has 3 free
parameters: $\theta_{\rm E}$, $q_{\rm lens}$, and $\phi_{\rm lens}$.  We assume
secondary, tertiary, etc., lenses are located at the same redshift as the
primary lens.

The total number of free parameters for any given system is $N_{\rm free} = 5 +
3 \times (N_{\rm lens} - 1) + 6 * N_{\rm source}$, where $N_{\rm source}$ is
the number of S\'ersic profiles used.

We use uniform priors for all model parameters.  The prior on the position of
the lenses covers $\pm0\farcs6$ ($1\farcs0$) in both RA and Dec, a value that
reflects the 1-$\sigma$ absolute astrometric solution between the ALMA and
optical/near-IR images of $0\farcs2$ ($0\farcs4$) for SDSS-based (2MASS-based)
astrometric calibration.  In section~\ref{sec:objectbyobject}, we discuss the
level of agreement between the astrometry from the images and the astrometry
from the lens modeling on an object-by-object basis.  For $\theta_{\rm E}$, the
prior covers $0\farcs1 - 6\arcsec$.  The axial ratios of the lenses and sources
are restricted to be $q_{\rm lens} > 0.3$ and $q_{\rm s} > 0.2$. No prior is
placed on the position angle of the lens or source.  The intrinsic flux density
for any source is allowed to vary from 0.1$\,$mJy to the total flux density
observed by the ALMA (we ensure that the posterior PDF of the intrinsic flux
density shows no signs of preferring a value lower than 0.1$\,$mJy).  The source
position is allowed to vary over any reasonable range necessary to fit the data
(typically, this is $\pm 1-2\arcsec$).  The effective radius is allowed to vary
from $0\farcs01 - 1\farcs5$.

The surface brightness map generated as part of {\sc uvmcmcfit} is then
converted to a ``simulated visibility'' dataset ($V_{\rm model}$) in much the
same way as MIRIAD's {\sc uvmodel} routine.  Indeed, the code used in {\sc
uvmcmcfit} is a direct Python port of {\sc uvmodel} (the use of {\sc uvmodel}
itself is not possible for the same reason as {\sc Gravlens}: constant
input/output makes parallel computing prohibitively expensive).  {\sc
uvmcmcfit} computes the Fourier transform of the surface brightness map and
samples the resulting visibilities in a way that closely matches the sampling
of the actual observed ALMA visibility dataset ($V_{\rm ALMA}$).

The quality of fit for a given set of model parameters is determined from the
maximum likelihood estimate $MLE$ according to the following equation:

\begin{equation}
    MLE = \sum_{u, v} \frac{|V_{\rm ALMA} - V_{\rm
    model}|^2}{\sigma^2} + log(2 \pi \sigma^2) 
\end{equation}

%\begin{equation}
%    MLE = -\frac{1}{2} (MLE_{\rm real} + MLE_{\rm imag}),
%\end{equation}

%\begin{equation}
%    MLE_{\rm real} = \sum_{u, v} \frac{[Re(V_{\rm ALMA}) - Re(V_{\rm
%    model})]^2}{\sigma^2} + log(2 \pi \sigma^2), 
%\end{equation}

%\begin{equation}
%    MLE_{\rm imag} = \sum_{u, v} \frac{[Im(V_{\rm ALMA}) - Im(V_{\rm
%    model})]^2}{\sigma^2} + log(2 \pi \sigma^2),
%\end{equation}

\noindent where $\sigma$ is the 1$\sigma$ uncertainty level for each
visibility and is determined from the scatter in the visibilities within a
single spectral window (this is a natural weighting scheme).

We use {\sc emcee} \citep{Foreman-Mackey:2013yq} to sample the posterior
probability density function (PDF) of our model parameters.  {\sc emcee} is a
Markov chain Monte Carlo (MCMC) code that uses an affine-invariant ensemble
sampler to obtain significant performance advantages over standard MCMC
sampling methods \citep{goodmanweare}.

We employ a ``burn-in'' phase with 512 walkers and 500-1000 iterations (i.e.,
$\approx 250,000-500,000$ samplings of the posterior PDF) to identify the
best-fit model parameters.  This position then serves as the basis to
initialize the ``final'' phase with 512 walkers and 10 iterations (i.e., 5,120
samplings of the posterior PDF) to determine uncertainties on the best-fit
model parameters.  
%The autocorrelation time for each parameter in a given ensemble of walkers and
%is of order unity for each parameter, implying that we have 5,000 independent
%samplings of the posterior PDF, more than enough to obtain a robust
%measurement of the mean and uncertainty on each parameter of the model.

During each MCMC iteration, we also measure the magnification factor at
870$\,\mu$m, $\mu_{870}$, for each source.  This is done simply by taking the
ratio of the total flux density in the lensed image of the model ($S_{\rm out}$
to the total flux density in the unlensed, intrinsic source model ($S_{\rm
in}$).  The use of an aperture when computing $\mu_{870}$ is important when
source profiles are used with significant flux at large radii (e.g., some types
of S\'ersic profiles).  For an elliptical Gaussian, such a step is unneccessary
(note that we did test this and found only $\approx 10\%$ difference between
$\mu_{870}$ computed with and without an aperture.  The best-fit value and
1$\sigma$ uncertainty on $\mu_{870}$ are drawn from the posterior PDF, as with
the other parameters of the model.

\subsection{Individual Model Fits}\label{sec:objectbyobject}

In this section, we present our model fits (as shown in
Figure~\ref{fig:uvmodels}) and describe each source in detail.

{\bf ADFS01:} Three sources are detected by ALMA, each of which is weakly
lensed by a bright foreground galaxy seen in the {\it HST} image.  Alternative
scenarios involving strong lensing can be ruled out by the location of the
lens: $\approx 2-3\arcsec$ north of the centroid of the ALMA sources (the rms
error in the astrometry is set from 2MASS at a level of $\approx 0\farcs4$) as
well as the unusual location and fluxes of the ALMA sources relative to each
other.  We assume an Einstein radius of $0\farcs5$ and fix the position angle
of the lens to be between 40-50 degrees to match the orientation seen in the
{\it HST} image.  Larger Einstein radii can be ruled out by the absence of
counter images north of the lens.

{\bf ADFS02:} Two sources are detected by ALMA, both of which are weakly lensed
by a foreground galaxy in the {\it HST} image.  The ALMA sources have the
largest separation of any in our sample overall: $\approx 10\arcsec$.  We
assume an Einstein radius of $1\farcs5$ for the foreground lens as a ``maximal
lensing'' scenario.  This results in magnification factors of $\mu_{870} = 2.3
\pm 0.1$ and $\mu_{870} = 1.2 \pm 0.1$ for the two sources.  Our constraints on
the true Einstein radius of the lens are weak, so these values for $\mu_{870}$
should be regarded as upper limits.

{\bf ADFS03:} Three sources are detected by ALMA, none of which appear to be
lensed (the closest bright {\it HST} source is located $\approx 13\arcsec$ away
from the ALMA sources).

{\bf ADFS04:} Three sources are detected by ALMA.  In this paper, we have
assumed that all three are unlensed.  There is a group of three sources
detected in our Gemini-S optical imaging located $\approx 7\arcsec$ east of the
ALMA sources.  This distance is so large that plausible mass ranges for the
Gemini-S sources would imply at most a factor of 1.1-1.2 boost in the apparent
flux densities of the ALMA sources.

{\bf ADFS05:} Two sources are detected by ALMA.  The nearest possible lens is
located $\approx 8\arcsec$ from the ALMA sources, indicating that lensing is
likely to be irrelevant in this system.  The two ALMA sources are similarly
bright ($S_{870} = 8.27 \pm 0.53\,$mJy and $S_{870} = 9.07 \pm 0.27\,$mJy) and
separated by $\approx 0\farcs8$, corresponding to a projected physical distance
of $\approx 6\,$kpc. This distance is typical of the pericentric passage
distance in both hydrodynamical simulations of major mergers
\citep[e.g.,][]{Hayward:2012lr} and CO observations of major mergers
\citep[e.g.,][]{2008ApJ...680..246T, 2010ApJ...724..233E, 2011ApJ...733L..11R,
2011MNRAS.412.1913I}.  Two plausible scenarios are that ADFS05 represents a
major merger that just experienced a first pass or is approaching final
coalescence, either of which significantly enhanced star-formation in the
system.

{\bf ADFS06:} Three sources are detected by ALMA, all of which are weakly
lensed by a foreground galaxy seen in the {\it HST} image.  We assume an
Einstein radius of $0\farcs5$ for the lens, as values larger than this produce
multiple images of the ALMA sources.  Based on the brightness of the lens, we
consider to be unlikely values for the Einstein radius that are smaller than
$0\farcs5$, so the results we report for this object should be robust.

{\bf ADFS07:} This is a single source that is strongly lensed by a foreground
galaxy seen in the {\it HST} image.  The lensed source is not detected by {\it
HST}.  The source is highly elongated ($q_s = 0.31 \pm 0.01$), but fits the
data very well.  The position of the lens according to the lens model is
consistent with the position in the {\it HST} image given the $0\farcs4$
fundamental uncertainty due to using the 2MASS system as the fundamental basis
for the astrometry.

{\bf ADFS\_M0:} Two sources are detected by ALMA, both of which are weakly
lensed by a group of small galaxies detected in the {\it HST} image.  We
represent the gravitational potential of the group with a single SIE lens and
an Einstein radius of $1\farcs0$.  Values larger than this produce additional
counter images that are not seen in the ALMA imaging.  We cannot rule out
smaller Einstein radii, but we consider these unlikely given the number of
sources and their brightness in the {\it HST} image.

{\bf CDFS\_M0:} This is a complex, very well constrained system.  Two sources
are detected by ALMA: one is strongly lensed and the other is weakly lensed.
In addition, the lens is detected by ALMA (this is one of two sources in the
entire ALMA sample that is unresolved by ALMA).  These facts work together to
provide very tight constraints on the system.  Since the lens is detected by
ALMA, its position relative to the lensed images is unambiguous.  Also, because
there is a strongly lensed source with multiple images, the Einstein radius of
the lens is unambiguous.  A byproduct of these two facts is that the
magnification factor of the weakly lensed source is known to very high
precision as well.  It experiences a magnification factor of $\mu_{870} =
1.520\pm0.002$ despite being located $\approx4\arcsec$ north of the lens (which
has an Einstein radius of $1.353\pm0.005$).  We use these numbers to inform our
estimates of the Einstein radius for weakly lensed sources without the
excellent contraints provided by this system.  Finally, this source is detected
(and unresolved) in the NRAO VLA Sky Survey \citep{Condon:1998uq}, having
$S_{\rm 1.4\,GHz} = 21.8 \pm 0.8\,$mJy.  Assuming all of this radio emission
originates from the lens, this implies a spectral slope of $\alpha = -0.24$ and
is consistent with non-thermal emission from the lens.

{\bf CDFS\_M1:} Two sources are detected by ALMA, both of which are weakly
lensed by a foreground galaxy seen in the {\it HST} image.  There is also a
3$\sigma$ peak coincident with {\it HST} source that may be an indication that
the lens has been detected by ALMA.  We do not attempt to model this 3$\sigma$
peak.  We assume an Einstein radius of $0\farcs5$ for the lens, since larger
values predict the existence of counter images that are not seen by ALMA.  The
second ALMA source is located $\approx5\arcsec$ from the lens and experiences a
small but significant magnification of $\mu_{870} = 1.12 \pm 0.02$.  Both ALMA
sources appear to be detected by IRAC and have similar mid-IR colors, suggesting
they lie at the same redshift (see Figure~\ref{fig:iraccolor}).

{\bf ECDFS02:} This system is very similar to ADFS05, except that here the two
ALMA sources are separated by $\approx 0\farcs4$ rather than $0\farcs8$ and one
source is brighter than the other by a factor of 2.  Assuming the two sources
have similar mass to light ratios, their brightness ratios indicate major
merger rather than minor merger activity.  The projected physical distance is
$\approx 2-3$kpc, assuming a redshift of $z=2$ for the ALMA sources.  This
could be an example of a major merger approaching final coalescence and
experiencing a significant boost in star-formation due to enhancements in the
local gas density brought about by tidal forces during the merger.

{\bf ElaisS1:} Four sources are detected by ALMA, all of which are weakly lensed
by a foreground galaxy seen in the {\it HST} image.  We assume an Einstein
radius of $1\farcs5$ for the lens as larger values begin to predict counter
images that are not seen by ALMA.  The magnification factors reported here
should be regarded as upper limits since we do not have strong constraints on
the lower limit of the Einstein radius of the lens (e.g., the magnication factor
for the source that is directly south of the lens is reported here to have
$\mu_{870} = 1.68 \pm 0.06$, but values as small as 1.1-1.2 are likely plausible
as well).  The ALMA sources are all detected by IRAC and their mid-IR colors are
similar, suggesting they lie at the same redshift (see
Figure~\ref{fig:iraccolor}).

{\bf COS01:} This system is similar to ADFS07: a single source that is strongly
lensed by a foreground galaxy seen in the {\it HST} image.  In fact, the
background source is also detected by {\it HST} as well as Keck/NIRC-II
adaptive optics imaging, and a lens model has been published based on these
data \citep{Calanog:2014lr}.  The morphology of the lensed emission is very
different between the Keck and ALMA imaging, suggesting differential
magnification is important in this object.  The very small sizes of the sources
are consistent with this as well ($r_s = 0.023 \pm 0.003\arcsec$, Keck and $r_s
= 0.055 \pm 0.007\arcsec$, ALMA).  Adopting a redshift of $z=2$ for the lensed
source implies physical sizes of $\approx 150\,$pc and $\approx 300\,$pc for
the rest-frame optical and rest-frame FIR, respectively.

{\bf COS02:} Five sources are detected by ALMA \citep[the brightest of which has
already been detected;][]{Smolcic:2012zl}, none of which appear to be lensed.
Previous research has shown this to be an overdense region \citep[this object is
called COSBO3 in][]{Aravena:2010fr} with a photometric redshift of $z=2.3-2.4$.
Our ALMA imaging offers the first convincing evidence that the associated
galaxies in the overdensity are sub-mm bright and thus intensely star-forming.
There are a number of $2-3\sigma$ peaks in the map that could be real.  This
would further increase the multiplicity rate for this object, but we caution
that there are also negative peaks of similar amplitude (i.e., $2-3\sigma$)
present in this map.  Some of the ALMA sources have counterparts detected in the
{\it HST} image, whereas all of the ALMA sources are detected by IRAC (see
Figure~\ref{fig:iraccolor}).  Their mid-IR colors are similar, providing further
evidence that the ALMA sources lie at the same redshift.

{\bf XMM01:} Three sources are detected by ALMA, all of which are weakly lensed
by two foreground galaxies seen in the {\it HST} and Keck/NIRC-II imaging.  The
ALMA imaging is broadly consistent with SMA data originally presented in
\citet{Fu:2013lr}, with two bright sources and a much fainter third source very
close to the more southern bright source.  We assume Einstein radii of
$0\farcs5$ for both lenses to reproduce the approach used in \citet{Fu:2013lr}.
This results in magnification factors for the three sources of $\mu_{870}
\approx 1.6 - 1.7$, similar to \citet{Fu:2013lr}.

{\bf XMM02:} Two sources are detected by ALMA, both of which are weakly lensed.
This system is similar to ADFS02, although the two ALMA sources are much closer
and the lens must be less massive in order to avoid producing multiple images
of the closest ALMA source.  The fainter ALMA source has a much lower
magnification factor than the brighter source ($\mu_{870} = 1.10 \pm 0.01$ vs.
$\mu_{870} = 1.63 \pm 0.11$).  As with ADFS02, we caution that these
magnification factors represent the ``maximal lensing'' scenario and hence
should be considered upper limits.  Both ALMA sources are detected by IRAC and
have similar mid-IR colors, suggesting they lie at a similar redshift (see
Figure~\ref{fig:iraccolor}).

{\bf XMM03:} One source is detected by ALMA, and it is weakly lensed by two
foreground galaxies seen in the {\it HST} images.  We assume an Einstein radius
of 1$\arcsec$ for the foreground lenses and fix the positions of both lenses
according to the location of the foreground galaxies in the {\it HST} image.
As with XMM02, this is the ``maximal lensing'' scenario, so our magnification
measurement of $\mu_{870} = 1.80 \pm 0.16$ should be considered an upper limit.

{\bf XMM04:} Two sources are detected by ALMA, none of which appear to be
lensed.  The brighter ALMA source is weakly detected in the CFHT $i$-band
image.

{\bf XMM05:} One source is detected by ALMA, and it is weakly lensed by a group
of foreground galaxies seen in the {\it HST} image.  We assume an Einstein
radius of $0\farcs2$ for the nearest lensing galaxy and allow a $\pm0\farcs4$
shift in its position relative to that indicated by the {\it HST} image (which
has its astrometry tied to SDSS).  We represent the remaining members of the
group as a single SIS located $4\farcs5$ south and $4\farcs5$ east of the image
centroid and having an Einstein radius of $2\farcs0$.  This is meant to
represent the ``maximal lensing'' scenario, so our measurement of $\mu_{870}$
should be regarded as an upper limit.  The presence of two $3\sigma$ peaks
located near the center of the residual image indicates that the model does not
fit the data perfectly.  This could be an indication that either of our
assumptions for the lens potential or source structure are oversimplifications.
Higher resolution imaging is needed to determine the most likely cause.

{\bf XMM06:} One source is detected by ALMA, and it is strongly lensed by one
foreground galaxy seen in the {\it HST} image.  The lensed source is not
detected in the {\it HST} image.  This object also has high quality SMA imaging
and an accompanying lens model that produces consistent results with those
given here \citep{Bussmann:2013lr}.

{\bf XMM16:} Three sources are detected by ALMA, all of which are weakly lensed
by a foreground galaxy detected in the {\it HST} image and located $\approx
6\arcsec$ from the ALMA sources.  The central source is much brighter than the
other two sources, which makes fitting a model challenging.  We forced the
positions of the second and third sources to be at least $0\farcs5$ and
$-0\farcs5$ away from the first source in declination, respectively.
Furthermore, we fixed the position of the lens to be located $2\farcs5$ west
and $0\farcs5$ south of the image centroid given in Table~\ref{tab:position}.
We also fixed the Einstein radius to be $1\farcs0$, a typical value for
isolated galaxies in this sample and in \citet{Bussmann:2013lr}.  Because the
source is so far from the lens, the magnification factor is only $\mu_{870} =
1.19 \pm 0.01$.

{\bf XMM101:} One source is detected by ALMA, and it appears to be unlensed.  A
faint smudge seen in the {\it HST} image of this source is due to a star
located $3\farcs5$ northeast of the ALMA source.

{\bf XMM102:} Five sources are detected by ALMA, none of which appear to be
lensed.  There are a few faint smudges seen in the {\it HST} image which are
likely to be the rest-frame optical counterparts to the ALMA sources.  The ALMA
sources are all arranged in a chain like shape, possibly suggestive of a larger
filamentary overdensity in which they might reside.  IRAC imaging provides
support for this hypothesis (see Figure~\ref{fig:iraccolor}), as all of the ALMA
sources are detected and have similar mid-IR colors (suggesting they lie at
similar redshift).

{\bf XMM108:} One source is detected by ALMA, and it is strongly lensed by one
foreground galaxy detected in the Gemini-S image.  There is a $\approx
0\farcs5$ offset in the position of the foreground galaxy between the lens
model and the Gemini-S image.  Given the absolute astrometric uncertainty of
$0\farcs2$ (based on SDSS), we do not consider this offset to be significant.
The presence of a handful of $\pm3\sigma$ peaks in the residual map is likely
an indication that our assumption of a single Gaussian to describe the source
morphology is an oversimplification.

{\bf XMM109:} One source is detected by ALMA, and it is strongly lensed by one
foreground galaxy detected in the Gemini-S image.  As with XMM108, there is a
$\approx 0\farcs5$ offset between the lens position according to the lens model
and the Gemini-S image.  We do not consider this offset significant.  An
alternative model in which the lens is sub-mm luminous cannot be ruled out, but
we consider this unlikely for a number of reasons.  First, it is a more complex
model (having two sources and one lens, rather than one source and one lens).
Second, lenses are very rarely detected in sub-mm imaging.  Third, the shape
and location of the ALMA sources relative to the Gemini-S source are typical of
strongly lensed objects (consistent with the very low residuals).  Fourth, the
alternative lens model predicts the lensed source to have an intrinsic flux
density of $\approx 13 \,$mJy, which would make it the brightest source in the
sample.

{\bf XMM110:} Two sources are detected by ALMA, neither of which are lensed.
The faint, diffuse emission seen in the CFHT $i$-band image is atypical of
lensing galaxies.  The nearest bright galaxy seen at $i$-band is located
$\approx 18\arcsec$ southeast of the ALMA sources.

{\bf XMM115:} One source is detected by ALMA, and it is weakly lensed by a
foreground galaxy seen in the {\it HST} image.  We assume an Einstein radius of
$0\farcs5$ to represent the ``maximal lensing'' scenario.  Due to the
elliptical nature of the lens, this results in a magnification factor of
$\mu_{870} = 3.72 \pm 0.42$.  The {\it HST} morphology is complex: diffuse
emission to the north of the lens could be a detection of the background source
or could be a long spiral arm associated with the lensing galaxy.

{\bf XMM119:} Two sources are detected by ALMA, both of which are weakly
lensed by a foreground galaxy detected in the {\it HST} image.  An Einstein
radius of $1\farcs5$ is used to represent the ``maximal lensing'' scenario and
results in magnification factors of $\mu_{870} = 2.25 \pm 0.17$ and $\mu_{870}
= 1.48 \pm 0.09$.

{\bf XMM124:} One source is detected by ALMA, and it is coincident (within the
astrometric uncertainty) with a late-type galaxy seen in the {\it HST} image.
Here, we assume that the {\it HST} source is the true counterpart to the ALMA
source, implying that no lensing is occuring.  Consistent with this hypothesis
is that the SPIRE photometry show blue colors that suggest this object is at low
redshift.

\begin{figure*}[!tbp] 
    \begin{centering}
%\epsscale{1.00} 
%\includegraphics[width=\textwidth]{cutouts_dec17.png}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS01_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS01_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS01_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS02_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS02_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS02_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS03_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS03_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS03_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS04_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS04_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS04_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS05_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS05_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS05_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS06_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS06_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS06_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS07_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS07_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS07_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS_M0_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS_M0_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS_M0_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/CDFS_M0_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/CDFS_M0_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/CDFS_M0_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/CDFS_M1_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/CDFS_M1_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/CDFS_M1_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ECDFS02_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ECDFS02_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ECDFS02_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/COS01_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/COS01_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/COS01_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/COS02_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/COS02_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/COS02_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ElaisS1_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ElaisS1_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ElaisS1_residual_bestfit.pdf}
\end{centering}

\caption{ Model fits for each target in the ALMA sample, 3 panels per target.
{\it Left}: ALMA 870$\mu$m imaging (red contours, starting at $\pm 3\sigma$ and
increasing by factors of 2) overlaid on best available optical or near-IR
imaging (grayscale, with telescope and filter printed in upper right corner).
The location and morphology of all sources used in the model are represented by
magenta ellipses.  If a lens is present, its location is given by a black
circle and its critical curve is traced by an orange line.  The FWHM size of
the ALMA synthesized beam is shown in the lower left corner of each panel.
{\it Middle}: Same as {\it left}, but showing best-fit model in grayscale.
{\it Right}: Same as {\it left}, but showing resdiual image obtained from
subtracting best-fit model from the data.  \label{fig:uvmodels}}
\addtocounter{figure}{-1}

\end{figure*}

%\begin{figure*}[!tbp] 
%    \begin{centering}
%%\epsscale{1.00} 
%%\includegraphics[width=\textwidth]{cutouts_dec17.png}
%\end{centering}
%
%\caption{ Continued.}
%\addtocounter{figure}{-1}
%
%\end{figure*}
%
%\begin{figure*}[!tbp] 
%    \begin{centering}
%%\epsscale{1.00} 
%%\includegraphics[width=\textwidth]{cutouts_dec17.png}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/CDFS_M0_optical_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/CDFS_M0_model_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/CDFS_M0_residual_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/CDFS_M1_optical_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/CDFS_M1_model_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/CDFS_M1_residual_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ECDFS02_optical_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ECDFS02_model_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ECDFS02_residual_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ElaisS1_optical_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ElaisS1_model_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ElaisS1_residual_bestfit.pdf}
%\end{centering}
%
%\caption{ Continued.}
%\addtocounter{figure}{-1}
%
%\end{figure*}

\begin{figure*}[!tbp] 
    \begin{centering}
%\epsscale{1.00} 
%\includegraphics[width=\textwidth]{cutouts_dec17.png}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM01_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM01_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM01_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM02_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM02_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM02_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM03_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM03_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM03_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM04_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM04_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM04_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM05_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM05_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM05_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM06_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM06_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM06_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM16_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM16_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM16_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM101_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM101_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM101_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM102_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM102_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM102_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM108_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM108_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM108_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM109_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM109_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM109_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM110_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM110_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM110_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM115_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM115_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM115_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM119_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM119_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM119_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM124_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM124_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM124_residual_bestfit.pdf}
\end{centering}

\caption{ Continued.}
\addtocounter{figure}{-1}

\end{figure*}

\input{table_lenses}
\input{table_intrinsic}

\begin{figure*}[!tbp] 
    \begin{centering}
%\epsscale{1.00} 
%\includegraphics[width=\textwidth]{cutouts_dec17.png}
\includegraphics[width=0.195\textwidth]{../Figures/CDFS_M1_rgb.pdf}
\includegraphics[width=0.195\textwidth]{../Figures/COS02_rgb.pdf}
\includegraphics[width=0.195\textwidth]{../Figures/ElaisS1_rgb.pdf}
\includegraphics[width=0.195\textwidth]{../Figures/XMM02_rgb.pdf}
\includegraphics[width=0.195\textwidth]{../Figures/XMM102_rgb.pdf}
\end{centering}

\caption{ ALMA 870$\,\mu$m imaging (white contours, starting at 4$\sigma$ and
increasing by factors of 2) overlaid on color composite IRAC imaging (blue =
3.6$\,\mu$m, green = 4.5$\,\mu$m, red = 8.0$\,\mu$m).  All panels are $9\farcs5$
on a side.  North is up and east is left.  The synthesize beam is represented in
the lower right corner of each panel.  Each of the ALMA counterparts are
detected in the IRAC imaging.  In addition, the IRAC colors of ALMA sources are
broadly consistent, providing some evidence that they are at the same redshift
and not physically unassociated blends along the line of
sight.}\label{fig:iraccolor}

\end{figure*}

%\begin{figure*}[!tbp] 
%    \begin{centering}
%%\epsscale{1.00} 
%%\includegraphics[width=\textwidth]{cutouts_dec17.png}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM03_optical_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM03_model_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM03_residual_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM04_optical_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM04_model_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM04_residual_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM05_optical_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM05_model_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM05_residual_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM06_optical_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM06_model_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM06_residual_bestfit.pdf}
%\end{centering}
%
%\caption{ Continued.}
%\addtocounter{figure}{-1}
%
%\end{figure*}
%
%\begin{figure*}[!tbp] 
%    \begin{centering}
%%\epsscale{1.00} 
%%\includegraphics[width=\textwidth]{cutouts_dec17.png}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM101_optical_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM101_model_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM101_residual_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM102_optical_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM102_model_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM102_residual_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM108_optical_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM108_model_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM108_residual_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM109_optical_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM109_model_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM109_residual_bestfit.pdf}
%\end{centering}
%
%\caption{ Continued.}
%\addtocounter{figure}{-1}
%
%\end{figure*}

%\begin{figure*}[!tbp] 
%    \begin{centering}
%%\epsscale{1.00} 
%%\includegraphics[width=\textwidth]{cutouts_dec17.png}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM110_optical_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM110_model_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM110_residual_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM115_optical_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM115_model_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM115_residual_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM119_optical_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM119_model_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM119_residual_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM124_optical_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM124_model_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM124_residual_bestfit.pdf}
%\includegraphics[width=0.1623\textwidth]{../Figures/modelfit/XMM16_optical_bestfit.pdf}
%\includegraphics[width=0.1623\textwidth]{../Figures/modelfit/XMM16_model_bestfit.pdf}
%\includegraphics[width=0.1623\textwidth]{../Figures/modelfit/XMM16_residual_bestfit.pdf}
%\end{centering}
%
%\caption{ Continued.}
%\addtocounter{figure}{-1}
%
%\end{figure*}

%\begin{figure*}[!tbp] 
%    \begin{centering}
%%\epsscale{1.00} 
%%\includegraphics[width=\textwidth]{cutouts_dec17.png}
%\includegraphics[width=0.1623\textwidth]{../Figures/modelfit/XMM16_optical_bestfit.pdf}
%\includegraphics[width=0.1623\textwidth]{../Figures/modelfit/XMM16_model_bestfit.pdf}
%\includegraphics[width=0.1623\textwidth]{../Figures/modelfit/XMM16_residual_bestfit.pdf}
%\end{centering}
%
%\caption{ Continued.}
%%\addtocounter{figure}{-1}
%
%\end{figure*}

\section{Results}\label{sec:results}

\subsection{De-lensing the ALMA Sample}\label{sec:lensing}

The combination of our optical or near-IR imaging and our deep, high-resolution
ALMA imaging permits us to map the foreground structure along the line of sight
to the ALMA sources.  With such maps in hand for all of our targets, we can
estimate the impact that lensing has on the intrinsic properties of the ALMA
sources.  In other words, we can ``de-lens'' the ALMA sample.

Figure~\ref{fig:delens} shows the observed (i.e., apparent) and intrinsic
(i.e., de-lensed) distributions of $S_{870}$, $r_s$, angular separation, and
$q_s$.  Here, angular separation is the angular distance between an ALMA source
and the centroid of all the ALMA sources for a given {\it Herschel} DSFG.
Lensing has the strongest effect on $S_{870}$: the median flux density in the
ALMA sample drops by a factor of 1.6 when lensing is taken into account, and a
two-sided Kolmogorov-Smirnov (KS) test yields a $p$-value of 0.044.  Even
if strongly lensed sources are removed from the sample, the median intrinsic
flux density is 1.3 times lower than the median apparent flux density.  If we
only consider examples of weak lensing (i.e., removing the unlensed sources),
the factor rises back to 1.6.  These factors will be significant sources of
error if they are incorrectly ignored.  When discussing the intrinsic
properties of bright sources discovered in wide-field FIR or mm surveys, it
is critical to consider the effects of lensing.

For comparison, we also show the cumulative distribution of $S_{870}$ for the
ALESS sample.  There is greater overlap in $S_{870}$ between our sample and
ALESS than there is in $S_{500}$ (recall Figure~\ref{fig:sample}).  This is
evidence that the DSFGs in our sample have higher $S_{500}/S_{870}$ ratios than
the DSFGs in ALESS.  This difference is likely due to differences in dust
temperature or redshift distributions of the two samples and likely arises from
selection effects.

The effect on the other source parameters ($r_s$, angular separation, and
$q_s$) is less pronounced.  The median source size decreases by a factor of 1.2
in the ALMA sample after accounting for lensing, but the two-sided KS test
reveals a $p$-value of 0.174, suggesting that we cannot rule out the null
hypothesis that both size distributions were drawn from the same parent
distribution.  We find no significant difference between the axial ratios of
the apparent and intrinsic distributions as well as between the angular
separations of apparent and intrinsic distributions (two-sided KS test
$p$-values of 0.984 and 0.920, respectively).

%It is worth noting that some of the effect of lensing is washed out by the
%presence of unlensed sources and strongly lensed sources in the ALMA sample.
%In both of these cases we assign the same value for axial ratio, angular
%separation, and size between the apparent and intrinsic distributions.  If only
%weakly lensed sources are considered, the two-sided KS test $p$-values are
%0.002, 0.039, and 0.304, respectively.  There is a factor of 1.4, 1.3, and 1.2
%difference in the median values for these three parameters between the apparent
%and intrinsic distributions.  It is something of a surprise that axial ratios
%are on average lower in the intrinsic distribution.  Observations at higher
%spatial resolution are needed to determine if this distinction is real.

Finally, the brightest single source in the ALMA sample is XMM16-Source0, with
an intrinsic flux density of $S_{870} = 15.42 \pm 0.43\,$mJy.  However, there
are also two objects with multiple sources that have separations smaller than
1$\arcsec$ that have summed flux densities comparable to this: ADFS05
(15.3$\,$mJy) and ECDFS02 (14.1$\,$mJy).  This is approaching the values found
in the most extreme systems, such as GN20
\citep[20.6$\,$mJy,][]{2006MNRAS.370.1185P} and HFLS3
\citep[15-20$\,$mJy;][]{Riechers:2013lr, Cooray:2014rm}.  It is a level that is
extremely difficult to reproduce in simulations
\citep[e.g.,][]{Narayanan:2010lr}.  One possibility is that the objects with
multiple sources represent blends of physically unassociated systems.  Testing
this possibility requires redshift determinations of each source and is beyond
the scope of this paper.

\begin{figure}[!tbp] 
%\epsscale{1.00} 
\includegraphics[width=\linewidth]{../Figures/f870_delens.pdf}
%\includegraphics[width=0.24\linewidth]{../Figures/reff_delens.pdf}
%\includegraphics[width=0.24\linewidth]{../Figures/offset_delens.pdf}
%\includegraphics[width=0.24\linewidth]{../Figures/q_delens.pdf}

\caption{ Cumulative distribution functions showing the effect of lensing on
the inferred properties of the ALMA sample, including: flux densities (far left
panel), effective radii (middle left panel), angular separation from centroid
(middle right panel), and axial ratio (far right panel).  The median flux
density in the ALMA sample drops by a factor of 1.3 when lensing is taken into
account.  } \label{fig:delens}

\end{figure}

\subsection{Multiplicity in the ALMA Sample}\label{sec:multiplicity}

The second key result from our deep, high-resolution ALMA imaging is a firm
measurement of the rate of multiplicity in {\it Herschel} DSFGs.  We find that
20/29 {\it Herschel} DSFGs break down into multiple ALMA sources, implying a
multiplicity rate of 69\%.  
%Four out of
%these 20 comprise ALMA sources that are separated by $<1\arcsec$ and could be
%gravitationally bound systems (ADFS05, ECDFS02, XMM04, and XMM16).  Depending
%on whether these 4 are considered multiples or not, the multiplicity rate in
%the ALMA sample is 55\% - 69\%.  
However, 5/9 of the single-component
systems are strongly lensed.  If these five are not considered, then the
multiplicty rate increases to 80\%.  Such a high rate of multiplicity is
consistent with theoretical models \citep{HN13, HB13}.

In comparison, the 69 DSFGs in the MAIN ALESS catalog show a multiplicity rate
of 35\% - 40\% \citep{Hodge:2013qy}.  Smoothing our ALMA images and adding
noise to match the resolution and sensitivity of ALESS results in a
multiplicity rate of 55\% (4 objects with sources that are separated by
$<1\arcsec$ become single systems).  The redshift distributions for sources
selected at $S_{500}$ and $S_{870}$ are expected to be very similar, with only
a slightly higher median redshift for the ALESS sample \citep[e.g., $z_{\rm
med} = 2.0$ vs.  $z_{\rm med} = 2.2$; see][]{Zavala:2014lr}.  Note though, that
our sample has somewhat bluer colors on average than a strictly 500$\,\mu$m
selected sample and is therefore likely to have a slightly lower mean redshift.
On the other hand, the ALESS sources are much fainter overall, having a median
870$\,\mu$m flux density of $S_{870} \approx 6\,$mJy compared to $S_{870}
=14.9\,$mJy in our ALMA sample.  Thus, the evidence favors brighter sources
having a higher multiplicity rate.  This result is also consistent with
multiplicity studies of $S_{870}$-selected DSFGs by \citet{Smolcic:2012zl} and
\citet{Barger:2012yg}, who use PdBI/1.1$\,$mm and SMA/870$\,\mu$m imaging to
determine rates of 22\% and 40\%, respectively.

One useful way to characterize multiplicity is with a comparison of the total
870$\,\mu$m flux density, $S_{\rm total}$, with the individual component
870$\,\mu$m flux density, $S_{\rm component}$.  Figure~\ref{fig:componentflux}
shows these values for our ALMA sample and compares to ALESS.  Lensing has a
significant impact on the apparent flux densities of many objects in our ALMA
sample, so we are careful to show only intrinsic flux densities in this
diagram.  This diagram reflects the known result that the multipicity rate in
ALESS rises and the average fractional contribution per component decreases
with increasing $S_{\rm total}$ \citep{Hodge:2013qy}.  A simple extrapolation
of this phenomenon to the flux density regime probed by our ALMA sample would
have suggested a very high multiplicity rate and a very low average fractional
contribution per component.  The multiplicity rate in our sample is indeed
higher, but we find that the average fractional contribution per component
hovers around 0.4 for essentially the full range in our sample.  This is a
reflection of the fact that the brightest {\it Herschel} DSFGs comprise 1-3
ALMA components, not 5-10 ALMA components as might have been expected from a
naive extrapolation of the ALESS results.

\begin{figure}[!tbp] 
%\epsscale{1.00} 
\includegraphics[width=\linewidth]{../Figures/fluxtotalcomponent.pdf}

\caption{ Comparison of the total 870$\,\mu$m flux density, $S_{\rm total}$,
with the individual component 870$\,\mu$m flux density, $S_{\rm component}$
(both of these are after accounting for lensing).  Objects falling along the
gray dashed line are single component systems (i.e., $S_{\rm total} = S_{\rm
component}$).  The solid lines trace the average ratio of component to total
flux for a given total flux.  Our sample of {\it Herschel} DSFGs (ALMA sample,
green squares) has a higher multiplicity and a lower average factional
contribution per component than the ALESS sample (pink diamonds), but not as
low as would be expected from a simple extrapolation of the trend in the ALESS
data alone.} \label{fig:componentflux}

\end{figure}

%Of the 9 {\it Herschel} DSFGs in our ALMA sample that have a single ALMA
%source, 5 are strongly lensed.  This leaves 4 objects that are single-component
%systems experiencing amplification factors less than 2 (XMM03, XMM101, XMM115,
%and XMM124).  XMM03 and XMM115 are likely lensed by factors of $\approx 1.5-2$
%(discussed further in Section~\ref{sec:lensing}).  XMM124 is the faintest
%object in our sample and has the lowest photometric redshift (by far).  XMM101
%appears to be unlensed, making it the brightest single system in our sample.

\subsection{Spatial Distribution of Multiple Sources}\label{sec:spatialdist}

We can dig further into our ALMA data by exploring the average number of ALMA
sources per annular area ($dN/dA$) as a function of how far they are from
each other.  Figure~\ref{fig:dNdA} shows the results of this analysis for both
our ALMA sample and ALESS.  We formulate the separation as an angular distance
between each ALMA source and the centroid of all of the ALMA sources for that
{\it Herschel} DSFG.  This is different from \citet{Hodge:2013qy}, who use a
simple pairwise separation distance estimator, a method that becomes
ill-defined when there are more than 2 ALMA counterparts (as is often the case
in our ALMA sample).  Figure~\ref{fig:dNdA} shows $dN/dA$ values for ALESS that
have been re-computed using our method.  We also show the median and 1$\sigma$
range found from simulated datasets for both ALESS and our ALMA sample.  The
simulated datasets consist of 200 runs of DSFGs with the same flux density and
multiplicity as the observed datasets (both the ALESS sample and our ALMA
sample), but placed randomly within the primary beam FWHM.  We also show
predictions from simulations by \citet{HB13} (see below for details).

We recover the result from \citet{Hodge:2013qy} that the ALESS DSFGs are
consistent with a uniformly distributed population.  Interestingly, however,
there is a dramatic rise in $dN/dA$ for angular separations less than
$2\arcsec$ in our ALMA sample.  Indeed, for an angular separation of
$0\farcs5$, we find an excess in $dN/dA$ by a factor of $\approx 10$ compared
to a random, uniformly distributed population.  This excess persists (although
at significantly lower amplitude) even when the quality of our ALMA
observations are degraded to match the typical sensitivity, spatial resolution,
and {\it uv} coverage of ALESS (as represented by observations of ALESS 122).
The persistence of the excess suggests that it is an intrinsic property of the
sample; i.e., that only the brightest DSFGs show an excess of sources on small
separation scales.

\begin{figure*}[!tbp] 
%\epsscale{1.00} 
\includegraphics[height=3in]{../Figures/AllPositions.pdf}
\includegraphics[height=3in]{../Figures/dNdA.pdf}

\caption{ {\it Left}: Spatial distribution of sources with multiple counterparts
found in our ALMA sample (green squares), in ALESS (pink diamonds), and in mock
catalogs from \citet{HB13} (color scale).  Sources identified in our ALMA sample
lie much closer to each other than they do in either ALESS or the \citet{HB13}
simulations.  {\it Right}: Number of ALMA sources per annular area as a function
of angular separation from the ALMA centroid.  Results are shown for our ALMA
sample (thick green line), ALESS (thick pink line), the \citet{HB13} simulations
(thick blue line), and our ALMA sample as would have been seen with ALESS
resolution and sensitivity (thick orange line).  We also show the range of
separations that would be seen if sources were randomly distributed within the
ALMA field of view (green hatched region with solid and dashed green lines).
The DSFGs in our ALMA sample show a much stronger excess on angular separation
scales $<2\arcsec$ compared to ALESS and the \citet{HB13} simulations, even when
taking into account the difference in sensitivity and spatial resolution between
our ALMA observations and those of ALESS.  } \label{fig:dNdA}

\end{figure*}

An excess of sources with small separations from each other could be a signpost
of interacting or merging systems.  However, it is also possible that the
sources are merely unrelated galaxies that appear blended due to projection
effects \citep{HB13}.  Spatially resolved spectroscopy is necessary to answer
this question definitely, but is not currently available.  Instead, to
investigate these possibilities further, we make use of mock catalogs of DSFGs
that are based on numerical simulations and presented by \citet{HB13}.  We
summarize the methodology used to generate $dN/dA$ values from the mock catalogs
here and refer the reader to \citet{HB13} for full details.

Halo catalogs are generated from the {\it Bolshoi} dark matter-only
cosmological simulation \citep{Klypin11} using the {\sc rockstar} halo finder
\citep{Behroozi13a,Behroozi13b}.  Catalogs of subhalos are created from eight
randomly chosen lightcones, each with an area of 1.4$^\circ \times 1.4^\circ$.
Galaxy properties such as stellar mass and SFR are assigned to the subhalos
using the abundance matching method of \citet{Behroozi13c}.  Dust masses are
assigned using an empirically determined redshift-dependent mass--metallicity
relation and an assumed dust-to-metal density ratio of 0.4 (see \citealt{HN13}
for details). Finally, submm flux densities are interpolated from the SFRs and
dust masses using a fitting function that is based on the results of dust
radiative transfer calculations performed on hydrodynamical simulations of
isolated and interacting galaxies \citep{H11,H12,HN13}.

A blended source is defined as any galaxy in the mock catalogs above a
threshold flux density ($S_{\rm thresh}$) that has at least one neighbor within
a projected angular distance $d_{\rm neighbor}$.  To obtain a direct comparison
with our ALMA sample, we use $S_{\rm thresh} = 1.0\,$mJy and $d_{\rm
neighbor} = 40\arcsec$.  We use the known positions in the mock catalogs for
all blended sources and compute centroid and separations for every blended
source using the same methodology as we applied to our ALMA sample and to
ALESS.

The $dN/dA$ values found in the mock catalogs are shown by the
thick blue line in Figure \ref{fig:dNdA}.  There is a significant increase in
$dN/dA$ on separations smaller than $\approx 0\farcs5$, but the amplitude of
the increase is much lower than what is apparent in our ALMA sample.

%\citet{HB13} identified blended sources as
%follows.  First, they discarded all mock galaxies with $S_{850} < 1$ mJy (this
%value closely matches the typical 5$\sigma$ limit in our ALMA sample). Then,
%for each mock galaxy, they searched for neighboring
%SMGs within a projected angular distance equal to the FWHM of the PSF of the
%telescope used for discovery. If one or more companions were found, the sources
%were considered to constitute a blended source with total $S_{850}$ equal to
%the sum of the $S_{850}$ values of the individual component sources. In
%\citet{HB13}, a distance of 15$\arcsec$ was used to represent the spatial
%resolution of typical groun-based sub-mm surveys.  For this work, 40$\arcsec$
%was chosen as it best matches the {\it Herschel} PSF at 500$\,\mu$m. For each
%of the blended sources, we computed the centroid of the component sources and
%measure their separations from the centroid using the same methodology as was
%applied to the ALMA and ALESS samples.

The \citet{HB13} model does not include SFR elevations induced by starbursts
(see section 4.5 of \citealt{HB13} for a detailed discussion of this
limitation). To explore whether interaction-induced starbursts are the origin
of the excess at small angular separations observed in our ALMA sample, we
modified the \citet{HB13} model to include a crude treatment of
interaction-induced SFR elevation. Mock galaxies with one or more neighbors
within a physical distance of 5$\,$kpc and with a stellar mass between
one-third and three times that of the galaxy under consideration (i.e.  a
`major merger') had their SFR increased by a factor of two. For distances
smaller than 1$\,$kpc, the imposed increase was a factor of ten.  Because these
SFR elevations are greater than suggested by simulations \citep[e.g.][]{Cox08,
H11, H14, Torrey12} or observations of local galaxy pairs
\citep[e.g.][]{Scudder12, Patton13}, we consider this test to provide an upper
limit on the possible effect of interactions on blended sources in the
\citet{HB13} model.  We find an insignificant effect on the values of $dN/dA$
when using the merger-induced model as described above.  The main reason for
this is that only two sources had their SFRs boosted by a factor of ten, and
$\approx150$ experienced a factor of two increase. In the \citet{HB13} model, a
factor of two increase in SFR corresponds to only a ~30\% increase in
$S_{870}$, so it is perhaps unsurprising that the weak boosts in SFR cause
little change in $dN/dA$.

Experiments with stronger interaction-induced SFR elevations showed that very
high elevations (e.g. a factor of 10 for separation of 5-15$\,$kpc and 100 for
separation of $<5\,$kpc) in major mergers were required to match the observed
excess in $dN/dA$ on small separations. Incorporating starbursts induced by minor-merger could possibly reduce the required SFR elevations. The tension
between the model prediction and observations may also indicate that a more
sophisticated treatment of blending is necessary.

\section{Implications for the Bright End of the DSFG Luminosity
Function}\label{sec:discuss}

%There is some evidence that the intrinsic luminosity function of DSFGs has a
%very steep dropoff at around 8-10$\,$mJy \citep[e.g.,][]{Simpson:2014lr}.  
The distribution of magnification factors for sources found in wide-field
surveys with the brightest apparent flux densities are highly sensitive to the
shape of the intrinsic luminosity function at the bright end.  In this section,
we combine our ALMA and SMA measurements of magnification factors to investigate
this as it pertains to DSFGs.

\subsection{Statistical Predictions for $\mu_{870}$}\label{sec:statpredict}

Our methodology follows the procedures outlined in previous efforts to predict
magnification factors for DSFGs with a given apparent flux density
\citep[chiefly,][]{Lima:2010fk, Wardlow:2013lr}.  We summarize the essential
elements here and highlight significant differences where appropriate.
Additional details may be found in Fialkov et al. (in prep.).

The key components of the model are the mass density profile of the lenses,
$\rho_{\rm lens}\,(r)$, the number density of lenses as a function of mass and
redshift, $n_{\rm lens}\,(M, \, z)$), the redshift distribution of the sources,
$dN_{\rm source}/dz$, and the intrinsic luminosity function of the sources,
$dn_{\rm source}/dS_{870}^\prime)$.  The latter component is the least certain
component and also has the strongest impact on the predicted apparent
luminosity function.  For these reasons, we fix all components of the model
except the shape of the intrinsic luminosity function.  Our goal is to take
luminosity functions that can successfully fit observed faint DSFG number
counts \citep{Karim:2013lr} and test whether they lead to predicted
magnification factors consistent with our ALMA and SMA observations.

To describe $\rho_{\rm lens}\,(r)$, we use a superposition of a singular
isothermal sphere (SIS) and a Navarro Frenk White (NFW) profile
\citep{Navarro:1997ys} that is truncated at the virial radius.  The NFW profile
describes the outskirts of dark matter halos better while the SIS profile is
preferred on smaller scales because it correctly fits the observed flat
rotational curves in galaxies.  We make sure that the resulting probability
density of lensing, $P\,(\mu)$, is normalized to unity.

To describe $n_{\rm lens}\,(M, \, z)$, we generate abundances of halos at
each mass and redshift using the \citet{Sheth:1999kx} formalism.

To describe $dN_{\rm source}/dz$, we adopt the following redshift distribution
which is based on photometric redshifts of optical counterparts to ALMA sources
identified in ALESS \citep{Simpson:2014lr}:

\begin{equation}
    dN/dz \propto \frac{1}{a_z\sigma_z \sqrt{2\pi}}
    \exp\left( \frac{-[\ln(a_z) - \ln(1 + z_\mu)]^2} {2\sigma_z^2 a_z} \right),
\end{equation}

\noindent where $a_z = 1 + z$, $z_\mu = 2.6$, and $\sigma_z = 0.2$.

We explore a variety of intrinsic luminosity functions that are described by
either a single Schechter function or a broken-power law.  These luminosity
functions are selected to represent the range of observed instrinsic luminosity
functions for DSFGs which are shown in the left panel of
Figure~\ref{fig:lensstats} and are drawn from the ALESS survey
\citep{Karim:2013lr} and from interferometric follow-up of the first AzTEC
survey in COSMOS \citep{Scott:2008qy} using the SMA \citep{Younger:2007fk,
Younger:2009lr} and PdBI (Miettinen et al., in prep.).  Interferometric
follow-up data in COSMOS \citep{Smolcic:2012zl} and GOODS-N
\citep{Barger:2012yg} is published, but unknown completeness corrections in the
single-dish surveys on which these follow-up datasets are based precludes their
usage here.

The Shechter function we use has the usual form \citep{Schechter:1976yq}:

\begin{equation}
\frac{dn}{dS^\prime} = \frac{n_\star}{S_\star}
\left(\frac{S^\prime}{S_\star}\right)^{-\alpha}
\exp\left(\frac{-S^\prime}{S_\star}\right),
\end{equation}

\noindent while the broken power-law has the form:

\begin{equation}
\frac{dn}{dS^\prime} = N_\star\left(\frac{S^\prime}{S_\star}\right)^{-\beta_1},~~~~\textrm{for}~S<S_\star,
\end{equation}

\begin{displaymath}
\frac{dn}{dS^\prime} = N_\star\left(\frac{S^\prime}{S_\star}\right)^{-\beta_2},~~~~\textrm{for}~S>S_\star.
\end{displaymath}

In Table~\ref{tab:models}, we provide information for three models tested in
this paper: the steepest plausible Schechter function, the \citet{Karim:2013lr}
broken power-law, and a broken power-law with an even steeper fall-off at
higher flux densities than used in \citet{Karim:2013lr}.

\input{table_lf}

The product of the model is the lensing optical depth for a given lensing galaxy
and source galaxy. The sum over the distribution of source redshifts and lens
masses and redshifts yields the total optical depth for lensing,  $f_\mu$. The
lensing probability with magnification larger than $\mu$ is then calculated via
$P(>\mu) = 1-\exp(-f_\mu)$ and the differential probability distribution is
$P(\mu) = -dP(>\mu)/d\mu$.  The sum over the distribution of source redshifts
and lens masses and redshifts yields the total probability distribution
function.

The fundamental measurement provided by the spatially resolved SMA and ALMA
imaging and associated lens models is the magnification factor of a source with
a given apparent $S_{870}$.  Due to the large size of the combined sample, we
can compute the average magnification as a function of $S_{870}$ from the data:
$<\mu_{870}>$.  The same quantity can also be directly computed from our
model as:

\begin{equation}
    <\mu_{870}> = \int_0^\infty \mu P(\mu|S_{870})  d\mu,
 \end{equation}

\noindent where the probability for lensing with magnification $\mu$ given the
apparent flux is:

\begin{equation}
    P(\mu|S_{870}) = \frac{1}{N} \frac{P(\mu)}{\mu} \frac{dn}{dS_{870}^\prime}
\left(\frac{S_{870}}{\mu}\right),
\end{equation}

\noindent and

\begin{equation}
    N = \int \frac{P(\mu)}{\mu} \frac{dn}{dS_{870}^\prime}
    \left(\frac{S_{870}}{\mu}\right)d\mu.
\end{equation}

\noindent Here $ dn/dS_{870}$ is the observed luminosity function and
$dn/dS_{870}^\prime$ is the intrinsic luminosity function.

As part of the lens models, the SMA and ALMA imaging also provide the
probability that a source with a given apparent $S_{870}$ experiences a
magnification above some threshold value, $\mu_{\rm min}$: $P\,(\mu > \mu_{\rm
min})$.  It is therefore of interest to make a similar prediction from our
model.  We use the following to do this:

\begin{equation}
    P(\mu>\mu_{\rm min}) = \frac{\int_\mu^\infty P(\mu|S_{obs})}{\int_0^\infty
    P(\mu|S_{obs})}.
\end{equation}

\subsection{Comparing Model with Data}

The middle panel of Figure~\ref{fig:lensstats} shows a direct comparison of the
measured $\mu_{870}$ values as a function of apparent $S_{870}$ for the ALMA
and SMA samples.  We also show a running average of the combined sample
(considering only $\mu_{870} > 1.1$ objects, since this is the level at which
magnification effects become as significant as absolute calibration
uncertainties) to serve as a direct comparison to our theoretical models.  We
compute this by interpolating the observed $\mu_{870}$ and $S_{870}$ onto a
fine grid using the Scipy {\sc griddata} package and then smoothing the
resulting grid using a gaussian filter (specifically, the Scipy {\sc
gaussian\_filter} package).  Also shown in this diagram are model predictions
for the average magnification as a function of $S_{870}$, $<\mu_{870}>$,
assuming the three intrinsic luminosity functions for DSFGs described in
Table~\ref{tab:models}.

\begin{figure*}[!tbp] 
%\epsscale{1.00} 
\includegraphics[width=0.335\textwidth]{../Figures/DifferentialNumberCounts.pdf}
\includegraphics[width=0.335\textwidth]{../Figures/s870_mu.pdf}
\includegraphics[width=0.335\textwidth]{../Figures/Pmu_S870.pdf}

\caption{ {\it Left}: Observed luminosity functions from interferometer
follow-up of mm sources in COSMOS \citep[black circles;][Miettinen et al., in
prep.]{Younger:2007fk, Younger:2009lr} and from ALESS \citep[pink
diamonds;][]{Karim:2013lr}.  In comparison, the magneta, purple, and blue lines
show three models for the intrinsic luminosity functions of DSFGs. {\it Middle}:
Magnification factors at 870$\,\mu$m as a function of apparent $S_{870}$ for
every source in our ALMA (green squares) and SMA (red circles) samples.  The
black line represents a running average of the magnification measurements when
sources with $\mu_{870} > 1.1$ are considered.  Colored lines show our model
predictions $<\mu_{870}>$ for $\mu_{870} > 1.1$ sources for the three intrinsic
luminosity functions shown on the left.  All three luminosity functions are
broadly consistent with the observed magnification factors.  {\it Right}:
Probability that a source with a given $S_{870}$ experiences $\mu_{870} > 1.1$
(solid lines) and $\mu_{870} > 2.0$ (dashed lines).  The black lines show the
running average from the SMA and ALMA data.  Colored lines are the same as in
the middle and left panels.  The Schechter function predicts too many unlensed
or weakly lensed sources with intrinsic flux densities of $S_{870}^\prime \sim
50\,$mJy.  Our choices for the broken power-law luminosity functions roughly
bracket the running average from the data.} \label{fig:lensstats}

\end{figure*}

At low apparent flux densities ($S_{870} < 10\,$mJy), all three models are
broadly consistent with each other as well as with the running average of the
data, considering the dispersion in the model predictions for $\mu_{870}$ at a
given $S_{870}$ are $\sigma_\mu \approx 1-2$ in this regime.

The regime between the low and high apparent flux density limits ($10\,$mJy$ <
S_{870} < 70\,$mJy) is where the three model predictions show the largest
difference in $<\mu_{870}>$.  The steep rise in the running average in this
area is best reproduced by the model with the steep broken power-law luminosity
function.  However, this model has a difficult time accounting for the
low-$\mu_{870}$, high-$S_{870}$ population that comprises about one-third of
the sources in this regime.  Because the dispersion in the model magnification
factors rises smoothly from $\sigma_\mu \approx 2$ to $\sigma_\mu \approx 8$
over this regime, this difference is significant.  The steep Schechter function
does a better job of reproducing the low-magnification sources, but it
under-predicts the running average over much of the range in $S_{870}$.
Furthermore, there are a number of high-$\mu_{870}$, $S_{870} \approx
10-20\,$mJy sources that are poorly accounted for by the steep Schechter
function.  The broken power-law luminosity function advocated in
\citet{Karim:2013lr} provides an intermediate result between the steep
Schechter function and steep broken power-law and therefore shares some of the
strengths and weaknesses of both.

At high apparent flux densities ($S_{870} > 70\,$mJy), all of the models
over-predict the running average of the magnification.  One plausible
explanation for this difference is a limitation in the spatial resolution of
the observations.  In both the ALMA and SMA samples, the spatial resolution is
$\approx 0\farcs5$.  This is nearly always sufficient to resolve the images of
the lensed galaxy, but it is not always sufficient to resolve the images
themselves.  Therefore, it may be the case that the lens models over-predict
the intrinsic sizes of the lensed galaxies and hence under-predict the
magnification factors.  If this is true, it would also affect the intermediate
$S_{870}$ regime.  A thorough investigation of this possibility is deferred to
future work.

One way to deal with this potential limitation in the data is to simplify the
quantity of interest.  In particular, we next consider the probability of a
given source experiencing a magnification above some threshold value, $\mu_{\rm
min}$.  As discussed previously, we expect our ALMA and SMA measurements to
provide a reliable estimate of this quantity.  The results of this are shown in
the right panel of Figure~\ref{fig:lensstats}.  We consider two limiting
thresholds: $\mu_{\rm min} = 1.1$ and $\mu_{\rm min} = 2.0$.  The models we
consider are the same as those used in the left panel of
Figure~\ref{fig:lensstats}, and our method of creating the running average is
also the same.

In the low flux density regime ($S_{870} < 10\,$mJy), each model predicts that
10\% of sources experience a magnification satisfying $\mu_{870} > 1.1$.  This
is in disagreement with the data, which show that $\sim 30\%$ of sources in
this flux density regime experience $\mu_{870} > 1.1$.  The cause of this
discrepancy is unclear.  One possibility is simply that we are dealing with
small number statistics.  We speculate that an alternative explanation might be
related to the excess number of sources $dN/dA$ found in our ALMA maps with
small separations from each other (reported in Section~\ref{sec:spatialdist}).
Essentially, if the {\it Herschel} sources have a high multiplicity rate with
ALMA counterparts located close to each other, then adding a lens in front of
the {\it Herschel} source will magnify {\it all} of the ALMA counterparts.  If,
on the other hand, the ALMA counterparts were located far away from each other,
then adding a lens in front of the {\it Herschel} source would not necessarily
cause all ALMA counterparts to be magnified significantly.  For this reason, it
is plausible that the observed values reported in this figure are biased
upwards relative to the simulations outlined in Section~\ref{sec:statpredict}.

In the high flux density regime ($S_{870} > 10\,$mJy), all
three models as well as the running average in the data show a sharp transition
from low probability to high probability of being lensed (for either $\mu_{\rm
min} = 1.1$ or $\mu_{\rm min} = 2.0$).  However, there are major differences in
where this transition occurs.  For example, the steep Schechter function
predicts that 50\% of sources with $S_{870} = 50\,$mJy have $\mu_{870} < 1.1$.
This is inconsistent with the data, which show that all sources with $S_{870} >
50\,$mJy have $\mu_{870} > 1.1$.  The discrepancy is similar, albeit less
severe, for the luminosity function from \citet{Karim:2013lr}, where 50\% of
$S_{870} = 28\,$mJy sources are unlensed.  In contrast, the very steep broken
power-law luminosity function yields a model in which 50\% of sources with
$S_{870} = 10\,$mJy experience $\mu_{870} > 1.1$.  This is reasonably
consistent with the running average from the data.  These results are
qualitatively similar if the magnification threshold is increased from
$\mu_{\rm min} = 1.1$ to $\mu_{\rm min} = 2.0$.

If the steep power-law luminosity function is correct, the implications are
significant.  We should then expect to find $\approx 1$ source satisfying
$S_{870} > 10\,$mJy in a one square degree survey.  This is about a factor of 3
lower than the best-fit model in \citet{Karim:2013lr} and a factor of 7 lower
than our steep Schechter function.  Moreover, it is a factor of 20 lower than
typical measurements from single-dish, broad-beam studies
\citep[e.g.,][]{Weis:2009ly}.  This suggests that very luminous galaxies such as
GN20 and HFLS3 may be much more rare than previously thought.

%The Schechter function used here is the steepest plausible given the observed
%luminosity function in \citet{Karim:2013lr}.  This model best matches the
%running average from the data at high apparent flux densities $S_{870} >
%30\,$mJy, but it tends to under-predict the running average at lower flux
%densities.  At the other extreme, the very steep broken power-law matches the
%running average very well up to $S_{870} \approx 20\,$mJy.  Beyond this flux
%density, the model over-predicts $<\mu_{870}>$.  Between these two extremes
%lies the broken power-law advocated in \citet{Karim:2013lr}.  At the highest
%apparent flux densities ($S_{870} \approx 100\,$mJy), all three models
%over-predict the average magnification.

%How much would the SMA mu values have to go up to be consistent with the model?

%How many GN20s do the different intrinsic luminosity functions predict in
%GOODS-N?

\section{Conclusions} \label{sec:conclusions}

We present ALMA 870$\,\mu$m $0\farcs45$ imaging of 29 {\it Herschel} DSFGs
selected from 55$\,$deg$^2$ of HerMES.  The {\it Herschel} sources have
$S_{500} = 25 - 130\,$mJy, placing them in a unique phase space between the
brightest sources found by {\it Herschel} and those found in ground-based
surveys at sub-mm wavelengths that include more typical, fainter galaxies.  Our
ALMA observations reveal 62 sources down to the 5$\sigma$ limit ($\sigma
\approx 0.2\,$mJy, typically).  We make use of optical and near-IR imaging to
assess the distribution of intervening galaxies along the line of sight.  We
introduce a new, publicly available software called {\sc uvmcmcfit} and use it
to develop lens models for all ALMA sources with nearby foreground
galaxy.  Our results from this effort are summarized as follows:

\begin{enumerate}

    \item 36/62 ALMA sources experience significant amplification from a nearby
        foreground galaxy ($\mu_{870} > 1.1$).  The median amplification in the
        sample is $\mu_{870} = 1.6$.  Only 6 sources show morphology typical of
        strong gravitational lensing and could be identified as lenses from the
        ALMA imaging alone.  A multi-wavelength approach is critical to
        identifying structure along the line of sight and determining an
        unbiased measurement of the flux densities in our sample.

    \item 20/29 {\it Herschel} DSFGs break down into multiple ALMA
        counterparts.  Of the 9 isolated systems, 5 are strongly lensed by
        factors of 5-10.  After correcting for amplification, the brightest
        source in the sample has $S_{870}^\prime = 15.42 \pm 0.43\,$mJy.  There
        is a weak trend towards even higher multiplicity at the highest total
        $S_{870}$ flux densities.

    \item When a {\it Herschel} source comprises multiple ALMA counterparts,
        these counterparts are located close together.  Their separations are
        much smaller than ALMA counterparts to ALESS sources as well as
        simulated sources from \citet{HB13}.  This conclusion remains true even
        when we degrade our ALMA observations to match the spatial resolution,
        sensitivity, and {\it uv} coverage of the ALESS observations.

    \item Model predictions for the range of magnifications experienced by
        DSFGs in our sample indicate that a single Schechter function
        under-predicts the number of lensed sources with apparent $S_{870} >
        10\,$mJy.  Intrinsic luminosity functions with a broken power-law and a
        very steep decrease above 8$\,$mJy make better predictions for the
        fraction of lensed sources with $S_{870} > 10\,$mJy, but they also
        predict somewhat higher average magnification factors than are seen in
        combined sample of ALMA and SMA lens models.  This latter result coud
        be explained by limitations in the spatial resolution of the ALMA and
        SMA imaging, which might lead to the lens models under-estimating the
        magnification factors.

\end{enumerate}

Our findings suggest that galaxies with intrinsic flux densities above
$S_{870}^\prime \approx 10\,$mJy are extremely rare.  One possible explanation
for their rarity is that they are simply the tip of the mass function among
starbursts.  An alternative is that they represent a very short phase in galaxy
evolution.  Consistent with this idea is the high multiplicity rate in our ALMA
sample as well as the small projected separations between multiple ALMA
counterparts.  The inability of numerical simulations to reproduce the small
projected separations seen in the data might reflect an incomplete theoretical
understanding of the enhancement in star-formation by interactions and mergers
of galaxies which are already forming stars at a very high rate.

In the future, higher spatial resolution imaging is needed to investigate the
morphologies of individual ALMA sources.  Tidal tails, multiple nuclei, and
other signs of mergers and interactions should become evident at $0\farcs1$
resolution.  In addition, molecular spectroscopy will be critical to determine
distances to individual ALMA sources and hence characterize what fraction of
{\it Herschel} sources are actually physically associated with each other (and
not just a function of projection effects along the line of sight).  Molecular
spectroscopy will also provide critical information about the inter-stellar
medium in these galaxies, yielding insight into the process of how gas turns
into stars.

\begin{acknowledgments}

This paper makes use of the following ALMA data: ADS/JAO.ALMA\# 2011.0.00539.S.
ALMA is a partnership of ESO (representing its member states), NSF (USA) and
NINS (Japan), together with NRC (Canada) and NSC and ASIAA (Taiwan), in
cooperation with the Republic of Chile. The Joint ALMA Observatory is operated
by ESO, AUI/NRAO and NAOJ.

The results described in this paper are based on observations obtained with
{\it Herschel}, an ESA space observatory with science instruments provided by
European-led Principal Investigator consortia and with important participation
from NASA.

This research has made use of data from the HerMES project
(http://hermes.sussex.ac.uk/). HerMES is a Herschel Key Programme utilizing
Guaranteed Time from the SPIRE instrument team, ESAC scientists, and a mission
scientist. HerMES is described in \citet{Oliver:2012lr}.  The HerMES data
presented in this paper will be released through the {\em Herschel} Database in
Marseille (HeDaM\footnote{http://hedam.oamp.fr/HerMES}).

SPIRE has been developed by a consortium of institutes led by Cardiff Univ.
(UK) and including: Univ. Lethbridge (Canada); NAOC (China); CEA, LAM (France);
IFSI, Univ. Padua (Italy); IAC (Spain); Stockholm Observatory (Sweden);
Imperial College London, RAL, UCL-MSSL, UKATC, Univ. Sussex (UK); and Caltech,
JPL, NHSC, Univ. Colorado (USA). This development has been supported by
national funding agencies: CSA (Canada); NAOC (China); CEA, CNES, CNRS
(France); ASI (Italy); MCINN (Spain); SNSB (Sweden); STFC, UKSA (UK); and NASA
(USA).

The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc."

Based on observations obtained at the Gemini Observatory, which is operated by
the Association of Universities for Research in Astronomy, Inc., under a
cooperative agreement with the NSF on behalf of the Gemini partnership: the
National Science Foundation (United States), the National Research Council
(Canada), CONICYT (Chile), the Australian Research Council (Australia),
Minist\'erio da Ci\^encia, Tecnologia e Inova\c{c}\~ao (Brazil) and Ministerio
de Ciencia, Tecnolog\'ia e Innovaci\'on Productiva (Argentina).

Facilities: ALMA, Gemini-S.

\end{acknowledgments}

\bibliographystyle{apj}

\bibliography{rbussman}

%\appendix

\end{document}

### 2014-12-16 Code/allpositions.py

@@ -1,0 +1,116 @@
+"""
+
+Shane Bussmann
+
+2014 August 20
+
+Plot dN/dA as a function of angular separation from the center of light.  dN =
+number of objects between radius 1 and radius 2.  dA = area between radius 1
+and radius 2.
+
+"""
+
+from astropy.table import Table
+import matplotlib
+import matplotlib.pyplot as plt
+from pylab import savefig
+import numpy
+import sep_util
+from scipy.io import readsav
+
+
+# set font properties
+font = {'family' : 'Arial',
+        'weight' : 'normal',
+        'size'   : 12}
+matplotlib.rc('font', **font)
+matplotlib.rcParams['axes.linewidth'] = 1.2
+
+fig = plt.figure(figsize=(5.8, 4.5))
+plt.clf()
+
+# Plotting parameters
+hodgecolor = 'LightPink'
+hodgesimcolor = 'LightPink'
+hodgems = 4
+hodgefmt = 'D'
+
+# Load the data
+fluxcomponent_file = '../Data/hodge2013.dat'
+fluxcomponent = Table.read(fluxcomponent_file, format='ascii')
+
+# filter out single source systems
+fluxcomponent = sep_util.rmSingles(fluxcomponent, targetstring='lessid')
+nmultiples = len(fluxcomponent)
+
+sep_hodge = sep_util.getSeparation(fluxcomponent, targetstring='lessid')
+avgsep_hodge = sep_hodge[0]
+wmeansep_hodge = sep_hodge[1]
+ra_hodge = numpy.array(sep_hodge[2]) * 3600
+dec_hodge = numpy.array(sep_hodge[3]) * 3600
+
+plt.plot(ra_hodge, dec_hodge, hodgefmt, alpha=0.8, color=hodgecolor,
+        ms=hodgems, label='Hodge+13')
+
+# ***********
+# ALMA sample
+# ***********
+
+# plotting parameters
+acolor = 'green'
+asimcolor = 'green'
+ams = 5
+afmt = 's'
+
+fluxcomponent_file = '../Data/table_positions.dat'
+fluxcomponent = Table.read(fluxcomponent_file, format='ascii')
+
+# filter out single source systems
+fluxcomponent = sep_util.rmSingles(fluxcomponent, targetstring='target')
[…]

### 2014-12-16 Code/apphot_HST.py

@@ -1,0 +1,201 @@
+"""
+Created by Shane Bussmann
+2012 January 11
+
+Purpose: compute aperture photometry and uncertainties within a
+circular aperture; relies on PHOTFNU header keyword in HST images
+
+Inputs: 
+    optical_band: instrument + filter combination of images
+    apcentloc: ascii file containing aperture centers and radii in arcsec
+
+Outputs: Aperture flux and 1-sigma uncertainty
+
+"""
+
+
+import numpy
+import asciitable
+import pywcs
+import glob
+import pyfits
+import matplotlib.pylab as plt
+
+# specify HST and filter combination
+optical_band = 'HST_F110W'
+
+# specify how many targets to skip
+skipnum = 0
+
+# read in images
+dataloc = 'images/'
+optical_band_locs = dataloc + '*XMM05*' + optical_band + '.fits.gz'
+optical_band_files = glob.glob(optical_band_locs)
+
+# read in aperture centers and radial extents
+centloc = 'apcent_' + optical_band + '.txt'
+centers = asciitable.read(centloc)
+target_names = centers['target_name']
+ra_centers = centers['RA']
+dec_centers = centers['Dec']
+radial_extents = centers['radial_extent']
+
+naper = len(centers)
+fluxes = numpy.zeros(naper)
+errors = numpy.zeros(naper)
+
+# initiate a counter to track the aperture number
+apnum = 0
+
+for file in optical_band_files[skipnum:]:
+
+    # load HST image
+    im = pyfits.getdata(file)
+    head = pyfits.getheader(file)
+
+    # get WCS data
+    wcs = pywcs.WCS(head)
+
+    # get pixel scale in HST image
+    CD1_1 = head['CD1_1'] * 3600
+    CD1_2 = head['CD1_2'] * 3600
+    CD2_1 = head['CD2_1'] * 3600
+    CD2_2 = head['CD2_2'] * 3600
+    cdelt1 = numpy.sqrt(CD1_1 ** 2 + CD1_2 ** 2)
+    cdelt2 = numpy.sqrt(CD2_1 ** 2 + CD2_2 ** 2)
+    pixelscale = numpy.sqrt(cdelt1 ** 2 + cdelt2 ** 2)
+
+    # scale image by photometry conversion factor, Jy / (electron/sec)
+    photfnu = head['PHOTFNU']
+    im = im * photfnu
+
+    # get the target name from the filename
+    indx_start = file.find('images') + 7
+    indx_end = file.find(optical_band) - 1
[…]

### 2014-12-16 Code/colflux.py

@@ -1,0 +1,299 @@
+"""
+Created 2013 March 12
+Shane Bussmann
+
+Purpose: Make color-flux plots of Herschel SPIRE photometry
+for lensed sample and compare with H-ATLAS galaxies
+From Wardlow et al. 2012: 
+    - F350/F500 vs. F500
+"""
+
+# import modules and define plot appearance
+from astropy.io import fits
+import matplotlib
+from astropy.table import Table
+from astropy.io import ascii
+#matplotlib.use('pdf')
+import numpy
+import matplotlib.pyplot as mpl
+from pylab import savefig
+import pdb
+
+
+# set font properties
+font = {'family' : 'Arial',
+        'weight' : 'bold',
+        'size'   : 14}
+matplotlib.rc('font', **font)
+matplotlib.rcParams['axes.linewidth'] = 1.5
+
+# read in the plotting color scheme
+colorschemeloc = 'colorscheme.txt'
+colorscheme = Table.read(colorschemeloc, format='ascii')
+ecolor = str(colorscheme['ecolor'][0])
+color3 = colorscheme['color3'][0]
+color4 = colorscheme['color4'][0]
+gray = colorscheme['color6'][0]
+
+# set SMA plotting parameters
+acolor = colorscheme['color5'][0]
+ams = 6
+afmt = 's'
+
+# set SMA plotting parameters
+bcolor = colorscheme['color1'][0]
+bms = 6
+bfmt = 'o'
+
+# set SPT plotting parameters
+hcolor = colorscheme['color2'][0]
+hms = 7
+hfmt = '*'
+
+# set the level at which a Herschel source is a lens candidate
+candidate1 = 0.10
+
+# read in the SPIRE photometry for the ALMA sample
+almaspirephotloc = '../Data/targetlist.dat'
+#print spirephotloc
+almaspirephot = Table.read(almaspirephotloc, format='ascii')
+
+alma_f250 = almaspirephot['f250']
+alma_f350 = almaspirephot['f350']
+alma_f500 = almaspirephot['f500']
+
+alma_e250 = almaspirephot['e250']
+alma_e350 = almaspirephot['e350']
[…]

### 2014-12-16 Code/collectposteriors.py

@@ -1,0 +1,555 @@
+"""
+ Plot posterior distributions of model parameters
+ Shane Bussmann
+ 2014 July 14
+
+"""
+
+#def plot(objname, redo, deltachi2):
+
+import math
+import numpy
+import os
+from astropy.table import Table
+#import aplpy
+import matplotlib.pyplot as mpl
+from pylab import savefig
+#from matplotlib import rcParams.update({'font.size': 8})
+from matplotlib import rc
+import pdb
+
+rc('font',**{'family':'sans-serif','sans-serif':['Arial'],'size':'6'})
+## for Palatino and other serif fonts use:
+#rc('font',**{'family':'serif','serif':['New Century Schoolbook']})
+#rc('text', usetex=True)
+
+#deltachi2 = 100
+
+# read in the sample targets
+anloc = '../../ModelFits/'
+dataphotloc = 'targetlist.dat'
+dataphot = Table.read(dataphotloc, format='ascii')
+dataname = dataphot['dataname']
+ntarg = dataname.size
+dataflag = numpy.zeros(ntarg)
+for i in numpy.arange(ntarg):
+    datanamei = dataname[i]
+    dataloc = anloc + datanamei + '/uvfit25'
+    if os.path.exists(dataloc):
+        dataflag[i] = 1
+
+yesmodel = dataflag == 1
+dataphot = dataphot[yesmodel]
+dataname = dataphot['dataname']
+nmodel = dataphot.size
+
+# examine each inputs_lens.dat file to determine total number of lenses
+nsources = 0
+for i in range(nmodel):
+
+    # Grab constraints on lens(es)
+    dir = anloc + dataname[i] + '/uvmcbest/'
+    bestfitloc = dir + 'inputs_source.dat'
+    fitinputs_source = Table.read(bestfitloc)
+    nsource = len(fitinputs_source['flux']) / 2
+    nsources = nsources + nsource
+
+# store each source separately
+dt = {'names':['iauname', 'ra_s', 'e_ra_s', 'dec_s', 'e_dec_s', 
+    'flux_s', 'e_flux_s', 'n_s', 'e_n_s', 'r_s', 'e_r_s', 'ell_s', 'e_ell_s',
+    'phi_s', 'e_phi_s', 'mu', 'e_mu', 'minchi2', 'rmschi2', 'ndof'],
+    'formats':['a30', 'f2', 'f2', 'f2', 'f2', 'f2', 'f2', 'f2', 'f2', 'f2', 
[…]

### 2014-12-16 Code/componentflux.py

@@ -1,0 +1,349 @@
+"""
+
+Shane Bussmann
+
+2014 August 15
+
+Plot total flux of an object vs. the individual component fluxes of that
+object.  Like Figure 5 in Hodge+13.
+
+"""
+
+from astropy.table import Table
+import matplotlib
+import matplotlib.pyplot as plt
+from pylab import savefig
+import numpy
+
+
+# set font properties
+font = {'family' : 'Arial',
+        'weight' : 'normal',
+        'size'   : 12}
+matplotlib.rc('font', **font)
+matplotlib.rcParams['axes.linewidth'] = 1.5
+
+# read in the plotting color scheme
+colorschemeloc = 'colorscheme.txt'
+colorscheme = Table.read(colorschemeloc, format='ascii')
+ecolor = str(colorscheme['ecolor'][0])
+color3 = colorscheme['color3'][0]
+color4 = colorscheme['color4'][0]
+gray = colorscheme['color6'][0]
+
+# *****************
+# Hodge+2013 sample
+# *****************
+
+# Plotting parameters
+hodgecolor = 'LightPink'
+hodgems = 3
+hodgefmt = 'D'
+
+# Load the data
+fluxcomponent_file = '../Data/hodge2013.dat'
+fluxcomponent = Table.read(fluxcomponent_file, format='ascii')
+
+nindiv = len(fluxcomponent)
+
+superfluxtotal = []
+e_superfluxtotal = []
+for icomp in range(nindiv):
+    target = fluxcomponent['lessid'][icomp]
+
+    match = fluxcomponent['lessid'] == target
+    fluxsources = fluxcomponent['best880'][match]
+    e_fluxsources = fluxcomponent['e_best880'][match]
+    ftot = fluxsources.sum()
+    e_ftot = e_fluxsources.sum()
+
+    superfluxtotal.append(ftot)
+    e_superfluxtotal.append(e_ftot)
+
+fluxcomponent_hodge = fluxcomponent['best880']
+fluxtotal_hodge = numpy.array(superfluxtotal)
+
+xxxhodge = numpy.array(superfluxtotal)
+xxxerrhodge = numpy.array(e_superfluxtotal)
+yyyhodge = fluxcomponent['best880']
[…]

### 2014-12-16 Code/cosmos_lumfunc.py

@@ -1,0 +1,277 @@
+"""
+
+Estimate luminosity function in COSMOS from interferometric follow-up of
+Miettinen+ 2014, Younger+ 2007, and Younger+2009.
+
+"""
+
+import numpy
+import matplotlib.pyplot as plt
+from pylab import savefig
+from astropy.table import Table
+import matplotlib
+
+
+def MonteCarloCounts(fluxes, errors):
+
+    hist890, bin_edges = numpy.histogram(fluxes)
+    nbins = bin_edges.size - 1
+
+    nsource = fluxes.size
+    nsim = 1000
+    obsPDF = numpy.zeros([nsource, nsim])
+    for i in range(nsource):
+        imean = fluxes[i]
+        irms = errors[i]
+        obsPDF[i, :] = numpy.random.normal(loc=imean, scale=irms, size=nsim)
+
+    histPDF = numpy.zeros([nbins, nsim])
+
+    for isim in range(nsim):
+
+        hist, bedge = numpy.histogram(obsPDF[:, isim], bins=bin_edges)
+        histPDF[:, isim] = hist
+
+    histmean = numpy.mean(histPDF, axis=1)
+    histrms = numpy.std(histPDF, axis=1)
+
+    return histmean, histrms, bin_edges
+
+S_1100 = [10.7, 9.0, 7.6, 6.8, 7.6, 7.9, 8.3, 5.5, 5.8, 4.7, 4.7, 4.5, 4.4,
+        4.3, 4.3, 4.2]
+S_1100 = numpy.array(S_1100)
+
+S_890 = [15.6, 12.4, 8.7, 14.4, 9.3, 8.6, 12.0, 19.7, 9.0, 5.3, 14.4,
+        13.5, 8.2, 5.0, 3.9, 4.4]
+e_S_890 = [1.1, 1.0, 1.5, 1.9, 1.3, 1.3, 1.5, 1.8, 2.2, 1.0, 2.9, 1.8, 1.8,
+        1.0, 1.0, 1.0]
+S_890 = numpy.array(S_890)
+e_S_890 = numpy.array(e_S_890) * 1.2
+
+plt.clf()
+plt.plot(S_1100, S_890/S_1100, 'o')
+
+# This plot illustrates that the typical correction factor from total 1.1mm
+# flux density to total 890um flux density is ~1.5
+
+Oskari1300 = [2.07, 2.15, 1.58, 1.53, 1.78, 1.04, 4.82, 5.72, 1.85, 3.37, 2.19,
[…]

### 2014-12-16 Code/delens.py

@@ -1,0 +1,161 @@
+"""
+
+2014 August 21
+Shane Bussmann
+
+Plot the distribution of observed and intrinsic properties for the ALMA sample;
+Flux, size, axial ratio, and angular separation.
+
+"""
+
+import matplotlib.pyplot as plt
+import numpy
+from pylab import savefig
+from astropy.table import Table
+import matplotlib
+import sep_util
+from scipy.stats import ks_2samp
+
+
+# set font properties
+font = {'family' : 'Arial',
+        'weight' : 'normal',
+        'size'   : 12}
+matplotlib.rc('font', **font)
+matplotlib.rcParams['axes.linewidth'] = 1.5
+
+def makehist(variable, binwidth, xlabel, ylabel, savefile):
+
+    # clear the plotting window
+    plt.clf()
+
+    #changed = observed[variable] / intrinsic[variable] != 1
+    goodobserved = observed#[changed]
+    goodintrinsic = intrinsic#[changed]
+
+    # distribution for observed values
+    if variable == 'logf870':
+        realvariable = 'f870'
+        values = goodobserved[realvariable]
+        tmpvalues = goodintrinsic[realvariable]
+    elif variable == 'separation':
+        #goodobserved = sep_util.rmSingles(goodobserved)
+        #goodintrinsic = sep_util.rmSingles(goodintrinsic)
+        values, wmean = sep_util.getSeparation(goodobserved, fluxstring='f870')
+        tmpvalues, wm = sep_util.getSeparation(goodintrinsic, fluxstring='f870')
+    else:
+        values = goodobserved[variable]
+        tmpvalues = goodintrinsic[variable]
+    m1 = 0
+    m2 = values.max()
+    tmpm2 = tmpvalues.max()
+    if tmpm2 > m2:
+        m2 = tmpvalues.max()
+    bins = numpy.arange(m1, m2*5, binwidth)
+    #plt.hist(values, bins = bins, histtype='stepfilled', edgecolor='black',
+    #        facecolor='none', label='Observed', normed=True, cumulative=True,
+    #        linewidth=2)
+    values.sort()
+    tmpvalues.sort()
+    nvalues = values.size
+    indsorted = numpy.linspace(0.0, 1.0, num=nvalues)
+    values = numpy.append(values, 1e5)
+    tmpvalues = numpy.append(tmpvalues, 1e5)
[…]

### 2014-12-16 Code/dnda.py

@@ -1,0 +1,180 @@
+"""
+
+Shane Bussmann
+
+2014 August 20
+
+Plot dN/dA as a function of angular separation from the center of light.  dN =
+number of objects between radius 1 and radius 2.  dA = area between radius 1
+and radius 2.
+
+"""
+
+from astropy.table import Table
+import matplotlib
+import matplotlib.pyplot as plt
+from pylab import savefig
+import numpy
+import sep_util
+
+
+# set font properties
+font = {'family' : 'Arial',
+        'weight' : 'normal',
+        'size'   : 12}
+matplotlib.rc('font', **font)
+matplotlib.rcParams['axes.linewidth'] = 1.2
+
+fig = plt.figure(figsize=(5.0, 4.5))
+
+nbins = 10
+binwidth = 1.0
+bin_edges = numpy.arange(0, nbins + 1, binwidth)
+
+# ***********
+# ALMA sample with ALESS uv coverage and 1.4 mJy flux limit
+# ***********
+
+# NOTE: scaling factor by which to reduce flux of each ALMA source in my
+# sample should be determined by comparing total 870um flux densities for each
+# Herschel source and each LESS source.  So far, the factor of 3 was meant to
+# reproduce the median S500 flux density ratio, but S870 will be more accurate.
+
+simcolor = 'orange'
+simms = 4
+simfmt = 's'
+
+fluxcomponent_file = '../Data/table_ALESSsim.dat'
+fluxcomponent = Table.read(fluxcomponent_file, format='ascii')
+
+# filter out single source systems
+fluxcomponent = sep_util.rmSingles(fluxcomponent, targetstring='target')
+
+# filter out objects below a given flux threshold
+fluxcomponent = sep_util.setThresh(fluxcomponent, 1.4, fluxstring='peakflux')
+nmultiples = len(fluxcomponent)
+
+simalma = sep_util.getSeparation(fluxcomponent, fluxstring='peakflux')
+avgsep_simalma, wmeansep_simalma, ra_simalma, dec_simalma = simalma
+
+sep_util.histArea(avgsep_simalma, nbins, color=simcolor, fmt=simfmt, ms=simms,
+        norm=nmultiples)
+
[…]

### 2014-12-16 Code/fluxplot.py

@@ -1,0 +1,71 @@
+"""
+
+2014 July 16
+Shane Bussmann
+
+Plot the distribution of fluxdensities for the ALMA sample.  Compare total
+observed flux (what a single-dish telescope with 20" FWHM resolution would see)
+with the individual observed flux (accounting for blending) and with the
+individual intrinsic flux (accounting for lensing).
+
+"""
+
+import matplotlib.pyplot as plt
+import getfluxes
+import numpy
+from pylab import savefig
+
+
+def getstat(fluxdist):
+    fmean = fluxdist.mean()
+    fstd = fluxdist.std()
+    return fmean, fstd
+
+# f1: total observed flux density
+# f2: per-source observed flux density
+# f3: per-source intrinsic flux density
+f1, f2, f3 = getfluxes.all('uvfit25', mu_estimate=True)
+fnu = f1['fnu']
+fnu = numpy.append(fnu, f2['fnu'])
+fnu = numpy.append(fnu, f3['fnu'])
+m1 = 0
+m2 = 1 + int(fnu.max())
+
+binwidth = 2
+bins = numpy.arange(m1, m2 + binwidth, binwidth)
+fluxarr = f1['fnu']
+plt.hist(fluxarr, bins = bins, histtype='stepfilled', edgecolor='black',
+        hatch='///', facecolor='none', label='Observed, Unresolved')
+fmean, fstd = getstat(fluxarr)
+strmean = '{0:.1f}'.format(fmean)
+strstd = '{0:.1f}'.format(fstd)
+s1 = 'Observed, Unresolved <S_870> = ' + strmean + ' +/- ' + strstd
+plt.text(65, 13, s1, ha='right', fontsize='large')
+
+binwidth = 2
+bins = numpy.arange(m1, m2 + binwidth, binwidth)
+fluxarr = f2['fnu']
+plt.hist(fluxarr, bins = bins, alpha=0.5, histtype='stepfilled', 
+        color='red', label='Observed, Resolved')
+fmean, fstd = getstat(fluxarr)
+strmean = '{0:.1f}'.format(fmean)
+strstd = '{0:.1f}'.format(fstd)
+s1 = 'Observed, Resolved <S_870> = ' + strmean + ' +/- ' + strstd
+plt.text(65, 11, s1, ha='right', fontsize='large')
+
+binwidth = 2
+fluxarr = f3['fnu']# / mu
[…]

### 2014-12-16 Code/getfluxes.py

@@ -1,0 +1,160 @@
+"""
+ Plot posterior distributions of model parameters
+ Shane Bussmann
+ 2014 July 14
+
+"""
+
+import numpy
+import os
+from astropy.table import Table
+import modifypdf
+import setuputil
+import yaml
+
+
+def all(goodfit, update=False, mu_estimate=False):
+
+    # Check to see whether we've already loaded the data
+    if not update:
+        ffile = 'flux_total_observed.dat'
+        if os.path.exists(ffile):
+            ffile = 'flux_total_observed.dat'
+            flux_total_observed = Table.read(ffile, format='ascii')
+            ffile = 'flux_indiv_observed.dat'
+            flux_indiv_observed = Table.read(ffile, format='ascii')
+            ffile = 'flux_indiv_intrinsic.dat'
+            flux_indiv_intrinsic = Table.read(ffile, format='ascii')
+        else:
+            update = True
+    if update:
+        cwd = os.getcwd()
+
+        # read in the sample targets
+        anloc = '../../ModelFits/'
+        dataphotloc = 'targetlist.dat'
+        dataphot = Table.read(dataphotloc, format='ascii')
+        dataname = dataphot['dataname']
+        ntarg = dataname.size
+        dataflag = numpy.zeros(ntarg)
+        for i in range(ntarg):
+            datanamei = dataname[i]
+            dataloc = anloc + datanamei + '/' + goodfit
+            if os.path.exists(dataloc):
+                dataflag[i] = 1
+
+        yesmodel = dataflag == 1
+        dataphot = dataphot[yesmodel]
+        dataname = dataphot['dataname']
+        ntarg = len(dataphot)
+
+        dataname_indiv = []
+        flux_total = []
+        e_flux_total = []
+        flux_indiv = []
+        e_flux_indiv = []
+        flux_indiv_int = []
+        e_flux_indiv_int = []
+        for itarg in range(0, ntarg):
+
+            # extract object name from directory
+            objname = dataname[itarg]
+            iauname = dataphot['iauname'][itarg]
+            fitdir = anloc + dataname[itarg] + '/' + goodfit + '/'
+            os.chdir(fitdir)
+
+            # ------------------------------------------------------------------------
+            # Read posterior probability distributions
+            fitloc = 'posteriorpdf.fits'
+            fitresults = Table.read(fitloc)
+            fitresults = fitresults[-5000:]
+            fitresultsgood = modifypdf.cleanColumns(fitresults)
[…]

### 2014-12-16 Code/herschel_alma_overlay.py

@@ -1,0 +1,561 @@
+"""
+Created by Shane Bussmann
+2012 January 9
+Last modified: 2013 April 14
+
+Purpose: plot cutouts of ALMA imaging + VIKING K + SPIRE 250um
+
+"""
+
+import math
+import numpy
+from astropy.table import Table
+from astropy import wcs
+from astropy.io import fits
+#from astropy.coordinates import ICRS
+from astropy.coordinates import Angle
+#from astropy import units as u
+from pylab import savefig
+import matplotlib
+#matplotlib.use('png')
+import matplotlib.pyplot as plt
+from matplotlib.patches import Ellipse
+import pdb
+from scipy import interpolate
+import aplpy
+import sys
+import imp
+import yaml
+
+# define the instrument and wavelength of the optical imaging
+#optical_band = 'HST_F110W'
+optical_band = 'SDSS_i'
+#optical_band = 'KeckAO_Ks'
+optical_filter = optical_band[-1]
+
+submm_band = 'ALMA_870um'
+
+# Set font parameters
+font = {'family': 'Arial Narrow',
+        'weight': 'bold',
+        'size': 10}
+matplotlib.rc('font', **font)
+matplotlib.rcParams['axes.linewidth'] = 1.5
+
+# set up the plot window
+fig = plt.figure(figsize=(6.5, 5.5))
+plt.subplots_adjust(left=0.05, right=1.03, top=0.98, bottom=0.05)
+
+# identify ALMA targets
+targetloc = '../Data/targetlist.dat'
+targets = Table.read(targetloc, format='ascii')
+ntargets = len(targets)
+
+# get the optical image locations
+opticallocs = '../Data/bestoptical.dat'
+opticals = Table.read(opticallocs, format='ascii')
+
+# center and size of overlays
+ra_centers = targets['ra_250']
+dec_centers = targets['dec_250']
+#radial_extents = centers['radial_extent']
+
+# define the location of the ALMA images
+almaloc = '../../../../ModelFits/'
+
+for targ in range(0, ntargets):
+
+    plt.clf()
+    # get the target name from the filename
+    dataname = targets['dataname'][targ]
+    iauname = targets['iauname'][targ]
+    lensgrade = targets['lensgrade'][targ]
+
[…]

### 2014-12-16 Code/iracstamps.py

@@ -1,0 +1,317 @@
+"""
+
+2014 November 13
+
+Shane Bussmann
+
+Overlay ALMA contours on IRAC 3.6um, 4.5um, 8.0um 3-color image.
+
+"""
+
+from astropy.table import Table
+#import aplpy
+#from PIL import Image
+import numpy
+from astropy.io import fits
+from astropy import wcs
+from pylab import savefig
+import img_scale
+import yaml
+import matplotlib.pyplot as plt
+import math
+from matplotlib.patches import Ellipse
+import matplotlib
+
+
+def transform(imloc, ra_center, dec_center, radial_extent, vmax=1.5):
+
+    """ Rescale and trim input image. """
+
+    hdu = fits.open(imloc)
+    im = hdu[0].data
+    thisisalma = False
+    if im.ndim == 4:
+        thisisalma = True
+        im = im[0, 0, :, :]
+    optical_header = hdu[0].header
+    bad = im * 0 != 0
+    good = im * 0 == 0
+    im[bad] = im[good].min()
+
+    # compute the (x, y) center and pixel scale in the optical image
+    wcs_optical = wcs.WCS(optical_header, naxis=2)
+    pixxy = wcs_optical.wcs_world2pix(ra_center, dec_center, 1)
+    x_optical = numpy.round(pixxy[0])
+    y_optical = numpy.round(pixxy[1])
+    headerkeys = optical_header.keys()
+    cd1_1 = headerkeys.count('CD1_1')
+    if cd1_1 == 0:
+        cdelt1_optical = numpy.abs(optical_header['CDELT1'] * 3600)
+        cdelt2_optical = numpy.abs(optical_header['CDELT2'] * 3600)
+    else:
+        cdelt1_optical = numpy.abs(optical_header['CD1_1'] * 3600)
+        cdelt2_optical = numpy.abs(optical_header['CD2_2'] * 3600)
+        cd11 = optical_header['CD1_1']
+        cd12 = optical_header['CD1_2']
+        cd21 = optical_header['CD2_1']
+        cd22 = optical_header['CD2_2']
+        cdelt1_optical = numpy.sqrt(cd11 ** 2 + cd12 ** 2) * 3600
+        cdelt2_optical = numpy.sqrt(cd21 ** 2 + cd22 ** 2) * 3600
+        if cd12 == 0:
+            cd12 = cd11 / 1e8
[…]

### 2014-12-16 Code/mag-flux.py

@@ -1,0 +1,472 @@
+"""
+
+Shane Bussmann
+
+2014 August 22
+
+Plot magnification factor vs. S500.  Compare with Schechter function and broken
+power-law predictions for the same.
+
+"""
+
+from astropy.table import Table
+import matplotlib.pyplot as plt
+from pylab import savefig
+import matplotlib
+import numpy
+from scipy.interpolate import griddata
+from scipy.ndimage.filters import gaussian_filter
+from sklearn.linear_model import LogisticRegression
+
+
+def TrimMu(Stot, oldmu, thresh, norm=True):
+
+    """ Remove mu measurements below the threshold and adjust mu measurements
+    above the threshold to unity if we seek P(mu > thresh). """
+
+    trim = oldmu > thresh
+    if norm:
+        oldmu[:] = 0
+        oldmu[trim] = 1
+    else:
+        oldmu = oldmu[trim]
+        Stot = Stot[trim]
+
+    return Stot, oldmu
+
+def model(x):
+    return 1 / (1 + numpy.exp(-x))
+
+def LogReg(trimset):
+
+    """ Classify P(mu>mu_min) based on total apparent flux using Logistic
+    Regression. """
+
+    Stot = numpy.log10(trimset[0])
+    #Stot = numpy.log(trimset[0])
+    #npre = 100
+    #prevector = numpy.linspace(-100, -1, npre)
+    #prevector1 = numpy.zeros(npre)
+    #Stot = trimset[0]#numpy.append(prevector, trimset[0])
+    newmu = trimset[1]#numpy.append(prevector1, trimset[1])
+    clf = LogisticRegression(C=1e5)
+    Stotmatrix = Stot.reshape(len(Stot), 1)
+    clf.fit(Stotmatrix, newmu)
+    #X_test = numpy.linspace(-5, 5, 300)
+    #X_test = numpy.linspace(0, 150, 300)
+    X_test = numpy.linspace(-2, 3, 300)
+
+    loss = model(X_test * clf.coef_ + clf.intercept_).ravel()
+    #import pdb; pdb.set_trace()
+    #plt.plot(X_test, loss, color='blue', linewidth=3)
+    #plt.show()
+    #return X_test, loss
+    #return numpy.exp(X_test), loss
+    return 10 ** (X_test), loss
+
[…]

### 2014-12-16 Code/maketable_aless.py

@@ -1,0 +1,35 @@
+"""
+
+2014 September 24
+
+Shane Bussmann
+
+Take observed sources from ALMA sample and modify them to match ALESS sample
+properties:
+
+    1. The flux density of each source is reduced by a factor of 3
+    2. Sources separated by less than 2" become a single source
+    3. Sources with flux densities below 1.2 mJy are removed
+
+"""
+
+from astropy.table import Table
+
+almasample = Table.read('table_positions.dat', format='ascii')
+
+objname_previous = ''
+
+nsources = len(almasample)
+
+for isource in range(nsources):
+    objname = almasample['target'][isource]
+
+    if objname == objname_previous:
+        match = almasample['target'] == objname
+        ra_match = almasample['ra_alma'][match]
+        dec_match = almasample['dec_alma'][match]
+
+        # compute the separations between each source
+
+
+    objname_previous = objname

### 2014-12-16 Code/maketable_muS500.py

@@ -1,0 +1,165 @@
+"""
+ Plot posterior distributions of model parameters
+ Shane Bussmann
+ 2014 July 14
+
+"""
+
+import numpy
+import os
+from astropy.table import Table
+import modifypdf
+import setuputil
+import yaml
+from astropy.coordinates import SkyCoord
+from astropy import units as u
+
+
+# get S500 and S850 values from Magnelli
+magnelli = Table.read('magnelli_fluxes.dat', format='ascii')
+ok = (magnelli['f850'] > 0) & (magnelli['f500'] > 0)
+magnelli = magnelli[ok]
+avg850to500 = numpy.median(magnelli['f850'] / magnelli['f500'])
+
+# get S500 values for ALMA sample from Herschel
+targetlist = Table.read('targetlist.dat', format='ascii')
+
+fluxcomponent_file = 'source_observed.dat'
+fluxcomponent = Table.read(fluxcomponent_file, format='ascii')
+
+nindiv = len(fluxcomponent)
+
+superfluxtotal = []
+e_superfluxtotal = []
+s500a = []
+s500b = []
+for icomp in range(nindiv):
+    target = fluxcomponent['target'][icomp]
+
+    match = fluxcomponent['target'] == target
+    fluxsources = fluxcomponent['f870'][match]
+    e_fluxsources = fluxcomponent['e_f870'][match]
+    ftot = fluxsources.sum()
+    e_ftot = e_fluxsources.sum()
+
+    superfluxtotal.append(ftot)
+    e_superfluxtotal.append(e_ftot)
+
+    match2 = targetlist['dataname'] == target
+    s500tot = targetlist['f500'][match2][0]
+    iflux = fluxcomponent['f870'][icomp]
+    s500a.append(iflux / ftot * s500tot)
+
+    s500b.append(iflux / avg850to500)
+
+fluxcomponent_alma = fluxcomponent['f870']
+fluxtotal_alma = numpy.array(superfluxtotal)
+s500a_alma = numpy.array(s500a)
+s500b_alma = numpy.array(s500b)
+
+goodfitloc = 'uvfitlist.dat'
+goodfitdat = Table.read(goodfitloc, format='ascii')
+mu_estimate = False
+
+cwd = os.getcwd()
+
+# read in the sample targets
+anloc = '../../ModelFits/'
+dataphotloc = 'targetlist.dat'
+dataphot = Table.read(dataphotloc, format='ascii')
[…]

### 2014-12-16 Code/maketable_source.py

@@ -1,0 +1,604 @@
+"""
+ Plot posterior distributions of model parameters
+ Shane Bussmann
+ 2014 July 14
+
+"""
+
+import numpy
+import os
+from astropy.table import Table
+import modifypdf
+import setuputil
+import yaml
+from astropy.coordinates import SkyCoord
+from astropy import units as u
+from astropy.io import ascii
+
+goodfitloc = '../Data/uvfitlist.dat'
+goodfitdat = Table.read(goodfitloc, format='ascii')
+mu_estimate = False
+
+cwd = os.getcwd()
+
+observed = ascii.read('../Data/table_observed.dat')
+
+# read in the sample targets
+anloc = '../../../../ModelFits/'
+dataphotloc = '../Data/targetlist.dat'
+dataphot = Table.read(dataphotloc, format='ascii')
+dataname = dataphot['dataname']
+ntarg = dataname.size
+dataflag = numpy.zeros(ntarg)
+#for i in range(ntarg):
+#    datanamei = dataname[i]
+#    dataloc = anloc + datanamei + '/' + goodfit
+#    if os.path.exists(dataloc):
+#        dataflag[i] = 1
+
+#yesmodel = dataflag == 1
+#dataphot = dataphot[yesmodel]
+dataname = dataphot['dataname']
+ntarg = len(dataphot)
+objname_previous = ''
+
+sourcecounter = 0
+
+for itarg in range(0, ntarg):
+
+    # extract object name from directory
+    objname = dataname[itarg]
+    iauname = dataphot['iauname'][itarg]
+    goodfit = goodfitdat['intrinsic'][itarg]
+    #goodfit = goodfitdat['observed'][itarg]
+    fitdir = anloc + dataname[itarg] + '/' + goodfit + '/'
+    os.chdir(fitdir)
+
+    # ------------------------------------------------------------------------
+    # Read posterior probability distributions
+    fitloc = 'posteriorpdf.fits'
+    fitresults = Table.read(fitloc)
+    fitresults = fitresults[-5000:]
+    fitresultsgood = modifypdf.cleanColumns(fitresults)
+    fitresultsgood = modifypdf.bigScoop(fitresultsgood)
+    fitresultsgood = modifypdf.prune(fitresultsgood, quiet=True)
+    nfits = len(fitresultsgood)
+
+    configfile = open('config.yaml')
+    config = yaml.load(configfile)
+    paramData = setuputil.loadParams(config)
+
[…]

### 2014-12-16 Code/modelcompare.py

@@ -1,0 +1,85 @@
+"""
+2014 February 11
+
+Shane Bussmann
+
+Compare uvfit10 and uvfit11 model results.
+
+uvfit10 = MLE + statwt + CASA-bin
+uvfit11 = chi2 + statwt + CASA-bin
+"""
+
+from astropy.table import Table
+import glob
+import modifypdf
+import matplotlib.pyplot as plt
+from pylab import savefig
+import matplotlib
+
+modelloc = '../../ModelFits/'
+uvfitdirs = ['uvfit08', 'uvfit09', 'uvfit10', 'uvfit11']
+pdflocs = 'posteriorpdf_burnin.*.dat'
+
+ncol = 2
+
+# set font properties
+font = {'family' : 'Arial Narrow',
+        'weight' : 'bold',
+        'size'   : 10}
+matplotlib.rc('font', **font)
+matplotlib.rcParams['axes.linewidth'] = 1.5
+
+targlistloc = 'targetlist.dat'
+targlist = Table.read(targlistloc, format='ascii')
+ntarg = len(targlist)
+
+for itarg in range(0, ntarg):
+    dataname = targlist['dataname'][itarg]
+    print "Working on " + dataname
+
+    for uvfitdir in uvfitdirs:
+
+        fitdir = modelloc + dataname + '/' + uvfitdir + '/'
+        fitfiles = glob.glob(fitdir + pdflocs)
+        fitfile = fitfiles[-1]
+        fitresults = Table.read(fitfile, format='ascii', data_start=-5000)
+
+        fitresults = modifypdf.prune(fitresults)
+        columnheaders = fitresults.keys()
+        columnheaders.sort()
+        nparam = len(columnheaders)
+        nrow = nparam / ncol + 1
+        if uvfitdir == uvfitdirs[0]:
+            fig = plt.figure(figsize=(8.0, 2.0 * nrow))
+
+        counter = 1
+        for key in columnheaders:
+            plt.subplot(nrow, ncol, counter)
+            if uvfitdir == 'uvfit08':
+                hatch = '//'
+                fc = 'none'
+                ec = 'red'
+                alpha = 1.0
+            if uvfitdir == 'uvfit09':
+                hatch = '\\'
+                fc = 'none'
+                ec = 'blue'
+                alpha = 1.0
+            if uvfitdir == 'uvfit10':
+                hatch = ''
+                fc = 'red'
+                ec = 'black'
+                alpha = 0.5
[…]

### 2014-12-16 Code/oircutouts.py

@@ -1,0 +1,429 @@
+"""
+Created by Shane Bussmann
+2012 January 9
+Last modified: 2013 April 14
+
+Purpose: plot cutouts of ALMA imaging + VIKING K + SPIRE 250um
+
+"""
+
+import math
+import numpy
+from astropy.table import Table
+from astropy import wcs
+from astropy.io import fits
+#from astropy.coordinates import ICRS
+from astropy.coordinates import Angle
+#from astropy import units as u
+from pylab import savefig
+import matplotlib
+#matplotlib.use('png')
+import matplotlib.pyplot as plt
+from matplotlib.patches import Ellipse
+import os
+import yaml
+#import phot
+
+
+# Set font parameters
+font = {'family': 'Arial',
+        'weight': 'bold',
+        'size': 10}
+matplotlib.rc('font', **font)
+matplotlib.rcParams['axes.linewidth'] = 1.5
+
+filterlist = ['u', 'g', 'r', 'i', 'z', 
+        'Y', 'F110W', 'J', 'H', 'Ks',
+        'irac1', 'irac2', 'irac3', 'irac4', '24',
+        'wise1', 'wise2', 'wise3', 'wise4']
+#filterlist = ['i']
+nfilters = len(filterlist)
+#midirdata = Table.read('../Data/bestmidir.dat', format='ascii')
+
+goodfitloc = '../Data/uvfitlist.dat'
+goodfitdat = Table.read(goodfitloc, format='ascii')
+
+targetlistloc = '../Data/targetlist.dat'
+targetlist = Table.read(targetlistloc, format='ascii')
+ntargets = len(targetlist)
+
+# center and size of overlays
+ra_centers = targetlist['ra_250']
+dec_centers = targetlist['dec_250']
+
+figwidth = 15.0#2.0 * nfilters
+figlength = 12.0# * ntargets
+fig = plt.figure(figsize=(figwidth, figlength))
+plt.subplots_adjust(left=0.05, right=0.97, top=0.98, bottom=0.09)
+
+# clear the plotting window
+plt.clf()
+
+for itarg in range(0, ntargets):
+
+    counter = 1
+    plt.clf()
+
+    # get the target name from the filename
+    dataname = targetlist['dataname'][itarg]
+    iauname = targetlist['iauname'][itarg]
+
+    # load the corresponding ALMA image
+    submm_band = '870'
+    ALMA_file = '../../fitscutouts/' + dataname + '_' + submm_band + '.fits'
+    ALMA_image = fits.getdata(ALMA_file)
[…]

### 2014-12-16 Code/pbcorrect.py

@@ -1,0 +1,84 @@
+"""
+
+2014 November 19
+
+Shane Bussmann
+
+Correct fluxes in source_observed.dat to account for primary beam fall-off.
+
+"""
+
+from astropy.io import ascii
+import astropy.coordinates as coord
+import astropy.units as u
+import yaml
+from astropy.io import fits
+import numpy
+
+
+observedloc = '../Data/table_observed.dat'
+observed = ascii.read(observedloc)
+nobs = len(observed)
+
+intrinsicloc = '../Data/table_intrinsic.dat'
+intrinsic = ascii.read(intrinsicloc)
+
+uvfitlistloc = '../Data/uvfitlist.dat'
+uvfitlist = ascii.read(uvfitlistloc)
+
+fitloc = '../../../../ModelFits/'
+
+for iobs in range(nobs):
+    ra = coord.Angle(observed['ra_alma'][iobs], unit=u.hour).degree
+    dec = coord.Angle(observed['dec_alma'][iobs], unit=u.deg).degree
+
+    target = observed['target'][iobs]
+
+    match = uvfitlist['dataname'] == target
+    fitdir = uvfitlist['observed'][match][0]
+
+    fullfitloc = fitloc + target + '/' + fitdir + '/'
+
+    configloc = fullfitloc + 'config.yaml'
+    configfile = open(configloc)
+    config = yaml.load(configfile)
+
+    imloc = fullfitloc + config['ImageName']
+    imhead = fits.getheader(imloc)
+
+    ra_center = imhead['CRVAL1']
+    dec_center = imhead['CRVAL2']
+
+    offra = (ra - ra_center) * numpy.cos(dec_center * numpy.pi / 180)
+    offdec = dec - dec_center
+    offset = numpy.sqrt(offra ** 2 + offdec ** 2) * 3600
+
+
+    diameter = 12.
+    lambda_obs = 870e-6
+    fwhm = 1.2 * lambda_obs / diameter * 206265
+    halfpower = fwhm / 2.355
+
+    pbcorr = numpy.exp(-0.5 * offset ** 2 / halfpower **2)
+    #import pdb; pdb.set_trace()
+
+    observedflux = observed['f870'][iobs]
+    e_observedflux = observed['e_f870'][iobs]
+    actualflux = observedflux / pbcorr
+    e_actualflux = e_observedflux / pbcorr
+
[…]

### 2014-12-16 Code/phot.py

@@ -1,0 +1,254 @@
+"""
+Created by Shane Bussmann
+2014 March 28
+
+Purpose: compute aperture photometry and uncertainties within a
+circular aperture
+
+Inputs: 
+    optical_band: instrument + filter combination of images
+    apcentloc: ascii file containing aperture centers and radii in arcsec
+
+Outputs: Aperture flux and 1-sigma uncertainty
+
+"""
+
+import numpy
+from astropy.table import Table
+from astropy.io import fits
+import os
+
+
+def rms(im, head, mask, apdiam, nrand=2000):
+
+    # load HST image
+    #im = hdulist[0].data
+    #head = hdulist[0].header
+    headkeys = head.keys()
+    cd1_1 = headkeys.count('CD1_1')
+    cd1_2 = headkeys.count('CD1_2')
+    cd2_1 = headkeys.count('CD2_1')
+    cd2_2 = headkeys.count('CD2_2')
+    if cd1_1 == 0:
+        cdelt1 = numpy.abs(head['CDELT1'] * 3600)
+        cdelt2 = numpy.abs(head['CDELT2'] * 3600)
+    else:
+        cdelt1 = numpy.abs(head['CD1_1'] * 3600)
+        cdelt2 = numpy.abs(head['CD2_2'] * 3600)
+        cd11 = head['CD1_1']
+        #cd12 = head['CD1_2']
+        #cd21 = head['CD2_1']
+        cd22 = head['CD2_2']
+        cdelt1 = numpy.sqrt(cd11 ** 2) * 3600
+        cdelt2 = numpy.sqrt(cd22 ** 2) * 3600
+        #if cd12 == 0:
+        #    cd12 = cd11 / 1e8
+        #cdratio = numpy.abs(cd11 / cd12)
+        #if cdratio < 1:
+        #    cdratio = 1 / cdratio
+        #if cdratio < 1e2:
+            #print "This shit ain't rotated yo!"
+            #import pdb; pdb.set_trace()
+    
+    # aperture radius in pixels
+    pixelscale = numpy.sqrt(cdelt1 ** 2 + cdelt2 ** 2)
+    radius = apdiam / 2. / pixelscale
+
+    # Define the mask region for computing rms
+    # We compute rms over the inner 1/2 region, excluding the source
+    nx = im[:,0].size
+    ny = im[0,:].size
+
+    # construct meshgrid of x, y coordinates
[…]

### 2014-12-16 Code/runsex.py

@@ -1,0 +1,83 @@
+"""
+2014 March 27
+Shane Bussmann
+
+Generate input files for SExtractor and run it.
+"""
+
+from astropy.table import Table
+from astropy.io import fits
+import os
+import numpy
+
+
+filterlist = ['u', 'g', 'r', 'i', 'z', 'Y', 'J', 'H', 'Ks']
+nfilters = len(filterlist)
+
+targetlistloc = 'targetlist.dat'
+targetlist = Table.read(targetlistloc, format='ascii')
+ntargets = len(targetlist)
+
+fitsdir = 'fitscutouts'
+os.chdir(fitsdir)
+
+for itarg in range(ntargets):
+
+    # get the target name from the filename
+    dataname = targetlist['dataname'][itarg]
+    iauname = targetlist['iauname'][itarg]
+
+    counter = 0
+    for ifilt in filterlist:
+
+        # load the appropriate optical image
+        imloc = dataname + '_' + ifilt + '_cut.fits'
+        if not os.path.exists(imloc):
+            continue
+        header = fits.getheader(imloc)
+
+        # estimate the photometric zeropoint of the data
+        gemzero = [24.91, 28.33, 28.33, 27.93, 26.84]
+        gemcolors = [0.38, 0.18, 0.1, 0.08, 0.05]
+        headerkeys = header.keys()
+        cautionflag = 1
+        #if headerkeys.count('AIRMASS') > 0:
+        #    gain = header['GAIN']
+        #    exptime = header['EXPTIME']
+        #    airmass = header['AIRMASS']
+        #    zpt = gemzero[counter] - 2.5 * numpy.log10(gain / exptime) - \
+        #        gemcolors[counter] * (airmass - 1.0)
+        #    cautionflag = 0
+        if headerkeys.count('PHOTZP') > 0:
+            zpt = header['PHOTZP']
+            cautionflag = 0
+        if headerkeys.count('MAGZPT') > 0:
+            zpt = header['MAGZPT']
+            cautionflag = 0
+        if cautionflag:
+            # go back to Gemini reduction directory to get needed header info
+            dataloc = '/Users/rbussman/Data/Gemini-South/'
+            oldimloc = dataloc + dataname + '_' + ifilt + '.fits'
+            oldheader = fits.getheader(oldimloc)
+            gain = oldheader['GAIN']
+            exptime = oldheader['EXPTIME']
[…]

### 2014-12-16 Code/sep_util.py

@@ -1,0 +1,204 @@
+"""
+
+Shane Bussmann
+
+2014 August 21
+
+Various utilities for calculating angular separations.
+
+"""
+
+
+import matplotlib.pyplot as plt
+import numpy
+from astropy import units as u
+from astropy.coordinates import SkyCoord
+
+
+def rmSingles(fluxcomponent, targetstring='target'):
+
+    """
+
+    Filter out targets in fluxcomponent that have only one ALMA source.
+
+    """
+
+    nindiv = len(fluxcomponent)
+
+    flagger = numpy.zeros(nindiv)
+    for icomp in range(nindiv):
+        target = fluxcomponent[targetstring][icomp]
+
+        match = fluxcomponent[targetstring] == target
+        nmatch = fluxcomponent[targetstring][match].size
+        if nmatch == 1:
+            flagger[icomp] = 1
+
+    goodflag = flagger == 0
+    fluxcomponent = fluxcomponent[goodflag]
+
+    return fluxcomponent
+
+def setThresh(fluxcomponent, thresh, fluxstring='f880'):
+
+    """
+
+    Filter out targets in fluxcomponent below a given `thresh` flux density.
+
+    """
+
+    if fluxstring == 'peakflux':
+        thresh /= 1e3
+    fluxhigh = fluxcomponent[fluxstring] > thresh
+    fluxcomponent = fluxcomponent[fluxhigh]
+
+    return fluxcomponent
+
+
+def getSeparation(fluxcomponent, rastring='ra_alma', decstring='dec_alma',
+        targetstring='target', fluxstring='f880'):
+
+    nindiv = len(fluxcomponent)
+
+    separation = []
+    ra_vector = []
+    dec_vector = []
+    fluxweighted = []
+    for icomp in range(nindiv):
+        target = fluxcomponent[targetstring][icomp]
+
+        match = fluxcomponent[targetstring] == target
+        ras = fluxcomponent[rastring][match]
+        decs = fluxcomponent[decstring][match]
+        fluxs = fluxcomponent[fluxstring][match]
+        nmatch = fluxcomponent[fluxstring][match].size
+        newra = numpy.zeros(nmatch)
+        newdec = numpy.zeros(nmatch)
+        for imatch in range(nmatch):
+            ira = ras[imatch]
+            idec = decs[imatch]
[…]

### 2014-12-16 Code/sigirlfir.py

@@ -1,0 +1,636 @@
+"""
+Created 2012 September 3
+Shane Bussmann
+
+Purpose: Plot SigmaFIR vs. LFIR
+"""
+
+# import modules and define plot appearance
+from astropy.table import Table
+import matplotlib
+import numpy
+import matplotlib.pyplot as plt
+from pylab import savefig
+#from scipy.interpolate import griddata
+#from scipy import interpolate
+from scipy.interpolate import Rbf
+from astropy import cosmology
+
+
+def interpolateLFIR(S870, z, S870_ref, z_ref, LFIR_ref):
+    #points, antipoints = numpy.meshgrid(z_ref, S870_ref)
+    #values = LFIR_ref
+    #xi = (z, S870)
+    #import pdb; pdb.set_trace()
+    #LFIR = griddata(points, values, xi)
+    #tck = interpolate.bisplrep(S870_ref, z_ref, LFIR_ref, s=0)
+    #LFIR = interpolate.bisplev(S870, z, tck)
+    rbf = Rbf(S870_ref, z_ref, LFIR_ref, epsilon=2, function='linear')
+    LFIR = rbf(S870, z)
+    return LFIR
+
+def simLFIR(S870dist, zdist, nsim, S870_ref, z_ref, LFIR_ref):
+    LFIRdist = numpy.zeros(nsim)
+    index = numpy.random.uniform(size=nsim)
+    intindex = (index * len(S870dist)).astype(int)
+    S870rand = S870dist[intindex]
+    intindex = (index * len(zdist)).astype(int)
+    zrand = zdist[intindex]
+    for isim in range(nsim):
+        iz = zrand[isim]
+        iS870 = S870rand[isim]
+        LFIRdist[isim] = interpolateLFIR(iS870, iz, S870_ref, z_ref, LFIR_ref)
+    return LFIRdist
+
+def sampleLFIR(sample_S870, sample_e_S870, sample_z, sample_e_z, S870_ref,
+        z_ref, LFIR_ref):
+    nsample = sample_S870.size
+    sample_LFIR = numpy.zeros(nsample)
+    sample_e_LFIR = numpy.zeros(nsample)
+    for isample in range(nsample):
+        loc = sample_S870[isample]
+        scale = sample_e_S870[isample]
[…]

### 2014-12-16 Code/spectrallinephot.py

@@ -1,0 +1,239 @@
+"""
+Created by Shane Bussmann
+2012 December 4
+
+Purpose: compute aperture photometry and uncertainties
+
+Inputs: Image, aperture center, aperture shape
+
+Outputs: Aperture flux and 1-sigma uncertainty
+
+"""
+
+
+import math
+import numpy
+import os
+from astropy.table import Table
+from astropy import wcs
+import glob
+#import distutils.dir_util
+from astropy.io import fits
+import matplotlib.pylab as plt
+from pylab import savefig
+
+# specify how many targets to skip at start
+skipnum = 14
+
+#--------------------------------------------------------------------------
+# Step 1: read in image and beam
+datadir = 'linesearch/'
+dataloc = datadir + '*linesearch.fits'
+files = glob.glob(dataloc)
+
+nfiles = len(files)
+bmaj = numpy.zeros(nfiles)
+bmin = numpy.zeros(nfiles)
+extents = numpy.zeros(nfiles)
+
+counter = 1
+for ifile in files[skipnum:skipnum+2]:
+    print ifile
+
+    # get the dataname from the filename
+    startname = 11
+    endname = ifile.find('.linesearch')
+    dataname = ifile[startname:endname]
+
+    # aperture info
+    imcentloc = datadir + dataname + '.apertures'
+    imcentdat = Table.read(imcentloc, format='ascii')
+    napers = len(imcentdat)
+
+    # load datacube
+    imfile = fits.open(ifile)
+    limfile = len(imfile)
+    smaimall = fits.getdata(ifile)
+    nchan = smaimall[0, :, 0, 0].size
+
+    # initialize the coadded spectrum
+    spec_coadd = 0
+
+    for iaper in range(napers):
+        ra_centroid = imcentdat['ra_centroid'][iaper]
+        dec_centroid = imcentdat['dec_centroid'][iaper]
+        extent = imcentdat['extent'][iaper]
+
+        spectrum = numpy.zeros(nchan)
+        e_spectrum = numpy.zeros(nchan)
+
+        for chan in range(nchan):
+
+            # convert to mJy/beam
+            smaim = smaimall[0,chan,:,:].copy() * 1e3
+            if smaim.sum() == 0:
+                continue
+            headsmaim = fits.getheader(ifile)
+
+            # get phase center of observations
+            smawcs = wcs.WCS(headsmaim, naxis=2)
[…]

### 2014-12-16 Code/trimposteriors.py

@@ -1,0 +1,49 @@
+"""
+2013 July 10
+Shane Bussmann
+
+Trim finalposterior.dat down to the final N iterations
+"""
+
+import glob
+from astropy.table import Table
+import numpy
+import os
+import modifypdf
+
+
+# set the uvfit ID to be trimmed and pruned
+fitid = 'uvfit11'
+
+# set the original iterations
+burninfile = 'posteriorpdf_burnin.*.dat'
+
+cwd = os.getcwd()
+anloc = '../../ModelFits/'
+dataphotloc = 'targetlist.dat'
+dataphot = Table.read(dataphotloc, format='ascii')
+dataname = dataphot['dataname']
+ntarg = dataname.size
+dataflag = numpy.zeros(ntarg)
+for itarg in range(0, ntarg):
+
+    dirloc = anloc + dataname[itarg] + '/' + fitid
+    print dirloc
+    #if dataname[itarg] == 'XMM01':
+    #    continue
+    os.chdir(dirloc)
+    burninfiles = glob.glob(burninfile)
+    burninlast = burninfiles[-1]
+    fitresults = Table.read(burninlast, format='ascii', data_start=-5000)
+    prunedpdf = modifypdf.prune(fitresults)
+    import matplotlib.pyplot as plt
+    plt.clf()
+    maxprob = fitresults['lnprob'].max() + 0.1
+    hist1 = numpy.log10(maxprob - fitresults['lnprob'])
+    plt.hist(hist1, bins=15, log=True)
+    hist1 = numpy.log10(maxprob - prunedpdf['lnprob'])
+    plt.hist(hist1, bins=15, log=True)
+    plt.title(dataname[itarg])
+    from pylab import savefig
+    savefig('prunecheck')
+    os.chdir(cwd)

### 2014-12-16 Code/updatemodel.py

@@ -1,0 +1,53 @@
+"""
+
+2014 July 1
+
+Shane Bussmann
+
+Copy best-fit model and residual images from uvfit* directory to modelfit/
+
+"""
+
+from astropy.table import Table
+import glob
+import os
+
+
+# the uvfit directory containing the best-fit model
+fitlist = Table.read('uvfitlist.dat', format='ascii')
+
+# identify ALMA targets
+targetloc = 'targetlist.dat'
+targets = Table.read(targetloc, format='ascii')
+ntargets = len(targets)
+
+for itarg in range(ntargets):
+
+    target = targets[itarg]['dataname']
+
+    fitdir = fitlist['intrinsic'][itarg]
+    fitloc = '../../ModelFits/' + target + '/' + fitdir + '/'
+
+    pdfmap = 'LensedSBmap.optical.bestfit.pdf'
+    origin = fitloc + pdfmap
+    destination = 'modelfit/' + target + '.optical.bestfit.pdf'
+    destination = destination.replace('.', '_', 2)
+    cmd = 'cp ' + origin + ' ' + destination
+    print(cmd)
+    os.system(cmd)
+
+    pdfmap = 'LensedSBmap.model.bestfit.pdf'
+    origin = fitloc + pdfmap
+    destination = 'modelfit/' + target + '.model.bestfit.pdf'
+    destination = destination.replace('.', '_', 2)
+    cmd = 'cp ' + origin + ' ' + destination
+    print(cmd)
+    os.system(cmd)
+
+    pdfmap = 'LensedSBmap.residual.bestfit.pdf'
+    origin = fitloc + pdfmap
+    destination = 'modelfit/' + target + '.residual.bestfit.pdf'
+    destination = destination.replace('.', '_', 2)
+    cmd = 'cp ' + origin + ' ' + destination
+    print(cmd)
+    os.system(cmd)

### 2015-01-20 LaTeX/ms.tex
Comments from Lingyu Wang
Also added code to compute mass inside einstein radius.

@@
 
-    The {\it Herschel} Multi-tiered Extragalactic Survey (HerMES) has identified
-    large numbers of dusty star-forming galaxies (DSFGs) over a wide range in
-    redshift.  A detailed understanding of these DSFGs is hampered by the poor
-    spatial resolution of {\it Herschel}.  We present 870$\,\mu$m 0$\farcs$45
-    imaging obtained in Cycle~0 with the Atacama Large Millimeter/submillimeter
-    Array (ALMA) of a sample of 29 HerMES DSFGs.  We identify a total of 62
-    sources down to the $5\sigma$ limit in our ALMA sample ($\sigma \approx
-    0.2\,$mJy).  Optical or near-infrared imaging indicates that 36 of the ALMA
-    sources experience a significant flux boost from gravitational lensing ($\mu
-    > 1.1$), but only 6 are strongly lensed and show multiple images.  We
-    introduce and make use of {\sc uvmcmcfit}, a general purpose and publicly
-    available Markov Chain Monte Carlo visibility plane analysis tool to analyze
-    the source properties.  Nearly 70\% of the {\it Herschel} sources break down
-    into multiple ALMA counterparts, consistent with previous research
-    indicating that the multiplicity rate is high in bright sources discovered
-    in sub-mm or FIR surveys with poor spatial resolution.  The ALMA
-    counterparts to our {\it Herschel} targets are located much closer to each
-    other than ALMA counterparts to sources found in the LABOCA ECDFS
-    Submillimeter Survey.  Hydrodynamical numerical simulations and
-    semi-analytical models both underpredict the excess in number of sources
-    with small separations from each other that is seen in our ALMA sample.
-    Combined with our previous work on brighter {\it Herschel} sources, the lens
-    models presented here constrain the shape of the intrinsic luminosity
-    function for DSFGs to have a break around 8$\,$mJy with a very steep fall
-    off at higher flux densities.  The high multiplicity rate and low projected
-    separations between sources seen in our sample argue in favor of
-    interactions and mergers driving the prodigious emission from the brightest
-    DSFGs.
+    The {\it Herschel} Multi-tiered Extragalactic Survey (HerMES) has
+    identified large numbers of dusty star-forming galaxies (DSFGs) over a wide
+    range in redshift.  A detailed understanding of these DSFGs is hampered by
+    the poor spatial resolution of {\it Herschel}.  We present 870$\,\mu$m
+    0$\farcs$45 imaging obtained in Cycle~0 with the Atacama Large
+    Millimeter/submillimeter Array (ALMA) of a sample of 29 HerMES DSFGs.  We
+    identify a total of 62 sources down to the $5\sigma$ limit in our ALMA
+    sample ($\sigma \approx 0.2\,$mJy).  Optical or near-infrared imaging
+    indicates that 36 of the ALMA sources experience a significant flux boost
+    from gravitational lensing ($\mu > 1.1$), but only 6 are strongly lensed
+    and show multiple images.  We introduce and make use of {\sc uvmcmcfit}, a
+    general purpose and publicly available Markov Chain Monte Carlo visibility
+    plane analysis tool to analyze the source properties.  Nearly 70\% of the
+    {\it Herschel} sources break down into multiple ALMA counterparts,
+    consistent with previous research indicating that the multiplicity rate is
+    high in bright sources discovered in sub-mm or FIR surveys with poor
+    spatial resolution.  The ALMA counterparts to our {\it Herschel} targets
+    are located much closer to each other than ALMA counterparts to sources
+    found in the LABOCA ECDFS Submillimeter Survey.  Theoretical models
+    underpredict the excess in number of sources with small separations from
+    each other that is seen in our ALMA sample.  Combined with our previous
+    work on brighter {\it Herschel} sources, the lens models presented here
+    constrain the shape of the intrinsic luminosity function for DSFGs to have
+    a break around 8$\,$mJy with a very steep fall off at higher flux
+    densities.  The high multiplicity rate and low projected separations
+    between sources seen in our sample argue in favor of interactions and
+    mergers driving the prodigious emission from the brightest DSFGs.
 
@@
 \citep{Diolaiti:2000qy} on the 250$\, \mu$m {\it Herschel} Spectral and
-Photometric Imaging REceiver \citep[SPIRE;][]{2010A&A...518L...3G} images.
+Photometric Imaging REceiver \citep[SPIRE;][]{2010A&A...518L...3G} images
+\citep{Wang:2014lr}.
 Photometry is obtained from the HerMES XID pipeline \citep{Roseboom:2010lk},

### 2015-01-20 Code/mass_einstein.py

@@ -1,0 +1,65 @@
+"""
+Created 2013 March 13
+Shane Bussmann
+
+Purpose: Returns mass and velocity dispersion inside Einstein radius given an
+Einstein radius (in arcsec), source redshift, and lens redshift
+
+Inputs must be in numpy array format!
+
+"""
+
+from math import pi
+from astropy.cosmology import WMAP9 as cosmo
+import numpy
+
+def me(theta_Es, e_theta_Es, zlenses, zsources):
+
+    ntarg = theta_Es.size
+    M_E = numpy.zeros(ntarg)
+    e_M_E = numpy.zeros(ntarg)
+    vdisp = numpy.zeros(ntarg)
+    e_vdisp = numpy.zeros(ntarg)
+
+    for targ in numpy.arange(ntarg):
+
+        zsource = zsources[targ]
+        zlens = zlenses[targ]
+        theta_E = theta_Es[targ]
+        e_theta_E = e_theta_Es[targ]
+
+        # luminosity distances
+        d_LS = cosmo.luminosity_distance(zsource).value * 3.08e24
+        d_LL = cosmo.luminosity_distance(zlens).value * 3.08e24
+
+        # comoving distances
+        d_MS = d_LS / (1 + zsource)
+        d_ML = d_LL / (1 + zlens)
+
+        # angular diameter distances
+        d_ALS = 1 / (1 + zsource) * ( d_MS - d_ML )
+        d_AL = d_LL / (1 + zlens)**2
+        d_AS = d_LS / (1 + zsource)**2
+
+        # einstein radius in cm (7.1 kpc/" at z=0.7)
+        theta_E_cm = theta_E / 206265. * d_AL
+        e_theta_E_cm = e_theta_E / 206265. * d_AL
+
+        # get a distribution of Einstein radii
+        niters = 1e3
+        theta_E_iters = numpy.random.normal(loc = theta_E_cm, \
+                scale = e_theta_E_cm, size = niters)
+
+        # compute the mass enclosed within the Einstein radius
+        c = 3e10
+        G = 6.67e-8
+        sigma_crit = c**2 / 4 / pi / G * d_AS / d_AL / d_ALS
+        M_E_iters = pi * sigma_crit * theta_E_iters**2 / 2e33
+        M_E[targ] = numpy.mean(M_E_iters)
[…]

### 2015-01-22 LaTeX/ms.tex
Alex Conley comments
Updated target names to be consistent with W13 and C14.

@@
 flux calibration: Callisto (CDFS targets), Neptune (XMM targets), Titan (COSMOS
-targets) and Uranus (ADFS and XMM targets).  For ElaisS1, no solar system
+targets) and Uranus (ADFS and XMM targets).  For HELAISS02, no solar system
 object was observed.  Instead, J2258$-$279 was used for absolute flux
 calibration, with the flux fixed according to a measurement made two days prior
-to the observations of ElaisS1.
+to the observations of HELAISS02.
 
@@
 location of the ALMA sources.  In one case where two ALMA sources are separated
-by $\approx 10\arcsec$ (ADFS02), the elongation in the SPIRE 250$\,\mu$m map is
+by $\approx 10\arcsec$ (HADFS08), the elongation in the SPIRE 250$\,\mu$m map is
 consistent with the angular separation of the two ALMA counterparts.
@@
 dataset --- these were excluded from our Gemini-S program.  The remaining
-targets are: ADFS01, ADFS02, ADFS03, ADFS04, ADFS05, ADFS06, ADFS07, ADFS\_M0,
-ElaisS1, XMM02, XMM05, XMM101, XMM108, XMM109, and XMM115.  Each of these
+targets are: HADFS03, HADFS08, HADFS09, HADFS10, HADFS02, HADFS04, HADFS01, HADFS11,
+HELAISS02, HXMM11, HXMM12, HXMM22, HXMM07, HXMM30, and HXMM04.  Each of these
 targets were observed for a total of 9$\,$minutes of on-source integration time
@@
 %\includegraphics[width=\textwidth]{cutouts_dec17.png}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/ADFS01_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/ADFS02_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/ADFS03_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/ADFS04_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/ADFS05_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/ADFS06_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/ADFS07_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/ADFS_M0_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/CDFS_M0_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/CDFS_M1_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/ECDFS02_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/COS01_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HELAISS02_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM02_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM31_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM29_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM07_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM20_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM01_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM04_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM09_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM03_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM11_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM23_870_250.pdf}
 \end{centering}
@@
 %\includegraphics[width=\textwidth]{cutouts_dec17.png}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/COS02_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/ElaisS1_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM01_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM02_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM03_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM04_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM05_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM06_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM16_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM101_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM102_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM108_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM22_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM05_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM30_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM12_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HECDFS12_870_500.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HECDFS04_870_500.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HECDFS13_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS04_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS02_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS11_870_500.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS10_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS01_870_250.pdf}
 \end{centering}
@@
     \begin{centering}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS09_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS08_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS03_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HCOSMOS02_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{../Figures/overlays/HCOSMOS01_870_250.pdf}
 %\epsscale{1.00} 
 %\includegraphics[width=\textwidth]{cutouts_dec17.png}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM109_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM110_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM115_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM119_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/XMM124_870_250.pdf}
 \end{centering}
@@
 
-{\bf ADFS01:} Three sources are detected by ALMA, each of which is weakly
-lensed by a bright foreground galaxy seen in the {\it HST} image.  Alternative
-scenarios involving strong lensing can be ruled out by the location of the
-lens: $\approx 2-3\arcsec$ north of the centroid of the ALMA sources (the rms
-error in the astrometry is set from 2MASS at a level of $\approx 0\farcs4$) as
-well as the unusual location and fluxes of the ALMA sources relative to each
-other.  We assume an Einstein radius of $0\farcs5$ and fix the position angle
-of the lens to be between 40-50 degrees to match the orientation seen in the
-{\it HST} image.  Larger Einstein radii can be ruled out by the absence of
-counter images north of the lens.
-
-{\bf ADFS02:} Two sources are detected by ALMA, both of which are weakly lensed
-by a foreground galaxy in the {\it HST} image.  The ALMA sources have the
-largest separation of any in our sample overall: $\approx 10\arcsec$.  We
-assume an Einstein radius of $1\farcs5$ for the foreground lens as a ``maximal
-lensing'' scenario.  This results in magnification factors of $\mu_{870} = 2.3
-\pm 0.1$ and $\mu_{870} = 1.2 \pm 0.1$ for the two sources.  Our constraints on
-the true Einstein radius of the lens are weak, so these values for $\mu_{870}$
-should be regarded as upper limits.
-
-{\bf ADFS03:} Three sources are detected by ALMA, none of which appear to be
-lensed (the closest bright {\it HST} source is located $\approx 13\arcsec$ away
-from the ALMA sources).
-
-{\bf ADFS04:} Three sources are detected by ALMA.  In this paper, we have
-assumed that all three are unlensed.  There is a group of three sources
-detected in our Gemini-S optical imaging located $\approx 7\arcsec$ east of the
-ALMA sources.  This distance is so large that plausible mass ranges for the
-Gemini-S sources would imply at most a factor of 1.1-1.2 boost in the apparent
-flux densities of the ALMA sources.
-
-{\bf ADFS05:} Two sources are detected by ALMA.  The nearest possible lens is
-located $\approx 8\arcsec$ from the ALMA sources, indicating that lensing is
-likely to be irrelevant in this system.  The two ALMA sources are similarly
-bright ($S_{870} = 8.27 \pm 0.53\,$mJy and $S_{870} = 9.07 \pm 0.27\,$mJy) and
-separated by $\approx 0\farcs8$, corresponding to a projected physical distance
-of $\approx 6\,$kpc. This distance is typical of the pericentric passage
-distance in both hydrodynamical simulations of major mergers
-\citep[e.g.,][]{Hayward:2012lr} and CO observations of major mergers
-\citep[e.g.,][]{2008ApJ...680..246T, 2010ApJ...724..233E, 2011ApJ...733L..11R,
-2011MNRAS.412.1913I}.  Two plausible scenarios are that ADFS05 represents a
-major merger that just experienced a first pass or is approaching final
-coalescence, either of which significantly enhanced star-formation in the
-system.
-
-{\bf ADFS06:} Three sources are detected by ALMA, all of which are weakly
+{\bf HELAISS02:} Four sources are detected by ALMA, all of which are weakly
 lensed by a foreground galaxy seen in the {\it HST} image.  We assume an
-Einstein radius of $0\farcs5$ for the lens, as values larger than this produce
-multiple images of the ALMA sources.  Based on the brightness of the lens, we
-consider to be unlikely values for the Einstein radius that are smaller than
-$0\farcs5$, so the results we report for this object should be robust.
-
-{\bf ADFS07:} This is a single source that is strongly lensed by a foreground
-galaxy seen in the {\it HST} image.  The lensed source is not detected by {\it
-HST}.  The source is highly elongated ($q_s = 0.31 \pm 0.01$), but fits the
-data very well.  The position of the lens according to the lens model is
-consistent with the position in the {\it HST} image given the $0\farcs4$
-fundamental uncertainty due to using the 2MASS system as the fundamental basis
-for the astrometry.
-
-{\bf ADFS\_M0:} Two sources are detected by ALMA, both of which are weakly
-lensed by a group of small galaxies detected in the {\it HST} image.  We
-represent the gravitational potential of the group with a single SIE lens and
-an Einstein radius of $1\farcs0$.  Values larger than this produce additional
-counter images that are not seen in the ALMA imaging.  We cannot rule out
-smaller Einstein radii, but we consider these unlikely given the number of
-sources and their brightness in the {\it HST} image.
-
-{\bf CDFS\_M0:} This is a complex, very well constrained system.  Two sources
+Einstein radius of $1\farcs5$ for the lens as larger values begin to predict
+counter images that are not seen by ALMA.  The magnification factors reported
+here should be regarded as upper limits since we do not have strong constraints
+on the lower limit of the Einstein radius of the lens (e.g., the magnication
+factor for the source that is directly south of the lens is reported here to
+have $\mu_{870} = 1.68 \pm 0.06$, but values as small as 1.1-1.2 are likely
+plausible as well).  The ALMA sources are all detected by IRAC and their mid-IR
+colors are similar, suggesting they lie at the same redshift (see
+Figure~\ref{fig:iraccolor}).
+
+{\bf HXMM02:} One source is detected by ALMA, and it is strongly lensed by one
+foreground galaxy seen in the {\it HST} image.  The lensed source is not
+detected in the {\it HST} image.  This object also has high quality SMA imaging
+and an accompanying lens model that produces consistent results with those
+given here \citep{Bussmann:2013lr}.
+
+{\bf HXMM31:} Two sources are detected by ALMA, neither of which are lensed.
+The faint, diffuse emission seen in the CFHT $i$-band image is atypical of
+lensing galaxies.  The nearest bright galaxy seen at $i$-band is located
+$\approx 18\arcsec$ southeast of the ALMA sources.
+
+{\bf HXMM29:} Two sources are detected by ALMA, none of which appear to be
+lensed.  The brighter ALMA source is weakly detected in the CFHT $i$-band
+image.
+
+{\bf HXMM07:} One source is detected by ALMA, and it is strongly lensed by one
+foreground galaxy detected in the Gemini-S image.  There is a $\approx
+0\farcs5$ offset in the position of the foreground galaxy between the lens
+model and the Gemini-S image.  Given the absolute astrometric uncertainty of
+$0\farcs2$ (based on SDSS), we do not consider this offset to be significant.
+The presence of a handful of $\pm3\sigma$ peaks in the residual map is likely
+an indication that our assumption of a single Gaussian to describe the source
+morphology is an oversimplification.
+
+{\bf HXMM20:} Five sources are detected by ALMA, none of which appear to be
+lensed.  There are a few faint smudges seen in the {\it HST} image which are
+likely to be the rest-frame optical counterparts to the ALMA sources.  The ALMA
+sources are all arranged in a chain like shape, possibly suggestive of a larger
+filamentary overdensity in which they might reside.  IRAC imaging provides
+support for this hypothesis (see Figure~\ref{fig:iraccolor}), as all of the ALMA
+sources are detected and have similar mid-IR colors (suggesting they lie at
+similar redshift).
+
+{\bf HXMM01:} Three sources are detected by ALMA, all of which are weakly lensed
+by two foreground galaxies seen in the {\it HST} and Keck/NIRC-II imaging.  The
+ALMA imaging is broadly consistent with SMA data originally presented in
+\citet{Fu:2013lr}, with two bright sources and a much fainter third source very
+close to the more southern bright source.  We assume Einstein radii of
+$0\farcs5$ for both lenses to reproduce the approach used in \citet{Fu:2013lr}.
+This results in magnification factors for the three sources of $\mu_{870}
+\approx 1.6 - 1.7$, similar to \citet{Fu:2013lr}.
+
+{\bf HXMM04:} One source is detected by ALMA, and it is weakly lensed by a
+foreground galaxy seen in the {\it HST} image.  We assume an Einstein radius of
+$0\farcs5$ to represent the ``maximal lensing'' scenario.  Due to the
+elliptical nature of the lens, this results in a magnification factor of
+$\mu_{870} = 3.72 \pm 0.42$.  The {\it HST} morphology is complex: diffuse
+emission to the north of the lens could be a detection of the background source
+or could be a long spiral arm associated with the lensing galaxy.
+
+{\bf HXMM09:} Two sources are detected by ALMA, both of which are weakly
+lensed by a foreground galaxy detected in the {\it HST} image.  An Einstein
+radius of $1\farcs5$ is used to represent the ``maximal lensing'' scenario and
+results in magnification factors of $\mu_{870} = 2.25 \pm 0.17$ and $\mu_{870}
+= 1.48 \pm 0.09$.
+
+{\bf HXMM03:} Three sources are detected by ALMA, all of which are weakly lensed
+by a foreground galaxy detected in the {\it HST} image and located $\approx
+6\arcsec$ from the ALMA sources.  The central source is much brighter than the
+other two sources, which makes fitting a model challenging.  We forced the
+positions of the second and third sources to be at least $0\farcs5$ and
+$-0\farcs5$ away from the first source in declination, respectively.
+Furthermore, we fixed the position of the lens to be located $2\farcs5$ west
+and $0\farcs5$ south of the image centroid given in Table~\ref{tab:position}.
+We also fixed the Einstein radius to be $1\farcs0$, a typical value for
+isolated galaxies in this sample and in \citet{Bussmann:2013lr}.  Because the
+source is so far from the lens, the magnification factor is only $\mu_{870} =
+1.19 \pm 0.01$.
+
+{\bf HXMM11:} Two sources are detected by ALMA, both of which are weakly lensed.
+This system is similar to HADFS08, although the two ALMA sources are much closer
+and the lens must be less massive in order to avoid producing multiple images
+of the closest ALMA source.  The fainter ALMA source has a much lower
+magnification factor than the brighter source ($\mu_{870} = 1.10 \pm 0.01$ vs.
+$\mu_{870} = 1.63 \pm 0.11$).  As with HADFS08, we caution that these
+magnification factors represent the ``maximal lensing'' scenario and hence
+should be considered upper limits.  Both ALMA sources are detected by IRAC and
+have similar mid-IR colors, suggesting they lie at a similar redshift (see
+Figure~\ref{fig:iraccolor}).
+
+{\bf HXMM23:} One source is detected by ALMA, and it is coincident (within the
+astrometric uncertainty) with a late-type galaxy seen in the {\it HST} image.
+Here, we assume that the {\it HST} source is the true counterpart to the ALMA
+source, implying that no lensing is occuring.  Consistent with this hypothesis
+is that the SPIRE photometry show blue colors that suggest this object is at low
+redshift.
+
+{\bf HXMM22:} One source is detected by ALMA, and it appears to be unlensed.  A
+faint smudge seen in the {\it HST} image of this source is due to a star
+located $3\farcs5$ northeast of the ALMA source.
+
+{\bf HXMM05:} One source is detected by ALMA, and it is weakly lensed by two
+foreground galaxies seen in the {\it HST} images.  We assume an Einstein radius
+of 1$\arcsec$ for the foreground lenses and fix the positions of both lenses
+according to the location of the foreground galaxies in the {\it HST} image.
+As with HXMM11, this is the ``maximal lensing'' scenario, so our magnification
+measurement of $\mu_{870} = 1.80 \pm 0.16$ should be considered an upper limit.
+
+{\bf HXMM30:} One source is detected by ALMA, and it is strongly lensed by one
+foreground galaxy detected in the Gemini-S image.  As with HXMM07, there is a
+$\approx 0\farcs5$ offset between the lens position according to the lens model
+and the Gemini-S image.  We do not consider this offset significant.  An
+alternative model in which the lens is sub-mm luminous cannot be ruled out, but
+we consider this unlikely for a number of reasons.  First, it is a more complex
+model (having two sources and one lens, rather than one source and one lens).
+Second, lenses are very rarely detected in sub-mm imaging.  Third, the shape
+and location of the ALMA sources relative to the Gemini-S source are typical of
+strongly lensed objects (consistent with the very low residuals).  Fourth, the
+alternative lens model predicts the lensed source to have an intrinsic flux
+density of $\approx 13 \,$mJy, which would make it the brightest source in the
+sample.
+
+{\bf HXMM12:} One source is detected by ALMA, and it is weakly lensed by a group
+of foreground galaxies seen in the {\it HST} image.  We assume an Einstein
+radius of $0\farcs2$ for the nearest lensing galaxy and allow a $\pm0\farcs4$
+shift in its position relative to that indicated by the {\it HST} image (which
+has its astrometry tied to SDSS).  We represent the remaining members of the
+group as a single SIS located $4\farcs5$ south and $4\farcs5$ east of the image
+centroid and having an Einstein radius of $2\farcs0$.  This is meant to
+represent the ``maximal lensing'' scenario, so our measurement of $\mu_{870}$
+should be regarded as an upper limit.  The presence of two $3\sigma$ peaks
+located near the center of the residual image indicates that the model does not
+fit the data perfectly.  This could be an indication that either of our
+assumptions for the lens potential or source structure are oversimplifications.
+Higher resolution imaging is needed to determine the most likely cause.
+
+{\bf HECDFS12:} This is a complex, very well constrained system.  Two sources
 are detected by ALMA: one is strongly lensed and the other is weakly lensed.
@@
 
-{\bf CDFS\_M1:} Two sources are detected by ALMA, both of which are weakly
+{\bf HECDFS04:} Two sources are detected by ALMA, both of which are weakly
 lensed by a foreground galaxy seen in the {\it HST} image.  There is also a
@@
 
-{\bf ECDFS02:} This system is very similar to ADFS05, except that here the two
+{\bf HECDFS13:} This system is very similar to HADFS02, except that here the two
 ALMA sources are separated by $\approx 0\farcs4$ rather than $0\farcs8$ and one
@@
 
-{\bf ElaisS1:} Four sources are detected by ALMA, all of which are weakly lensed
-by a foreground galaxy seen in the {\it HST} image.  We assume an Einstein
-radius of $1\farcs5$ for the lens as larger values begin to predict counter
-images that are not seen by ALMA.  The magnification factors reported here
-should be regarded as upper limits since we do not have strong constraints on
-the lower limit of the Einstein radius of the lens (e.g., the magnication factor
-for the source that is directly south of the lens is reported here to have
-$\mu_{870} = 1.68 \pm 0.06$, but values as small as 1.1-1.2 are likely plausible
-as well).  The ALMA sources are all detected by IRAC and their mid-IR colors are
-similar, suggesting they lie at the same redshift (see
-Figure~\ref{fig:iraccolor}).
-
-{\bf COS01:} This system is similar to ADFS07: a single source that is strongly
-lensed by a foreground galaxy seen in the {\it HST} image.  In fact, the
-background source is also detected by {\it HST} as well as Keck/NIRC-II
+{\bf HADFS04:} Three sources are detected by ALMA, all of which are weakly
+lensed by a foreground galaxy seen in the {\it HST} image.  We assume an
+Einstein radius of $0\farcs5$ for the lens, as values larger than this produce
+multiple images of the ALMA sources.  Based on the brightness of the lens, we
+consider to be unlikely values for the Einstein radius that are smaller than
+$0\farcs5$, so the results we report for this object should be robust.
+
+{\bf HADFS02:} Two sources are detected by ALMA.  The nearest possible lens is
+located $\approx 8\arcsec$ from the ALMA sources, indicating that lensing is
+likely to be irrelevant in this system.  The two ALMA sources are similarly
+bright ($S_{870} = 8.27 \pm 0.53\,$mJy and $S_{870} = 9.07 \pm 0.27\,$mJy) and
+separated by $\approx 0\farcs8$, corresponding to a projected physical distance
+of $\approx 6\,$kpc. This distance is typical of the pericentric passage
+distance in both hydrodynamical simulations of major mergers
+\citep[e.g.,][]{Hayward:2012lr} and CO observations of major mergers
+\citep[e.g.,][]{2008ApJ...680..246T, 2010ApJ...724..233E, 2011ApJ...733L..11R,
+2011MNRAS.412.1913I}.  Two plausible scenarios are that HADFS02 represents a
+major merger that just experienced a first pass or is approaching final
+coalescence, either of which significantly enhanced star-formation in the
+system.
+
+{\bf HADFS11:} Two sources are detected by ALMA, both of which are weakly
+lensed by a group of small galaxies detected in the {\it HST} image.  We
+represent the gravitational potential of the group with a single SIE lens and
+an Einstein radius of $1\farcs0$.  Values larger than this produce additional
+counter images that are not seen in the ALMA imaging.  We cannot rule out
+smaller Einstein radii, but we consider these unlikely given the number of
+sources and their brightness in the {\it HST} image.
+
+{\bf HADFS10:} Three sources are detected by ALMA.  In this paper, we have
+assumed that all three are unlensed.  There is a group of three sources
+detected in our Gemini-S optical imaging located $\approx 7\arcsec$ east of the
+ALMA sources.  This distance is so large that plausible mass ranges for the
+Gemini-S sources would imply at most a factor of 1.1-1.2 boost in the apparent
+flux densities of the ALMA sources.
+
+{\bf HADFS01:} This is a single source that is strongly lensed by a foreground
+galaxy seen in the {\it HST} image.  The lensed source is not detected by {\it
+HST}.  The source is highly elongated ($q_s = 0.31 \pm 0.01$), but fits the
+data very well.  The position of the lens according to the lens model is
+consistent with the position in the {\it HST} image given the $0\farcs4$
+fundamental uncertainty due to using the 2MASS system as the fundamental basis
+for the astrometry.
+
+{\bf HADFS09:} Three sources are detected by ALMA, none of which appear to be
+lensed (the closest bright {\it HST} source is located $\approx 13\arcsec$ away
+from the ALMA sources).
+
+{\bf HADFS08:} Two sources are detected by ALMA, both of which are weakly lensed
+by a foreground galaxy in the {\it HST} image.  The ALMA sources have the
+largest separation of any in our sample overall: $\approx 10\arcsec$.  We
+assume an Einstein radius of $1\farcs5$ for the foreground lens as a ``maximal
+lensing'' scenario.  This results in magnification factors of $\mu_{870} = 2.3
+\pm 0.1$ and $\mu_{870} = 1.2 \pm 0.1$ for the two sources.  Our constraints on
+the true Einstein radius of the lens are weak, so these values for $\mu_{870}$
+should be regarded as upper limits.
+
+{\bf HADFS03:} Three sources are detected by ALMA, each of which is weakly
+lensed by a bright foreground galaxy seen in the {\it HST} image.  Alternative
+scenarios involving strong lensing can be ruled out by the location of the
+lens: $\approx 2-3\arcsec$ north of the centroid of the ALMA sources (the rms
+error in the astrometry is set from 2MASS at a level of $\approx 0\farcs4$) as
+well as the unusual location and fluxes of the ALMA sources relative to each
+other.  We assume an Einstein radius of $0\farcs5$ and fix the position angle
+of the lens to be between 40-50 degrees to match the orientation seen in the
+{\it HST} image.  Larger Einstein radii can be ruled out by the absence of
+counter images north of the lens.
+
+{\bf HCOSMOS02:} Five sources are detected by ALMA \citep[the brightest of
+which has already been detected;][]{Smolcic:2012zl}, none of which appear to be
+lensed.  Previous research has shown this to be an overdense region \citep[this
+object is called COSBO3 in][]{Aravena:2010fr} with a photometric redshift of
+$z=2.3-2.4$.  Our ALMA imaging offers the first convincing evidence that the
+associated galaxies in the overdensity are sub-mm bright and thus intensely
+star-forming.  There are a number of $2-3\sigma$ peaks in the map that could be
+real.  This would further increase the multiplicity rate for this object, but
+we caution that there are also negative peaks of similar amplitude (i.e.,
+$2-3\sigma$) present in this map.  Some of the ALMA sources have counterparts
+detected in the {\it HST} image, whereas all of the ALMA sources are detected
+by IRAC (see Figure~\ref{fig:iraccolor}).  Their mid-IR colors are similar,
+providing further evidence that the ALMA sources lie at the same redshift.
+
+{\bf HCOSMOS01:} This system is similar to HADFS01: a single source that is
+strongly lensed by a foreground galaxy seen in the {\it HST} image.  In fact,
+the background source is also detected by {\it HST} as well as Keck/NIRC-II
 adaptive optics imaging, and a lens model has been published based on these
@@
 
-{\bf COS02:} Five sources are detected by ALMA \citep[the brightest of which has
-already been detected;][]{Smolcic:2012zl}, none of which appear to be lensed.
-Previous research has shown this to be an overdense region \citep[this object is
-called COSBO3 in][]{Aravena:2010fr} with a photometric redshift of $z=2.3-2.4$.
-Our ALMA imaging offers the first convincing evidence that the associated
-galaxies in the overdensity are sub-mm bright and thus intensely star-forming.
-There are a number of $2-3\sigma$ peaks in the map that could be real.  This
-would further increase the multiplicity rate for this object, but we caution
-that there are also negative peaks of similar amplitude (i.e., $2-3\sigma$)
-present in this map.  Some of the ALMA sources have counterparts detected in the
-{\it HST} image, whereas all of the ALMA sources are detected by IRAC (see
-Figure~\ref{fig:iraccolor}).  Their mid-IR colors are similar, providing further
-evidence that the ALMA sources lie at the same redshift.
-
-{\bf XMM01:} Three sources are detected by ALMA, all of which are weakly lensed
-by two foreground galaxies seen in the {\it HST} and Keck/NIRC-II imaging.  The
-ALMA imaging is broadly consistent with SMA data originally presented in
-\citet{Fu:2013lr}, with two bright sources and a much fainter third source very
-close to the more southern bright source.  We assume Einstein radii of
-$0\farcs5$ for both lenses to reproduce the approach used in \citet{Fu:2013lr}.
-This results in magnification factors for the three sources of $\mu_{870}
-\approx 1.6 - 1.7$, similar to \citet{Fu:2013lr}.
-
-{\bf XMM02:} Two sources are detected by ALMA, both of which are weakly lensed.
-This system is similar to ADFS02, although the two ALMA sources are much closer
-and the lens must be less massive in order to avoid producing multiple images
-of the closest ALMA source.  The fainter ALMA source has a much lower
-magnification factor than the brighter source ($\mu_{870} = 1.10 \pm 0.01$ vs.
-$\mu_{870} = 1.63 \pm 0.11$).  As with ADFS02, we caution that these
-magnification factors represent the ``maximal lensing'' scenario and hence
-should be considered upper limits.  Both ALMA sources are detected by IRAC and
-have similar mid-IR colors, suggesting they lie at a similar redshift (see
-Figure~\ref{fig:iraccolor}).
-
-{\bf XMM03:} One source is detected by ALMA, and it is weakly lensed by two
-foreground galaxies seen in the {\it HST} images.  We assume an Einstein radius
-of 1$\arcsec$ for the foreground lenses and fix the positions of both lenses
-according to the location of the foreground galaxies in the {\it HST} image.
-As with XMM02, this is the ``maximal lensing'' scenario, so our magnification
-measurement of $\mu_{870} = 1.80 \pm 0.16$ should be considered an upper limit.
-
-{\bf XMM04:} Two sources are detected by ALMA, none of which appear to be
-lensed.  The brighter ALMA source is weakly detected in the CFHT $i$-band
-image.
-
-{\bf XMM05:} One source is detected by ALMA, and it is weakly lensed by a group
-of foreground galaxies seen in the {\it HST} image.  We assume an Einstein
-radius of $0\farcs2$ for the nearest lensing galaxy and allow a $\pm0\farcs4$
-shift in its position relative to that indicated by the {\it HST} image (which
-has its astrometry tied to SDSS).  We represent the remaining members of the
-group as a single SIS located $4\farcs5$ south and $4\farcs5$ east of the image
-centroid and having an Einstein radius of $2\farcs0$.  This is meant to
-represent the ``maximal lensing'' scenario, so our measurement of $\mu_{870}$
-should be regarded as an upper limit.  The presence of two $3\sigma$ peaks
-located near the center of the residual image indicates that the model does not
-fit the data perfectly.  This could be an indication that either of our
-assumptions for the lens potential or source structure are oversimplifications.
-Higher resolution imaging is needed to determine the most likely cause.
-
-{\bf XMM06:} One source is detected by ALMA, and it is strongly lensed by one
-foreground galaxy seen in the {\it HST} image.  The lensed source is not
-detected in the {\it HST} image.  This object also has high quality SMA imaging
-and an accompanying lens model that produces consistent results with those
-given here \citep{Bussmann:2013lr}.
-
-{\bf XMM16:} Three sources are detected by ALMA, all of which are weakly lensed
-by a foreground galaxy detected in the {\it HST} image and located $\approx
-6\arcsec$ from the ALMA sources.  The central source is much brighter than the
-other two sources, which makes fitting a model challenging.  We forced the
-positions of the second and third sources to be at least $0\farcs5$ and
-$-0\farcs5$ away from the first source in declination, respectively.
-Furthermore, we fixed the position of the lens to be located $2\farcs5$ west
-and $0\farcs5$ south of the image centroid given in Table~\ref{tab:position}.
-We also fixed the Einstein radius to be $1\farcs0$, a typical value for
-isolated galaxies in this sample and in \citet{Bussmann:2013lr}.  Because the
-source is so far from the lens, the magnification factor is only $\mu_{870} =
-1.19 \pm 0.01$.
-
-{\bf XMM101:} One source is detected by ALMA, and it appears to be unlensed.  A
-faint smudge seen in the {\it HST} image of this source is due to a star
-located $3\farcs5$ northeast of the ALMA source.
-
-{\bf XMM102:} Five sources are detected by ALMA, none of which appear to be
-lensed.  There are a few faint smudges seen in the {\it HST} image which are
-likely to be the rest-frame optical counterparts to the ALMA sources.  The ALMA
-sources are all arranged in a chain like shape, possibly suggestive of a larger
-filamentary overdensity in which they might reside.  IRAC imaging provides
-support for this hypothesis (see Figure~\ref{fig:iraccolor}), as all of the ALMA
-sources are detected and have similar mid-IR colors (suggesting they lie at
-similar redshift).
-
-{\bf XMM108:} One source is detected by ALMA, and it is strongly lensed by one
-foreground galaxy detected in the Gemini-S image.  There is a $\approx
-0\farcs5$ offset in the position of the foreground galaxy between the lens
-model and the Gemini-S image.  Given the absolute astrometric uncertainty of
-$0\farcs2$ (based on SDSS), we do not consider this offset to be significant.
-The presence of a handful of $\pm3\sigma$ peaks in the residual map is likely
-an indication that our assumption of a single Gaussian to describe the source
-morphology is an oversimplification.
-
-{\bf XMM109:} One source is detected by ALMA, and it is strongly lensed by one
-foreground galaxy detected in the Gemini-S image.  As with XMM108, there is a
-$\approx 0\farcs5$ offset between the lens position according to the lens model
-and the Gemini-S image.  We do not consider this offset significant.  An
-alternative model in which the lens is sub-mm luminous cannot be ruled out, but
-we consider this unlikely for a number of reasons.  First, it is a more complex
-model (having two sources and one lens, rather than one source and one lens).
-Second, lenses are very rarely detected in sub-mm imaging.  Third, the shape
-and location of the ALMA sources relative to the Gemini-S source are typical of
-strongly lensed objects (consistent with the very low residuals).  Fourth, the
-alternative lens model predicts the lensed source to have an intrinsic flux
-density of $\approx 13 \,$mJy, which would make it the brightest source in the
-sample.
-
-{\bf XMM110:} Two sources are detected by ALMA, neither of which are lensed.
-The faint, diffuse emission seen in the CFHT $i$-band image is atypical of
-lensing galaxies.  The nearest bright galaxy seen at $i$-band is located
-$\approx 18\arcsec$ southeast of the ALMA sources.
-
-{\bf XMM115:} One source is detected by ALMA, and it is weakly lensed by a
-foreground galaxy seen in the {\it HST} image.  We assume an Einstein radius of
-$0\farcs5$ to represent the ``maximal lensing'' scenario.  Due to the
-elliptical nature of the lens, this results in a magnification factor of
-$\mu_{870} = 3.72 \pm 0.42$.  The {\it HST} morphology is complex: diffuse
-emission to the north of the lens could be a detection of the background source
-or could be a long spiral arm associated with the lensing galaxy.
-
-{\bf XMM119:} Two sources are detected by ALMA, both of which are weakly
-lensed by a foreground galaxy detected in the {\it HST} image.  An Einstein
-radius of $1\farcs5$ is used to represent the ``maximal lensing'' scenario and
-results in magnification factors of $\mu_{870} = 2.25 \pm 0.17$ and $\mu_{870}
-= 1.48 \pm 0.09$.
-
-{\bf XMM124:} One source is detected by ALMA, and it is coincident (within the
-astrometric uncertainty) with a late-type galaxy seen in the {\it HST} image.
-Here, we assume that the {\it HST} source is the true counterpart to the ALMA
-source, implying that no lensing is occuring.  Consistent with this hypothesis
-is that the SPIRE photometry show blue colors that suggest this object is at low
-redshift.
-
 \begin{figure*}[!tbp] 
@@
 %\includegraphics[width=\textwidth]{cutouts_dec17.png}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS01_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS01_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS01_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS02_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS02_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS02_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS03_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS03_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS03_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS04_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS04_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS04_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS05_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS05_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS05_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS06_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS06_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS06_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS07_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS07_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS07_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS_M0_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS_M0_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ADFS_M0_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/CDFS_M0_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/CDFS_M0_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/CDFS_M0_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/CDFS_M1_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/CDFS_M1_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/CDFS_M1_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ECDFS02_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ECDFS02_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ECDFS02_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/COS01_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/COS01_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/COS01_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/COS02_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/COS02_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/COS02_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ElaisS1_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ElaisS1_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ElaisS1_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS03_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS03_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS03_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS08_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS08_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS08_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS09_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS09_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS09_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS10_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS10_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS10_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS02_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS02_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS02_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS04_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS04_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS04_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS01_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS01_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS01_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS11_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS11_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS11_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS01_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS01_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS01_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS02_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS02_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS02_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_residual_bestfit.pdf}
 \end{centering}
@@
 %%\includegraphics[width=\textwidth]{cutouts_dec17.png}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/CDFS_M0_optical_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/CDFS_M0_model_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/CDFS_M0_residual_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/CDFS_M1_optical_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/CDFS_M1_model_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/CDFS_M1_residual_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ECDFS02_optical_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ECDFS02_model_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ECDFS02_residual_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ElaisS1_optical_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ElaisS1_model_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/ElaisS1_residual_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_optical_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_model_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_residual_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_optical_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_model_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_residual_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_optical_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_model_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_residual_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_optical_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_model_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_residual_bestfit.pdf}
 %\end{centering}
@@
 %\includegraphics[width=\textwidth]{cutouts_dec17.png}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM01_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM01_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM01_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM02_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM02_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM02_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM03_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM03_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM03_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM04_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM04_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM04_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM05_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM05_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM05_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM06_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM06_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM06_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM16_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM16_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM16_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM101_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM101_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM101_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM102_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM102_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM102_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM108_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM108_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM108_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM109_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM109_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM109_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM110_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM110_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM110_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM115_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM115_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM115_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM119_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM119_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM119_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM124_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM124_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM124_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM01_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM01_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM01_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM11_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM11_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM11_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM05_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM05_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM05_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM29_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM29_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM29_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM12_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM12_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM12_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM02_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM02_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM02_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM03_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM03_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM03_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM22_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM22_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM22_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM20_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM20_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM20_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM07_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM07_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM07_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM30_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM30_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM30_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM31_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM31_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM31_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM04_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM04_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM04_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM09_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM09_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM09_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM23_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM23_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM23_residual_bestfit.pdf}
 \end{centering}
@@
 %\includegraphics[width=\textwidth]{cutouts_dec17.png}
-\includegraphics[width=0.195\textwidth]{../Figures/CDFS_M1_rgb.pdf}
-\includegraphics[width=0.195\textwidth]{../Figures/COS02_rgb.pdf}
-\includegraphics[width=0.195\textwidth]{../Figures/ElaisS1_rgb.pdf}
-\includegraphics[width=0.195\textwidth]{../Figures/XMM02_rgb.pdf}
-\includegraphics[width=0.195\textwidth]{../Figures/XMM102_rgb.pdf}
+\includegraphics[width=0.195\textwidth]{../Figures/HECDFS04_rgb.pdf}
+\includegraphics[width=0.195\textwidth]{../Figures/HCOSMOS02_rgb.pdf}
+\includegraphics[width=0.195\textwidth]{../Figures/HELAISS02_rgb.pdf}
+\includegraphics[width=0.195\textwidth]{../Figures/HXMM11_rgb.pdf}
+\includegraphics[width=0.195\textwidth]{../Figures/HXMM20_rgb.pdf}
 \end{centering}
@@
 %%\includegraphics[width=\textwidth]{cutouts_dec17.png}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM03_optical_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM03_model_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM03_residual_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM04_optical_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM04_model_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM04_residual_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM05_optical_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM05_model_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM05_residual_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM06_optical_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM06_model_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM06_residual_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM05_optical_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM05_model_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM05_residual_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM29_optical_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM29_model_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM29_residual_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM12_optical_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM12_model_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM12_residual_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM02_optical_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM02_model_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM02_residual_bestfit.pdf}
 %\end{centering}
@@
 %%\includegraphics[width=\textwidth]{cutouts_dec17.png}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM101_optical_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM101_model_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM101_residual_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM102_optical_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM102_model_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM102_residual_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM108_optical_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM108_model_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM108_residual_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM109_optical_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM109_model_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM109_residual_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM22_optical_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM22_model_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM22_residual_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM20_optical_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM20_model_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM20_residual_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM07_optical_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM07_model_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM07_residual_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM30_optical_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM30_model_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM30_residual_bestfit.pdf}
 %\end{centering}
@@
 %%\includegraphics[width=\textwidth]{cutouts_dec17.png}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM110_optical_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM110_model_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM110_residual_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM115_optical_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM115_model_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM115_residual_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM119_optical_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM119_model_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM119_residual_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM124_optical_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM124_model_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/XMM124_residual_bestfit.pdf}
-%\includegraphics[width=0.1623\textwidth]{../Figures/modelfit/XMM16_optical_bestfit.pdf}
-%\includegraphics[width=0.1623\textwidth]{../Figures/modelfit/XMM16_model_bestfit.pdf}
-%\includegraphics[width=0.1623\textwidth]{../Figures/modelfit/XMM16_residual_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM31_optical_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM31_model_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM31_residual_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM04_optical_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM04_model_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM04_residual_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM09_optical_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM09_model_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM09_residual_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM23_optical_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM23_model_bestfit.pdf}
+%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM23_residual_bestfit.pdf}
+%\includegraphics[width=0.1623\textwidth]{../Figures/modelfit/HXMM03_optical_bestfit.pdf}
+%\includegraphics[width=0.1623\textwidth]{../Figures/modelfit/HXMM03_model_bestfit.pdf}
+%\includegraphics[width=0.1623\textwidth]{../Figures/modelfit/HXMM03_residual_bestfit.pdf}
 %\end{centering}
@@
 %%\includegraphics[width=\textwidth]{cutouts_dec17.png}
-%\includegraphics[width=0.1623\textwidth]{../Figures/modelfit/XMM16_optical_bestfit.pdf}
-%\includegraphics[width=0.1623\textwidth]{../Figures/modelfit/XMM16_model_bestfit.pdf}
-%\includegraphics[width=0.1623\textwidth]{../Figures/modelfit/XMM16_residual_bestfit.pdf}
+%\includegraphics[width=0.1623\textwidth]{../Figures/modelfit/HXMM03_optical_bestfit.pdf}
+%\includegraphics[width=0.1623\textwidth]{../Figures/modelfit/HXMM03_model_bestfit.pdf}
+%\includegraphics[width=0.1623\textwidth]{../Figures/modelfit/HXMM03_residual_bestfit.pdf}
 %\end{centering}
@@
 
-Finally, the brightest single source in the ALMA sample is XMM16-Source0, with
+Finally, the brightest single source in the ALMA sample is HXMM03-Source0, with
 an intrinsic flux density of $S_{870} = 15.42 \pm 0.43\,$mJy.  However, there
 are also two objects with multiple sources that have separations smaller than
-1$\arcsec$ that have summed flux densities comparable to this: ADFS05
-(15.3$\,$mJy) and ECDFS02 (14.1$\,$mJy).  This is approaching the values found
+1$\arcsec$ that have summed flux densities comparable to this: HADFS02
+(15.3$\,$mJy) and HECDFS13 (14.1$\,$mJy).  This is approaching the values found
 in the most extreme systems, such as GN20
@@
 %these 20 comprise ALMA sources that are separated by $<1\arcsec$ and could be
-%gravitationally bound systems (ADFS05, ECDFS02, XMM04, and XMM16).  Depending
+%gravitationally bound systems (HADFS02, HECDFS13, HXMM29, and HXMM03).  Depending
 %on whether these 4 are considered multiples or not, the multiplicity rate in
@@
 %source, 5 are strongly lensed.  This leaves 4 objects that are single-component
-%systems experiencing amplification factors less than 2 (XMM03, XMM101, XMM115,
-%and XMM124).  XMM03 and XMM115 are likely lensed by factors of $\approx 1.5-2$
-%(discussed further in Section~\ref{sec:lensing}).  XMM124 is the faintest
-%object in our sample and has the lowest photometric redshift (by far).  XMM101
+%systems experiencing amplification factors less than 2 (HXMM05, HXMM22, HXMM04,
+%and HXMM23).  HXMM05 and HXMM04 are likely lensed by factors of $\approx 1.5-2$
+%(discussed further in Section~\ref{sec:lensing}).  HXMM23 is the faintest
+%object in our sample and has the lowest photometric redshift (by far).  HXMM22
 %appears to be unlensed, making it the brightest single system in our sample.

### 2015-01-22 Code/herschel_alma_overlay.py

@@ -68,6 +68,7 @@ for targ in range(0, ntargets):
     plt.clf()
     # get the target name from the filename
     dataname = targets['dataname'][targ]
+    shortname = targets['shortname'][targ]
     iauname = targets['iauname'][targ]
     lensgrade = targets['lensgrade'][targ]
 
@@ -193,15 +194,15 @@ for targ in range(0, ntargets):
                       stretch='normal', #family='sans-serif', \
                       style='normal', variant='normal')
     gc.colorbar.set_axis_label_font(size='x-large', weight='bold')
-    rename = dataname.replace('.', '_')
-    gc.add_label(0.06, 0.9, dataname, relative=True, size='24', 
+    rename = shortname.replace('.', '_')
+    gc.add_label(0.06, 0.9, shortname, relative=True, size='24', 
             color='white', horizontalalignment='left')
     gc.add_label(0.94, 0.9, 'Lens Grade: '+lensgrade, relative=True, size='24', 
             color='white', horizontalalignment='right')
     gc.add_label(0.94, 0.1, 'SPIRE '+herschel_band, relative=True, size='24', 
             color='white', horizontalalignment='right')
     savefig('../Figures/overlays/' + rename + '_870_' + herschel_band + '.pdf')
-    print(dataname)
+    print(shortname)
     continue
 
     # compute the (x, y) center and pixel scale in the optical image

### 2015-01-22 Code/iracstamps.py

@@ -170,9 +170,10 @@ for itarget in range(ntarget):
 
     # get the appropriate image center and radial extent
     target = iractargetlist['target'][itarget]
-    match = goodfitdat['dataname'] == target
+    match = goodfitdat['shortname'] == target
     goodfit = goodfitdat['intrinsic'][match][0]
-    modfitloc = '../../../../ModelFits/' + target + '/' + goodfit
+    dataname = goodfitdat['dataname'][match][0]
+    modfitloc = '../../../../ModelFits/' + dataname + '/' + goodfit
     configloc = modfitloc + '/config.yaml'
     configfile = open(configloc)
     config = yaml.load(configfile)
@@ -182,7 +183,7 @@ for itarget in range(ntarget):
     radial_extent = 9.5#config['Region0']['RadialExtent']
 
     # Make the RGB image
-    imdir = '../../fitscutouts/' + target
+    imdir = '../../fitscutouts/' + dataname
     blueimloc = imdir + '_' + blue + '.fits'
     blueim = transform(blueimloc, ra_center, dec_center, radial_extent,
             vmax=0.7)
@@ -207,7 +208,7 @@ for itarget in range(ntarget):
 
     # load the corresponding ALMA image
     submm_band = '870'
-    ALMA_file = '../../fitscutouts/' + target + '_' + submm_band + '.fits'
+    ALMA_file = '../../fitscutouts/' + dataname + '_' + submm_band + '.fits'
     ALMA_hdu = fits.open(ALMA_file)
     ALMA_fullimage = ALMA_hdu[0].data
     ALMA_trimmed = transform(ALMA_file, ra_center, dec_center, radial_extent)

### 2015-01-22 Code/maketable_source.py

@@ -17,6 +17,7 @@ from astropy.io import ascii
 
 goodfitloc = '../Data/uvfitlist.dat'
 goodfitdat = Table.read(goodfitloc, format='ascii')
+goodfitdat.sort('iauname')
 mu_estimate = False
 
 cwd = os.getcwd()
@@ -27,6 +28,7 @@ observed = ascii.read('../Data/table_observed.dat')
 anloc = '../../../../ModelFits/'
 dataphotloc = '../Data/targetlist.dat'
 dataphot = Table.read(dataphotloc, format='ascii')
+dataphot.sort('ra_250')
 dataname = dataphot['dataname']
 ntarg = dataname.size
 dataflag = numpy.zeros(ntarg)
@@ -39,6 +41,7 @@ dataflag = numpy.zeros(ntarg)
 #yesmodel = dataflag == 1
 #dataphot = dataphot[yesmodel]
 dataname = dataphot['dataname']
+shortname = dataphot['shortname']
 ntarg = len(dataphot)
 objname_previous = ''
 
@@ -104,7 +107,7 @@ for itarg in range(0, ntarg):
 
             # Lens RA
             sl = str(ilens)
-            datanamelens = dataname[itarg] + '.Lens' + sl
+            datanamelens = shortname[itarg] + '.Lens' + sl
             tag1 = 'DeltaRA_Lens' + sl + '_Region' + sr
             thisparam = 1
             if tag1 not in fitresults.keys():
@@ -332,10 +335,10 @@ for itarg in range(0, ntarg):
             phi_indiv = dist.mean()
             e_phi_indiv = dist.std()
 
-            #msg = '{0:15} & ${1:12}\pm{2:5.3f}$ & ${3:12}\pm{4:4.2f}$ & ${5:.3f}\pm{6:.3f}$ & ${7:.3f}\pm{8:0.3f}$ & ${9:3.0f}\pm{10:3.0f}$'
-            #msgfmt = msg.format(datanamelens, fullRA, eRA, fullDec, eDec, 
-            #        einstein_indiv, e_einstein_indiv, q_indiv, e_q_indiv,
-            #        phi_indiv, e_phi_indiv)
+            msg = '{0:15} & ${1:12}\pm{2:5.3f}$ & ${3:12}\pm{4:4.2f}$ & ${5:.3f}\pm{6:.3f}$ & ${7:.3f}\pm{8:0.3f}$ & ${9:3.0f}\pm{10:3.0f}$'
[…]

### 2015-01-22 Code/updatemodel.py

@@ -13,41 +13,55 @@ import glob
 import os
 
 
+# store the current directory
+cwd = os.getcwd()
+
 # the uvfit directory containing the best-fit model
-fitlist = Table.read('uvfitlist.dat', format='ascii')
+fitlist = Table.read('../Data/uvfitlist.dat', format='ascii')
 
 # identify ALMA targets
-targetloc = 'targetlist.dat'
+targetloc = '../Data/targetlist.dat'
 targets = Table.read(targetloc, format='ascii')
 ntargets = len(targets)
 
-for itarg in range(ntargets):
+i = 28
 
-    target = targets[itarg]['dataname']
+for itarg in range(i, i + 1):
+
+    dataname = targets[itarg]['dataname']
+    shortname = targets[itarg]['shortname']
 
     fitdir = fitlist['intrinsic'][itarg]
-    fitloc = '../../ModelFits/' + target + '/' + fitdir + '/'
+    fitloc = '../../../../ModelFits/' + dataname + '/' + fitdir + '/'
+
+    #print(dataname + '/' + fitdir + '/config.yaml')
+
+    # change into that directory and run visualize.bestFit()
+    os.chdir(fitloc)
+    import visualize
+    visualize.bestFit(interactive=False, showOptical=True)
+    os.chdir(cwd)
 
     pdfmap = 'LensedSBmap.optical.bestfit.pdf'
     origin = fitloc + pdfmap
-    destination = 'modelfit/' + target + '.optical.bestfit.pdf'
-    destination = destination.replace('.', '_', 2)
+    destination = '../Figures/modelfit/' + shortname + '.optical.bestfit.pdf'
+    #destination = destination.replace('.', '_', 2)
     cmd = 'cp ' + origin + ' ' + destination
     print(cmd)
     os.system(cmd)
 
     pdfmap = 'LensedSBmap.model.bestfit.pdf'
     origin = fitloc + pdfmap
-    destination = 'modelfit/' + target + '.model.bestfit.pdf'
-    destination = destination.replace('.', '_', 2)
+    destination = '../Figures/modelfit/' + shortname + '.model.bestfit.pdf'
+    #destination = destination.replace('.', '_', 2)
     cmd = 'cp ' + origin + ' ' + destination
     print(cmd)
     os.system(cmd)
 
     pdfmap = 'LensedSBmap.residual.bestfit.pdf'
     origin = fitloc + pdfmap
[…]

### 2015-01-22 LaTeX/ms.tex
Sort model fits by RA
Edo Ibar comments
Very minor.

@@
 %\includegraphics[width=\textwidth]{cutouts_dec17.png}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS03_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS03_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS03_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS08_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS08_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS08_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS09_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS09_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS09_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS10_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS10_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS10_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS02_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS02_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS02_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS04_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS04_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS04_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS01_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS01_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS01_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS11_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS11_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS11_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS01_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS01_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS01_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS02_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS02_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS02_residual_bestfit.pdf}
 \includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_optical_bestfit.pdf}
@@
 \includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM02_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM02_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM02_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM31_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM31_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM31_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM29_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM29_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM29_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM07_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM07_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM07_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM20_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM20_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM20_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM01_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM01_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM01_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM04_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM04_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM04_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM09_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM09_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM09_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM03_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM03_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM03_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM11_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM11_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM11_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM23_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM23_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM23_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM22_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM22_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM22_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM05_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM05_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM05_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM30_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM30_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM30_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM12_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM12_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM12_residual_bestfit.pdf}
 \end{centering}
@@
 
-%\begin{figure*}[!tbp] 
-%    \begin{centering}
-%%\epsscale{1.00} 
-%%\includegraphics[width=\textwidth]{cutouts_dec17.png}
-%\end{centering}
-%
-%\caption{ Continued.}
-%\addtocounter{figure}{-1}
-%
-%\end{figure*}
-%
-%\begin{figure*}[!tbp] 
-%    \begin{centering}
-%%\epsscale{1.00} 
-%%\includegraphics[width=\textwidth]{cutouts_dec17.png}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_optical_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_model_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_residual_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_optical_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_model_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_residual_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_optical_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_model_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_residual_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_optical_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_model_bestfit.pdf}
-%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_residual_bestfit.pdf}
-%\end{centering}
-%
-%\caption{ Continued.}
-%\addtocounter{figure}{-1}
-%
-%\end{figure*}
-
 \begin{figure*}[!tbp] 
     \begin{centering}
-%\epsscale{1.00} 
-%\includegraphics[width=\textwidth]{cutouts_dec17.png}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM01_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM01_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM01_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM11_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM11_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM11_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM05_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM05_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM05_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM29_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM29_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM29_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM12_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM12_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM12_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM02_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM02_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM02_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM03_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM03_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM03_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM22_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM22_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM22_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM20_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM20_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM20_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM07_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM07_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM07_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM30_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM30_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM30_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM31_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM31_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM31_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM04_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM04_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM04_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM09_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM09_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM09_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM23_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM23_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM23_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS04_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS04_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS04_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS02_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS02_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS02_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS11_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS11_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS11_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS10_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS10_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS10_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS01_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS01_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS01_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS09_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS09_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS09_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS08_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS08_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS08_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS03_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS03_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS03_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS02_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS02_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS02_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS01_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS01_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS01_residual_bestfit.pdf}
 \end{centering}
@@
 \caption{ Continued.}
-\addtocounter{figure}{-1}
+%\addtocounter{figure}{-1}
 
@@
 $\rho_{\rm lens}\,(r)$, the number density of lenses as a function of mass and
-redshift, $n_{\rm lens}\,(M, \, z)$), the redshift distribution of the sources,
+redshift, $n_{\rm lens}\,(M, \, z)$, the redshift distribution of the sources,
 $dN_{\rm source}/dz$, and the intrinsic luminosity function of the sources,
-$dn_{\rm source}/dS_{870}^\prime)$.  The latter component is the least certain
+$dn_{\rm source}/dS_{870}^\prime$.  The latter component is the least certain
 component and also has the strongest impact on the predicted apparent
@@
         factors of 5-10.  After correcting for amplification, the brightest
-        source in the sample has $S_{870}^\prime = 15.42 \pm 0.43\,$mJy.  There
+        source in the sample has $S_{870} = 15.42 \pm 0.43\,$mJy.  There
         is a weak trend towards even higher multiplicity at the highest total

### 2015-01-22 LaTeX/ms.tex
Duncan Farrah comments

@@
 Galaxies selected in blind surveys at far-infrared (FIR) or sub-millimieter
-(sub-mm) wavelengths are generally known as dusty star-forming galaxies (DSFGs).
-They are found primarily at $z \sim2$ \citep{2005ApJ...622..772C,
-Bothwell:2013lr} \citep[but extend down to $z \sim 1$ and up to $z > 6$;
-see][]{Messias:2014fk, Riechers:2013lr} and represent the most FIR-luminous
-objects in existence during this epoch.   They are signposts of significant
-over-densities \citep{Daddi:2009qy, Capak:2011qy} and likely represent the
-formative stages of the most massive elliptical galaxies found in the local
+(sub-mm) wavelengths are generally known as dusty star-forming galaxies
+(DSFGs).  They cover a wide range in redshift from $z \sim 0.5$ to $z > 6$
+\citep{2005ApJ...622..772C, Casey:2012qy, Messias:2014fk, Riechers:2013lr},
+with a significant component at $z \sim 2$ \citep{Casey:2012uq,
+Bothwell:2013lr}, when they represent the most FIR-luminous objects in
+existence during this epoch.   They are signposts of significant over-densities
+\citep{Daddi:2009qy, Capak:2011qy} and likely represent
+the formative stages of the most massive elliptical galaxies found in the local
 Universe \citep[e.g.,][]{Ivison:2013fk, Fu:2013lr}.  Moreover, they constitute
 an important component of the overall galaxy population at $z \sim 2$
-\citep[e.g.,][]{2005ApJ...632..169L}, when the star-formation rate density in
+\citep[e.g.,][]{Magnelli:2011ul}, when the star-formation rate density in
 the Universe peaked \citep[e.g.,][]{Lilly:1996uq, 1996MNRAS.283.1388M}.
@@
 forward thanks in large part to the advent of the {\it Herschel Space
-Observatory} \citep[{\it Herschel};][]{Pilbratt:2010fk}.  This has resulted in a
-revolution in the size and depth of blind surveys at FIR and sub-mm wavelengths.
-In particular, the {\it Herschel} Multi-tiered Extragalactic Survey
-\citep[HerMES;][]{Oliver:2012lr} and the {\it Herschel} Astrophysical Terahertz
-Large Area Survey \citep[H-ATLAS;][]{2010PASP..122..499E} together have surveyed
-$\approx 650\,$deg$^2$ at 250$\,\mu$m, 350$\,\mu$m, and 500$\,\mu$m to the
-confusion limit of {\it Herschel} \citep[$\sigma \approx 6-7\,$mJy in each
-band][]{Nguyen:2010fk}, plus an additional $\approx 350\,$deg$^2$ to a level
-approximately double the confusion limit.  A similar effort has been undertaken
-at longer wavelengths by the South Pole Telescope
-\citep[SPT;][]{Carlstrom:2011qy} and the Atacama Cosmology Telescope
-\citep{Swetz:2011qy}.
+Observatory} \citep[{\it Herschel};][]{Pilbratt:2010fk}.  This has resulted in
+a revolution in the size and depth of blind surveys at FIR and sub-mm
+wavelengths.  In particular, the {\it Herschel} Multi-tiered Extragalactic
+Survey \citep[HerMES;][]{Oliver:2012lr} and the {\it Herschel} Astrophysical
+Terahertz Large Area Survey \citep[H-ATLAS;][]{2010PASP..122..499E} together
+have surveyed $\approx 650\,$deg$^2$ at 250$\,\mu$m, 350$\,\mu$m, and
+500$\,\mu$m to the confusion limit of {\it Herschel} \citep[$\sigma \approx
+6-7\,$mJy in each band][]{Nguyen:2010fk}, plus an additional $\approx
+350\,$deg$^2$ to a level approximately double the confusion limit.  A similar
+effort to survey large areas of the sky has been undertaken at longer
+wavelengths by the South Pole Telescope \citep[SPT;][]{Carlstrom:2011qy} and
+the Atacama Cosmology Telescope \citep{Swetz:2011qy}.
 
@@
 Bussmann:2012lr, Wardlow:2013lr, Bussmann:2013lr}.  Sources discovered in SPT
-surveys have also been shown to have a high probibility of being strongly lensed
+surveys have also been shown to have a high probability of being strongly lensed
 \citep{Vieira:2013fk, Hezaveh:2013fk}.  However, statistical models
@@
 %lensed ($\mu_{870} < 2$) sources.  
-Three aspects of our dataset make it unique.  First, the sample occupies a
-distinct regime in flux density between the brightest {\it Herschel} DSFGs
-(almost all of which are lensed) and much fainter DSFGs found in ground-based
-surveys \citep[most of which are expected to be unlensed;
-e.g.,][]{Hodge:2013qy}.  Second, the ALMA images are extremely sensitive
-($\sigma \approx 0.2\,$mJy) and all 29 HerMES DSFGs are detected \citep[such is
-not the case in previous similar studies with shallower imaging;
+Three aspects of our dataset make it uniquely suited to improving our
+understanding of the bright end of the intrinsic DSFG luminosity function.
+First, the sample occupies a distinct regime in flux density between the
+brightest {\it Herschel} DSFGs (almost all of which are lensed) and much
+fainter DSFGs found in ground-based surveys \citep[most of which are expected
+to be unlensed; e.g.,][]{Hodge:2013qy}.  Second, the ALMA images are extremely
+sensitive ($\sigma \approx 0.2\,$mJy per beam) and all 29 HerMES DSFGs are detected
+\citep[such is not the case in previous similar studies with shallower imaging;
 e.g.,][]{Smolcic:2012zl, Barger:2012yg, Hodge:2013qy}.  Third, the typical
@@
 identify lensing galaxies which are typically early-types with little on-going
-star-formation and therefore very weak sub-mm emission.
+star-formation and therefore exhibit very weak sub-mm emission.
 
@@
 
-Our sample includes 29 DSFGs drawn from five independent fields in HerMES
-totaling $55\,$deg$^2$ that are accessible to ALMA and have SPIRE sensitivity
-that reaches the confusion limit.  The sample is selected primarily on the
-basis of $S_{500}$ and covers a range of $20 < S_{500}/{\rm (mJy)} \lesssim
-100$.  Additional selection criteria based on the $S_{500}/S_{350}$ and
-$S_{350}/S_{250}$ colors lead to the sample being split roughly evenly between
-``blue'' (typically implying $z < 2$) and ``green'' ($z = 2-3.5$) SPIRE colors.
-We caution that redshifts based strictly on SPIRE colors are uncertain due to
-the degeneracy between dust temperature and redshift as well as the fact that
-the multiplicity rate is high in our sample.  It is not clear that the colors
-of each individual ALMA counterpart are the same as the summed colors seen by
-{\it Herschel}.  Low redshift contaminants to our sample ($z < 0.1$) are
-trivially removed by searching for spatially resolved counterparts in SDSS
-imaging.  There is also a small contamination from blazars, which are
-non-thermal emitters and are easily identified and excised from the sample
-using data from the NVSS or the Very Large Array Faint Images of the Radio Sky
-at Twenty-Centimeters survey \citep[FIRST;][]{Becker:1995fj}.
+Our sample includes 29 DSFGs drawn from five independent, confusion-limited
+fields in HerMES with declinations $> 2 ^\circ$ and totaling $55\,$deg$^2$.
+The sample was originally selected to be a complete, flux-limited set of
+objects satisfying $S_{500} > 95 \, {\rm mJy}$ that are not known radio AGN,
+nearby late type galaxies, or Galactic emission.  The intention was to assemble
+the largest possible sample of lenses in the HerMES fields that are accessible
+to ALMA.  However, the original selection was based on the HerMES ``V5''
+catalog because this was the only one available at the time of the ALMA Cycle~0
+deadline.  Subsequently, improved efforts to deblend SPIRE photometry at
+$500\,\mu$m were introduced that led to the development of the ``V21'' catalog
+that formed the basis of the lens selection criteria used in
+\citet{Wardlow:2013lr}.  A number of objects in the sample in this paper have
+significantly lower $S_{500}$ values in the V21 catalog, indicating that their
+$S_{500}$ in the V5 catalog was boosted by blending with nearby sources rather
+than by gravitational lensing.  For this reason, the objects in this sample
+comprise a combination of lenses and blends of multiple sources.
+
+%selected primarily on the
+%basis of $S_{500}$ and covers a range of $20 < S_{500}/{\rm (mJy)} \lesssim
+%100$.  Additional selection criteria based on the $S_{500}/S_{350}$ and
+%$S_{350}/S_{250}$ colors lead to the sample being split roughly evenly between
+%``blue'' (typically implying $z < 2$) and ``green'' ($z = 2-3.5$) SPIRE colors.
+%We caution that redshifts based strictly on SPIRE colors are uncertain due to
+%the degeneracy between dust temperature and redshift as well as the fact that
+%the multiplicity rate is high in our sample.  It is not clear that the colors
+%of each individual ALMA counterpart are the same as the summed colors seen by
+%{\it Herschel}.  Low redshift contaminants to our sample ($z < 0.1$) are
+%trivially removed by searching for spatially resolved counterparts in SDSS
+%imaging.  There is also a small contamination from blazars, which are
+%non-thermal emitters and are easily identified and excised from the sample
+%using data from the NVSS or the Very Large Array Faint Images of the Radio Sky
+%at Twenty-Centimeters survey \citep[FIRST;][]{Becker:1995fj}.
 
@@
 synthesized beamsize of $\approx 0\farcs45$ FWHM while ensuring that no flux was
-resolved out by the interferometer.  When possible, track-sharing of multiple
+resolved out by the interferometer (since our targets all have size scales
+smaller than $1-2 \arcsec$.  When possible, track-sharing of multiple
 targets in a single track was used to optimize the {\it uv} coverage.
@@
 astrometrically calibrated Gemini-S images served as the basis for aligning
-higher resolution, smaller field-of-view imaging from {\it HST} or Keck that
-were originally presented in \citet{Calanog:2014lr}.
+higher resolution, smaller field-of-view imaging from {\it HST} or Keck (when
+available) that were originally presented in \citet{Calanog:2014lr}.
 
@@
 Gaussian represents a simplification from the S\'ersic profile
-\citep{1968adga.book.....S}  that is justified based on the relatively weak
+\citep{1968adga.book.....S}  that is permitted based on the relatively weak
 constraints on the S\'ersic index found in our previous work
@@
 sight, {\sc uvmcmcfit} accounts for the deflection of light caused by this
-structure using a simple ray-tracing routine that is adopted from a 
-Python routine written by A.~Bolton
+structure using a simple ray-tracing routine that is adopted from a Python
+routine written by A.~Bolton
 \footnote{http://www.physics.utah.edu/$\sim$bolton/python\_lens\_demo/}.  This
@@
 \citet{Bussmann:2013lr}, where we used the publicly available {\sc Gravlens}
-software \citep{Keeton:2001lr} to map emission from the source plane to
-the image plane for a given lensing mass distribution.  {\sc Gravlens} has a
-wide range of lens mass profiles as well as a sophisticated algorithm for
-mapping source-plane emission to the image-plane, but it also comes with a
-significant input/output penalty that makes parallel computing prohibitively
-expensive.  The use of pure-Python code for tracing the deflection of light
-rays is a critical component of making {\sc uvmcmcfit} computationally
-feasible.
+software \citep{Keeton:2001lr} to map emission from the source plane to the
+image plane for a given lensing mass distribution.  {\sc Gravlens} has a wide
+range of lens mass profiles as well as a sophisticated algorithm for mapping
+source-plane emission to the image-plane, but it also comes with a significant
+input/output penalty that makes parallel computing prohibitively expensive.
+For example, modeling a simple system comprising one lens and one source
+typically required 24-48$\,$hours using the old software, whereas the same
+system can be modeled in less than one hour with the pure-Python code.  The use
+of pure-Python code for tracing the deflection of light rays is a critical
+component of making {\sc uvmcmcfit} computationally feasible.
 
@@
 for a recent review, see][]{Treu:2010fk}.  Each SIE is fully described by the
-following five free parameters: the position of the lens relative to the
-arbitrarily chosen ``image center'' based on the ALMA 870$\,\mu$m emission and
-any lensing galaxies seen in the optical or near-IR ($\Delta \alpha_{\rm lens}$
-and $\Delta \delta_{\rm lens}$; these can be compared with the position of the
-optical or near-IR counterpart relative to the ``image center'': $\Delta
+following five free parameters: the position of the lens on the sky relative to
+the arbitrarily chosen ``image center'' based on the ALMA 870$\,\mu$m emission
+and any lensing galaxies seen in the optical or near-IR ($\Delta \alpha_{\rm
+lens}$ and $\Delta \delta_{\rm lens}$; these can be compared with the position
+of the optical or near-IR counterpart relative to the ``image center'': $\Delta
 \alpha_{\rm NIR}$ and $\Delta \delta_{\rm NIR}$), the mass of the lens
@@
 a projected angular distance $d_{\rm neighbor}$.  To obtain a direct comparison
-with our ALMA sample, we use $S_{\rm thresh} = 1.0\,$mJy and $d_{\rm
-neighbor} = 40\arcsec$.  We use the known positions in the mock catalogs for
-all blended sources and compute centroid and separations for every blended
-source using the same methodology as we applied to our ALMA sample and to
-ALESS.
+with our ALMA sample, we use $S_{\rm thresh} = 1.0\,$mJy (corresponding to the
+5$\sigma$ limit of the ALMA data) and $d_{\rm neighbor} = 40\arcsec$
+(reflecting the size of the {\it Herschel} beam at 500$\,\mu$m).  We use the
+known positions in the mock catalogs for all blended sources and compute
+centroid and separations for every blended source using the same methodology as
+we applied to our ALMA sample and to ALESS.
 

### 2015-01-22 LaTeX/ms.tex
Rob Ivison comments

@@
 \newcommand{\tnt}{\tablenotetext}
+\maxdeadcycles=10000
 
@@
     from gravitational lensing ($\mu > 1.1$), but only 6 are strongly lensed
-    and show multiple images.  We introduce and make use of {\sc uvmcmcfit}, a
-    general purpose and publicly available Markov Chain Monte Carlo visibility
-    plane analysis tool to analyze the source properties.  Nearly 70\% of the
-    {\it Herschel} sources break down into multiple ALMA counterparts,
-    consistent with previous research indicating that the multiplicity rate is
-    high in bright sources discovered in sub-mm or FIR surveys with poor
-    spatial resolution.  The ALMA counterparts to our {\it Herschel} targets
-    are located much closer to each other than ALMA counterparts to sources
-    found in the LABOCA ECDFS Submillimeter Survey.  Theoretical models
-    underpredict the excess in number of sources with small separations from
-    each other that is seen in our ALMA sample.  Combined with our previous
-    work on brighter {\it Herschel} sources, the lens models presented here
-    constrain the shape of the intrinsic luminosity function for DSFGs to have
-    a break around 8$\,$mJy with a very steep fall off at higher flux
-    densities.  The high multiplicity rate and low projected separations
-    between sources seen in our sample argue in favor of interactions and
-    mergers driving the prodigious emission from the brightest DSFGs.
+    and show multiple images.  Combined with our previous work on brighter {\it
+    Herschel} sources, the lens models presented here constrain the shape of
+    the intrinsic luminosity function for DSFGs to have a break near 8$\,$mJy
+    at 880$\,\mu$m with a very steep fall off at higher flux densities.  We
+    introduce and make use of {\sc uvmcmcfit}, a general purpose and publicly
+    available Markov Chain Monte Carlo visibility plane analysis tool to
+    analyze the source properties.  Nearly 70\% of the {\it Herschel} sources
+    break down into multiple ALMA counterparts, consistent with previous
+    research indicating that the multiplicity rate is high in bright sources
+    discovered in single-dish sub-mm or FIR surveys.  The ALMA counterparts to
+    our {\it Herschel} targets are located much closer to each other than ALMA
+    counterparts to sources found in the LABOCA ECDFS Submillimeter Survey.
+    Theoretical models underpredict the excess in number of sources with small
+    separations seen in our ALMA sample.  The high multiplicity rate and low
+    projected separations between sources seen in our sample argue in favor of
+    interactions and mergers plausibly driving both the prodigious emission
+    from the brightest DSFGs as well as the sharp downturn above $S_{880} =
+    8\,$mJy.
 
@@
 existence during this epoch.   They are signposts of significant over-densities
-\citep{Daddi:2009qy, Capak:2011qy} and likely represent
-the formative stages of the most massive elliptical galaxies found in the local
-Universe \citep[e.g.,][]{Ivison:2013fk, Fu:2013lr}.  Moreover, they constitute
-an important component of the overall galaxy population at $z \sim 2$
-\citep[e.g.,][]{Magnelli:2011ul}, when the star-formation rate density in
-the Universe peaked \citep[e.g.,][]{Lilly:1996uq, 1996MNRAS.283.1388M}.
+\citep{Daddi:2009qy, Capak:2011qy} \citep[c.f.][]{Robson:2014xy} and
+likely represent the formative stages of the most massive elliptical galaxies
+found in the local Universe \citep[e.g.,][]{Ivison:2013fk, Fu:2013lr}.
+Moreover, they constitute an important component of the overall galaxy
+population at $z \sim 2$ \citep[e.g.,][]{Magnelli:2011ul}, when the
+star-formation rate density in the Universe peaked
+\citep[e.g.,][]{Lilly:1996uq, 1996MNRAS.283.1388M}.
 
 Our collective understanding of DSFGs is currently taking a dramatic leap
-forward thanks in large part to the advent of the {\it Herschel Space
-Observatory} \citep[{\it Herschel};][]{Pilbratt:2010fk}.  This has resulted in
-a revolution in the size and depth of blind surveys at FIR and sub-mm
-wavelengths.  In particular, the {\it Herschel} Multi-tiered Extragalactic
-Survey \citep[HerMES;][]{Oliver:2012lr} and the {\it Herschel} Astrophysical
-Terahertz Large Area Survey \citep[H-ATLAS;][]{2010PASP..122..499E} together
-have surveyed $\approx 650\,$deg$^2$ at 250$\,\mu$m, 350$\,\mu$m, and
-500$\,\mu$m to the confusion limit of {\it Herschel} \citep[$\sigma \approx
-6-7\,$mJy in each band][]{Nguyen:2010fk}, plus an additional $\approx
-350\,$deg$^2$ to a level approximately double the confusion limit.  A similar
-effort to survey large areas of the sky has been undertaken at longer
-wavelengths by the South Pole Telescope \citep[SPT;][]{Carlstrom:2011qy} and
-the Atacama Cosmology Telescope \citep{Swetz:2011qy}.
+forward thanks in large part to the {\it Herschel Space Observatory}
+\citep[{\it Herschel};][]{Pilbratt:2010fk}.  This has revolutized the size and
+depth of blind surveys at FIR wavelengths.  In particular, the {\it Herschel}
+Multi-tiered Extragalactic Survey \citep[HerMES;][]{Oliver:2012lr} and the {\it
+Herschel} Astrophysical Terahertz Large Area Survey
+\citep[H-ATLAS;][]{2010PASP..122..499E} together have surveyed $\approx
+650\,$deg$^2$ at 250$\,\mu$m, 350$\,\mu$m, and 500$\,\mu$m to the confusion
+limit of {\it Herschel} \citep[$\sigma \approx 6-7\,$mJy in each
+band][]{Nguyen:2010fk}, plus an additional $\approx 350\,$deg$^2$ to a level
+approximately double the confusion limit.  A similar effort to survey large
+areas of the sky has been undertaken at longer wavelengths by the South Pole
+Telescope \citep[SPT;][]{Carlstrom:2011qy} and the Atacama Cosmology Telescope
+\citep{Swetz:2011qy}.
 
@@
 phase~I catalog with S/N$ > 3$ at 250$\,\mu$m, 350$\,\mu$m, and 500$\,\mu$m
-(grayscale).  The sample of HerMES sources in this paper are shown with green
-squares (the ``ALMA sample'').  The very bright {\it Herschel} DSFGs from
-\citet{Bussmann:2013lr} (the ``SMA sample'') are shown by red circles, and the
-overall sample of candidate lensed {\it Herschel} DSFGs are highlighted by
-yellow circles.  Lensed SMGs discovered by the SPT that have published lens
-models are represented by cyan stars \citep{Hezaveh:2013fk}.  A magenta diamond
-shows the location in this diagram of the stacked signal from ALESS DSFGs.
-Representative error bars are shown in the lower left corner.  The ALMA sample
-fills the gap in 500$\,\mu$m flux density space between SMA/SPT and ALESS
-samples.} \label{fig:sample}
+(log of number of galaxies shown in grayscale).  The sample of HerMES sources
+in this paper are shown with green squares (the ``ALMA sample'').  The very
+bright {\it Herschel} DSFGs from \citet{Bussmann:2013lr} (the ``SMA sample'')
+are shown by red circles, and the overall sample of candidate lensed {\it
+Herschel} DSFGs are highlighted by yellow circles.  Lensed SMGs discovered by
+the SPT that have published lens models are represented by cyan stars
+\citep{Hezaveh:2013fk}.  A magenta diamond shows the location in this diagram
+of the stacked signal from ALESS DSFGs.  Representative error bars are shown in
+the lower left corner.  The ALMA sample fills the gap in 500$\,\mu$m flux
+density space between SMA/SPT and ALESS samples.} \label{fig:sample}
 
@@
 
-ALMA data were obtained during Cycle~0 over a period from 2012 June to 2012
-December (Program 2011.0.00539.S; PI: D. Riechers).  The observations were
-carried out in good 870$\,\mu$m weather conditions which resulted in typical
-system temperatures of $T_{\rm sys} \sim 130\,$K and phase fluctuations of $\sim
-10\,$deg.  Each target was observed until an rms noise level of $\sigma \approx
-0.2\,$mJy was achieved.  This typically required 10 minutes of on-source
-integration time.  For the observations targeting the CDFS, Elais-S, and COSMOS
-fields, the weather was of sufficient quality to reach $\sigma \approx
-0.14\,$mJy.  The number of antennas used varied from 15 to 25.  The antennas
-were configured with baseline lengths of 20$\,$m to 400$\,$m, providing a
-synthesized beamsize of $\approx 0\farcs45$ FWHM while ensuring that no flux was
+ALMA data were obtained during Cycle~0 over the from 2012 June to 2012 December
+(Program 2011.0.00539.S; PI: D. Riechers).  The observations were carried out
+in good 870$\,\mu$m weather conditions which resulted in typical system
+temperatures of $T_{\rm sys} \sim 130\,$K and phase fluctuations of $\sim
+10\,$deg.  Each target was observed until an rms noise level near the phase
+center of $\sigma \approx 0.2\,$mJy was achieved.  This typically required 10
+minutes of on-source integration time.  For the observations targeting the
+CDFS, ELAISS, and COSMOS fields, the data reach $\sigma \approx 0.14\,$mJy.
+The number of antennas used varied from 15 to 25.  The antennas were configured
+with baseline lengths of 20$\,$m to 400$\,$m, providing a synthesized beamsize
+of $\approx 0\farcs5 \times 0\farcs4$ FWHM while ensuring that no flux was
 resolved out by the interferometer (since our targets all have size scales
-smaller than $1-2 \arcsec$.  When possible, track-sharing of multiple
-targets in a single track was used to optimize the {\it uv} coverage.
+smaller than $1-2 \arcsec$.  When possible, track-sharing of multiple targets
+in a single track was used to optimize the {\it uv} coverage.
 
@@
 sensitivity is $\sigma \approx 8\,$mJy$\,$beam$^{-1}$ in 15$\,$km$\,$sec$^{-1}$
-bins).
+bins).  Given that our observations cover a total of 217.5$\,$GHz in badwidth,
+the lack of lines seems more likely to be due to limited sensitivity than
+limited bandwidth.
 
@@
 signal-to-noise ratio (S/N) greater than 20, we obtained a $\approx 10\%$
-improvement in S/N by using the CASA {\sc selfcal} task to improve the phase
-gain corrections.  Finally, we updated the absolute flux calibration to use the
-Butler-JPL-Horizons 2012 solar system models.
+improvement in S/N by using the CASA {\sc selfcal} task with the clean component
+model as input to improve the phase gain corrections.  Finally, we updated the
+absolute flux calibration to use the Butler-JPL-Horizons 2012 solar system
+models.
 
@@
 the {\it Herschel} SPIRE images (black-white contours) originally used to
-select the targets and noted in each panel as either 250$\,\mu$m or
-350$\,\mu$m.  Each panel is centered on the phase center of the ALMA
+select the targets and noted in each panel as either 250$\,\mu$m, 350$\,\mu$m,
+or 500$\,\mu$m.  Each panel is centered on the phase center of the ALMA
 observations of that target and a white circle traces the FWHM of the primary
-beam of an ALMA 12$\,$m antenna at 870$\,\mu$m.  A white dashed box represents
-the region of each image that is shown in greater detail in
-Figure~\ref{fig:uvmodels}.
+beam of an ALMA 12$\,$m antenna at 870$\,\mu$m.  All flux density measurements
+given in this paper have been corrected for the primary beam by dividing the
+total flux density by the primary beam correction factor at the center of the
+source.  This is a valid approach because all sources have sizes $< 1\arcsec$,
+such that the variation in the primary beam correction factor across the source
+is insignificant.  A white dashed box represents the region of each image that
+is shown in greater detail in Figure~\ref{fig:uvmodels}.
 
@@
 \citep[GMOS-S;][]{Hook:2004qy} were conducted in queue mode during the 2013B
-semester as part of program GS-2013B-Q-77 (PI: R.~S.~Bussmann).  The goal of the
-program is to use shallow $u$, $g$, $r$, $i$, and $z$ imaging to identify
+semester as part of program GS-2013B-Q-77 (PI: R.~S.~Bussmann).  The goal of
+the program is to use shallow $u$, $g$, $r$, $i$, and $z$ imaging to identify
 structure at $z<1$ and determine which of the ALMA sources are affected by
@@
 dataset --- these were excluded from our Gemini-S program.  The remaining
-targets are: HADFS03, HADFS08, HADFS09, HADFS10, HADFS02, HADFS04, HADFS01, HADFS11,
-HELAISS02, HXMM11, HXMM12, HXMM22, HXMM07, HXMM30, and HXMM04.  Each of these
-targets were observed for a total of 9$\,$minutes of on-source integration time
-in each of $u$, $g$, $r$, $i$, and $z$.  The observations were obtained during
-dark time in with adequate seeing conditions (image quality $ = 85\% \approx
-1.1\arcsec$.
+targets are: HADFS03, HADFS08, HADFS09, HADFS10, HADFS02, HADFS04, HADFS01,
+HADFS11, HELAISS02, HXMM11, HXMM12, HXMM22, HXMM07, HXMM30, and HXMM04.  Each
+of these targets were observed for a total of 9$\,$minutes of on-source
+integration time in each of $u$, $g$, $r$, $i$, and $z$.  The observations were
+obtained during dark time in with adequate seeing conditions (image quality in
+the 85th percentile, corresponding to $\approx 1.1\arcsec$.
 
@@
 \caption{ ALMA 870$\mu$m images (color scale, units of mJy/beam) of HerMES
-DSFGs.  Contours (black and white) trace 250$\,\mu$m emission from {\it
-Herschel}.  The FWHM size of the ALMA synthesized beam is shown in the lower
-left corner of each panel.  A solid white circle shows the FWHM size of the
-primary beam.  Dashed squares identify the regions of each image that are shown
-in greater detail in Figure~\ref{fig:uvmodels}.  \label{fig:imaging}}
-\addtocounter{figure}{-1}
+DSFGs (images have not been corrected for primary beam attenuation).  Contours
+(black and white) trace 250$\,\mu$m emission from {\it Herschel}.  The FWHM
+size of the ALMA synthesized beam is shown in the lower left corner of each
+panel.  A solid white circle shows the FWHM size of the primary beam.  Dashed
+squares identify the regions of each image that are shown in greater detail in
+Figure~\ref{fig:uvmodels}.  \label{fig:imaging}} \addtocounter{figure}{-1}
 
@@
 range of lens mass profiles as well as a sophisticated algorithm for mapping
-source-plane emission to the image-plane, but it also comes with a significant
+source plane emission to the image plane, but it also comes with a significant
 input/output penalty that makes parallel computing prohibitively expensive.
@@
 for any source is allowed to vary from 0.1$\,$mJy to the total flux density
-observed by the ALMA (we ensure that the posterior PDF of the intrinsic flux
+observed by ALMA (we ensure that the posterior PDF of the intrinsic flux
 density shows no signs of preferring a value lower than 0.1$\,$mJy).  The source
@@
 0\farcs5$ offset in the position of the foreground galaxy between the lens
-model and the Gemini-S image.  Given the absolute astrometric uncertainty of
-$0\farcs2$ (based on SDSS), we do not consider this offset to be significant.
-The presence of a handful of $\pm3\sigma$ peaks in the residual map is likely
-an indication that our assumption of a single Gaussian to describe the source
-morphology is an oversimplification.
+model and the Gemini-S image.  Given the absolute astrometric rms uncertainty
+of $0\farcs2$ (based on SDSS), we do not consider this offset to be
+significant.  The presence of a handful of $\pm3\sigma$ peaks in the residual
+map is likely an indication that our assumption of a single Gaussian to
+describe the source morphology is an oversimplification.
 
@@
 support for this hypothesis (see Figure~\ref{fig:iraccolor}), as all of the ALMA
-sources are detected and have similar mid-IR colors (suggesting they lie at
-similar redshift).
+sources are detected and have similar mid-IR colors.
 
@@
 {\bf HXMM09:} Two sources are detected by ALMA, both of which are weakly
-lensed by a foreground galaxy detected in the {\it HST} image.  An Einstein
+lensed by a single foreground galaxy detected in the {\it HST} image.  An Einstein
 radius of $1\farcs5$ is used to represent the ``maximal lensing'' scenario and
@@
 is that the SPIRE photometry show blue colors that suggest this object is at low
-redshift.
+redshift.  Note that models in which the late-type galaxy is lensing the ALMA
+source by a modest amount ($\mu_{870} < 1.2$) cannot be ruled out with the
+present data.
 
@@
 
-{\bf HXMM12:} One source is detected by ALMA, and it is weakly lensed by a group
-of foreground galaxies seen in the {\it HST} image.  We assume an Einstein
-radius of $0\farcs2$ for the nearest lensing galaxy and allow a $\pm0\farcs4$
-shift in its position relative to that indicated by the {\it HST} image (which
-has its astrometry tied to SDSS).  We represent the remaining members of the
-group as a single SIS located $4\farcs5$ south and $4\farcs5$ east of the image
-centroid and having an Einstein radius of $2\farcs0$.  This is meant to
-represent the ``maximal lensing'' scenario, so our measurement of $\mu_{870}$
-should be regarded as an upper limit.  The presence of two $3\sigma$ peaks
-located near the center of the residual image indicates that the model does not
-fit the data perfectly.  This could be an indication that either of our
-assumptions for the lens potential or source structure are oversimplifications.
-Higher resolution imaging is needed to determine the most likely cause.
-
-{\bf HECDFS12:} This is a complex, very well constrained system.  Two sources
+{\bf HXMM12:} One source is detected by ALMA, and it is weakly lensed by a
+group of foreground galaxies seen in the {\it HST} image.  We assume an
+Einstein radius of $0\farcs2$ for the nearest lensing galaxy and allow a
+$\pm0\farcs4$ (i.e., 2$\sigma$) shift in its position relative to that
+indicated by the {\it HST} image (which has its astrometry tied to SDSS).  We
+represent the remaining members of the group as a single SIS located $4\farcs5$
+south and $4\farcs5$ east of the image centroid and having an Einstein radius
+of $2\farcs0$.  This is meant to represent the ``maximal lensing'' scenario, so
+our measurement of $\mu_{870}$ should be regarded as an upper limit.  The
+presence of two $3\sigma$ peaks located near the center of the residual image
+indicates that the model does not fit the data perfectly.  This could be an
+indication that either of our assumptions for the lens potential or source
+structure are oversimplifications.  Higher resolution imaging is needed to
+determine the most likely cause.
+
+{\bf HECDFS12:} This is a complex, well-constrained system.  Two sources
 are detected by ALMA: one is strongly lensed and the other is weakly lensed.
@@
 Einstein radius of $0\farcs5$ for the lens, as values larger than this produce
-multiple images of the ALMA sources.  Based on the brightness of the lens, we
-consider to be unlikely values for the Einstein radius that are smaller than
-$0\farcs5$, so the results we report for this object should be robust.
+multiple images of the ALMA sources.  Values for the Einstein radius that are
+smaller than $0\farcs5$ are unlikely based on the brightness of the lens, so
+the results we report for this object should be robust.
 
@@
 distance in both hydrodynamical simulations of major mergers
-\citep[e.g.,][]{Hayward:2012lr} and CO observations of major mergers
-\citep[e.g.,][]{2008ApJ...680..246T, 2010ApJ...724..233E, 2011ApJ...733L..11R,
-2011MNRAS.412.1913I}.  Two plausible scenarios are that HADFS02 represents a
-major merger that just experienced a first pass or is approaching final
-coalescence, either of which significantly enhanced star-formation in the
-system.
+\citep[e.g.,][]{Hayward:2012lr} and observations of major mergers
+\citep[e.g.,][]{Ivison:2007qv, 2008ApJ...680..246T, 2010ApJ...724..233E,
+2011ApJ...733L..11R, 2011MNRAS.412.1913I}.  Two plausible scenarios are that
+HADFS02 represents a major merger that just experienced a first pass or is
+approaching final coalescence, either of which significantly enhanced
+star-formation in the system.
 
@@
 {\bf HADFS03:} Three sources are detected by ALMA, each of which is weakly
-lensed by a bright foreground galaxy seen in the {\it HST} image.  Alternative
-scenarios involving strong lensing can be ruled out by the location of the
-lens: $\approx 2-3\arcsec$ north of the centroid of the ALMA sources (the rms
-error in the astrometry is set from 2MASS at a level of $\approx 0\farcs4$) as
-well as the unusual location and fluxes of the ALMA sources relative to each
-other.  We assume an Einstein radius of $0\farcs5$ and fix the position angle
-of the lens to be between 40-50 degrees to match the orientation seen in the
-{\it HST} image.  Larger Einstein radii can be ruled out by the absence of
-counter images north of the lens.
+lensed by a single bright foreground galaxy seen in the {\it HST} image.
+Alternative scenarios involving strong lensing can be ruled out by the location
+of the lens: $\approx 2-3\arcsec$ north of the centroid of the ALMA sources
+(the rms error in the astrometry is set from 2MASS at a level of $\approx
+0\farcs4$) as well as the unusual location and fluxes of the ALMA sources
+relative to each other.  We assume an Einstein radius of $0\farcs5$ and fix the
+position angle of the lens to be between 40-50 degrees to match the orientation
+seen in the {\it HST} image.  Larger Einstein radii can be ruled out by the
+absence of counter images north of the lens.
+
+\input{table_lenses}
 
@@
 lensed.  Previous research has shown this to be an overdense region \citep[this
-object is called COSBO3 in][]{Aravena:2010fr} with a photometric redshift of
-$z=2.3-2.4$.  Our ALMA imaging offers the first convincing evidence that the
-associated galaxies in the overdensity are sub-mm bright and thus intensely
-star-forming.  There are a number of $2-3\sigma$ peaks in the map that could be
-real.  This would further increase the multiplicity rate for this object, but
-we caution that there are also negative peaks of similar amplitude (i.e.,
-$2-3\sigma$) present in this map.  Some of the ALMA sources have counterparts
-detected in the {\it HST} image, whereas all of the ALMA sources are detected
-by IRAC (see Figure~\ref{fig:iraccolor}).  Their mid-IR colors are similar,
-providing further evidence that the ALMA sources lie at the same redshift.
+object is called COSBO3 in][]{Aravena:2010fr} with an optical and near-IR
+photometric redshift of $z=2.3-2.4$.  Our ALMA imaging offers the first
+convincing evidence that the associated galaxies in the overdensity are sub-mm
+bright and thus intensely star-forming.  There are a number of $2-3\sigma$
+peaks in the map that could be real.  This would further increase the
+multiplicity rate for this object, but we caution that there are also negative
+peaks of similar amplitude (i.e., $2-3\sigma$) present in this map.  Some of
+the ALMA sources have counterparts detected in the {\it HST} image, whereas all
+of the ALMA sources are detected by IRAC (see Figure~\ref{fig:iraccolor}).
+Their mid-IR colors are similar, providing further evidence that the ALMA
+sources lie at the same redshift.
 
@@
 
-\input{table_lenses}
 \input{table_intrinsic}
@@
 the DSFGs in ALESS.  This difference is likely due to differences in dust
-temperature or redshift distributions of the two samples and likely arises from
-selection effects.
+temperature and/or redshift distributions of the two samples and likely arises
+from selection effects.
 
@@
 \citep[20.6$\,$mJy,][]{2006MNRAS.370.1185P} and HFLS3
-\citep[15-20$\,$mJy;][]{Riechers:2013lr, Cooray:2014rm}.  It is a level that is
-extremely difficult to reproduce in simulations
+\citep[15-20$\,$mJy;][]{Riechers:2013lr, Cooray:2014rm, Robson:2014xy}.  It is
+a level that is extremely difficult to reproduce in simulations
 \citep[e.g.,][]{Narayanan:2010lr}.  One possibility is that the objects with
@@
 having a higher multiplicity rate.  This result is also consistent with
-multiplicity studies of $S_{870}$-selected DSFGs by \citet{Smolcic:2012zl} and
-\citet{Barger:2012yg}, who use PdBI/1.1$\,$mm and SMA/870$\,\mu$m imaging to
-determine rates of 22\% and 40\%, respectively.
+multiplicity studies of $S_{870}$-selected DSFGs by \citet{Ivison:2007qv},
+\citet{Smolcic:2012zl}, and \citet{Barger:2012yg}, who use VLA, PdBI/1.1$\,$mm,
+and SMA/870$\,\mu$m imaging to determine rates of 18\%, 22\%, and 40\%,
+respectively.
 
@@
 
-\subsection{Comparing Model with Data}
+\subsection{Comparing Models with Data}
 
@@
 fine grid using the Scipy {\sc griddata} package and then smoothing the
-resulting grid using a gaussian filter (specifically, the Scipy {\sc
+resulting grid using a Gaussian filter (specifically, the Scipy {\sc
 gaussian\_filter} package).  Also shown in this diagram are model predictions
@@
 the intrinsic sizes of the lensed galaxies and hence under-predict the
-magnification factors.  If this is true, it would also affect the intermediate
-$S_{870}$ regime.  A thorough investigation of this possibility is deferred to
-future work.
+magnification factors.  For example, the half-light sizes of unlensed DSFGs
+have been found recently to be $\approx 0.8 \,$kpc \citep{Ikarashi:2014nr} and
+$\approx1.2\,$kpc \citep{Simpson:2015ty}.  In contrast, we reported a median
+half-light radius of $1.53\,$kpc in \citet{Bussmann:2013lr}.  If this
+difference is significant, it may also affect the intermediate $S_{870}$
+regime.  A thorough investigation of this possibility is deferred to future
+work.
 
@@
 
+R.J.I. acknowledges support from European Research Council Advanced
+Investigator Grant, Cosmicism, 321302.
+
 Facilities: ALMA, Gemini-S.

### 2015-01-22 Code/colflux.py

@@ -80,17 +80,31 @@ e250 = spirephot['e250']
 e350 = spirephot['e350']
 e500 = spirephot['e500']
 
-# read in SPIRE photometry for all H-ATLAS galaxies
+# read in SPIRE photometry for all HerMES galaxies in fields accessible to ALMA
+hermesloc = '../../HerMESCatalog/'
 atlasloc = '../../HATLASCatalog/'
+fieldnames = ['L1-ECDFS', 'L2-COSMOS', 'L4-UDS', 'L4-VVDS', 'L5-CDFS-SWIRE', \
+        'L6-ADFS', 'L6-ELAIS-S1-SWIRE', 'L6-XMM-LSS-SWIRE']
+s350 = []
+s500 = []
+for i, fieldname in enumerate(fieldnames):
+    tableloc = hermesloc + fieldname + '/' + fieldname + '_xID250_DR2.fits'
+    d1 = Table.read(tableloc)
+    if i == 0:
+        s350 = numpy.array(d1['F350'].data)
+        s500 = numpy.array(d1['F500'].data)
+    else:
+        s350 = numpy.append(s350, numpy.array(d1['F350'].data))
+        s500 = numpy.append(s500, numpy.array(d1['F500'].data))
 g09 = fits.getdata(atlasloc+'G09_Phase1_release_v2_allids.fits.gz', 1)
 g12 = fits.getdata(atlasloc+'G12_Phase1_release_v2_allids.fits.gz', 1)
 g15 = fits.getdata(atlasloc+'G15_Phase1_release_v2_allids.fits.gz', 1)
-ngpaloc = atlasloc+'NGP-h1-v1-v2_madx5_19-Feb-2011-110650_id_ac_names.dat'
-ngpa = Table.read(ngpaloc, format='ascii')
-ngpbloc = atlasloc+'NGP-h5-h7-v5_madx5_19-Feb-2011-104234_id_ac_names.dat'
-ngpb = Table.read(ngpbloc, format='ascii')
-ngpcloc = atlasloc+'NGP-h6-h8-v7_madx5_19-Feb-2011-014156_id_ac_names.dat'
-ngpc = Table.read(ngpcloc, format='ascii')
+#ngpaloc = hermesloc+'NGP-h1-v1-v2_madx5_19-Feb-2011-110650_id_ac_names.dat'
+#ngpa = Table.read(ngpaloc, format='ascii')
[…]

### 2015-01-22 Code/maketable_source.py

@@ -148,8 +148,8 @@ for itarg in range(0, ntarg):
                     crlp = config[parname[0]][parname[1]][parname[2]]
                     off_lens = crlp['Limits'][1]
             dist = dist_lens + off_lens
-            dradeg_lens = dist.mean() / 3600
-            eRA = dist.std() / 15
+            dradeg_lens = dist.mean()# / 3600
+            eRA = dist.std()# / 15
             if ilens == 0:
                 RA0 = dist
 
@@ -190,7 +190,7 @@ for itarg in range(0, ntarg):
                     crlp = config[parname[0]][parname[1]][parname[2]]
                     off_lens = crlp['Limits'][1]
             dist = dist_lens + off_lens
-            ddecdeg_lens = dist.mean() / 3600
+            ddecdeg_lens = dist.mean()# / 3600
             eDec = dist.std()
             if ilens == 0:
                 Dec0 = dist
@@ -335,15 +335,15 @@ for itarg in range(0, ntarg):
             phi_indiv = dist.mean()
             e_phi_indiv = dist.std()
 
-            msg = '{0:15} & ${1:12}\pm{2:5.3f}$ & ${3:12}\pm{4:4.2f}$ & ${5:.3f}\pm{6:.3f}$ & ${7:.3f}\pm{8:0.3f}$ & ${9:3.0f}\pm{10:3.0f}$'
-            msgfmt = msg.format(datanamelens, fullRA, eRA, fullDec, eDec, 
+            msg = '{0:15} & ${1:5.2f}\pm{2:5.2f}$ & ${3:5.2f}\pm{4:5.2f}$ & ${5:.3f}\pm{6:.3f}$ & ${7:.3f}\pm{8:0.3f}$ & ${9:3.0f}\pm{10:3.0f}$'
+            msgfmt = msg.format(datanamelens, dradeg_lens, eRA, ddecdeg_lens, eDec, 
                     einstein_indiv, e_einstein_indiv, q_indiv, e_q_indiv,
                     phi_indiv, e_phi_indiv)
             #msg = '{0:3.0f} {1:3.0f}'
             #msgfmt = msg.format(phi_indiv, e_phi_indiv)            
             #msg = '{0:.2f} {1:.2f}'
             #msgfmt = msg.format(mu_indiv, e_mu_indiv)            
-            #print(msgfmt)
+            print(msgfmt)
 
         for isource in range(nsource):
 
[…]

### 2015-01-26 LaTeX/ms.tex
Douglas Scott comments

@@
 
-\title{HerMES: Spatially resolved ALMA Imaging of {\it
-Herschel}$^{\dagger}$-selected Dusty Star-forming Galaxies}
+\title{HerMES: ALMA Imaging of {\it Herschel}$^{\dagger}$-selected Dusty
+Star-forming Galaxies}
 
@@
     introduce and make use of {\sc uvmcmcfit}, a general purpose and publicly
-    available Markov Chain Monte Carlo visibility plane analysis tool to
+    available Markov chain Monte Carlo visibility plane analysis tool to
     analyze the source properties.  Nearly 70\% of the {\it Herschel} sources
@@
     counterparts to sources found in the LABOCA ECDFS Submillimeter Survey.
-    Theoretical models underpredict the excess in number of sources with small
+    Theoretical models underpredict the excess number of sources with small
     separations seen in our ALMA sample.  The high multiplicity rate and low
@@
 
-Galaxies selected in blind surveys at far-infrared (FIR) or sub-millimieter
+Galaxies selected in blind surveys at far-infrared (FIR) or sub-millimeter
 (sub-mm) wavelengths are generally known as dusty star-forming galaxies
-(DSFGs).  They cover a wide range in redshift from $z \sim 0.5$ to $z > 6$
-\citep{2005ApJ...622..772C, Casey:2012qy, Messias:2014fk, Riechers:2013lr},
-with a significant component at $z \sim 2$ \citep{Casey:2012uq,
-Bothwell:2013lr}, when they represent the most FIR-luminous objects in
-existence during this epoch.   They are signposts of significant over-densities
-\citep{Daddi:2009qy, Capak:2011qy} \citep[c.f.][]{Robson:2014xy} and
-likely represent the formative stages of the most massive elliptical galaxies
-found in the local Universe \citep[e.g.,][]{Ivison:2013fk, Fu:2013lr}.
-Moreover, they constitute an important component of the overall galaxy
-population at $z \sim 2$ \citep[e.g.,][]{Magnelli:2011ul}, when the
-star-formation rate density in the Universe peaked
-\citep[e.g.,][]{Lilly:1996uq, 1996MNRAS.283.1388M}.
+\citep[DSFGs; for a recent review, see][]{Casey:2014lr}.  They cover a wide
+range in redshift from $z \sim 0.5$ to $z > 6$ \citep{2005ApJ...622..772C,
+Casey:2012qy, Messias:2014fk, Riechers:2013lr}, with a significant component at
+$z \sim 2$ \citep{Casey:2012uq, Bothwell:2013lr}, when they represent the most
+FIR-luminous objects in existence during this epoch.   They are usually
+signposts of significant over-densities \citep{Daddi:2009qy, Capak:2011qy}
+\citep[c.f.][]{Robson:2014xy} and likely represent the formative stages of the
+most massive elliptical galaxies found in the local Universe
+\citep[e.g.,][]{Ivison:2013fk, Fu:2013lr}.  Moreover, they constitute an
+important component of the overall galaxy population at $z \sim 2$
+\citep[e.g.,][]{Magnelli:2011ul}, when the star-formation rate density in the
+Universe peaked \citep[e.g.,][]{Lilly:1996uq, 1996MNRAS.283.1388M}.
 
@@
 sensitive ($\sigma \approx 0.2\,$mJy per beam) and all 29 HerMES DSFGs are detected
-\citep[such is not the case in previous similar studies with shallower imaging;
+\citep[which was not the case in previous similar studies with shallower imaging;
 e.g.,][]{Smolcic:2012zl, Barger:2012yg, Hodge:2013qy}.  Third, the typical
@@
 
-We also obtained Gemini-South optical imaging to complement our existing array
+We also obtained Gemini-South optical imaging to complement our existing set
 of ancillary multi-wavelength imaging.  We use those data in this paper to
-identify lensing galaxies which are typically early-types with little on-going
+identify lensing galaxies, which are typically early-types with little on-going
 star-formation and therefore exhibit very weak sub-mm emission.
@@
 In Section~\ref{sec:obs}, we characterize our sample and present our ALMA and
-Gemini-South imaging.  Section~\ref{sec:modelfits} presents model fitting
-methodology and model fits to all ALMA sources (lensed and unlensed) using {\sc
+Gemini-South imaging.  Section~\ref{sec:modelfits} presents our model fitting
+methodology and model fits for all ALMA sources (lensed and unlensed) using {\sc
 uvmcmcfit}, a publicly available
-\footnote{https://github.com/sbussmann/uvmcmcfit} modified version of the
+\footnote{\url https://github.com/sbussmann/uvmcmcfit} modified version of the
 visibility plane lens modeling software used in \citet{Bussmann:2012lr,
-Bussmann:2013lr}.  Results on the effect of lensing on the observed properties
-of the {\it Herschel} DSFGs in our sample as well as the multiplicity rate and
-typical angular separation between sources after delensing the ALMA sources
+Bussmann:2013lr}.  Results on the effect of lensing for the observed properties
+of the {\it Herschel} DSFGs in our sample, as well as the multiplicity rate and
+typical angular separation between sources after delensing the ALMA sources,
 appear in Section~\ref{sec:results}.  We scrutinize statistical predictions for
@@
 The starting point for the sample selection is source extraction and
-photometry.  Sources are detected using the {\sc StarFinder} code
-\citep{Diolaiti:2000qy} on the 250$\, \mu$m {\it Herschel} Spectral and
-Photometric Imaging REceiver \citep[SPIRE;][]{2010A&A...518L...3G} images
-\citep{Wang:2014lr}.
-Photometry is obtained from the HerMES XID pipeline \citep{Roseboom:2010lk},
-which allocates flux density based on the 250$\, \mu$m position priors from
-{\sc StarFinder}.
-
+photometry.  For the objects in this paper, individual catalogs were generated
+for each of the 250$\, \mu$m, 350$\,\mu$m, and 500$\,\mu$m {\it Herschel}
+Spectral and Photometric Imaging REceiver \citep[SPIRE;][]{2010A&A...518L...3G}
+channels using the SUSSEXtractor peak finder algorithm \citep{Savage:2007sf}.
 Our sample includes 29 DSFGs drawn from five independent, confusion-limited
 fields in HerMES with declinations $> 2 ^\circ$ and totaling $55\,$deg$^2$.
-The sample was originally selected to be a complete, flux-limited set of
-objects satisfying $S_{500} > 95 \, {\rm mJy}$ that are not known radio AGN,
-nearby late type galaxies, or Galactic emission.  The intention was to assemble
-the largest possible sample of lenses in the HerMES fields that are accessible
-to ALMA.  However, the original selection was based on the HerMES ``V5''
-catalog because this was the only one available at the time of the ALMA Cycle~0
-deadline.  Subsequently, improved efforts to deblend SPIRE photometry at
-$500\,\mu$m were introduced that led to the development of the ``V21'' catalog
+
+The sample was selected to be a complete, flux-limited set of objects
+satisfying $S_{500} > 95\,$mJy that are not known radio AGN, nearby late-type
+galaxies, or Galactic emission. The selection was designed to assemble a large
+sample of lensed galaxies in the ALMA-accesible HerMES fields, and was
+constructed from the SUSSEXtractor catalogs, which were available prior to the
+ALMA Cycle~0 deadline.  Subsequently, improved efforts to deblend SPIRE
+photometry at 500$\,\mu$m using StarFinder \citep{Wang:2014lr} were introduced
 that formed the basis of the lens selection criteria used in
-\citet{Wardlow:2013lr}.  A number of objects in the sample in this paper have
-significantly lower $S_{500}$ values in the V21 catalog, indicating that their
-$S_{500}$ in the V5 catalog was boosted by blending with nearby sources rather
-than by gravitational lensing.  For this reason, the objects in this sample
-comprise a combination of lenses and blends of multiple sources.
+\citet{Wardlow:2013lr}.  As a result of the improved deblending algorithms in
+the StarFinder catalogues and \citet{Wardlow:2013lr} a number of objects in our
+sample have significantly lower $S_{500}$ values in the StarFinder catalog than
+in the original SUSSEXtractor catalogs.  This and further investigation into
+the StarFinder catalogs shows that their original flux was boosted by blending
+with nearby sources rather than by gravitational lensing.  For this reason, the
+objects in this sample comprise a combination of lenses and blends of multiple
+sources.
 
@@
 
-Figure~\ref{fig:sample} shows that the ALMA sample is set clearly apart from the
-very bright {\it Herschel} DSFGs that are selected to have $S_{500} > 100 \,
-$mJy and have been shown to be almost entirely lensed DSFGs
-\citep{Negrello:2010fk, Wardlow:2013lr, Bussmann:2013lr}.  In contrast, the
-sample in this paper should include a more diverse mix of lensed and unlensed
-DSFGs.  On the other hand, this sample is selected from a survey with an area
-that is 200 times larger than that of ALESS.  It is no surprise then, that the
-median $S_{500}$ in our sample is $\sim3.5$ times brighter than the median
-$S_{500}$ in ALESS.  Our ALMA sample opens a new window of discovery space on
-the bright end of the DSFG luminosity function.
+Figure~\ref{fig:sample} shows that the {\it Herschel}-ALMA sample is set
+clearly apart from the very bright {\it Herschel} DSFGs that are selected to
+have $S_{500} > 100 \, $mJy and have been shown to be almost entirely lensed
+DSFGs \citep{Negrello:2010fk, Wardlow:2013lr, Bussmann:2013lr}.  In contrast,
+the sample in this paper should include a more diverse mix of lensed and
+unlensed DSFGs.  On the other hand, this sample is selected from a survey with
+an area that is 200 times larger than that of the Large Apex Bolometer Camera
+Extended Chandra Deep Field Survey \citep[LESS][]{Weis:2009ly}.  It is no
+surprise then, that the median $S_{500}$ in our sample is $\sim3.5$ times
+brighter than the median $S_{500}$ in the sample of ALMA-detected sources in
+LESS, known as ALESS \citep{Hodge:2013qy}.  Our {\it Herschel}-ALMA sample
+opens a new window of discovery space on the bright end of the DSFG luminosity
+function.
 
@@
 
-\caption{ {\it Herschel}/SPIRE photometry of all galaxies in the H-ATLAS
-phase~I catalog with S/N$ > 3$ at 250$\,\mu$m, 350$\,\mu$m, and 500$\,\mu$m
-(log of number of galaxies shown in grayscale).  The sample of HerMES sources
-in this paper are shown with green squares (the ``ALMA sample'').  The very
-bright {\it Herschel} DSFGs from \citet{Bussmann:2013lr} (the ``SMA sample'')
-are shown by red circles, and the overall sample of candidate lensed {\it
-Herschel} DSFGs are highlighted by yellow circles.  Lensed SMGs discovered by
-the SPT that have published lens models are represented by cyan stars
-\citep{Hezaveh:2013fk}.  A magenta diamond shows the location in this diagram
-of the stacked signal from ALESS DSFGs.  Representative error bars are shown in
-the lower left corner.  The ALMA sample fills the gap in 500$\,\mu$m flux
-density space between SMA/SPT and ALESS samples.} \label{fig:sample}
+\caption{ {\it Herschel}/SPIRE photometry of all galaxies in the HerMES phase~I
+catalog with declination $< +2\,^\circ$ and signal to noise ratio greater than
+1 at 250$\,\mu$m, 350$\,\mu$m, and 500$\,\mu$m (log of number of galaxies shown
+in grayscale).  The sample of HerMES sources in this paper are shown with green
+squares (``{\it Herschel}-ALMA'').  The very bright {\it Herschel} DSFGs from
+\citet{Bussmann:2013lr} (``{\it Herschel}-SMA'') are shown by red circles, and
+lensed SMGs discovered by the SPT that have published lens models
+(``SPT-ALMA'') are represented by cyan stars \citep{Hezaveh:2013fk}.  A magenta
+diamond shows the location in this diagram of the stacked signal from ALESS
+DSFGs.  Representative error bars are shown in the lower left corner.  The {\it
+Herschel}-ALMA sample fills the gap in 500$\,\mu$m flux density space between
+50-100$\,$mJy.} \label{fig:sample}
 
@@
 
-In detail, two of the sources in the ALMA sample (HXMM01 and HXMM02) overlap
-with the ``confirmed lensed'' sample in \citet{Wardlow:2013lr} as well as with
-the SMA sample in \citet{Bussmann:2013lr}.  A further 8 appear in the
-``Supplementary sample'' in \citet{Wardlow:2013lr}.  The remainder have
-$S_{500} < 80\,$mJy and thus do not appear in \citet{Wardlow:2013lr}.
+In detail, two of the sources in the {\it Herschel}-ALMA sample (HXMM01 and
+HXMM02) overlap with the ``confirmed lensed'' sample in \citet{Wardlow:2013lr}
+as well as with the {\it Herschel}-SMA sample in \citet{Bussmann:2013lr}.  A
+further eght appear in the ``Supplementary sample'' of \citet{Wardlow:2013lr}.
+The remainder have $S_{500} < 80\,$mJy and thus do not appear in
+\citet{Wardlow:2013lr}.
 
@@
 
-Table~\ref{tab:position} provides reference data for the ALMA sample, including
+Table~\ref{tab:position} provides reference data for the {\it Herschel}-ALMA sample, including
 centroid positions measured from the ALMA 870$\, \mu$m imaging (see
-section~\ref{sec:almaobs}).
+Section~\ref{sec:almaobs}).
 
@@
 (Program 2011.0.00539.S; PI: D. Riechers).  The observations were carried out
-in good 870$\,\mu$m weather conditions which resulted in typical system
-temperatures of $T_{\rm sys} \sim 130\,$K and phase fluctuations of $\sim
-10\,$deg.  Each target was observed until an rms noise level near the phase
+in good 870$\,\mu$m weather conditions, which resulted in typical system
+temperatures of $T_{\rm sys} \approx 130\,$K and phase fluctuations of $\sim
+10\,^\circ$.  Each target was observed until an rms noise level near the phase
 center of $\sigma \approx 0.2\,$mJy was achieved.  This typically required 10
@@
 gain calibration.  The following solar system objects were used for absolute
-flux calibration: Callisto (CDFS targets), Neptune (XMM targets), Titan (COSMOS
-targets) and Uranus (ADFS and XMM targets).  For HELAISS02, no solar system
+flux calibration: Callisto (CDFS targets); Neptune (XMM targets); Titan (COSMOS
+targets); and Uranus (ADFS and XMM targets).  For HELAISS02, no solar system
 object was observed.  Instead, J2258$-$279 was used for absolute flux
@@
 We used the Common Astronomy Software Applications (CASA, version 4.2.1)
-package to investigate the quality of the reduced data provided by the North
-American ALMA Science Center (NAASC).  Overall, the quality of the processed
-data from the NAASC was very high.  We achieved a significant improvement in
-the case of the ADFS and XMM targets by excluding datasets with moderate
-$T_{\rm sys}$ and poor phase fluctuations.  For a handful of targets with peak
-signal-to-noise ratio (S/N) greater than 20, we obtained a $\approx 10\%$
-improvement in S/N by using the CASA {\sc selfcal} task with the clean component
-model as input to improve the phase gain corrections.  Finally, we updated the
-absolute flux calibration to use the Butler-JPL-Horizons 2012 solar system
-models.
-
-For imaging, we used the CASA {\sc Clean} task with Briggs weighting and robust
-= $+$0.5 to achieve an optimal balance between sensitivity and spatial
+package to re-reduce the data provided by the North American ALMA Science
+Center (NAASC).  We found that the quality of the processed data from the NAASC
+was very high.  However, we achieved a significant improvement in the case of
+the ADFS and XMM targets by excluding data sets with moderate $T_{\rm sys}$ and
+poor phase fluctuations.  For a handful of targets with peak signal-to-noise
+ratio (S/N) greater than 20, we obtained a $\approx 10\%$ improvement in S/N by
+using the CASA {\sc selfcal} task with the clean component model as input to
+improve the phase gain corrections.  Finally, we updated the absolute flux
+calibration to use the Butler-JPL-Horizons 2012 solar system models
+\footnote{\url
+https://science.nrao.edu/facilities/alma/aboutALMA/Technology/ALMA\_Memo\_Series/alma594/abs594}.
+
+For imaging, we used the CASA {\sc Clean} task with Briggs weighting and ``robust
+= $+$0.5'' to achieve an optimal balance between sensitivity and spatial
 resolution.  We selected the multi-frequency synthesis option to optimize {\it
@@
 
-Figure~\ref{fig:imaging} presents our ALMA images (colorscale) in comparison to
+Figure~\ref{fig:imaging} presents our ALMA images (color scale) in comparison to
 the {\it Herschel} SPIRE images (black-white contours) originally used to
@@
 the program is to use shallow $u$, $g$, $r$, $i$, and $z$ imaging to identify
-structure at $z<1$ and determine which of the ALMA sources are affected by
+structure at redshifts below unity and determine which of the ALMA sources are affected by
 gravitational lensing.  Nearly half of the ALMA sources lie in regions with
-existing deep optical imaging thanks to the extensive HerMES multi-wavelength
+existing deep optical imaging, thanks to the extensive HerMES multi-wavelength
 dataset --- these were excluded from our Gemini-S program.  The remaining
@@
 integration time in each of $u$, $g$, $r$, $i$, and $z$.  The observations were
-obtained during dark time in with adequate seeing conditions (image quality in
-the 85th percentile, corresponding to $\approx 1.1\arcsec$.
+obtained during dark time in adequate seeing conditions (image quality in
+the 85th percentile, corresponding to $\approx 1.1\arcsec$).
 
@@
 from the Gemini observatory webpage
-\footnote{http://www.gemini.edu/sciops/data-and-results/processing-software/getting-started\#gmos}.
+\footnote{\url http://www.gemini.edu/sciops/data-and-results/processing-software/getting-started\#gmos}.
 
@@
 higher resolution, smaller field-of-view imaging from {\it HST} or Keck (when
-available) that were originally presented in \citet{Calanog:2014lr}.
+available), which were originally presented in \citet{Calanog:2014lr}.
 
@@
 
-\caption{ ALMA 870$\mu$m images (color scale, units of mJy/beam) of HerMES
+\caption{ ALMA 870$\,\mu$m images (color scale, units of mJy$\,$beam$^{-1}$) of HerMES
 DSFGs (images have not been corrected for primary beam attenuation).  Contours
@@
 squares identify the regions of each image that are shown in greater detail in
-Figure~\ref{fig:uvmodels}.  \label{fig:imaging}} \addtocounter{figure}{-1}
+Fig.~\ref{fig:uvmodels}.  \label{fig:imaging}} \addtocounter{figure}{-1}
 
@@
 lens model derived from a visibility-plane analysis of interferometric imaging
-of a strongly lensed DSFG discovered in wide-field submm surveys as well as
-\citet{Bussmann:2013lr}, who extended this work to a statistically significant
-sample of 30 objects.  It also bears some resemblence to the method used in
-\citet{Hezaveh:2013fk}, who undertake lens modeling of interferometric data in
-the visibility plane.  We summarize important information on the methodology
-here, taking care to highlight where any differences occur between this work and
-that of our previous efforts.
+of a strongly lensed DSFG discovered in wide-field submm surveys as well as in
+\citet{Bussmann:2013lr}, where this work was extended to a
+statistically significant sample of 30 objects.  It also bears some resemblence
+to the method used in \citet{Hezaveh:2013fk}, who undertake lens modeling of
+interferometric data in the visibility plane.  We summarize important
+information on the methodology here, taking care to highlight where any
+differences occur between this work and that of our previous efforts.
 
 We created and made publicly available custom software, called {\sc uvmcmcfit},
-that is capable of modeling all of the ALMA sources in this paper efficiently
+which is capable of modeling all of the ALMA sources in this paper efficiently
 and reliably.
@@
 following six free parameters: the position of the source (relative to the
-primary lens if a lens is present) ($\Delta \alpha_{\rm s}$ and $\Delta
+primary lens if a lens is present, $\Delta \alpha_{\rm s}$ and $\Delta
 \delta_{\rm s}$), the total intrinsic flux density ($S_{\rm in}$), the
-effective radius intermediate axis length ($r_{\rm s} = \sqrt{a_{\rm s} b_{\rm
-s}}$), the axial ratio ($q_{\rm s}$ =  $b_{\rm s}/a_{\rm s}$), and the position
-angle ($\phi_{\rm s}$, degrees east of north).  The use of an elliptical
-Gaussian represents a simplification from the S\'ersic profile
+effective radius length ($r_{\rm s} = \sqrt{a_{\rm s} b_{\rm s}}$), the axial
+ratio ($q_{\rm s}$ =  $b_{\rm s}/a_{\rm s}$), and the position angle
+($\phi_{\rm s}$, degrees east of north).  The use of an elliptical Gaussian
+represents a simplification from the S\'ersic profile
 \citep{1968adga.book.....S}  that is permitted based on the relatively weak
@@
 typically required 24-48$\,$hours using the old software, whereas the same
-system can be modeled in less than one hour with the pure-Python code.  The use
-of pure-Python code for tracing the deflection of light rays is a critical
-component of making {\sc uvmcmcfit} computationally feasible.
+system can be modeled in less than one hour with the pure-Python code (tests of
+the Bolton ray-tracing routine indicate it produces results consistent with
+{\sc Gravlens}).  The use of pure-Python code for tracing the deflection of
+light rays is a critical component of making {\sc uvmcmcfit} computationally
+feasible.
 
@@
 \alpha_{\rm NIR}$ and $\Delta \delta_{\rm NIR}$), the mass of the lens
-(parameterized in terms of the intermediate axis angular Einstein radius,
-$\theta_{\rm E}$), the axial ratio of the lens ($q_{\rm lens} = b_{\rm lens} /
-a_{\rm lens}$), and the position angle of the lens ($\phi_{\rm lens}$; degrees
-east of north).  Unless otherwise stated, when optical or near-IR imaging
-suggests the presence of additional lenses (see Figure~\ref{fig:uvmodels}), we
-estimate centroids for each lens by-eye and fix the positions of the additional
-lenses with respect to the primary lens.  Each additional lens thus has 3 free
-parameters: $\theta_{\rm E}$, $q_{\rm lens}$, and $\phi_{\rm lens}$.  We assume
-secondary, tertiary, etc., lenses are located at the same redshift as the
-primary lens.
+(parameterized in terms of the angular Einstein radius, $\theta_{\rm E}$), the
+axial ratio of the lens ($q_{\rm lens} = b_{\rm lens} / a_{\rm lens}$), and the
+position angle of the lens ($\phi_{\rm lens}$; degrees east of north).  Unless
+otherwise stated, when optical or near-IR imaging suggests the presence of
+additional lenses (see Figure~\ref{fig:uvmodels}), we estimate centroids for
+each lens by eye and fix the positions of the additional lenses with respect to
+the primary lens.  Each additional lens thus has three parameters:
+$\theta_{\rm E}$, $q_{\rm lens}$, and $\phi_{\rm lens}$.  We assume secondary,
+tertiary, etc., lenses are located at the same redshift as the primary lens.
 
@@
 3 \times (N_{\rm lens} - 1) + 6 * N_{\rm source}$, where $N_{\rm source}$ is
-the number of S\'ersic profiles used.
+the number of Gaussian profiles used.
 
@@
 optical/near-IR images of $0\farcs2$ ($0\farcs4$) for SDSS-based (2MASS-based)
-astrometric calibration.  In section~\ref{sec:objectbyobject}, we discuss the
+astrometric calibration.  In Section~\ref{sec:objectbyobject}, we discuss the
 level of agreement between the astrometry from the images and the astrometry
@@
 position is allowed to vary over any reasonable range necessary to fit the data
-(typically, this is $\pm 1-2\arcsec$).  The effective radius is allowed to vary
-from $0\farcs01 - 1\farcs5$.
+(typically, this is $\pm $1-2$\arcsec$).  The effective radius is allowed to vary
+from $0\farcs01 $-$ 1\farcs5$.
 
@@
 
-The quality of fit for a given set of model parameters is determined from the
-maximum likelihood estimate $MLE$ according to the following equation:
+The goodness of fit for a given set of model parameters is determined from the
+maximum likelihood estimate $L$ according to:
 
 \begin{equation}
-    MLE = \sum_{u, v} \frac{|V_{\rm ALMA} - V_{\rm
-    model}|^2}{\sigma^2} + log(2 \pi \sigma^2) 
+    L = \sum_{u, v}\left( \frac{|V_{\rm ALMA} - V_{\rm
+    model}|^2}{\sigma^2} + {\rm log}(2 \pi \sigma^2) \right)
 \end{equation}
-
-%\begin{equation}
-%    MLE = -\frac{1}{2} (MLE_{\rm real} + MLE_{\rm imag}),
-%\end{equation}
-
-%\begin{equation}
-%    MLE_{\rm real} = \sum_{u, v} \frac{[Re(V_{\rm ALMA}) - Re(V_{\rm
-%    model})]^2}{\sigma^2} + log(2 \pi \sigma^2), 
-%\end{equation}
-
-%\begin{equation}
-%    MLE_{\rm imag} = \sum_{u, v} \frac{[Im(V_{\rm ALMA}) - Im(V_{\rm
-%    model})]^2}{\sigma^2} + log(2 \pi \sigma^2),
-%\end{equation}
 
@@
 870$\,\mu$m, $\mu_{870}$, for each source.  This is done simply by taking the
-ratio of the total flux density in the lensed image of the model ($S_{\rm out}$
-to the total flux density in the unlensed, intrinsic source model ($S_{\rm
-in}$).  The use of an aperture when computing $\mu_{870}$ is important when
-source profiles are used with significant flux at large radii (e.g., some types
-of S\'ersic profiles).  For an elliptical Gaussian, such a step is unneccessary
-(note that we did test this and found only $\approx 10\%$ difference between
-$\mu_{870}$ computed with and without an aperture.  The best-fit value and
-1$\sigma$ uncertainty on $\mu_{870}$ are drawn from the posterior PDF, as with
-the other parameters of the model.
+ratio of the total flux density in the lensed image of the model ($S_{\rm
+out}$) to the total flux density in the unlensed, intrinsic source model
+($S_{\rm in}$).  The use of an aperture when computing $\mu_{870}$ is important
+when source profiles are used with significant flux at large radii (e.g., some
+types of S\'ersic profiles).  For an elliptical Gaussian, such a step is
+unneccessary (note that we did test this and found only $\approx 10\%$
+difference between $\mu_{870}$ computed with and without an aperture).  The
+best-fit value and 1$\sigma$ uncertainty on $\mu_{870}$ are drawn from the
+posterior PDF, as with the other parameters of the model.  Exceptions are made
+for cases of weakly lensed sources where we have only upper limits on the
+Einstein radius (and hence upper limits on $\mu_{870}$).  In such instances, we
+re-compute $\mu_{870}$ as the arithmetic mean of the limiting $\mu_{870}$ and
+unity: $\mu_{870} = (\mu_{\rm 870-limit} + 1) / 2$.  The uncertainty in
+$\mu_{870}$ is assumed to be equal to $\mu_{\rm 870-limit} - 1) / 2$.
 
@@
 {\bf HELAISS02:} Four sources are detected by ALMA, all of which are weakly
-lensed by a foreground galaxy seen in the {\it HST} image.  We assume an
-Einstein radius of $1\farcs5$ for the lens as larger values begin to predict
-counter images that are not seen by ALMA.  The magnification factors reported
-here should be regarded as upper limits since we do not have strong constraints
-on the lower limit of the Einstein radius of the lens (e.g., the magnication
-factor for the source that is directly south of the lens is reported here to
-have $\mu_{870} = 1.68 \pm 0.06$, but values as small as 1.1-1.2 are likely
-plausible as well).  The ALMA sources are all detected by IRAC and their mid-IR
-colors are similar, suggesting they lie at the same redshift (see
-Figure~\ref{fig:iraccolor}).
+lensed by a foreground galaxy seen in the {\it HST} image.  To estimate the
+maximal magnification factor, we assume an Einstein radius of $1\farcs5$ for
+the lens (larger values predict counter images that are not seen by ALMA).  The
+ALMA sources are all detected by IRAC and their mid-IR colors are similar,
+suggesting they lie at the same redshift (see Figure~\ref{fig:iraccolor}).
 
@@
 foreground galaxy seen in the {\it HST} image.  The lensed source is not
-detected in the {\it HST} image.  This object also has high quality SMA imaging
-and an accompanying lens model that produces consistent results with those
-given here \citep{Bussmann:2013lr}.
+detected in the {\it HST} image.  This object was first detected by
+\citet{Ikarashi:2011qy} and also has high quality SMA imaging and an
+accompanying lens model that produces consistent results with those given here
+\citep{Bussmann:2013lr}.
 
@@
 
-{\bf HXMM01:} Three sources are detected by ALMA, all of which are weakly lensed
-by two foreground galaxies seen in the {\it HST} and Keck/NIRC-II imaging.  The
-ALMA imaging is broadly consistent with SMA data originally presented in
-\citet{Fu:2013lr}, with two bright sources and a much fainter third source very
-close to the more southern bright source.  We assume Einstein radii of
-$0\farcs5$ for both lenses to reproduce the approach used in \citet{Fu:2013lr}.
-This results in magnification factors for the three sources of $\mu_{870}
-\approx 1.6 - 1.7$, similar to \citet{Fu:2013lr}.
+{\bf HXMM01:} Three sources are detected by ALMA, all of which are weakly
+lensed by two foreground galaxies seen in the {\it HST} and Keck/NIRC-II
+imaging.  The ALMA imaging is broadly consistent with SMA data originally
+presented in \citet{Fu:2013lr}, with two bright sources and a much fainter
+third source very close to the more southern bright source.  We assume Einstein
+radii of $0\farcs5$ for both lenses in order to reproduce the approach used in
+\citet{Fu:2013lr}.  This results in magnification factors for the three sources
+of $\mu_{870} \approx 1.6 - 1.7$, consistent with \citet{Fu:2013lr}.
 
@@
 $0\farcs5$ to represent the ``maximal lensing'' scenario.  Due to the
-elliptical nature of the lens, this results in a magnification factor of
-$\mu_{870} = 3.72 \pm 0.42$.  The {\it HST} morphology is complex: diffuse
+elliptical nature of the lens, this results in a maximum magnification factor of
+$\mu_{\rm 870-limit} = 3.72 \pm 0.42$.  The {\it HST} morphology is complex: diffuse
 emission to the north of the lens could be a detection of the background source
@@
 
-{\bf HXMM09:} Two sources are detected by ALMA, both of which are weakly
-lensed by a single foreground galaxy detected in the {\it HST} image.  An Einstein
+{\bf HXMM09:} Two sources are detected by ALMA, both of which are weakly lensed
+by a single foreground galaxy detected in the {\it HST} image.  An Einstein
 radius of $1\farcs5$ is used to represent the ``maximal lensing'' scenario and
-results in magnification factors of $\mu_{870} = 2.25 \pm 0.17$ and $\mu_{870}
-= 1.48 \pm 0.09$.
-
-{\bf HXMM03:} Three sources are detected by ALMA, all of which are weakly lensed
-by a foreground galaxy detected in the {\it HST} image and located $\approx
-6\arcsec$ from the ALMA sources.  The central source is much brighter than the
-other two sources, which makes fitting a model challenging.  We forced the
-positions of the second and third sources to be at least $0\farcs5$ and
+results in maximal magnification factors of $\mu_{\rm 870-limit} = 2.25 \pm
+0.17$ and $\mu_{\rm 870-limit} = 1.48 \pm 0.09$.
+
+{\bf HXMM03:} Three sources are detected by ALMA, all of which are weakly
+lensed by a foreground galaxy detected in the {\it HST} image and located
+$\approx 6\arcsec$ from the ALMA sources.  The central source is much brighter
+than the other two sources, which makes fitting a model challenging.  We forced
+the positions of the second and third sources to be at least $0\farcs5$ and
 $-0\farcs5$ away from the first source in declination, respectively.
@@
 isolated galaxies in this sample and in \citet{Bussmann:2013lr}.  Because the
-source is so far from the lens, the magnification factor is only $\mu_{870} =
-1.19 \pm 0.01$.
-
-{\bf HXMM11:} Two sources are detected by ALMA, both of which are weakly lensed.
-This system is similar to HADFS08, although the two ALMA sources are much closer
-and the lens must be less massive in order to avoid producing multiple images
-of the closest ALMA source.  The fainter ALMA source has a much lower
-magnification factor than the brighter source ($\mu_{870} = 1.10 \pm 0.01$ vs.
-$\mu_{870} = 1.63 \pm 0.11$).  As with HADFS08, we caution that these
-magnification factors represent the ``maximal lensing'' scenario and hence
-should be considered upper limits.  Both ALMA sources are detected by IRAC and
-have similar mid-IR colors, suggesting they lie at a similar redshift (see
-Figure~\ref{fig:iraccolor}).
+source is so far from the lens, the maximal magnification factor is only
+$\mu_{\rm 870-limit} = 2.0 \pm 0.1$.
+
+{\bf HXMM11:} Two sources are detected by ALMA, both of which are weakly
+lensed.  This system is similar to HADFS08, although the two ALMA sources are
+much closer and the lens must be less massive in order to avoid producing
+multiple images of the closest ALMA source.  The fainter ALMA source has a much
+lower maximal magnification factor than the brighter source ($\mu_{\rm
+870-limit} = 1.10 \pm 0.01$ vs.  $\mu_{\rm 870-limit} = 1.63 \pm 0.11$).  Both
+ALMA sources are detected by IRAC and have similar mid-IR colors, suggesting
+they lie at similar redshifts (see Figure~\ref{fig:iraccolor}).
 
@@
 {\bf HXMM05:} One source is detected by ALMA, and it is weakly lensed by two
-foreground galaxies seen in the {\it HST} images.  We assume an Einstein radius
-of 1$\arcsec$ for the foreground lenses and fix the positions of both lenses
-according to the location of the foreground galaxies in the {\it HST} image.
-As with HXMM11, this is the ``maximal lensing'' scenario, so our magnification
-measurement of $\mu_{870} = 1.80 \pm 0.16$ should be considered an upper limit.
+foreground galaxies seen in the {\it HST} images.  To compute the maximum
+magnification factor, we assume an Einstein radius of 1$\arcsec$ for the
+foreground lenses and fix the positions of both lenses according to the
+location of the foreground galaxies in the {\it HST} image.
 
@@
 south and $4\farcs5$ east of the image centroid and having an Einstein radius
-of $2\farcs0$.  This is meant to represent the ``maximal lensing'' scenario, so
-our measurement of $\mu_{870}$ should be regarded as an upper limit.  The
-presence of two $3\sigma$ peaks located near the center of the residual image
-indicates that the model does not fit the data perfectly.  This could be an
-indication that either of our assumptions for the lens potential or source
+of $2\farcs0$.  This is meant to represent the ``maximal lensing'' scenario.
+The presence of two $3\sigma$ peaks located near the center of the residual
+image indicates that the model does not fit the data perfectly.  This could be
+an indication that either of our assumptions for the lens potential or source
 structure are oversimplifications.  Higher resolution imaging is needed to
@@
 
-{\bf HECDFS12:} This is a complex, well-constrained system.  Two sources
-are detected by ALMA: one is strongly lensed and the other is weakly lensed.
-In addition, the lens is detected by ALMA (this is one of two sources in the
-entire ALMA sample that is unresolved by ALMA).  These facts work together to
-provide very tight constraints on the system.  Since the lens is detected by
-ALMA, its position relative to the lensed images is unambiguous.  Also, because
-there is a strongly lensed source with multiple images, the Einstein radius of
-the lens is unambiguous.  A byproduct of these two facts is that the
-magnification factor of the weakly lensed source is known to very high
+{\bf HECDFS12:} This is a complex, well-constrained system.  Two sources are
+detected by ALMA: one is strongly lensed and the other is weakly lensed.  In
+addition, the lens is detected by ALMA (this is one of two sources in the
+entire {\it Herschel}-ALMA sample that is unresolved by ALMA).  These facts
+work together to provide very tight constraints on the system.  Since the lens
+is detected by ALMA, its position relative to the lensed images is unambiguous.
+Also, because there is a strongly lensed source with multiple images, the
+Einstein radius of the lens is unambiguous.  A byproduct of these two facts is
+that the magnification factor of the weakly lensed source is known to very high
 precision as well.  It experiences a magnification factor of $\mu_{870} =
 1.520\pm0.002$ despite being located $\approx4\arcsec$ north of the lens (which
-has an Einstein radius of $1.353\pm0.005$).  We use these numbers to inform our
-estimates of the Einstein radius for weakly lensed sources without the
-excellent contraints provided by this system.  Finally, this source is detected
-(and unresolved) in the NRAO VLA Sky Survey \citep{Condon:1998uq}, having
-$S_{\rm 1.4\,GHz} = 21.8 \pm 0.8\,$mJy.  Assuming all of this radio emission
-originates from the lens, this implies a spectral slope of $\alpha = -0.24$ and
-is consistent with non-thermal emission from the lens.
+has an Einstein radius of $1.353\pm0.005$; it is the tight constraint on the
+Einstein radius that permits such a tight constraint on $\mu_{870}$ for the
+weakly lensed source).  We use these numbers to inform our estimates of the
+Einstein radius for weakly lensed sources without the excellent contraints
+provided by this system.  Finally, this source is detected (and unresolved) in
+the NRAO VLA Sky Survey \citep{Condon:1998uq}, having $S_{\rm 1.4\,GHz} = 21.8
+\pm 0.8\,$mJy.  Assuming all of this radio emission originates from the lens,
+this implies a spectral slope of $\alpha = -0.24$ and is consistent with
+non-thermal emission from the lens.
 
@@
 lensed by a foreground galaxy seen in the {\it HST} image.  There is also a
-3$\sigma$ peak coincident with {\it HST} source that may be an indication that
-the lens has been detected by ALMA.  We do not attempt to model this 3$\sigma$
-peak.  We assume an Einstein radius of $0\farcs5$ for the lens, since larger
-values predict the existence of counter images that are not seen by ALMA.  The
-second ALMA source is located $\approx5\arcsec$ from the lens and experiences a
-small but significant magnification of $\mu_{870} = 1.12 \pm 0.02$.  Both ALMA
-sources appear to be detected by IRAC and have similar mid-IR colors, suggesting
-they lie at the same redshift (see Figure~\ref{fig:iraccolor}).
+3$\sigma$ peak coincident with an {\it HST} source that may be an indication
+that the lens has been detected by ALMA.  We do not attempt to model this
+3$\sigma$ peak.  We assume an Einstein radius of $0\farcs5$ for the lens, since
+larger values predict the existence of counter images that are not seen by
+ALMA.  The second ALMA source is located $\approx5\arcsec$ from the lens and
+experiences a small but significant magnification of $\mu_{\rm 870-limit} =
+1.12 \pm 0.02$.  Both ALMA sources appear to be detected by IRAC and have
+similar mid-IR colors, suggesting they lie at the same redshift (see
+Figure~\ref{fig:iraccolor}).
 
@@
 source is brighter than the other by a factor of 2.  Assuming the two sources
-have similar mass to light ratios, their brightness ratios indicate major
+have similar mass-to-light ratios, their brightness ratios indicate major
 merger rather than minor merger activity.  The projected physical distance is
-$\approx 2-3$kpc, assuming a redshift of $z=2$ for the ALMA sources.  This
+$\approx 2-3\,$kpc, assuming a redshift of $z=2$ for the ALMA sources.  This
 could be an example of a major merger approaching final coalescence and
@@
 HADFS02 represents a major merger that just experienced a first pass or is
-approaching final coalescence, either of which significantly enhanced
+approaching final coalescence, either of which would significantly enhance
 star-formation in the system.
@@
 {\bf HADFS11:} Two sources are detected by ALMA, both of which are weakly
-lensed by a group of small galaxies detected in the {\it HST} image.  We
-represent the gravitational potential of the group with a single SIE lens and
-an Einstein radius of $1\farcs0$.  Values larger than this produce additional
-counter images that are not seen in the ALMA imaging.  We cannot rule out
-smaller Einstein radii, but we consider these unlikely given the number of
-sources and their brightness in the {\it HST} image.
-
-{\bf HADFS10:} Three sources are detected by ALMA.  In this paper, we have
-assumed that all three are unlensed.  There is a group of three sources
+lensed by a group of small galaxies detected in the {\it HST} image.  To
+estimate the maximum magnification factor, we represent the gravitational
+potential of the group with a single SIE lens and an Einstein radius of
+$1\farcs0$.  Values larger than this produce additional counter images that are
+not seen in the ALMA imaging.
+
+{\bf HADFS10:} Three sources are detected by ALMA.  We 
+assume that all three are unlensed.  There is a group of three sources
 detected in our Gemini-S optical imaging located $\approx 7\arcsec$ east of the
 ALMA sources.  This distance is so large that plausible mass ranges for the
-Gemini-S sources would imply at most a factor of 1.1-1.2 boost in the apparent
+Gemini-S sources would imply at most a factor of 1.1$-$1.2 boost in the apparent
 flux densities of the ALMA sources.
@@
 galaxy seen in the {\it HST} image.  The lensed source is not detected by {\it
-HST}.  The source is highly elongated ($q_s = 0.31 \pm 0.01$), but fits the
+HST}.  The source is highly elongated ($q_{\rm s} = 0.31 \pm 0.01$), but fits the
 data very well.  The position of the lens according to the lens model is
-consistent with the position in the {\it HST} image given the $0\farcs4$
+consistent with the position in the {\it HST} image, given the $0\farcs4$
 fundamental uncertainty due to using the 2MASS system as the fundamental basis
@@
 
-{\bf HADFS08:} Two sources are detected by ALMA, both of which are weakly lensed
-by a foreground galaxy in the {\it HST} image.  The ALMA sources have the
-largest separation of any in our sample overall: $\approx 10\arcsec$.  We
+{\bf HADFS08:} Two sources are detected by ALMA, both of which are weakly
+lensed by a foreground galaxy in the {\it HST} image.  The ALMA sources have
+the largest separation of any in our sample overall, around $10\arcsec$.  We
 assume an Einstein radius of $1\farcs5$ for the foreground lens as a ``maximal
-lensing'' scenario.  This results in magnification factors of $\mu_{870} = 2.3
-\pm 0.1$ and $\mu_{870} = 1.2 \pm 0.1$ for the two sources.  Our constraints on
-the true Einstein radius of the lens are weak, so these values for $\mu_{870}$
-should be regarded as upper limits.
+lensing'' scenario.  This results in maximum magnification factors of $\mu_{\rm
+870-limit} = 2.3 \pm 0.1$ and $\mu_{\rm 870-limit} = 1.2 \pm 0.1$ for the two
+sources.
 
@@
 (the rms error in the astrometry is set from 2MASS at a level of $\approx
-0\farcs4$) as well as the unusual location and fluxes of the ALMA sources
-relative to each other.  We assume an Einstein radius of $0\farcs5$ and fix the
-position angle of the lens to be between 40-50 degrees to match the orientation
-seen in the {\it HST} image.  Larger Einstein radii can be ruled out by the
-absence of counter images north of the lens.
+0\farcs4$) as well as the atypical location and fluxes of the ALMA sources
+relative to each other.  To obtain the maximum magnification factor, we assume
+an Einstein radius of $0\farcs5$ and fix the position angle of the lens to be
+between 40-50$\,^\circ$ to match the orientation seen in the {\it HST} image.
+Larger Einstein radii can be ruled out by the absence of counter images north
+of the lens.
 
@@
 {\bf HCOSMOS02:} Five sources are detected by ALMA \citep[the brightest of
-which has already been detected;][]{Smolcic:2012zl}, none of which appear to be
+which was already known;][]{Smolcic:2012zl}, none of which appear to be
 lensed.  Previous research has shown this to be an overdense region \citep[this
@@
 magnification is important in this object.  The very small sizes of the sources
-are consistent with this as well ($r_s = 0.023 \pm 0.003\arcsec$, Keck and $r_s
-= 0.055 \pm 0.007\arcsec$, ALMA).  Adopting a redshift of $z=2$ for the lensed
-source implies physical sizes of $\approx 150\,$pc and $\approx 300\,$pc for
-the rest-frame optical and rest-frame FIR, respectively.
+are consistent with this as well ($r_{\rm s} = 0.023 \pm 0.003\arcsec$, Keck
+and $r_{\rm s} = 0.055 \pm 0.007\arcsec$, ALMA).  Adopting a redshift of $z=2$
+for the lensed source implies physical sizes of $\approx 150\,$pc and $\approx
+300\,$pc for the rest-frame optical and rest-frame FIR, respectively.
 
@@
 
-\caption{ Model fits for each target in the ALMA sample, 3 panels per target.
+\caption{ Model fits for each target in the {\it Herschel}-ALMA sample, 3 panels per target.
 {\it Left}: ALMA 870$\mu$m imaging (red contours, starting at $\pm 3\sigma$ and
@@
 3.6$\,\mu$m, green = 4.5$\,\mu$m, red = 8.0$\,\mu$m).  All panels are $9\farcs5$
-on a side.  North is up and east is left.  The synthesize beam is represented in
+on a side.  North is up and east is left.  The synthesized beam is represented in
 the lower right corner of each panel.  Each of the ALMA counterparts are
@@
 estimate the impact that lensing has on the intrinsic properties of the ALMA
-sources.  In other words, we can ``de-lens'' the ALMA sample.
+sources.  In other words, we can ``de-lens'' the {\it Herschel}-ALMA sample.
 
 Figure~\ref{fig:delens} shows the observed (i.e., apparent) and intrinsic
-(i.e., de-lensed) distributions of $S_{870}$, $r_s$, angular separation, and
-$q_s$.  Here, angular separation is the angular distance between an ALMA source
-and the centroid of all the ALMA sources for a given {\it Herschel} DSFG.
-Lensing has the strongest effect on $S_{870}$: the median flux density in the
-ALMA sample drops by a factor of 1.6 when lensing is taken into account, and a
-two-sided Kolmogorov-Smirnov (KS) test yields a $p$-value of 0.044.  Even
-if strongly lensed sources are removed from the sample, the median intrinsic
-flux density is 1.3 times lower than the median apparent flux density.  If we
-only consider examples of weak lensing (i.e., removing the unlensed sources),
-the factor rises back to 1.6.  These factors will be significant sources of
-error if they are incorrectly ignored.  When discussing the intrinsic
-properties of bright sources discovered in wide-field FIR or mm surveys, it
-is critical to consider the effects of lensing.
+(i.e., de-lensed) distributions of $S_{870}$, $r_{\rm s}$, angular separation,
+and $q_{\rm s}$.  Here, angular separation is the angular distance between an
+ALMA source and the centroid of all the ALMA sources for a given {\it Herschel}
+DSFG.  Lensing has the strongest effect on $S_{870}$: the median flux density
+in the {\it Herschel}-ALMA sample drops by a factor of 1.6 when lensing is
+taken into account. A two-sided Kolmogorov-Smirnov (KS) test yields a $p$-value
+of 0.044, suggesting the apparent and intrinsic flux density distributions are
+inconsistent with being drawn from the same parent population.  Even if
+strongly lensed sources are removed from the sample, the median intrinsic flux
+density is 1.3 times lower than the median apparent flux density.  If we only
+consider examples of weak lensing (i.e., removing the unlensed sources), the
+factor rises back to 1.6.  These factors will be significant sources of error
+if they are incorrectly ignored.  When discussing the intrinsic properties of
+bright sources \citep[including their luminosity functions,
+e.g.][]{Wyithe:2011rm} discovered in wide-field FIR or mm surveys, it is
+critical to consider the effects of lensing.
 
@@
 the DSFGs in ALESS.  This difference is likely due to differences in dust
-temperature and/or redshift distributions of the two samples and likely arises
+temperature and/or redshift distributions of the two samples and probably arises
 from selection effects.
 
-The effect on the other source parameters ($r_s$, angular separation, and
-$q_s$) is less pronounced.  The median source size decreases by a factor of 1.2
-in the ALMA sample after accounting for lensing, but the two-sided KS test
+The effect on the other source parameters ($r_{\rm s}$, angular separation, and
+$q_{\rm s}$) is less pronounced.  The median source size decreases by a factor of 1.2
+in the {\it Herschel}-ALMA sample after accounting for lensing, but the two-sided KS test
 reveals a $p$-value of 0.174, suggesting that we cannot rule out the null
@@
 distribution.  We find no significant difference between the axial ratios of
-the apparent and intrinsic distributions as well as between the angular
+the apparent and intrinsic distributions, as well as between the angular
 separations of apparent and intrinsic distributions (two-sided KS test
@@
 
-Finally, the brightest single source in the ALMA sample is HXMM03-Source0, with
-an intrinsic flux density of $S_{870} = 15.42 \pm 0.43\,$mJy.  However, there
-are also two objects with multiple sources that have separations smaller than
-1$\arcsec$ that have summed flux densities comparable to this: HADFS02
-(15.3$\,$mJy) and HECDFS13 (14.1$\,$mJy).  This is approaching the values found
-in the most extreme systems, such as GN20
+Finally, the brightest single source in the {\it Herschel}-ALMA sample is
+HADFS11.0, with an intrinsic flux density of $S_{870} = 17.5 \pm
+0.4\,$mJy.  However, there are also two objects with multiple sources that
+have separations smaller than 1$\arcsec$, which have summed flux densities
+comparable to this; namely HADFS02 (16.8$\,$mJy) and HECDFS13 (15.3$\,$mJy).  This is
+approaching the values found in the most extreme systems, such as GN20
 \citep[20.6$\,$mJy,][]{2006MNRAS.370.1185P} and HFLS3
@@
 \caption{ Cumulative distribution functions showing the effect of lensing on
-the inferred properties of the ALMA sample, including: flux densities (far left
+the inferred properties of the {\it Herschel}-ALMA sample, including: flux densities (far left
 panel), effective radii (middle left panel), angular separation from centroid
 (middle right panel), and axial ratio (far right panel).  The median flux
-density in the ALMA sample drops by a factor of 1.3 when lensing is taken into
+density in the {\it Herschel}-ALMA sample drops by a factor of 1.3 when lensing is taken into
 account.  } \label{fig:delens}
@@
 multiplicty rate increases to 80\%.  Such a high rate of multiplicity is
-consistent with theoretical models \citep{HN13, HB13}.
+consistent with theoretical models \citep[e.g.,][]{HN13, HB13}.
 
 In comparison, the 69 DSFGs in the MAIN ALESS catalog show a multiplicity rate
-of 35\% - 40\% \citep{Hodge:2013qy}.  Smoothing our ALMA images and adding
+of 35 - 40\% \citep{Hodge:2013qy}.  Smoothing our ALMA images and adding
 noise to match the resolution and sensitivity of ALESS results in a
-multiplicity rate of 55\% (4 objects with sources that are separated by
+multiplicity rate of 55\% (four objects with sources that are separated by
 $<1\arcsec$ become single systems).  The redshift distributions for sources
@@
 our sample has somewhat bluer colors on average than a strictly 500$\,\mu$m
-selected sample and is therefore likely to have a slightly lower mean redshift.
+selected sample and is therefore likely to have a lower mean redshift.
 On the other hand, the ALESS sources are much fainter overall, having a median
-870$\,\mu$m flux density of $S_{870} \approx 6\,$mJy compared to $S_{870}
-=14.9\,$mJy in our ALMA sample.  Thus, the evidence favors brighter sources
+870$\,\mu$m flux density of $S_{870} \approx 6\,$mJy, compared to $S_{870}
+=14.9\,$mJy in our {\it Herschel}-ALMA sample.  Thus, the evidence favors brighter sources
 having a higher multiplicity rate.  This result is also consistent with
@@
 870$\,\mu$m flux density, $S_{\rm component}$.  Figure~\ref{fig:componentflux}
-shows these values for our ALMA sample and compares to ALESS.  Lensing has a
+shows these values for our {\it Herschel}-ALMA sample and compares to ALESS.  Lensing has a
 significant impact on the apparent flux densities of many objects in our ALMA
@@
 with increasing $S_{\rm total}$ \citep{Hodge:2013qy}.  A simple extrapolation
-of this phenomenon to the flux density regime probed by our ALMA sample would
+of this phenomenon to the flux density regime probed by our {\it Herschel}-ALMA sample would
 have suggested a very high multiplicity rate and a very low average fractional
@@
 component}$).  The solid lines trace the average ratio of component to total
-flux for a given total flux.  Our sample of {\it Herschel} DSFGs (ALMA sample,
+flux for a given total flux.  Our sample of {\it Herschel} DSFGs ({\it
+Herschel}-ALMA sample,
 green squares) has a higher multiplicity and a lower average factional
@@
 We can dig further into our ALMA data by exploring the average number of ALMA
-sources per annular area ($dN/dA$) as a function of how far they are from
-each other.  Figure~\ref{fig:dNdA} shows the results of this analysis for both
-our ALMA sample and ALESS.  We formulate the separation as an angular distance
-between each ALMA source and the centroid of all of the ALMA sources for that
-{\it Herschel} DSFG.  This is different from \citet{Hodge:2013qy}, who use a
-simple pairwise separation distance estimator, a method that becomes
-ill-defined when there are more than 2 ALMA counterparts (as is often the case
-in our ALMA sample).  Figure~\ref{fig:dNdA} shows $dN/dA$ values for ALESS that
-have been re-computed using our method.  We also show the median and 1$\sigma$
-range found from simulated datasets for both ALESS and our ALMA sample.  The
+sources per annular area ($dN/dA$) as a function of how far they are from each
+other.  Figure~\ref{fig:dNdA} shows the results of this analysis for both our
+{\it Herschel}-ALMA sample and ALESS.  We formulate the separation as an
+angular distance between each ALMA source (using the lensing-corrected data)
+and the centroid of all of the ALMA sources for that {\it Herschel} DSFG.  This
+is different from the pairwise separation distance estimator used by
+\citet{Hodge:2013qy} that becomes ill-defined when there are more than two ALMA
+counterparts (as is often the case in our {\it Herschel}-ALMA sample).
+Figure~\ref{fig:dNdA} shows $dN/dA$ values for ALESS that have been re-computed
+using our method.  We also show the median and 1$\sigma$ range found from
+simulated datasets for both ALESS and our {\it Herschel}-ALMA sample.  The
 simulated datasets consist of 200 runs of DSFGs with the same flux density and
@@
 there is a dramatic rise in $dN/dA$ for angular separations less than
-$2\arcsec$ in our ALMA sample.  Indeed, for an angular separation of
+$2\arcsec$ in our {\it Herschel}-ALMA sample.  Indeed, for an angular separation of
 $0\farcs5$, we find an excess in $dN/dA$ by a factor of $\approx 10$ compared
@@
 \caption{ {\it Left}: Spatial distribution of sources with multiple counterparts
-found in our ALMA sample (green squares), in ALESS (pink diamonds), and in mock
-catalogs from \citet{HB13} (color scale).  Sources identified in our ALMA sample
+found in our {\it Herschel}-ALMA sample (green squares), in ALESS (pink diamonds), and in mock
+catalogs from \citet{HB13} (color scale).  Sources identified in our {\it
+Herschel}-ALMA sample
 lie much closer to each other than they do in either ALESS or the \citet{HB13}
@@
 sample (thick green line), ALESS (thick pink line), the \citet{HB13} simulations
-(thick blue line), and our ALMA sample as would have been seen with ALESS
+(thick blue line), and our {\it Herschel}-ALMA sample as would have been seen with ALESS
 resolution and sensitivity (thick orange line).  We also show the range of
@@
 ALMA field of view (green hatched region with solid and dashed green lines).
-The DSFGs in our ALMA sample show a much stronger excess on angular separation
+The DSFGs in our {\it Herschel}-ALMA sample show a much stronger excess on angular separation
 scales $<2\arcsec$ compared to ALESS and the \citet{HB13} simulations, even when
@@
 
-An excess of sources with small separations from each other could be a signpost
-of interacting or merging systems.  However, it is also possible that the
-sources are merely unrelated galaxies that appear blended due to projection
-effects \citep{HB13}.  Spatially resolved spectroscopy is necessary to answer
-this question definitely, but is not currently available.  Instead, to
-investigate these possibilities further, we make use of mock catalogs of DSFGs
-that are based on numerical simulations and presented by \citet{HB13}.  We
-summarize the methodology used to generate $dN/dA$ values from the mock catalogs
-here and refer the reader to \citet{HB13} for full details.
+An excess of sources with small separations from each other could be an
+indication of interacting or merging systems.  However, it is also possible
+that the sources are merely unrelated galaxies that appear blended due to
+projection effects \citep{HB13}.  Spatially resolved spectroscopy is necessary
+to answer this question definitely, but is not currently available.  Instead,
+to investigate these possibilities further, we make use of mock catalogs of
+DSFGs that are based on numerical simulations and presented by \citet{HB13}.
+We summarize the methodology used to generate $dN/dA$ values from the mock
+catalogs here and refer the reader to \citet{HB13} for full details.
 
@@
 a projected angular distance $d_{\rm neighbor}$.  To obtain a direct comparison
-with our ALMA sample, we use $S_{\rm thresh} = 1.0\,$mJy (corresponding to the
+with our {\it Herschel}-ALMA sample, we use $S_{\rm thresh} = 1.0\,$mJy (corresponding to the
 5$\sigma$ limit of the ALMA data) and $d_{\rm neighbor} = 40\arcsec$
@@
 centroid and separations for every blended source using the same methodology as
-we applied to our ALMA sample and to ALESS.
+we applied to our {\it Herschel}-ALMA sample and to ALESS.
 
@@
 $dN/dA$ on separations smaller than $\approx 0\farcs5$, but the amplitude of
-the increase is much lower than what is apparent in our ALMA sample.
+the increase is much lower than is apparent in our {\it Herschel}-ALMA sample.
 
@@
 
-The \citet{HB13} model does not include SFR elevations induced by starbursts
-(see section 4.5 of \citealt{HB13} for a detailed discussion of this
+The \citet{HB13} model does not include SFR enhancements induced by starbursts
+(see Section 4.5 of \citealt{HB13} for a detailed discussion of this
 limitation). To explore whether interaction-induced starbursts are the origin
-of the excess at small angular separations observed in our ALMA sample, we
+of the excess at small angular separations observed in our {\it Herschel}-ALMA sample, we
 modified the \citet{HB13} model to include a crude treatment of
-interaction-induced SFR elevation. Mock galaxies with one or more neighbors
+interaction-induced SFR enhancement. Mock galaxies with one or more neighbors
 within a physical distance of 5$\,$kpc and with a stellar mass between
 one-third and three times that of the galaxy under consideration (i.e.  a
-`major merger') had their SFR increased by a factor of two. For distances
+`major merger') had their SFRs increased by a factor of two. For distances
 smaller than 1$\,$kpc, the imposed increase was a factor of ten.  Because these
-SFR elevations are greater than suggested by simulations \citep[e.g.][]{Cox08,
+SFR enhancements are greater than suggested by simulations \citep[e.g.][]{Cox08,
 H11, H14, Torrey12} or observations of local galaxy pairs
@@
 
-Experiments with stronger interaction-induced SFR elevations showed that very
-high elevations (e.g. a factor of 10 for separation of 5-15$\,$kpc and 100 for
-separation of $<5\,$kpc) in major mergers were required to match the observed
-excess in $dN/dA$ on small separations. Incorporating starbursts induced by minor-merger could possibly reduce the required SFR elevations. The tension
+Experiments with stronger interaction-induced SFR enhancements showed that very
+high enhancements (e.g. a factor of 10 for separation of 5-15$\,$kpc and 100 for
+separation of $<5\,$kpc) in major mergers are required to match the observed
+excess in $dN/dA$ on small separations. Incorporating starbursts induced by
+minor-merger could possibly reduce the required SFR enhancements. The tension
 between the model prediction and observations may also indicate that a more
@@
 $\rho_{\rm lens}\,(r)$, the number density of lenses as a function of mass and
-redshift, $n_{\rm lens}\,(M, \, z)$, the redshift distribution of the sources,
+redshift, $n_{\rm lens}\,(M, \, z),$ the redshift distribution of the sources,
 $dN_{\rm source}/dz$, and the intrinsic luminosity function of the sources,
 $dn_{\rm source}/dS_{870}^\prime$.  The latter component is the least certain
-component and also has the strongest impact on the predicted apparent
-luminosity function.  For these reasons, we fix all components of the model
-except the shape of the intrinsic luminosity function.  Our goal is to take
-luminosity functions that can successfully fit observed faint DSFG number
-counts \citep{Karim:2013lr} and test whether they lead to predicted
-magnification factors consistent with our ALMA and SMA observations.
+and also has the strongest impact on the predicted apparent luminosity
+function.  For these reasons, we fix all components of the model except the
+shape of the intrinsic luminosity function.  Our goal is to take luminosity
+functions that can successfully fit observed faint DSFG number counts
+\citep{Karim:2013lr} and test whether they lead to predicted magnification
+factors consistent with our ALMA and SMA observations.
 
 To describe $\rho_{\rm lens}\,(r)$, we use a superposition of a singular
-isothermal sphere (SIS) and a Navarro Frenk White (NFW) profile
+isothermal sphere (SIS) and a Navarro-Frenk-White (NFW) profile
 \citep{Navarro:1997ys} that is truncated at the virial radius.  The NFW profile
-describes the outskirts of dark matter halos better while the SIS profile is
+describes the outskirts of dark matter halos better, while the SIS profile is
 preferred on smaller scales because it correctly fits the observed flat
 rotational curves in galaxies.  We make sure that the resulting probability
-density of lensing, $P\,(\mu)$, is normalized to unity.
-
-To describe $n_{\rm lens}\,(M, \, z)$, we generate abundances of halos at
-each mass and redshift using the \citet{Sheth:1999kx} formalism.
-
-To describe $dN_{\rm source}/dz$, we adopt the following redshift distribution
-which is based on photometric redshifts of optical counterparts to ALMA sources
-identified in ALESS \citep{Simpson:2014lr}:
+density of lensing, $P\,(\mu)$, is normalized to unity.  To describe $n_{\rm
+lens}\,(M, \, z)$, we generate the abundance of halos at each mass and redshift
+using the \citet{Sheth:1999kx} formalism.  To describe $dN_{\rm source}/dz$, we
+adopt the following redshift distribution which is based on photometric
+redshifts of optical counterparts to ALMA sources identified in ALESS
+\citep{Simpson:2014lr} and has been modified to a lower redshift to reflect the
+relatively blue SPIRE colors of the sample:
 
@@
 
-\noindent where $a_z = 1 + z$, $z_\mu = 2.6$, and $\sigma_z = 0.2$.
+\noindent where $a_z = 1 + z$, $z_\mu = 1.5$, and $\sigma_z = 0.2$.
 
@@
 functions are selected to represent the range of observed instrinsic luminosity
-functions for DSFGs which are shown in the left panel of
+functions for DSFGs, which are shown in the left panel of
 Figure~\ref{fig:lensstats} and are drawn from the ALESS survey
@@
 follow-up data in COSMOS \citep{Smolcic:2012zl} and GOODS-N
-\citep{Barger:2012yg} is published, but unknown completeness corrections in the
+\citep{Barger:2012yg} are published, but unknown completeness corrections in the
 single-dish surveys on which these follow-up datasets are based precludes their
-usage here.
-
-The Shechter function we use has the usual form \citep{Schechter:1976yq}:
+use here.
+
+The Shechter function we adopt has the usual form \citep{Schechter:1976yq}
 
 \begin{equation}
-\frac{dn}{dS^\prime} = \frac{n_\star}{S_\star}
-\left(\frac{S^\prime}{S_\star}\right)^{-\alpha}
-\exp\left(\frac{-S^\prime}{S_\star}\right),
+\frac{dn}{dS^\prime} = \frac{n_\ast}{S_\ast}
+\left(\frac{S^\prime}{S_\ast}\right)^{-\alpha}
+\exp\left(\frac{-S^\prime}{S_\ast}\right),
 \end{equation}
 
-\noindent while the broken power-law has the form:
+\noindent while the broken power-law has the form
 
 \begin{equation}
-\frac{dn}{dS^\prime} = N_\star\left(\frac{S^\prime}{S_\star}\right)^{-\beta_1},~~~~\textrm{for}~S<S_\star,
+\frac{dn}{dS^\prime} = N_\ast\left(\frac{S^\prime}{S_\ast}\right)^{-\beta_1},~~~~\textrm{for}~S<S_\ast,
 \end{equation}
@@
 \begin{displaymath}
-\frac{dn}{dS^\prime} = N_\star\left(\frac{S^\prime}{S_\star}\right)^{-\beta_2},~~~~\textrm{for}~S>S_\star.
+\frac{dn}{dS^\prime} = N_\ast\left(\frac{S^\prime}{S_\ast}\right)^{-\beta_2},~~~~\textrm{for}~S>S_\ast.
 \end{displaymath}
@@
 In Table~\ref{tab:models}, we provide information for three models tested in
-this paper: the steepest plausible Schechter function, the \citet{Karim:2013lr}
-broken power-law, and a broken power-law with an even steeper fall-off at
-higher flux densities than used in \citet{Karim:2013lr}.
+this paper: the steepest plausible Schechter function; the \citet{Karim:2013lr}
+broken power-law; and a broken power-law with a brighter break point ($S_\ast =
+15\,$mJy) than used in \citet{Karim:2013lr}.
 
@@
 can compute the average magnification as a function of $S_{870}$ from the data:
-$<\mu_{870}>$.  The same quantity can also be directly computed from our
-model as:
+$\langle\mu_{870}\rangle$.  The same quantity can also be directly computed from our
+model as
 
 \begin{equation}
-    <\mu_{870}> = \int_0^\infty \mu P(\mu|S_{870})  d\mu,
+    \langle\mu_{870}\rangle = \int_0^\infty \mu P(\mu|S_{870})  d\mu,
  \end{equation}
@@
 The middle panel of Figure~\ref{fig:lensstats} shows a direct comparison of the
-measured $\mu_{870}$ values as a function of apparent $S_{870}$ for the ALMA
-and SMA samples.  We also show a running average of the combined sample
-(considering only $\mu_{870} > 1.1$ objects, since this is the level at which
-magnification effects become as significant as absolute calibration
-uncertainties) to serve as a direct comparison to our theoretical models.  We
-compute this by interpolating the observed $\mu_{870}$ and $S_{870}$ onto a
-fine grid using the Scipy {\sc griddata} package and then smoothing the
-resulting grid using a Gaussian filter (specifically, the Scipy {\sc
-gaussian\_filter} package).  Also shown in this diagram are model predictions
-for the average magnification as a function of $S_{870}$, $<\mu_{870}>$,
-assuming the three intrinsic luminosity functions for DSFGs described in
-Table~\ref{tab:models}.
+measured $\mu_{870}$ values as a function of apparent $S_{870}$ for the {\it
+Herschel}-ALMA and {\it Herschel}-SMA samples.  We also show a running average
+of the combined sample (considering only $\mu_{870} > 1.1$ objects, since this
+is the level at which magnification effects become as significant as absolute
+calibration uncertainties) to serve as a direct comparison to our theoretical
+models.  We compute this by interpolating the observed $\mu_{870}$ and
+$S_{870}$ onto a fine grid using the {\sc Scipy} {\sc griddata} package and
+then smoothing the resulting grid using a Gaussian filter (specifically, the
+Scipy {\sc gaussian\_filter} package).  Also shown in this diagram are model
+predictions for the average magnification as a function of $S_{870}$,
+$\langle\mu_{870}\rangle$, assuming the three intrinsic luminosity functions
+for DSFGs described in Table~\ref{tab:models}.
 
@@
 At low apparent flux densities ($S_{870} < 10\,$mJy), all three models are
-broadly consistent with each other as well as with the running average of the
+broadly consistent with each other, as well as with the running average of the
 data, considering the dispersion in the model predictions for $\mu_{870}$ at a
@@
 S_{870} < 70\,$mJy) is where the three model predictions show the largest
-difference in $<\mu_{870}>$.  The steep rise in the running average in this
+difference in $\langle\mu_{870}\rangle$.  The steep rise in the running average in this
 area is best reproduced by the model with the steep broken power-law luminosity
@@
 explanation for this difference is a limitation in the spatial resolution of
-the observations.  In both the ALMA and SMA samples, the spatial resolution is
-$\approx 0\farcs5$.  This is nearly always sufficient to resolve the images of
-the lensed galaxy, but it is not always sufficient to resolve the images
-themselves.  Therefore, it may be the case that the lens models over-predict
-the intrinsic sizes of the lensed galaxies and hence under-predict the
-magnification factors.  For example, the half-light sizes of unlensed DSFGs
-have been found recently to be $\approx 0.8 \,$kpc \citep{Ikarashi:2014nr} and
-$\approx1.2\,$kpc \citep{Simpson:2015ty}.  In contrast, we reported a median
-half-light radius of $1.53\,$kpc in \citet{Bussmann:2013lr}.  If this
-difference is significant, it may also affect the intermediate $S_{870}$
-regime.  A thorough investigation of this possibility is deferred to future
-work.
+the observations.  In both the {\it Herschel}-ALMA and {\it Herschel}-SMA
+samples, the spatial resolution is $\approx 0\farcs5$.  This is nearly always
+sufficient to resolve the images of the lensed galaxy, but it is not always
+sufficient to resolve the images themselves.  Therefore, it may be the case
+that the lens models over-predict the intrinsic sizes of the lensed galaxies
+and hence under-predict the magnification factors.  For example, the half-light
+sizes of unlensed DSFGs have been found recently to be $\approx 0.8 \,$kpc
+\citep{Ikarashi:2014nr} and $\approx1.2\,$kpc \citep{Simpson:2015ty}.  In
+contrast, we reported a median half-light radius of $1.53\,$kpc in
+\citet{Bussmann:2013lr}.  If this difference is significant, it may also affect
+the intermediate $S_{870}$ regime.  A thorough investigation of this
+possibility is deferred to future work.
 
@@
 small separations from each other (reported in Section~\ref{sec:spatialdist}).
-Essentially, if the {\it Herschel} sources have a high multiplicity rate with
+Essentially, if the {\it Herschel} sources have a high multiplicity rate, with
 ALMA counterparts located close to each other, then adding a lens in front of
@@
 significant.  We should then expect to find $\approx 1$ source satisfying
-$S_{870} > 10\,$mJy in a one square degree survey.  This is about a factor of 3
+$S_{870} > 10\,$mJy in a 1$\,$deg$^2$ survey.  This is about a factor of 3
 lower than the best-fit model in \citet{Karim:2013lr} and a factor of 7 lower
@@
         factors of 5-10.  After correcting for amplification, the brightest
-        source in the sample has $S_{870} = 15.42 \pm 0.43\,$mJy.  There
+        source in the sample has $S_{870} = 17.5 \pm 0.4\,$mJy.  There
         is a weak trend towards even higher multiplicity at the highest total
@@
     \item When a {\it Herschel} source comprises multiple ALMA counterparts,
-        these counterparts are located close together.  Their separations are
-        much smaller than ALMA counterparts to ALESS sources as well as
-        simulated sources from \citet{HB13}.  This conclusion remains true even
-        when we degrade our ALMA observations to match the spatial resolution,
-        sensitivity, and {\it uv} coverage of the ALESS observations.
+        these counterparts are typically located within 2$\arcsec$ of each
+        other.  Their separations are much smaller than ALMA counterparts to
+        ALESS sources as well as simulated sources from \citet{HB13}.  This
+        conclusion remains true even when we degrade our ALMA observations to
+        match the spatial resolution, sensitivity, and {\it uv} coverage of the
+        ALESS observations.
 
@@
         predict somewhat higher average magnification factors than are seen in
-        combined sample of ALMA and SMA lens models.  This latter result coud
+        combined sample of ALMA and SMA lens models.  This latter result could
         be explained by limitations in the spatial resolution of the ALMA and
-        SMA imaging, which might lead to the lens models under-estimating the
+        SMA imaging, which might lead to the lens models underestimating the
         magnification factors.
@@
 resolution.  In addition, molecular spectroscopy will be critical to determine
-distances to individual ALMA sources and hence characterize what fraction of
-{\it Herschel} sources are actually physically associated with each other (and
-not just a function of projection effects along the line of sight).  Molecular
-spectroscopy will also provide critical information about the inter-stellar
-medium in these galaxies, yielding insight into the process of how gas turns
-into stars.
+distances to and dynamics of individual ALMA sources and hence characterize
+what fraction of {\it Herschel} sources are actually physically associated with
+each other (and not just a result of projection effects along the line of
+sight).  %Molecular spectroscopy will also provide critical information about
+%the inter-stellar medium in these galaxies, yielding insight into the process
+%of how gas turns into stars.
 
@@
 
-The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc."
-
-Based on observations obtained at the Gemini Observatory, which is operated by
-the Association of Universities for Research in Astronomy, Inc., under a
-cooperative agreement with the NSF on behalf of the Gemini partnership: the
-National Science Foundation (United States), the National Research Council
-(Canada), CONICYT (Chile), the Australian Research Council (Australia),
-Minist\'erio da Ci\^encia, Tecnologia e Inova\c{c}\~ao (Brazil) and Ministerio
-de Ciencia, Tecnolog\'ia e Innovaci\'on Productiva (Argentina).
+The National Radio Astronomy Observatory is a facility of the National Science
+Foundation operated under cooperative agreement by Associated Universities,
+Inc.  The Dark Cosmology Centre is funded by the Danish National Research
+Foundation.
+
+This paper is partly based on observations obtained at the Gemini Observatory,
+which is operated by the Association of Universities for Research in Astronomy,
+Inc., under a cooperative agreement with the NSF on behalf of the Gemini
+partnership: the National Science Foundation (United States), the National
+Research Council (Canada), CONICYT (Chile), the Australian Research Council
+(Australia), Minist\'erio da Ci\^encia, Tecnologia e Inova\c{c}\~ao (Brazil)
+and Ministerio de Ciencia, Tecnolog\'ia e Innovaci\'on Productiva (Argentina).
 

### 2015-01-26 Code/allpositions.py

@@ -43,14 +43,15 @@ fluxcomponent = Table.read(fluxcomponent_file, format='ascii')
 fluxcomponent = sep_util.rmSingles(fluxcomponent, targetstring='lessid')
 nmultiples = len(fluxcomponent)
 
-sep_hodge = sep_util.getSeparation(fluxcomponent, targetstring='lessid')
+sep_hodge = sep_util.getSeparation(fluxcomponent, targetstring='lessid',
+        rastring='ra_alma', decstring='dec_alma')
 avgsep_hodge = sep_hodge[0]
 wmeansep_hodge = sep_hodge[1]
 ra_hodge = numpy.array(sep_hodge[2]) * 3600
 dec_hodge = numpy.array(sep_hodge[3]) * 3600
 
 plt.plot(ra_hodge, dec_hodge, hodgefmt, alpha=0.8, color=hodgecolor,
-        ms=hodgems, label='Hodge+13')
+        ms=hodgems, label='ALESS')
 
 # ***********
 # ALMA sample
@@ -62,21 +63,21 @@ asimcolor = 'green'
 ams = 5
 afmt = 's'
 
-fluxcomponent_file = '../Data/table_positions.dat'
+fluxcomponent_file = '../Data/table_intrinsic.dat'
 fluxcomponent = Table.read(fluxcomponent_file, format='ascii')
 
 # filter out single source systems
 fluxcomponent = sep_util.rmSingles(fluxcomponent, targetstring='target')
 nmultiples = len(fluxcomponent)
 
-sep_alma = sep_util.getSeparation(fluxcomponent, fluxstring='S_870_observed')
+sep_alma = sep_util.getSeparation(fluxcomponent, fluxstring='f870')
 avgsep_alma = sep_alma[0]
 wmeansep_alma = sep_alma[1]
 ra_alma = numpy.array(sep_alma[2]) * 3600
 dec_alma = numpy.array(sep_alma[3]) * 3600
 
 plt.plot(ra_alma, dec_alma, afmt, alpha=0.8, color=acolor, ms=ams, 
-        label='ALMA Sample')
+        label='Herschel-ALMA')
 
 # add Hayward et al. simulated galaxies
 h13 = readsav('../Data/shane_data.sav')

### 2015-01-26 Code/componentflux.py

@@ -115,9 +115,9 @@ yyyerrbarger = fluxcomponent['S850'] / 10.
 # **********
 
 # Plotting parameters
-bargcolor = 'LightBlue'
+bargcolor = 'Black'
 bargms = 4
-bargfmt = 'o'
+bargfmt = '.'
 
 # Load the data
 #fluxcomponent_file = '../Data/barger2012.dat'
@@ -313,7 +313,7 @@ ax1.plot(xxxbarger, yyybarger, bargfmt, ms=bargms, color=bargcolor,
 
 ax1.errorbar(xxxalma, yyyalma, yerr=yyyerralma, xerr=xxxerralma, fmt=',',
         ecolor='gray', capsize=0)
-ax1.plot(xxxalma, yyyalma, afmt, ms=ams, color=acolor, label='Herschel DSFGs')
+ax1.plot(xxxalma, yyyalma, afmt, ms=ams, color=acolor, label='Herschel-ALMA')
 
 # customize plot
 #plt.xlabel(r'${\rm Total} \, S_{870}\,({\rm mJy}$)', fontsize='x-large')

### 2015-01-26 Code/dnda.py

@@ -54,7 +54,8 @@ fluxcomponent = sep_util.rmSingles(fluxcomponent, targetstring='target')
 fluxcomponent = sep_util.setThresh(fluxcomponent, 1.4, fluxstring='peakflux')
 nmultiples = len(fluxcomponent)
 
-simalma = sep_util.getSeparation(fluxcomponent, fluxstring='peakflux')
+simalma = sep_util.getSeparation(fluxcomponent, rastring='ra_alma', \
+        decstring='dec_alma', fluxstring='peakflux')
 avgsep_simalma, wmeansep_simalma, ra_simalma, dec_simalma = simalma
 
 sep_util.histArea(avgsep_simalma, nbins, color=simcolor, fmt=simfmt, ms=simms,
@@ -77,8 +78,8 @@ fluxcomponent = Table.read(fluxcomponent_file, format='ascii')
 fluxcomponent = sep_util.rmSingles(fluxcomponent, targetstring='lessid')
 nmultiples = len(fluxcomponent)
 
-hodge = sep_util.getSeparation(fluxcomponent, 
-        targetstring='lessid')
+hodge = sep_util.getSeparation(fluxcomponent, rastring='ra_alma', \
+        decstring = 'dec_alma', targetstring='lessid')
 avgsep_hodge, wmeansep_hodge, ra_hodge, dec_hodge = hodge
 
 deltasep = avgsep_hodge.max() - avgsep_hodge.min()
@@ -110,19 +111,19 @@ asimcolor = 'green'
 ams = 5
 afmt = 's'
 
-fluxcomponent_file = '../Data/table_positions.dat'
+fluxcomponent_file = '../Data/table_intrinsic.dat'
 fluxcomponent = Table.read(fluxcomponent_file, format='ascii')
 
 # filter out single source systems
 fluxcomponent = sep_util.rmSingles(fluxcomponent, targetstring='target')
 nmultiples = len(fluxcomponent)
 
-alma = sep_util.getSeparation(fluxcomponent, fluxstring='S_870_observed')
+alma = sep_util.getSeparation(fluxcomponent, fluxstring='f870')
 avgsep_alma, wmeansep_alma, ra_alma, dec_alma = alma
 
 indexsort = numpy.argsort(avgsep_alma)
 avgsep_alma = avgsep_alma[indexsort]
-flux_alma = fluxcomponent['S_870_observed'][indexsort]
[…]

### 2015-01-26 Code/mag-flux.py

@@ -200,9 +200,9 @@ def Pmu_model(modloc, linestyle='solid', lf='Powerlaw', fill=False):
             #plt.fill_between(xx, y1, y2, facecolor=color, zorder=-4, alpha=0.3)
             #plt.fill_between(xx, y1, y2, facecolor='none', zorder=-4,
             #        edgecolor=color, hatch='\\\\')
-        #if addlabel:
-        #    plt.plot(xx, yy, color=color, linestyle=linestyle, 
-        #            label='Karim+ 2013', linewidth=1.5)
+        if addlabel:
+            plt.plot(xx, yy, color=color, linestyle=linestyle, 
+                    label='Karim+ 2013', linewidth=1.5)
 
         # predicted P(mu) for Steep LF
         yy = fractiondata['break15']
@@ -211,7 +211,7 @@ def Pmu_model(modloc, linestyle='solid', lf='Powerlaw', fill=False):
         print(xx[find_nearest(yy, 0.5)])
         if addlabel:
             plt.plot(xx, yy, color=color, linestyle=linestyle, 
-                    label='Theoretical Prediction', linewidth=1.5)
+                    label=r'$S_\star = 15\,$mJy', linewidth=1.5)
 
         if fill:
             sigmadata = Table.read('../Data/Sig_1p1_30powerlaw.txt',
@@ -271,18 +271,18 @@ fcolor = 'purple'
 # Schechter luminosity function
 #Pmu_model('../Data/Mu_1p1_30Sc.txt', linestyle='dotted', lf='Schechter')
 #Pmu_model('../Data/Mu_1p2_30Sc.txt', linestyle='--', lf='Schechter')
-#Pmu_model('../Data/Mu_2_30Sc.txt', linestyle='solid', lf='Schechter')
+Pmu_model('../Data/Mu_SH_2_30_z1p5.txt', linestyle='solid', lf='Schechter')
 
 # Broken power-law luminosity function
 #Pmu_model('../Data/Mu_1p1_30powerlaw.txt', linestyle='solid', fill=True)
-Pmu_model('../Data/Mu_PL_1p1_30_z1p5.txt', linestyle='solid', fill=True)
[…]

### 2015-01-26 Code/sep_util.py

@@ -55,7 +55,7 @@ def setThresh(fluxcomponent, thresh, fluxstring='f880'):
     return fluxcomponent
 
 
-def getSeparation(fluxcomponent, rastring='ra_alma', decstring='dec_alma',
+def getSeparation(fluxcomponent, rastring='offra', decstring='offdec',
         targetstring='target', fluxstring='f880'):
 
     nindiv = len(fluxcomponent)
@@ -72,23 +72,31 @@ def getSeparation(fluxcomponent, rastring='ra_alma', decstring='dec_alma',
         decs = fluxcomponent[decstring][match]
         fluxs = fluxcomponent[fluxstring][match]
         nmatch = fluxcomponent[fluxstring][match].size
-        newra = numpy.zeros(nmatch)
-        newdec = numpy.zeros(nmatch)
-        for imatch in range(nmatch):
-            ira = ras[imatch]
-            idec = decs[imatch]
-            sc = SkyCoord(ira, idec, "icrs", unit=(u.hourangle, u.degree))
-            newra[imatch] = sc.ra.deg
-            newdec[imatch] = sc.dec.deg
+        try:
+            avgra = ras.mean() / 3600
+            avgdec = decs.mean() / 3600
+            ra = fluxcomponent[rastring][icomp] / 3600
+            dec = fluxcomponent[decstring][icomp] / 3600
+            newra = ras / 3600
+            newdec = decs / 3600
+        except:
+            newra = numpy.zeros(nmatch)
+            newdec = numpy.zeros(nmatch)
+            for imatch in range(nmatch):
+                ira = ras[imatch]
+                idec = decs[imatch]
+                sc = SkyCoord(ira, idec, "icrs", unit=(u.hourangle, u.degree))
+                newra[imatch] = sc.ra.deg
+                newdec[imatch] = sc.dec.deg
 
-        ra = fluxcomponent[rastring][icomp]
-        dec = fluxcomponent[decstring][icomp]
-        sc = SkyCoord(ra, dec, "icrs", unit=(u.hourangle, u.degree))
-        ra = sc.ra.deg
-        dec = sc.dec.deg
+            ra = fluxcomponent[rastring][icomp]
+            dec = fluxcomponent[decstring][icomp]
+            sc = SkyCoord(ra, dec, "icrs", unit=(u.hourangle, u.degree))
+            ra = sc.ra.deg
+            dec = sc.dec.deg
+            avgra = newra.mean()
+            avgdec = newdec.mean()
         
[…]

### 2015-03-25 LaTeX/ms.tex
Minor edits

@@
 
-\caption{ Model fits for each target in the {\it Herschel}-ALMA sample, 3 panels per target.
-{\it Left}: ALMA 870$\mu$m imaging (red contours, starting at $\pm 3\sigma$ and
-increasing by factors of 2) overlaid on best available optical or near-IR
-imaging (grayscale, with telescope and filter printed in upper right corner).
-The location and morphology of all sources used in the model are represented by
-magenta ellipses.  If a lens is present, its location is given by a black
-circle and its critical curve is traced by an orange line.  The FWHM size of
-the ALMA synthesized beam is shown in the lower left corner of each panel.
-{\it Middle}: Same as {\it left}, but showing best-fit model in grayscale.
-{\it Right}: Same as {\it left}, but showing resdiual image obtained from
-subtracting best-fit model from the data.  \label{fig:uvmodels}}
+\caption{ Model fits for each target in the {\it Herschel}-ALMA sample, 3
+panels per target.  {\it Left}: ALMA 870$\mu$m imaging (red contours, starting
+at $\pm 3\sigma$ and increasing by factors of 2) overlaid on best available
+optical or near-IR imaging (grayscale, with telescope and filter printed in
+upper right corner).  The location and morphology of all sources used in the
+model are represented by magenta ellipses.  If a lens is present, its location
+is given by a black circle and its critical curve is traced by an orange line.
+The FWHM size of the ALMA synthesized beam is shown in the lower left corner of
+each panel.  {\it Middle}: Same as {\it left}, but showing best-fit model in
+grayscale.  {\it Right}: Same as {\it left}, but showing resdiual image
+obtained from subtracting best-fit model from the data.  \label{fig:uvmodels}}
 \addtocounter{figure}{-1}
@@
 there is a dramatic rise in $dN/dA$ for angular separations less than
-$2\arcsec$ in our {\it Herschel}-ALMA sample.  Indeed, for an angular separation of
-$0\farcs5$, we find an excess in $dN/dA$ by a factor of $\approx 10$ compared
-to a random, uniformly distributed population.  This excess persists (although
-at significantly lower amplitude) even when the quality of our ALMA
-observations are degraded to match the typical sensitivity, spatial resolution,
-and {\it uv} coverage of ALESS (as represented by observations of ALESS 122).
-The persistence of the excess suggests that it is an intrinsic property of the
-sample; i.e., that only the brightest DSFGs show an excess of sources on small
-separation scales.
+$2\arcsec$ in our {\it Herschel}-ALMA sample.  Indeed, for an angular
+separation of $0\farcs5$, we find an excess in $dN/dA$ by a factor of $\approx
+10$ compared to a random, uniformly distributed population.  This excess
+persists (although at significantly lower amplitude) even when the quality of
+our ALMA observations are degraded to match the typical sensitivity, spatial
+resolution, and {\it uv} coverage of ALESS (as represented by observations of
+ALESS 122).  The persistence of the excess suggests that it is an intrinsic
+property of the sample; i.e., that only the brightest DSFGs show an excess of
+sources on small separation scales.
 
@@
 
-\caption{ {\it Left}: Spatial distribution of sources with multiple counterparts
-found in our {\it Herschel}-ALMA sample (green squares), in ALESS (pink diamonds), and in mock
-catalogs from \citet{HB13} (color scale).  Sources identified in our {\it
-Herschel}-ALMA sample
-lie much closer to each other than they do in either ALESS or the \citet{HB13}
-simulations.  {\it Right}: Number of ALMA sources per annular area as a function
-of angular separation from the ALMA centroid.  Results are shown for our ALMA
-sample (thick green line), ALESS (thick pink line), the \citet{HB13} simulations
-(thick blue line), and our {\it Herschel}-ALMA sample as would have been seen with ALESS
-resolution and sensitivity (thick orange line).  We also show the range of
-separations that would be seen if sources were randomly distributed within the
-ALMA field of view (green hatched region with solid and dashed green lines).
-The DSFGs in our {\it Herschel}-ALMA sample show a much stronger excess on angular separation
-scales $<2\arcsec$ compared to ALESS and the \citet{HB13} simulations, even when
-taking into account the difference in sensitivity and spatial resolution between
-our ALMA observations and those of ALESS.  } \label{fig:dNdA}
+\caption{ {\it Left}: Spatial distribution of sources with multiple
+counterparts found in our {\it Herschel}-ALMA sample (green squares), in ALESS
+(pink diamonds), and in mock catalogs from \citet{HB13} (color scale).  Sources
+identified in our {\it Herschel}-ALMA sample lie much closer to each other than
+they do in either ALESS or the \citet{HB13} simulations.  {\it Right}: Number
+of ALMA sources per annular area as a function of angular separation from the
+ALMA centroid.  Results are shown for our ALMA sample (thick green line), ALESS
+(thick pink line), the \citet{HB13} simulations (thick blue line), and our {\it
+Herschel}-ALMA sample as would have been seen with ALESS resolution and
+sensitivity (thick orange line).  We also show the range of separations that
+would be seen if sources were randomly distributed within the ALMA field of
+view (green hatched region with solid and dashed green lines).  The DSFGs in
+our {\it Herschel}-ALMA sample show a much stronger excess on angular
+separation scales $<2\arcsec$ compared to ALESS and the \citet{HB13}
+simulations, even when taking into account the difference in sensitivity and
+spatial resolution between our ALMA observations and those of ALESS.  }
+\label{fig:dNdA}
 
@@
 projection effects \citep{HB13}.  Spatially resolved spectroscopy is necessary
-to answer this question definitely, but is not currently available.  Instead,
+to answer this question definitively, but is not currently available.  Instead,
 to investigate these possibilities further, we make use of mock catalogs of
@@
 survey in COSMOS \citep{Scott:2008qy} using the SMA \citep{Younger:2007fk,
-Younger:2009lr} and PdBI (Miettinen et al., in prep.).  Interferometric
-follow-up data in COSMOS \citep{Smolcic:2012zl} and GOODS-N
-\citep{Barger:2012yg} are published, but unknown completeness corrections in the
-single-dish surveys on which these follow-up datasets are based precludes their
-use here.
+Younger:2009lr} and PdBI \citep{Miettinen:2015lr}.  Interferometric follow-up
+data in COSMOS \citep{Smolcic:2012zl} and GOODS-N \citep{Barger:2012yg} are
+published, but unknown completeness corrections in the single-dish surveys on
+which these follow-up datasets are based precludes their use here.
 
@@
 
-In Table~\ref{tab:models}, we provide information for three models tested in
-this paper: the steepest plausible Schechter function; the \citet{Karim:2013lr}
-broken power-law; and a broken power-law with a brighter break point ($S_\ast =
-15\,$mJy) than used in \citet{Karim:2013lr}.
+In Table~\ref{tab:models}, we provide information for two models tested in this
+paper: the \citet{Karim:2013lr} broken power-law that provides a good fit to
+ALESS number counts; and a broken power-law with a brighter break point
+($S_\ast = 15\,$mJy) that provides a good fit to the COSMOS luminosity function
+from \citet{Miettinen:2015lr}.  The data and corresponding luminosity functions
+are shown in the left panel of Figure~\ref{fig:lensstats}.
 
@@
 Herschel}-ALMA and {\it Herschel}-SMA samples.  We also show a running average
-of the combined sample (considering only $\mu_{870} > 1.1$ objects, since this
-is the level at which magnification effects become as significant as absolute
-calibration uncertainties) to serve as a direct comparison to our theoretical
-models.  We compute this by interpolating the observed $\mu_{870}$ and
-$S_{870}$ onto a fine grid using the {\sc Scipy} {\sc griddata} package and
-then smoothing the resulting grid using a Gaussian filter (specifically, the
-Scipy {\sc gaussian\_filter} package).  Also shown in this diagram are model
-predictions for the average magnification as a function of $S_{870}$,
-$\langle\mu_{870}\rangle$, assuming the three intrinsic luminosity functions
-for DSFGs described in Table~\ref{tab:models}.
+of the combined sample (considering only $\mu_{870} > 2.0$ objects) to serve as
+a direct comparison to our theoretical models.  We compute this by
+interpolating the observed $\mu_{870}$ and $S_{870}$ onto a fine grid using the
+{\sc Scipy} {\sc griddata} package and then smoothing the resulting grid using
+a Gaussian filter in the Scipy {\sc gaussian\_filter} package.
+Also shown in this diagram are model predictions for the average magnification
+as a function of $S_{870}$, $\langle\mu_{870}\rangle$, assuming the two
+intrinsic luminosity functions for DSFGs described in Table~\ref{tab:models}.
 
@@
 \includegraphics[width=0.335\textwidth]{../Figures/DifferentialNumberCounts.pdf}
-\includegraphics[width=0.335\textwidth]{../Figures/s870_mu.pdf}
-\includegraphics[width=0.335\textwidth]{../Figures/Pmu_S870.pdf}
+\includegraphics[width=0.335\textwidth]{../Figures/s870_mu_z1p5.pdf}
+\includegraphics[width=0.335\textwidth]{../Figures/Pmu_S870_z1p5.pdf}
 
 \caption{ {\it Left}: Observed luminosity functions from interferometer
-follow-up of mm sources in COSMOS \citep[black circles;][Miettinen et al., in
-prep.]{Younger:2007fk, Younger:2009lr} and from ALESS \citep[pink
-diamonds;][]{Karim:2013lr}.  In comparison, the magneta, purple, and blue lines
-show three models for the intrinsic luminosity functions of DSFGs. {\it Middle}:
-Magnification factors at 870$\,\mu$m as a function of apparent $S_{870}$ for
-every source in our ALMA (green squares) and SMA (red circles) samples.  The
-black line represents a running average of the magnification measurements when
-sources with $\mu_{870} > 1.1$ are considered.  Colored lines show our model
-predictions $<\mu_{870}>$ for $\mu_{870} > 1.1$ sources for the three intrinsic
-luminosity functions shown on the left.  All three luminosity functions are
-broadly consistent with the observed magnification factors.  {\it Right}:
-Probability that a source with a given $S_{870}$ experiences $\mu_{870} > 1.1$
-(solid lines) and $\mu_{870} > 2.0$ (dashed lines).  The black lines show the
-running average from the SMA and ALMA data.  Colored lines are the same as in
-the middle and left panels.  The Schechter function predicts too many unlensed
-or weakly lensed sources with intrinsic flux densities of $S_{870}^\prime \sim
-50\,$mJy.  Our choices for the broken power-law luminosity functions roughly
-bracket the running average from the data.} \label{fig:lensstats}
+follow-up of mm sources in COSMOS \citep[black circles;][]{Younger:2007fk,
+Younger:2009lr, Miettinen:2015lr} and from ALESS \citep[pink
+diamonds;][]{Karim:2013lr}.  The magneta and blue lines represent the range of
+plausible intrinsic luminosity functions for DSFGs given these two datasets.
+{\it Middle}: Magnification factors at 870$\,\mu$m as a function of apparent
+$S_{870}$ for every source in our ALMA (green squares) and SMA (red circles)
+samples.  The black line represents a running average of the magnification
+measurements when sources with $\mu_{870} > 2.0$ are considered (grey shaded
+region highlights the 1$\sigma$ uncertainty), and is truncated at the minimum
+flux density at which we have observed $\mu_{870} > 2.0$.  Colored lines show
+the average magnification factor, $\langle\mu_{870}\rangle$, predicted by our
+models for the two intrinsic luminosity functions shown on the left.  The model
+luminosity functions predict higher $\langle\mu_{870}\rangle$ than are seen in
+the data.  {\it Right}: Probability that a source with a given $S_{870}$
+experiences $\mu_{870} > 2.0$.  The black line (grey shaded region) shows a
+logistic regression fit to the SMA and ALMA data (grey shaded region highlights
+the 1$\sigma$ uncertainty).  Colored lines are the same as in the middle and
+left panels.  The intrinsic luminosity function that provides a good fit to the
+COSMOS data predicts too many unlensed or weakly lensed sources with intrinsic
+flux densities of $S_{870}^\prime \sim 50\,$mJy.} \label{fig:lensstats}
 
@@
 
-At low apparent flux densities ($S_{870} < 10\,$mJy), all three models are
-broadly consistent with each other, as well as with the running average of the
-data, considering the dispersion in the model predictions for $\mu_{870}$ at a
-given $S_{870}$ are $\sigma_\mu \approx 1-2$ in this regime.
-
-The regime between the low and high apparent flux density limits ($10\,$mJy$ <
-S_{870} < 70\,$mJy) is where the three model predictions show the largest
-difference in $\langle\mu_{870}\rangle$.  The steep rise in the running average in this
-area is best reproduced by the model with the steep broken power-law luminosity
-function.  However, this model has a difficult time accounting for the
-low-$\mu_{870}$, high-$S_{870}$ population that comprises about one-third of
-the sources in this regime.  Because the dispersion in the model magnification
-factors rises smoothly from $\sigma_\mu \approx 2$ to $\sigma_\mu \approx 8$
-over this regime, this difference is significant.  The steep Schechter function
-does a better job of reproducing the low-magnification sources, but it
-under-predicts the running average over much of the range in $S_{870}$.
-Furthermore, there are a number of high-$\mu_{870}$, $S_{870} \approx
-10-20\,$mJy sources that are poorly accounted for by the steep Schechter
-function.  The broken power-law luminosity function advocated in
-\citet{Karim:2013lr} provides an intermediate result between the steep
-Schechter function and steep broken power-law and therefore shares some of the
-strengths and weaknesses of both.
-
-At high apparent flux densities ($S_{870} > 70\,$mJy), all of the models
-over-predict the running average of the magnification.  One plausible
-explanation for this difference is a limitation in the spatial resolution of
-the observations.  In both the {\it Herschel}-ALMA and {\it Herschel}-SMA
-samples, the spatial resolution is $\approx 0\farcs5$.  This is nearly always
-sufficient to resolve the images of the lensed galaxy, but it is not always
-sufficient to resolve the images themselves.  Therefore, it may be the case
-that the lens models over-predict the intrinsic sizes of the lensed galaxies
-and hence under-predict the magnification factors.  For example, the half-light
-sizes of unlensed DSFGs have been found recently to be $\approx 0.8 \,$kpc
-\citep{Ikarashi:2014nr} and $\approx1.2\,$kpc \citep{Simpson:2015ty}.  In
-contrast, we reported a median half-light radius of $1.53\,$kpc in
-\citet{Bussmann:2013lr}.  If this difference is significant, it may also affect
-the intermediate $S_{870}$ regime.  A thorough investigation of this
-possibility is deferred to future work.
-
-One way to deal with this potential limitation in the data is to simplify the
-quantity of interest.  In particular, we next consider the probability of a
-given source experiencing a magnification above some threshold value, $\mu_{\rm
-min}$.  As discussed previously, we expect our ALMA and SMA measurements to
-provide a reliable estimate of this quantity.  The results of this are shown in
-the right panel of Figure~\ref{fig:lensstats}.  We consider two limiting
-thresholds: $\mu_{\rm min} = 1.1$ and $\mu_{\rm min} = 2.0$.  The models we
-consider are the same as those used in the left panel of
-Figure~\ref{fig:lensstats}, and our method of creating the running average is
-also the same.
+%At low apparent flux densities ($S_{870} < 10\,$mJy), all three models are
+%broadly consistent with each other, as well as with the running average of the
+%data, considering the dispersion in the model predictions for $\mu_{870}$ at a
+%given $S_{870}$ are $\sigma_\mu \approx 1-2$ in this regime.
+
+%The regime between the low and high apparent flux density limits ($10\,$mJy$ <
+%S_{870} < 70\,$mJy) is where the three model predictions show the largest
+%difference in $\langle\mu_{870}\rangle$.  The steep rise in the running
+%average in this area is best reproduced by the model with the steep broken
+%power-law luminosity function.  
+Both models predict higher $\langle\mu_{870}\rangle$ than are seen in the data
+by factors of 5-10.  However, the dispersion in the predicted
+$\langle\mu_{870}\rangle$ values for both intrinsic luminosity functions rises
+smoothly from $\sigma_\mu \approx 2$ at $S_{870} = 15\,$mJy to $\sigma_\mu
+\approx 8$ at $S_{870} = 100\,$mJy, so this difference is not statistically
+significant.  Furthermore, there is reason to believe that the data may be
+biased against high magnification factor measurements.  In both the {\it
+Herschel}-ALMA and {\it Herschel}-SMA samples, the spatial resolution is
+$\approx 0\farcs5$.  This is nearly always sufficient to resolve the images of
+the lensed galaxy, but it is not always sufficient to resolve the images
+themselves.  Therefore, it may be the case that the lens models over-predict
+the intrinsic sizes of the lensed galaxies and hence under-predict the
+magnification factors.  For example, the half-light sizes of unlensed DSFGs
+have been found recently to be $\approx 0.8 \,$kpc \citep{Ikarashi:2014nr} and
+$\approx1.2\,$kpc \citep{Simpson:2015ty}.  In contrast, we reported a median
+half-light radius of $1.53\,$kpc in \citet{Bussmann:2013lr}.  Early lens models
+from higher resolution data with ALMA suggest that magnification factors could
+increase by a factor of $\approx 1.5$ \citep{Rybak:2015fk}.  Therefore, it is
+plausible that both of the intrinsic luminosity functions tested here provide
+statistically consistent fits to the data.
+
+A related but distinct test of the intrinsic luminosity functions for DSFGs
+comes from the probability of a given source experiencing a magnification above
+some threshold value, $\mu_{\rm min}$.  Unlike the case with the average
+magnification factor measurements, our ALMA and SMA data should provide a
+reliable estimate of this quantity.  The results of this are shown in the right
+panel of Figure~\ref{fig:lensstats}.  For clarity of presentation, we show one
+choice of $\mu_{\rm min}$: $\mu_{\rm min} = 2.0$.  The shape of the curves
+varies with  $\mu_{\rm min}$, but the overall results are qualitatively the
+same.  The models we consider are the same as those used in the left panel of
+Figure~\ref{fig:lensstats}.  Instead of computing a running average of the
+data, we show a logistic regression fit to the data \citep[obtained with the
+{\sc Scikit-learn package;][]{scikit-learn}.
 

### 2015-03-25 Code/mag-flux.py

@@ -154,11 +154,14 @@ def find_nearest(array, value):
     idx = (numpy.abs(array-value)).argmin()
     return idx
 
-def Pmu_model(modloc, linestyle='solid', lf='Powerlaw', fill=False):
+def Pmu_model(modloc, linestyle='solid', lf='Powerlaw', fill=False,
+        truncate=0):
 
     # read in Fialkov data
     fractiondata = Table.read(modloc, format='ascii')
+
     xx = fractiondata['S870']
+    min
 
     addlabel = True
     #if modloc[8:10] == 'Mu':
@@ -177,10 +180,11 @@ def Pmu_model(modloc, linestyle='solid', lf='Powerlaw', fill=False):
         plt.plot(xx, yy, color=color, linestyle=linestyle, linewidth=1.5)
         print(xx[find_nearest(yy, 0.5)])
         if fill:
-            sigmadata = Table.read('../Data/Sig_1p1_30sh.txt',
-                    format='ascii')
-            y1 = fractiondata['steep'] - sigmadata['steep']
-            y2 = fractiondata['steep'] + sigmadata['steep']
+            pass
+            #sigmadata = Table.read('../Data/Sig_1p1_30sh.txt',
+            #        format='ascii')
+            #y1 = fractiondata['steep'] - sigmadata['steep']
+            #y2 = fractiondata['steep'] + sigmadata['steep']
             #plt.fill_between(xx, y1, y2, facecolor='none', zorder=-3,
             #        hatch='/', edgecolor=color)
         if addlabel:
@@ -188,15 +192,19 @@ def Pmu_model(modloc, linestyle='solid', lf='Powerlaw', fill=False):
                     label='Schechter', linewidth=1.5)
     else:
         key = 'karim'
+        ok = fractiondata['S870'] > truncate
+        fractiondata = fractiondata[ok]
+        xx = fractiondata['S870']
         yy = fractiondata[key]
         color = 'magenta'
         #plt.plot(xx, yy, color=color, linestyle=linestyle, linewidth=1.5)
         #print(xx[find_nearest(yy, 0.5)])
         if fill:
[…]

### 2015-03-30 LaTeX/ms.tex
Comments + plotseds
95% of comments complete.  Plot SEDs to inspect flux densities from J.
Scudders.

@@
 J.~Wardlow\altaffilmark{15}}
+\altaffiltext{$\dagger$}{Herschel is an ESA space observatory with science
+instruments provided by European-led Principal Investigator consortia and with
+important participation from NASA.}
 \altaffiltext{1}{Department of Astronomy, Space Science Building, Cornell University, Ithaca, NY, 14853-6801}
@@
     0$\farcs$45 imaging obtained in Cycle~0 with the Atacama Large
-    Millimeter/submillimeter Array (ALMA) of a sample of 29 HerMES DSFGs.  We
-    identify a total of 62 sources down to the $5\sigma$ limit in our ALMA
-    sample ($\sigma \approx 0.2\,$mJy).  Optical or near-infrared imaging
-    indicates that 36 of the ALMA sources experience a significant flux boost
-    from gravitational lensing ($\mu > 1.1$), but only 6 are strongly lensed
-    and show multiple images.  Combined with our previous work on brighter {\it
-    Herschel} sources, the lens models presented here constrain the shape of
-    the intrinsic luminosity function for DSFGs to have a break near 8$\,$mJy
-    at 880$\,\mu$m with a very steep fall off at higher flux densities.  We
-    introduce and make use of {\sc uvmcmcfit}, a general purpose and publicly
-    available Markov chain Monte Carlo visibility plane analysis tool to
-    analyze the source properties.  Nearly 70\% of the {\it Herschel} sources
-    break down into multiple ALMA counterparts, consistent with previous
-    research indicating that the multiplicity rate is high in bright sources
-    discovered in single-dish sub-mm or FIR surveys.  The ALMA counterparts to
-    our {\it Herschel} targets are located much closer to each other than ALMA
-    counterparts to sources found in the LABOCA ECDFS Submillimeter Survey.
-    Theoretical models underpredict the excess number of sources with small
-    separations seen in our ALMA sample.  The high multiplicity rate and low
-    projected separations between sources seen in our sample argue in favor of
-    interactions and mergers plausibly driving both the prodigious emission
-    from the brightest DSFGs as well as the sharp downturn above $S_{880} =
-    8\,$mJy.
+    Millimeter/submillimeter Array (ALMA) of a sample of 29 HerMES DSFGs.  The
+    ALMA imaging reveals that these DSFGs comprise a total of 62 sources (down
+    to the $5\sigma$ limit in our ALMA sample; $\sigma \approx 0.2\,$mJy).
+    Optical or near-infrared imaging indicates that 36 of the ALMA sources
+    experience a significant flux boost from gravitational lensing ($\mu >
+    1.1$), but only 6 are strongly lensed and show multiple images.  Combined
+    with our previous work on brighter {\it Herschel} sources, the lens models
+    presented here constrain the shape of the intrinsic luminosity function for
+    DSFGs to have a break near 8$\,$mJy at 880$\,\mu$m with a very steep fall
+    off at higher flux densities.  We introduce and make use of {\sc
+    uvmcmcfit}, a general purpose and publicly available Markov chain Monte
+    Carlo visibility plane analysis tool to analyze the source properties.
+    Nearly 70\% of the {\it Herschel} sources break down into multiple ALMA
+    counterparts, consistent with previous research indicating that the
+    multiplicity rate is high in bright sources discovered in single-dish
+    sub-mm or FIR surveys.  The ALMA counterparts to our {\it Herschel} targets
+    are located significantly closer to each other than ALMA counterparts to
+    sources found in the LABOCA ECDFS Submillimeter Survey.  Theoretical models
+    underpredict the excess number of sources with small separations seen in
+    our ALMA sample.  The high multiplicity rate and low projected separations
+    between sources seen in our sample argue in favor of interactions and
+    mergers plausibly driving both the prodigious emission from the brightest
+    DSFGs as well as the sharp downturn above $S_{880} = 8\,$mJy.
 
@@
 limit of {\it Herschel} \citep[$\sigma \approx 6-7\,$mJy in each
-band][]{Nguyen:2010fk}, plus an additional $\approx 350\,$deg$^2$ to a level
-approximately double the confusion limit.  A similar effort to survey large
-areas of the sky has been undertaken at longer wavelengths by the South Pole
-Telescope \citep[SPT;][]{Carlstrom:2011qy} and the Atacama Cosmology Telescope
-\citep{Swetz:2011qy}.
+band][]{Nguyen:2010fk}, plus an additional $\approx 350\,$deg$^2$ to a
+shallower level (approximately double the confusion limit).  A similar effort
+to survey large areas of the sky has been undertaken at longer wavelengths by
+the South Pole Telescope \citep[SPT;][]{Carlstrom:2011qy} and the Atacama
+Cosmology Telescope \citep{Swetz:2011qy}.
 
 Theoretical expectations based on the redshift distribution and luminosity
-function of DSFGs suggested that HerMES and H-ATLAS would be efficient tools for
-discovering strongly lensed DSFGs \citep[e.g.,][]{1996MNRAS.283.1340B,
+function of DSFGs suggested that HerMES and H-ATLAS would be efficient tools
+for discovering strongly lensed DSFGs \citep[e.g.,][]{1996MNRAS.283.1340B,
 2007MNRAS.377.1557N}.  Submillimeter Array \citep[SMA;][]{Ho:2004lr} imaging at
@@
 of the brightest sources found by {\it Herschel} ($S_{500} > 100\,$mJy) being
-gravitationally lensed by an intevening galaxy or group of galaxies along the
+gravitationally lensed by an intervening galaxy or group of galaxies along the
 line of sight \citep{Negrello:2010fk, Conley:2011lr, Riechers:2011uq,
 Bussmann:2012lr, Wardlow:2013lr, Bussmann:2013lr}.  Sources discovered in SPT
-surveys have also been shown to have a high probability of being strongly lensed
-\citep{Vieira:2013fk, Hezaveh:2013fk}.  However, statistical models
-significantly over-predict the median magnification factor experienced by a {\it
-Herschel} DSFG of a given $S_{500}$ \citep{Bussmann:2013lr}.  This could
-indicate a deficiency in our understanding of the bright end of the intrinsic
-DSFG luminosity function.
+surveys have also been shown to have a high probability of being strongly
+lensed \citep{Vieira:2013fk, Hezaveh:2013fk}.  However, statistical models
+significantly over-predict the median magnification factor experienced by a
+{\it Herschel} DSFG of a given $S_{500}$ \citep{Bussmann:2013lr}.  This could
+indicate herald new insights in our understanding of the bright end of the
+intrinsic DSFG luminosity function or in the nature of the deflectors.
 
@@
 
-\caption{ ALMA 870$\,\mu$m images (color scale, units of mJy$\,$beam$^{-1}$) of HerMES
-DSFGs (images have not been corrected for primary beam attenuation).  Contours
-(black and white) trace 250$\,\mu$m emission from {\it Herschel}.  The FWHM
-size of the ALMA synthesized beam is shown in the lower left corner of each
-panel.  A solid white circle shows the FWHM size of the primary beam.  Dashed
-squares identify the regions of each image that are shown in greater detail in
-Fig.~\ref{fig:uvmodels}.  \label{fig:imaging}} \addtocounter{figure}{-1}
+\caption{ ALMA 870$\,\mu$m images (color scale, units of mJy$\,$beam$^{-1}$) of
+HerMES DSFGs (images have not been corrected for primary beam attenuation).
+Contours (black and white) trace 250$\,\mu$m emission from {\it Herschel}
+(starting at 4$\sigma$ and increasing by factors of 2, where $\sigma=7\,$mJy).
+The FWHM size of the ALMA synthesized beam is shown in the lower left corner of
+each panel.  A solid white circle shows the FWHM size of the primary beam.
+Dashed squares identify the regions of each image that are shown in greater
+detail in Fig.~\ref{fig:uvmodels}.  \label{fig:imaging}}
+\addtocounter{figure}{-1}
 
@@
 each lens by eye and fix the positions of the additional lenses with respect to
-the primary lens.  Each additional lens thus has three parameters:
-$\theta_{\rm E}$, $q_{\rm lens}$, and $\phi_{\rm lens}$.  We assume secondary,
-tertiary, etc., lenses are located at the same redshift as the primary lens.
+the primary lens.  Each additional lens thus has three parameters: $\theta_{\rm
+E}$, $q_{\rm lens}$, and $\phi_{\rm lens}$.
 
@@
 the number of Gaussian profiles used.
+
+We assume secondary, tertiary, etc., lenses are located at the same redshift as
+the primary lens.  If this assumption were incorrect, to first order only the
+conversion from an angular Einstein radius to a physical mass of the lensing
+galaxy would be affected.  As the physical masses of the lensing galaxies are
+not the focus of this work, this assumption is reasonable.
 
@@
 observed by ALMA (we ensure that the posterior PDF of the intrinsic flux
-density shows no signs of preferring a value lower than 0.1$\,$mJy).  The source
-position is allowed to vary over any reasonable range necessary to fit the data
-(typically, this is $\pm $1-2$\arcsec$).  The effective radius is allowed to vary
-from $0\farcs01 $-$ 1\farcs5$.
+density shows no signs of preferring a value lower than 0.1$\,$mJy).  The
+source position is allowed to vary over any reasonable range necessary to fit
+the data (typically, this is $\pm $1-2$\arcsec$).  The effective radius is
+allowed to vary from $0\farcs01 $-$ 1\farcs5$.
 
@@
 
-{\bf HECDFS12:} This is a complex, well-constrained system.  Two sources are
-detected by ALMA: one is strongly lensed and the other is weakly lensed.  In
-addition, the lens is detected by ALMA (this is one of two sources in the
-entire {\it Herschel}-ALMA sample that is unresolved by ALMA).  These facts
-work together to provide very tight constraints on the system.  Since the lens
-is detected by ALMA, its position relative to the lensed images is unambiguous.
-Also, because there is a strongly lensed source with multiple images, the
-Einstein radius of the lens is unambiguous.  A byproduct of these two facts is
-that the magnification factor of the weakly lensed source is known to very high
-precision as well.  It experiences a magnification factor of $\mu_{870} =
-1.520\pm0.002$ despite being located $\approx4\arcsec$ north of the lens (which
-has an Einstein radius of $1.353\pm0.005$; it is the tight constraint on the
-Einstein radius that permits such a tight constraint on $\mu_{870}$ for the
-weakly lensed source).  We use these numbers to inform our estimates of the
-Einstein radius for weakly lensed sources without the excellent contraints
-provided by this system.  Finally, this source is detected (and unresolved) in
-the NRAO VLA Sky Survey \citep{Condon:1998uq}, having $S_{\rm 1.4\,GHz} = 21.8
-\pm 0.8\,$mJy.  Assuming all of this radio emission originates from the lens,
-this implies a spectral slope of $\alpha = -0.24$ and is consistent with
-non-thermal emission from the lens.
+{\bf HECDFS12:} This is a complex, well-constrained system.  Two background
+sources are detected by ALMA: one is multiply imaged and the other is singly
+imaged.  In addition, the lens is detected by ALMA (this is one of two sources
+in the entire {\it Herschel}-ALMA sample that is unresolved by ALMA).  These
+facts work together to provide very tight constraints on the system.  Since the
+lens is detected by ALMA, its position relative to the lensed images is
+unambiguous.  Also, because there is a strongly lensed source with multiple
+images, the Einstein radius of the lens is unambiguous.  A byproduct of these
+two facts is that the magnification factor of the weakly lensed source is known
+to very high precision as well.  It experiences a magnification factor of
+$\mu_{870} = 1.520\pm0.002$ (note that this error bar is valid under the
+assumptions of our model, most notably the assumption that the singly imaged
+source is located at the same redshift as the multiply imaged source; the true
+uncertainty is likely a factor of a few larger).  despite being located
+$\approx4\arcsec$ north of the lens (which has an Einstein radius of
+$1.353\pm0.005$; it is the tight constraint on the Einstein radius that permits
+such a tight constraint on $\mu_{870}$ for the weakly lensed source).  We use
+these numbers to inform our estimates of the Einstein radius for weakly lensed
+sources without the excellent contraints provided by this system.  Finally,
+this source is detected (and unresolved) in the NRAO VLA Sky Survey
+\citep{Condon:1998uq}, having $S_{\rm 1.4\,GHz} = 21.8 \pm 0.8\,$mJy.  Assuming
+all of this radio emission originates from the lens, this implies a spectral
+slope of $\alpha = -0.24$ and is consistent with non-thermal emission from the
+lens.
 
@@
 
-{\bf HADFS10:} Three sources are detected by ALMA.  We 
-assume that all three are unlensed.  There is a group of three sources
-detected in our Gemini-S optical imaging located $\approx 7\arcsec$ east of the
-ALMA sources.  This distance is so large that plausible mass ranges for the
-Gemini-S sources would imply at most a factor of 1.1$-$1.2 boost in the apparent
-flux densities of the ALMA sources.
+{\bf HADFS10:} Three sources are detected by ALMA.  We assume that all three
+are unlensed.  There is a group of three sources detected in our Gemini-S
+optical imaging located $\approx 7\arcsec$ east of the ALMA sources.  This
+distance is so large that plausible mass ranges for the Gemini-S sources would
+imply at most a factor of 1.1$-$1.2 boost in the apparent flux densities of the
+ALMA sources.  We also tested a single-lens, single-source model in which the
+source is triply-imaged in the manner that is observed.  The lens in this case
+has an Einstein radius of $\approx 1\farcs2$, requiring a very high mass to
+light ratio or a very high lens redshift to be consistent with the
+non-detection in the Gemini-S data.  Deep near-IR imaging is needed to confirm
+that this target is unlensed.
 
@@
 For comparison, we also show the cumulative distribution of $S_{870}$ for the
-ALESS sample.  There is greater overlap in $S_{870}$ between our sample and
-ALESS than there is in $S_{500}$ (recall Figure~\ref{fig:sample}).  This is
-evidence that the DSFGs in our sample have higher $S_{500}/S_{870}$ ratios than
-the DSFGs in ALESS.  This difference is likely due to differences in dust
-temperature and/or redshift distributions of the two samples and probably arises
-from selection effects.
+ALESS sample.  ALESS is the only existing sample of DSFGs with interferometric
+follow-up of a sensitivity and angular resolution that is comparable to our
+ALMA data, so it is the best sample with which to compare our results.  There
+is greater overlap in $S_{870}$ between our sample and ALESS than there is in
+$S_{500}$ (recall Figure~\ref{fig:sample}).  This is evidence that the DSFGs in
+our sample have higher $S_{500}/S_{870}$ ratios than the DSFGs in ALESS.  This
+difference is likely due to differences in dust temperature and/or redshift
+distributions of the two samples and probably arises from selection effects.
 
@@
 ($S_\ast = 15\,$mJy) that provides a good fit to the COSMOS luminosity function
-from \citet{Miettinen:2015lr}.  The data and corresponding luminosity functions
-are shown in the left panel of Figure~\ref{fig:lensstats}.
+from \citet{Miettinen:2015lr}.  The interferometric observations in
+\citet{Miettinen:2015lr} show that all of the sources in their survey are
+either unlensed or lensed by magnification factors $<2$.  Therefore, the ALESS
+and COSMOS luminosity functions bracket the plausible range of intrinsic
+luminosity functions for DSFGs.  The data and corresponding luminosity
+functions are shown in the left panel of Figure~\ref{fig:lensstats}.
 

### 2015-03-30 Code/plotseds.py

@@ -1,0 +1,55 @@
+"""
+
+Shane Bussmann
+
+2015 March 30
+
+Plot SEDs for each Herschel source using new Herschel photometry from J.
+Scudders.
+
+"""
+
+from astropy.table import Table
+import matplotlib.pyplot as plt
+from pylab import savefig
+
+
+def plot(filename, color='black', label=''):
+
+    data = Table.read(filename, format='ascii')
+    
+    ndata = len(data)
+
+    for i in range(ndata):
+        plt.figure(i + 1)
+        flux = [data['250med'][i], data['350med'][i], data['500med'][i]]
+        wave = [250, 350, 500]
+        plt.plot(wave, flux, color=color, label=label)
+
+
+# plot the total 870um fluxes without 24um data
+plot('../Data/totalfluxes/total_870_fluxes.txt', color='red', 
+        label='Ignoring 24um sources')
+
+# plot the total 870um fluxes with 24um data where 24um source > 2.5" from
+# 870um source
+plot('../Data/totalfluxes/total_870_24_fluxes.txt', color='blue', 
+        label='Using 24um sources if not near 870um')
+
+# plot the total 870um fluxes with 24um data
+plot('../Data/totalfluxes/total_870_24_nodel_fluxes.txt', color='green', 
+        label='Using all 24um sources')
+
+datadummy = Table.read('../Data/totalfluxes/total_870_fluxes.txt', 
+        format='ascii')
+
+ndata = len(datadummy)
+fieldname = datadummy['Field']
+for i in range(ndata):
+    plt.figure(i + 1)
+    plt.legend(loc='best')
+    plt.title(fieldname[i])
+    plt.xlabel('Wavelength (microns)')
+    plt.ylabel('Flux density (mJy)')
+    savefig('../Figures/SEDplot_' + fieldname[i] + '.png')
+

### 2015-03-31 LaTeX/ms.tex
Added appendix with SPIRE fluxes

@@
 each panel.  {\it Middle}: Same as {\it left}, but showing best-fit model in
-grayscale.  {\it Right}: Same as {\it left}, but showing resdiual image
+grayscale.  {\it Right}: Same as {\it left}, but showing residual image
 obtained from subtracting best-fit model from the data.  \label{fig:uvmodels}}
@@
 follow-up of a sensitivity and angular resolution that is comparable to our
-ALMA data, so it is the best sample with which to compare our results.  There
-is greater overlap in $S_{870}$ between our sample and ALESS than there is in
-$S_{500}$ (recall Figure~\ref{fig:sample}).  This is evidence that the DSFGs in
-our sample have higher $S_{500}/S_{870}$ ratios than the DSFGs in ALESS.  This
-difference is likely due to differences in dust temperature and/or redshift
-distributions of the two samples and probably arises from selection effects.
+ALMA data, so it is the best sample with which to compare our results.  The
+significant overlap in $S_{870}$ between our sample and ALESS is evidence that
+the DSFGs in our sample have higher $S_{500}/S_{870}$ ratios than the DSFGs in
+ALESS (recall Figure~\ref{fig:sample}, which shows that ALESS sources have much
+lower $S_{500}$ than our targets).  This difference is likely due to
+differences in dust temperature and/or redshift distributions of the two
+samples and probably arises from selection effects.
 
@@
 data, we show a logistic regression fit to the data \citep[obtained with the
-{\sc Scikit-learn package;][]{scikit-learn}.
+{\sc Scikit-learn} package;][]{scikitlearn}.
 
@@
 
-%\appendix
+\appendix
+
+\section{{\it Herschel}/SPIRE Photometry}
+
+We present in Table~\ref{tab:photometry} SPIRE photometry ($S_{250}$,
+$S_{350}$, and $S_{500}$) for each {\it Herschel} source in our sample using as
+priors the ALMA and {\it Spitzer} 24$\,\mu$m counterpart positions.  Many of
+the {\it Herschel} sources in our sample have multiple 24$\,\mu$m counterparts
+close enough to the ALMA counterparts that they can make a significant
+contribution to the SPIRE flux at the position of the ALMA counterparts.  For
+this reason, it is critical to include the 24$\,\mu$m data when estimating {\it
+Herschel}/SPIRE photometry.  In cases where the {\it Spitzer} 24$\,\mu$m and
+ALMA counterparts spatially overlap (defined here as having a separation
+smaller than $2\farcs5$), we exclude the {\it Spitzer} counterpart from the
+calculations.
+
+Note that in the case of HELAISS02, we exclude a 24$\,\mu$m source associated
+with the lensing galaxy, despite being more than $2\farcs5$ away from the
+nearest ALMA counterpart.  This is because the ALMA counterparts are arranged
+so that they surround the 24$\mu$m source completely.  The extended emission
+seen in the SPIRE maps is therefore most likely attributable to the ALMA
+counterparts rather than the 24$\,\mu$m source.
+
+One of the key results from this analysis is that the use of StarFinder to
+deconvolve the SPIRE beam will lead to the removal of a portion of the targets
+with extended emission from a flux-limited sample.  This is by design, as the
+goal outlined in \citet{Wardlow:2013lr} was to develop the purest sample of
+lens candidates as possible from HerMES data.  Blends were considered by these
+authors to be unlikely to be lensed.  This method is effective for lenses where
+the Einstein radius is smaller than $\approx 2\arcsec$.  However, it selects
+against deeper potential wells, such as those of groups or clusters
+\citep[e.g., HLock01][]{Gavazzi:2011lr}, that produce images separated by
+scales that comprise a significant fraction of the SPIRE PSF.
+
+It is worth emphasizing that blends likely constitute an interesting path of
+study for future work, as they potentially represent proto-groups or
+proto-clusters during a particular active stage of their evolution.  They are
+also prime examples of systems of sources that are poorly reproduced in
+simulations, as evidenced by the investigations in
+Section~\ref{sec:spatialdist} in this paper.  Table~\ref{tab:photometry} shows
+that one possible means of selecting candidate blends is by comparing the
+SUSSEXtractor and StarFinder flux densities, particularly at 500$\,\mu$m.  A
+large difference between these two measurements likely indicates multiple
+components separated by scales that are a significant fraction of the SPIRE
+beam (e.g., HELAISS02, HXMM20, and HCOSMOS02).
+
+\clearpage
+\input{table_photometry}
 

### 2015-03-31 Code/maketable_source.py

@@ -54,6 +54,15 @@ for itarg in range(0, ntarg):
     iauname = dataphot['iauname'][itarg]
     goodfit = goodfitdat['intrinsic'][itarg]
     #goodfit = goodfitdat['observed'][itarg]
+    s250 = dataphot['f250'][itarg]
+    s350 = dataphot['f350'][itarg]
+    s500 = dataphot['f500'][itarg]
+    e250 = dataphot['e250'][itarg]
+    e350 = dataphot['e350'][itarg]
+    e500 = dataphot['e500'][itarg]
+    strfmt = '{0:12} ${1:4.0f} \pm {2:2.0f}$ & ${3:4.0f} \pm {4:2.0f}$ & ' \
+            + '${5:4.0f} \pm {6:2.0f}$'
+    print(strfmt.format(objname, s250, e250, s350, e350, s500, e500))
     fitdir = anloc + dataname[itarg] + '/' + goodfit + '/'
     os.chdir(fitdir)
 
@@ -343,7 +352,7 @@ for itarg in range(0, ntarg):
             #msgfmt = msg.format(phi_indiv, e_phi_indiv)            
             #msg = '{0:.2f} {1:.2f}'
             #msgfmt = msg.format(mu_indiv, e_mu_indiv)            
-            print(msgfmt)
+            #print(msgfmt)
 
         for isource in range(nsource):
 
@@ -586,8 +595,8 @@ for itarg in range(0, ntarg):
                 ddecdeg_source, e_ddecdeg_source, 
                 flux_indiv, e_flux_indiv, size_indiv, e_size_indiv, q_indiv, 
                 e_q_indiv, phi_indiv, e_phi_indiv, mu_indiv, e_mu_indiv)
-            #msg = '{0:3.0f} {1:3.0f}'
-            #msgfmt = msg.format(phi_indiv, e_phi_indiv)            
+            if nsource > 1:
+                print('             --- & --- & --- ')
             #msg = '{0:.2f} {1:.2f}'
             #msgfmt = msg.format(mu_indiv, e_mu_indiv)            
             #msg = '{0:15} {1:29} {2:.2f} {3:.2f} {4:.2f} {5:.2f} {6:.2f}'

### 2015-03-31 Code/printspireflux.py

@@ -1,0 +1,37 @@
+"""
+
+2015 March 31
+
+Shane Bussmann
+
+Print SPIRE flux densities from latest Monte Carlo simulations on Herschel maps
+using ALMA and Spitzer positions as priors (fiducial), from lens candidate
+catalog (StarFinder), and from original catalog used to select targets for ALMA
+observations (SUSSEXtractor).
+
+"""
+
+from astropy.io import ascii
+
+
+# read in fiducial flux densities
+fiducial = ascii.read('../Data/targetlist.dat')
+
+# read in StarFinder flux densities
+starfinder = ascii.read('../Data/targetlist_starfinder.dat')
+
+# read in SUSSEXtractor flux densities
+sussex = ascii.read('../Data/targetlist_sussextractor.dat')
+
+ntarg = len(fiducial)
+
+for i in range(ntarg):
+    ifid = fiducial[i]
+    isf = starfinder[i]
+    isussex = sussex[i]
+    strfmt = '{0:12} {1:5.0f} {2:5.0f} {3:5.0f} {4:5.0f} ' + \
+            '{5:5.0f} {6:5.0f} {7:5.0f} {8:5.0f} {9:5.0f}'
+    print(strfmt.format(ifid['shortname'], 
+        ifid['f250'], ifid['f350'], ifid['f500'],
+        isf['f250'], isf['f350'], isf['f500'],
+        isussex['f250'], isussex['f350'], isussex['f500']))

### 2015-04-05 LaTeX/ms.tex
Finished addressing comments.
Almost there.
Stay on target, stay on target.

@@
 
-The sample was selected to be a complete, flux-limited set of objects
-satisfying $S_{500} > 95\,$mJy that are not known radio AGN, nearby late-type
-galaxies, or Galactic emission. The selection was designed to assemble a large
-sample of lensed galaxies in the ALMA-accesible HerMES fields, and was
-constructed from the SUSSEXtractor catalogs, which were available prior to the
-ALMA Cycle~0 deadline.  Subsequently, improved efforts to deblend SPIRE
-photometry at 500$\,\mu$m using StarFinder \citep{Wang:2014lr} were introduced
-that formed the basis of the lens selection criteria used in
-\citet{Wardlow:2013lr}.  As a result of the improved deblending algorithms in
-the StarFinder catalogues and \citet{Wardlow:2013lr} a number of objects in our
-sample have significantly lower $S_{500}$ values in the StarFinder catalog than
-in the original SUSSEXtractor catalogs.  This and further investigation into
-the StarFinder catalogs shows that their original flux was boosted by blending
-with nearby sources rather than by gravitational lensing.  For this reason, the
-objects in this sample comprise a combination of lenses and blends of multiple
-sources.
+The sample was selected to be the 29 brightest DSFGs in the Southern sky that
+are not known radio AGN, nearby late-type galaxies, or Galactic emission. The
+selection was designed to assemble a large sample of lensed galaxies in the
+ALMA-accesible HerMES fields, and was constructed from the SUSSEXtractor
+catalogs, which were available prior to the ALMA Cycle~0 deadline.
+Subsequently, improved efforts to deblend SPIRE photometry at 500$\,\mu$m using
+StarFinder \citep{Wang:2014lr} were introduced that formed the basis of the
+lens selection criteria used in \citet{Wardlow:2013lr}.  As a result of the
+improved deblending algorithms in the StarFinder catalogues and
+\citet{Wardlow:2013lr} a number of objects in our sample have significantly
+lower $S_{500}$ values in the StarFinder catalog than in the original
+SUSSEXtractor catalogs.  This and further investigation into the StarFinder
+catalogs shows that their original flux was boosted by blending with nearby
+sources rather than by gravitational lensing.  For this reason, the objects in
+this sample comprise a combination of lenses and blends of multiple sources.
+
+We used positional priors based on the ALMA data presented in this paper to
+obtain the best possible estimates of the total SPIRE flux densities for each
+{\it Herschel} source.  We also used {\it Spitzer}/MIPS
+\citep{2004ApJS..154...25R} imaging to take into consideration the presence of
+nearby 24$\,\mu$m sources that are not detected by ALMA but may still
+contribute to the 250$\,\mu$m emission detected by {\it Herschel}.  Additional
+details on our methodology are provided in Section~\ref{sec:photometry}.  The
+SPIRE flux densities measured in this way represent our ``fiducial'' flux
+densities and are presented in Table~\ref{tab:positions}.  Interested readers
+may refer to Table~\ref{tab:photometry} for a comparison of the fiducial,
+StarFinder and SUSSEXtractor flux densities in tabular form.
 
@@
 DSFGs \citep{Negrello:2010fk, Wardlow:2013lr, Bussmann:2013lr}.  In contrast,
-the sample in this paper should include a more diverse mix of lensed and
-unlensed DSFGs.  On the other hand, this sample is selected from a survey with
-an area that is 200 times larger than that of the Large Apex Bolometer Camera
-Extended Chandra Deep Field Survey \citep[LESS][]{Weis:2009ly}.  It is no
-surprise then, that the median $S_{500}$ in our sample is $\sim3.5$ times
-brighter than the median $S_{500}$ in the sample of ALMA-detected sources in
-LESS, known as ALESS \citep{Hodge:2013qy}.  Our {\it Herschel}-ALMA sample
-opens a new window of discovery space on the bright end of the DSFG luminosity
-function.
+the sample in this paper is expected to include a mix of lensed and unlensed
+DSFGs.  On the other hand, the HerMES survey area is 200 times larger than that
+of the Large Apex Bolometer Camera Extended Chandra Deep Field Survey
+\citep[LESS][]{Weis:2009ly}.  This explains why the median $S_{500}$ in our
+sample is $\sim4$ times brighter than the median $S_{500}$ in the sample of
+ALMA-detected sources in LESS, known as ALESS \citep{Hodge:2013qy}.  Our {\it
+Herschel}-ALMA sample opens a new window of discovery space on the bright end
+of the DSFG luminosity function.
 
@@
 
-Table~\ref{tab:position} provides reference data for the {\it Herschel}-ALMA sample, including
-centroid positions measured from the ALMA 870$\, \mu$m imaging (see
-Section~\ref{sec:almaobs}).
+Table~\ref{tab:position} provides reference data for the {\it Herschel}-ALMA
+sample, including centroid positions measured from the ALMA 870$\, \mu$m
+imaging (see Section~\ref{sec:almaobs}).
 
@@
 The effect on the other source parameters ($r_{\rm s}$, angular separation, and
-$q_{\rm s}$) is less pronounced.  The median source size decreases by a factor of 1.2
-in the {\it Herschel}-ALMA sample after accounting for lensing, but the two-sided KS test
-reveals a $p$-value of 0.174, suggesting that we cannot rule out the null
-hypothesis that both size distributions were drawn from the same parent
-distribution.  We find no significant difference between the axial ratios of
-the apparent and intrinsic distributions, as well as between the angular
-separations of apparent and intrinsic distributions (two-sided KS test
+$q_{\rm s}$) is less pronounced.  The median source size decreases by a factor
+of 1.2 in the {\it Herschel}-ALMA sample after accounting for lensing, but the
+two-sided KS test reveals a $p$-value of 0.174, suggesting that we cannot rule
+out the null hypothesis that both size distributions were drawn from the same
+parent distribution.  We find no significant difference between the axial
+ratios of the apparent and intrinsic distributions, as well as between the
+angular separations of apparent and intrinsic distributions (two-sided KS test
 $p$-values of 0.984 and 0.920, respectively).
@@
 magnification factors for DSFGs with a given apparent flux density
-\citep[chiefly,][]{Lima:2010fk, Wardlow:2013lr}.  We summarize the essential
-elements here and highlight significant differences where appropriate.
-Additional details may be found in Fialkov et al. (in prep.).
+\citep[chiefly,][]{Lima:2010fk, Wardlow:2013lr, Fialkov:2015eu}.  We summarize
+the essential elements here and highlight significant differences where
+appropriate.
 
@@
 redshifts of optical counterparts to ALMA sources identified in ALESS
-\citep{Simpson:2014lr} and has been modified to a lower redshift to reflect the
-relatively blue SPIRE colors of the sample:
+\citep{Simpson:2014lr}:
 
@@
 
-\noindent where $a_z = 1 + z$, $z_\mu = 1.5$, and $\sigma_z = 0.2$.
-
-We explore a variety of intrinsic luminosity functions that are described by
-either a single Schechter function or a broken-power law.  These luminosity
-functions are selected to represent the range of observed instrinsic luminosity
-functions for DSFGs, which are shown in the left panel of
-Figure~\ref{fig:lensstats} and are drawn from the ALESS survey
-\citep{Karim:2013lr} and from interferometric follow-up of the first AzTEC
-survey in COSMOS \citep{Scott:2008qy} using the SMA \citep{Younger:2007fk,
-Younger:2009lr} and PdBI \citep{Miettinen:2015lr}.  Interferometric follow-up
-data in COSMOS \citep{Smolcic:2012zl} and GOODS-N \citep{Barger:2012yg} are
-published, but unknown completeness corrections in the single-dish surveys on
-which these follow-up datasets are based precludes their use here.
-
-The Shechter function we adopt has the usual form \citep{Schechter:1976yq}
-
-\begin{equation}
-\frac{dn}{dS^\prime} = \frac{n_\ast}{S_\ast}
-\left(\frac{S^\prime}{S_\ast}\right)^{-\alpha}
-\exp\left(\frac{-S^\prime}{S_\ast}\right),
-\end{equation}
-
-\noindent while the broken power-law has the form
+\noindent where $a_z = 1 + z$, $z_\mu = 1.5$ (to reflect the relatively blue
+SPIRE colors of the sample), and $\sigma_z = 0.2$.  Alternative
+values for $z_\mu$ and $\sigma_z$ yield second-order perturbations which are
+not significant at the level of our current analysis.
+
+We explore two intrinsic luminosity functions that are intended to bracket the
+plausible range of values for DSFGs based on two interferometric surveys.  One
+is the luminosity function measured in ALESS \citep{Karim:2013lr}, and the
+other is from interferometric follow-up of the first AzTEC survey in COSMOS
+\citep{Scott:2008qy} using the SMA \citep{Younger:2007fk, Younger:2009lr} and
+PdBI \citep{Miettinen:2015lr}.  These interferometric observations have shown
+show that all of the sources in their surveys are either unlensed or lensed by
+magnification factors $<2$.  This is why the ALESS and COSMOS luminosity
+functions represent a plausible range of intrinsic luminosity functions for
+DSFGs.  These luminosity functions are shown in the left panel of
+Figure~\ref{fig:lensstats}.  Interferometric follow-up data in COSMOS
+\citep{Smolcic:2012zl} and GOODS-N \citep{Barger:2012yg} are published, but
+unknown completeness corrections in the single-dish surveys on which these
+follow-up datasets are based precludes their use here.
+
+In detail, we use a broken power-law of the form
 
@@
 
-In Table~\ref{tab:models}, we provide information for two models tested in this
-paper: the \citet{Karim:2013lr} broken power-law that provides a good fit to
-ALESS number counts; and a broken power-law with a brighter break point
-($S_\ast = 15\,$mJy) that provides a good fit to the COSMOS luminosity function
-from \citet{Miettinen:2015lr}.  The interferometric observations in
-\citet{Miettinen:2015lr} show that all of the sources in their survey are
-either unlensed or lensed by magnification factors $<2$.  Therefore, the ALESS
-and COSMOS luminosity functions bracket the plausible range of intrinsic
-luminosity functions for DSFGs.  The data and corresponding luminosity
-functions are shown in the left panel of Figure~\ref{fig:lensstats}.
+Table~\ref{tab:models} provides values for the parameters of the broken
+power-law for the ALESS and COSMOS luminosity functions.  The data and
+corresponding luminosity functions are shown in the left panel of
+Figure~\ref{fig:lensstats}.
 
@@
 
-The product of the model is the lensing optical depth for a given lensing galaxy
-and source galaxy. The sum over the distribution of source redshifts and lens
-masses and redshifts yields the total optical depth for lensing,  $f_\mu$. The
-lensing probability with magnification larger than $\mu$ is then calculated via
-$P(>\mu) = 1-\exp(-f_\mu)$ and the differential probability distribution is
-$P(\mu) = -dP(>\mu)/d\mu$.  The sum over the distribution of source redshifts
-and lens masses and redshifts yields the total probability distribution
-function.
+The product of the model is the lensing optical depth for a given lensing
+galaxy and source galaxy,  $f_\mu$. The lensing probability with magnification
+larger than $\mu$ is then calculated via $P(>\mu) = 1-\exp(-f_\mu)$ and the
+differential probability distribution is $P(\mu) = -dP(>\mu)/d\mu$.  The sum
+over the distribution of source redshifts and lens masses and redshifts yields
+the total probability distribution function.
 
@@
 imaging and associated lens models is the magnification factor of a source with
-a given apparent $S_{870}$.  Due to the large size of the combined sample, we
-can compute the average magnification as a function of $S_{870}$ from the data:
-$\langle\mu_{870}\rangle$.  The same quantity can also be directly computed from our
-model as
+a given apparent $S_{870}$.  We use the combined sample to compute the average
+magnification as a function of $S_{870}$ from the data:
+$\langle\mu_{870}\rangle$.  The same quantity can also be directly computed
+from our model as
 
@@
 $\approx1.2\,$kpc \citep{Simpson:2015ty}.  In contrast, we reported a median
-half-light radius of $1.53\,$kpc in \citet{Bussmann:2013lr}.  Early lens models
-from higher resolution data with ALMA suggest that magnification factors could
-increase by a factor of $\approx 1.5$ \citep{Rybak:2015fk}.  Therefore, it is
-plausible that both of the intrinsic luminosity functions tested here provide
-statistically consistent fits to the data.
+half-light radius of $1.53\,$kpc in \citet{Bussmann:2013lr}.  Lens models from
+higher resolution data with ALMA suggest that magnification factors could
+increase by a factor of $\approx 1.5-2$ \citep{Rybak:2015fk, Tamura:2015lq,
+Dye:2015fp}.  Therefore, it is plausible that both of the intrinsic luminosity
+functions tested here provide statistically consistent fits to the data.
 
@@
 
-In the low flux density regime ($S_{870} < 10\,$mJy), each model predicts that
-10\% of sources experience a magnification satisfying $\mu_{870} > 1.1$.  This
-is in disagreement with the data, which show that $\sim 30\%$ of sources in
-this flux density regime experience $\mu_{870} > 1.1$.  The cause of this
-discrepancy is unclear.  One possibility is simply that we are dealing with
-small number statistics.  We speculate that an alternative explanation might be
-related to the excess number of sources $dN/dA$ found in our ALMA maps with
-small separations from each other (reported in Section~\ref{sec:spatialdist}).
-Essentially, if the {\it Herschel} sources have a high multiplicity rate, with
-ALMA counterparts located close to each other, then adding a lens in front of
-the {\it Herschel} source will magnify {\it all} of the ALMA counterparts.  If,
-on the other hand, the ALMA counterparts were located far away from each other,
-then adding a lens in front of the {\it Herschel} source would not necessarily
-cause all ALMA counterparts to be magnified significantly.  For this reason, it
-is plausible that the observed values reported in this figure are biased
-upwards relative to the simulations outlined in Section~\ref{sec:statpredict}.
-
-In the high flux density regime ($S_{870} > 10\,$mJy), all
-three models as well as the running average in the data show a sharp transition
-from low probability to high probability of being lensed (for either $\mu_{\rm
-min} = 1.1$ or $\mu_{\rm min} = 2.0$).  However, there are major differences in
-where this transition occurs.  For example, the steep Schechter function
-predicts that 50\% of sources with $S_{870} = 50\,$mJy have $\mu_{870} < 1.1$.
-This is inconsistent with the data, which show that all sources with $S_{870} >
-50\,$mJy have $\mu_{870} > 1.1$.  The discrepancy is similar, albeit less
-severe, for the luminosity function from \citet{Karim:2013lr}, where 50\% of
-$S_{870} = 28\,$mJy sources are unlensed.  In contrast, the very steep broken
-power-law luminosity function yields a model in which 50\% of sources with
-$S_{870} = 10\,$mJy experience $\mu_{870} > 1.1$.  This is reasonably
-consistent with the running average from the data.  These results are
-qualitatively similar if the magnification threshold is increased from
-$\mu_{\rm min} = 1.1$ to $\mu_{\rm min} = 2.0$.
-
-If the steep power-law luminosity function is correct, the implications are
-significant.  We should then expect to find $\approx 1$ source satisfying
-$S_{870} > 10\,$mJy in a 1$\,$deg$^2$ survey.  This is about a factor of 3
-lower than the best-fit model in \citet{Karim:2013lr} and a factor of 7 lower
-than our steep Schechter function.  Moreover, it is a factor of 20 lower than
+%In the low flux density regime ($S_{870} < 10\,$mJy), each model predicts that
+%10\% of sources experience a magnification satisfying $\mu_{870} > 1.1$.  This
+%is in disagreement with the data, which show that $\sim 30\%$ of sources in
+%this flux density regime experience $\mu_{870} > 1.1$.  The cause of this
+%discrepancy is unclear.  One possibility is simply that we are dealing with
+%small number statistics.  We speculate that an alternative explanation might be
+%related to the excess number of sources $dN/dA$ found in our ALMA maps with
+%small separations from each other (reported in Section~\ref{sec:spatialdist}).
+%Essentially, if the {\it Herschel} sources have a high multiplicity rate, with
+%ALMA counterparts located close to each other, then adding a lens in front of
+%the {\it Herschel} source will magnify {\it all} of the ALMA counterparts.  If,
+%on the other hand, the ALMA counterparts were located far away from each other,
+%then adding a lens in front of the {\it Herschel} source would not necessarily
+%cause all ALMA counterparts to be magnified significantly.  For this reason, it
+%is plausible that the observed values reported in this figure are biased
+%upwards relative to the simulations outlined in Section~\ref{sec:statpredict}.
+
+Both models tested in this paper exhibit a sharp transition from low
+probability to high probability of being lensed, consistent with the data.
+However, there are significant differences in where this transition flux
+density, $S_{\rm trans}$, occurs --- i.e., where $P(\mu>\mu_{870}$ > 2).  In
+the data, the logistic regression fit yields $S_{\rm trans} = 24\,$mJy,
+whereas the models based on the ALESS and COSMOS luminosity functions yield
+$S_{\rm trans} = 37\,$mJy $S_{\rm trans} = 69\,$mJy, respectively.
+
+Note caveats.
+
+This analysis highlights the difficulty encountered with the luminosity
+function based on the COSMOS data: unlensed sources with $S_{870} > 50\,$mJy
+are over-predicted and lensed sources with $S_{870} < 50\,$mJy are
+under-predicted.  If the ALESS luminosity function continues to be supported by
+the evidence as additional data are obtained, the implications are significant.
+We should then expect to find $\approx 3$ sources satisfying $S_{870} >
+10\,$mJy in a 1$\,$deg$^2$ survey.  This is about a factor of 7 lower than
 typical measurements from single-dish, broad-beam studies
-\citep[e.g.,][]{Weis:2009ly}.  This suggests that very luminous galaxies such as
-GN20 and HFLS3 may be much more rare than previously thought.
+\citep[e.g.,][]{Weis:2009ly}.  This suggests that very luminous galaxies such
+as GN20 and HFLS3 may be much more rare than previously thought.
 
@@
         counterparts.  Of the 9 isolated systems, 5 are strongly lensed by
-        factors of 5-10.  After correcting for amplification, the brightest
+        factors of 5-10 (HECDFS12 is a non-isolated system with a strongly
+        lensed source in it).  After correcting for amplification, the brightest
         source in the sample has $S_{870} = 17.5 \pm 0.4\,$mJy.  There
@@
         these counterparts are typically located within 2$\arcsec$ of each
-        other.  Their separations are much smaller than ALMA counterparts to
-        ALESS sources as well as simulated sources from \citet{HB13}.  This
-        conclusion remains true even when we degrade our ALMA observations to
-        match the spatial resolution, sensitivity, and {\it uv} coverage of the
-        ALESS observations.
-
-    \item Model predictions for the range of magnifications experienced by
-        DSFGs in our sample indicate that a single Schechter function
-        under-predicts the number of lensed sources with apparent $S_{870} >
-        10\,$mJy.  Intrinsic luminosity functions with a broken power-law and a
-        very steep decrease above 8$\,$mJy make better predictions for the
-        fraction of lensed sources with $S_{870} > 10\,$mJy, but they also
-        predict somewhat higher average magnification factors than are seen in
-        combined sample of ALMA and SMA lens models.  This latter result could
-        be explained by limitations in the spatial resolution of the ALMA and
-        SMA imaging, which might lead to the lens models underestimating the
-        magnification factors.
+        other.  Their separations are significantly smaller than ALMA
+        counterparts to ALESS sources as well as simulated sources from
+        \citet{HB13}.  This conclusion remains true even when we degrade our
+        ALMA observations to match the spatial resolution, sensitivity, and
+        {\it uv} coverage of the ALESS observations.
+
+    \item An intrinsic luminosity function for DSFGs with a form that matches
+        observations in COSMOS \citep{Miettinen:2015lr} under-predicts the
+        number of lensed sources with apparent $S_{870} > 10\,$mJy.  A
+        luminosity function based on ALESS observations provides a better match
+        to our magnification measurements.  The interpretation of these results
+        is complicated by the fact that our sample is likely biased towards
+        blends of multiple sources within a {\it Herschel} beam.  Our primary
+        goal is to draw attention to this analysis method as a means to test
+        luminosity functions of DSFGs using wide-field {\it Herschel} data.
 
@@
 
-Our findings suggest that galaxies with intrinsic flux densities above
-$S_{870}^\prime \approx 10\,$mJy are extremely rare.  One possible explanation
-for their rarity is that they are simply the tip of the mass function among
-starbursts.  An alternative is that they represent a very short phase in galaxy
-evolution.  Consistent with this idea is the high multiplicity rate in our ALMA
+If the ALESS luminosity function continues to provide the best predicted
+magnification factors in larger samples with weaker biases, this suggests that
+galaxies with intrinsic flux densities above $S_{870}^\prime \approx 10\,$mJy
+are extremely rare.  One possible explanation for their rarity is that they are
+simply the tip of the mass function among starbursts.  An alternative is that
+they represent a very short phase in galaxy evolution.  It is interesting to
+note that consistent with this idea is the high multiplicity rate in our ALMA
 sample as well as the small projected separations between multiple ALMA
 counterparts.  The inability of numerical simulations to reproduce the small
-projected separations seen in the data might reflect an incomplete theoretical
-understanding of the enhancement in star-formation by interactions and mergers
-of galaxies which are already forming stars at a very high rate.
+projected separations seen in the data might highlight a productive path
+forward to improve our theoretical understanding of the enhancement in
+star-formation by interactions and mergers of galaxies which are already
+forming stars at a very high rate.
 
@@
 
-\section{{\it Herschel}/SPIRE Photometry}
+\section{{\it Herschel}/SPIRE Photometry}\label{sec:photometry}
 

### 2015-04-05 Code/mag-flux.py

@@ -198,7 +198,7 @@ def Pmu_model(modloc, linestyle='solid', lf='Powerlaw', fill=False,
         yy = fractiondata[key]
         color = 'magenta'
         #plt.plot(xx, yy, color=color, linestyle=linestyle, linewidth=1.5)
-        #print(xx[find_nearest(yy, 0.5)])
+        #print(key, xx[find_nearest(yy, 0.5)])
         if fill:
             pass
             #sigmadata = Table.read('../Data/Sig_1p1_30powerlaw.txt',
@@ -220,7 +220,7 @@ def Pmu_model(modloc, linestyle='solid', lf='Powerlaw', fill=False,
         yy = fractiondata[key]
         color = 'blue'
         plt.plot(xx, yy, color=color, linestyle=linestyle, linewidth=1.5)
-        print(xx[find_nearest(yy, 0.5)])
+        print(key, xx[find_nearest(yy, 0.5)])
         if addlabel:
             plt.plot(xx, yy, color=color, linestyle=linestyle, 
                     label=r'$S_\star = 15\,$mJy', linewidth=1.5)

### 2015-04-15 LaTeX/Bussmann14_text_WCv1p0.tex
Revised draft
Nearly ready for submission…

We also compare our results to mock catalogues based on the methodology presented in \cite{Cowley14}, for full details we refer the reader to Cowley et al. but summarise it briefly here. An updated version of the \galform \citep[e.g.][Lacey et al. in preparation]{Cole00} semi-analytic galaxy formation model is used to populate halo merger trees \citep[e.g.][]{PCH08,Jiang14} derived from a Millennium style $N$-body dark matter only simulation \citep{Springel05,Guo13} with WMAP7 cosmology \citep{Komatsu11}.  Submm flux is calculated using a model based on the radiative transfer.  Dust is assumed to exist in two components,  dense molecular clouds and a diffuse ISM.  Energy absorbed from starlight by each dust component is calculated self-consistently. The dust is then assumed to emit radiation as a modified blackbody, assuming thermal equilibrium.

Three randomly orientated 20 deg$^2$ lightcone catalogues are generated using the method described in \cite{Merson13}.  We choose as the lower flux limit for inclusion of simulated galaxies into our lightcone catalogue $S_{500\mu\rm{m}}>0.1$ mJy, as this is the limit at which we recover 90 per cent of the extragalactic background light (EBL) as predicted by our model (122 Jy deg$^{-2}$). This is in excellent agreement with observations from the \emph{COBE} satellite \citep[e.g.][]{Puget96,Fixsen98}. This ensures we have a realistic 500 $\mu$m  background in our mock images.

Mock imaging is created by binning the lightcone galaxies onto a pixelated grid which is then convolved with a  36 arcsec FWHM Gaussian ($\sim$ \emph{Herschel} SPIRE beam at 500 $\mu$m).  The image is then constrained to have a zero mean by the subtraction of a uniform background.  For simplicity we do not attempt to add any instrumental noise, nor perform any further filtering of the mock image.

This procedure is repeated at 350 and 250 $\mu$m in order to provide simulated \emph{Herschel} photometry.  We adjust the FWHM of the Gaussian PSF to 25 (18) arcsec at 350 (250) $\mu$m, and change the lower limit of inclusion into our lightcone to ensure 90 per cent of the predicted EBL is recovered at each wavelength.

Source positions are then selected as maxima in the mock 250 $\mu$m image, with the position and flux of the source being recorded as the center and value of the maximal pixel.  To simulate `deblended' \emph{Herschel} photometry we simply read off the value of the pixel located at the position of the $250$ $\mu$m maxima in the 350 and 500 $\mu$m images. For all \emph{Herschel} sources with $S_{500\mu\rm{m}}>50$ mJy we then identify galaxies from our lightcone catalogues within a 9 arcsec radius ($\sim$ ALMA primary beam) of the source position, modelling the ALMA primary beam profile as a Gaussian with an 18 arcsec FWHM and a maximum sensitivity of 1 mJy.

### 2015-04-15 LaTeX/ms.tex
Revised draft
Nearly ready for submission…

@@
 
-%./authors_list hermes_authors_data_dr1_20121108.txt apj rsb dr fialkov hayward cowley almalens
-
+%./authors_list hermes_authors_data_dr1_20121108.txt apj rsb dr fialkov scudders hayward cowley almalens
 \author{R.~S.~Bussmann\altaffilmark{1},
@@
 A.~Fialkov\altaffilmark{2},
-C.~Hayward\altaffilmark{3,4},
-W.~Cowley\altaffilmark{5},
-J.~Bock\altaffilmark{6,7},
-J.~Calanog\altaffilmark{8},
-A.~Cooray\altaffilmark{8},
-F.~De Bernardis\altaffilmark{8},
-R.~Hopwood\altaffilmark{9},
-M.~Jarvis\altaffilmark{10},
-C.~Lacey\altaffilmark{5},
-A.~Loeb\altaffilmark{4},
-S.~J.~Oliver\altaffilmark{11},
-I.~P{\'e}rez-Fournon\altaffilmark{12,13},
-I.~G.~Roseboom\altaffilmark{11,14},
-A.~J.~Smith\altaffilmark{11},
-L.~Wang\altaffilmark{11},
-J.~Wardlow\altaffilmark{15}}
+J.~Scudders\altaffilmark{3},
+C.~Hayward\altaffilmark{4,5},
+W.~Cowley\altaffilmark{6},
+J.~Bock\altaffilmark{7,8},
+J.~Calanog\altaffilmark{9},
+S.~C.~Chapman\altaffilmark{10},
+A.~Cooray\altaffilmark{9},
+F.~De Bernardis\altaffilmark{9},
+Hai~Fu\altaffilmark{11},
+R.~Gavazzi\altaffilmark{12},
+R.~Hopwood\altaffilmark{13},
+R.~J.~Ivison\altaffilmark{14,15},
+M.~Jarvis\altaffilmark{16},
+C.~Lacey\altaffilmark{6},
+A.~Loeb\altaffilmark{5},
+S.~J.~Oliver\altaffilmark{3},
+I.~P{\'e}rez-Fournon\altaffilmark{17,18},
+D.~Rigopoulou\altaffilmark{19,20},
+I.~G.~Roseboom\altaffilmark{3,15},
+Douglas~Scott\altaffilmark{21},
+A.~J.~Smith\altaffilmark{3},
+L.~Wang\altaffilmark{3},
+J.~Wardlow\altaffilmark{22}}
 \altaffiltext{$\dagger$}{Herschel is an ESA space observatory with science
@@
 \altaffiltext{2}{Departement de Physique, Ecole Normale Sup erieure, CNRS, 24 rue Lhomond, Paris, 75005 France}
-\altaffiltext{3}{TAPIR 350-17, California Institute of Technology, 1200 E. California Boulevard, Pasadena, CA 91125}
-\altaffiltext{4}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
-\altaffiltext{5}{Institute for Computational Cosmology, Department of Physics, University of Durham, South Road, Durham, DH1 3LE, UK}
-\altaffiltext{6}{California Institute of Technology, 1200 E. California Blvd., Pasadena, CA 91125}
-\altaffiltext{7}{Jet Propulsion Laboratory, 4800 Oak Grove Drive, Pasadena, CA 91109}
-\altaffiltext{8}{Dept. of Physics \& Astronomy, University of California, Irvine, CA 92697}
-\altaffiltext{9}{Astrophysics Group, Imperial College London, Blackett Laboratory, Prince Consort Road, London SW7 2AZ, UK}
-\altaffiltext{10}{Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Hertfordshire AL10 9AB, UK}
-\altaffiltext{11}{Astronomy Centre, Dept. of Physics \& Astronomy, University of Sussex, Brighton BN1 9QH, UK}
-\altaffiltext{12}{Instituto de Astrof{\'\i}sica de Canarias (IAC), E-38200 La Laguna, Tenerife, Spain}
-\altaffiltext{13}{Departamento de Astrof{\'\i}sica, Universidad de La Laguna (ULL), E-38205 La Laguna, Tenerife, Spain}
-\altaffiltext{14}{Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
-\altaffiltext{15}{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 Copenhagen, Denmark}
+\altaffiltext{3}{Astronomy Centre, Dept. of Physics \& Astronomy, University of Sussex, Brighton BN1 9QH, UK}
+\altaffiltext{4}{TAPIR 350-17, California Institute of Technology, 1200 E. California Boulevard, Pasadena, CA 91125}
+\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
+\altaffiltext{6}{Institute for Computational Cosmology, Department of Physics, University of Durham, South Road, Durham, DH1 3LE, UK}
+\altaffiltext{7}{California Institute of Technology, 1200 E. California Blvd., Pasadena, CA 91125}
+\altaffiltext{8}{Jet Propulsion Laboratory, 4800 Oak Grove Drive, Pasadena, CA 91109}
+\altaffiltext{9}{Dept. of Physics \& Astronomy, University of California, Irvine, CA 92697}
+\altaffiltext{10}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}
+\altaffiltext{11}{Department of Physics and Astronomy, The University of Iowa, 203 Van Allen Hall, Iowa City, IA 52242}
+\altaffiltext{12}{Institut d'Astrophysique de Paris, UMR 7095, CNRS, UPMC Univ. Paris 06, 98bis boulevard Arago, F-75014 Paris, France}
+\altaffiltext{13}{Astrophysics Group, Imperial College London, Blackett Laboratory, Prince Consort Road, London SW7 2AZ, UK}
+\altaffiltext{14}{UK Astronomy Technology Centre, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
+\altaffiltext{15}{Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
+\altaffiltext{16}{Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Hertfordshire AL10 9AB, UK}
+\altaffiltext{17}{Instituto de Astrof{\'\i}sica de Canarias (IAC), E-38200 La Laguna, Tenerife, Spain}
+\altaffiltext{18}{Departamento de Astrof{\'\i}sica, Universidad de La Laguna (ULL), E-38205 La Laguna, Tenerife, Spain}
+\altaffiltext{19}{RAL Space, Rutherford Appleton Laboratory, Chilton, Didcot, Oxfordshire OX11 0QX, UK}
+\altaffiltext{20}{Department of Astrophysics, Denys Wilkinson Building, University of Oxford, Keble Road, Oxford OX1 3RH, UK}
+\altaffiltext{21}{Department of Physics \& Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T~1Z1, Canada}
+\altaffiltext{22}{Dark Cosmology Centre, Niels Bohr Institute, University of
+Copenhagen, Juliane Maries Vej 30, 2100 Copenhagen, Denmark}
 
@@
     experience a significant flux boost from gravitational lensing ($\mu >
-    1.1$), but only 6 are strongly lensed and show multiple images.  Combined
-    with our previous work on brighter {\it Herschel} sources, the lens models
-    presented here constrain the shape of the intrinsic luminosity function for
-    DSFGs to have a break near 8$\,$mJy at 880$\,\mu$m with a very steep fall
-    off at higher flux densities.  We introduce and make use of {\sc
-    uvmcmcfit}, a general purpose and publicly available Markov chain Monte
-    Carlo visibility plane analysis tool to analyze the source properties.
-    Nearly 70\% of the {\it Herschel} sources break down into multiple ALMA
-    counterparts, consistent with previous research indicating that the
-    multiplicity rate is high in bright sources discovered in single-dish
-    sub-mm or FIR surveys.  The ALMA counterparts to our {\it Herschel} targets
-    are located significantly closer to each other than ALMA counterparts to
-    sources found in the LABOCA ECDFS Submillimeter Survey.  Theoretical models
-    underpredict the excess number of sources with small separations seen in
-    our ALMA sample.  The high multiplicity rate and low projected separations
-    between sources seen in our sample argue in favor of interactions and
-    mergers plausibly driving both the prodigious emission from the brightest
-    DSFGs as well as the sharp downturn above $S_{880} = 8\,$mJy.
+    1.1$), but only 6 are strongly lensed and show multiple images.  We
+    introduce and make use of {\sc uvmcmcfit}, a general purpose and publicly
+    available Markov chain Monte Carlo visibility plane analysis tool to
+    analyze the source properties.  Combined with our previous work on brighter
+    {\it Herschel} sources, the lens models presented here tentatively favor
+    intrinsic luminosity functions for DSFGs with a break near 8$\,$mJy at
+    880$\,\mu$m and a steep fall off at higher flux densities.  Nearly 70\% of
+    the {\it Herschel} sources break down into multiple ALMA counterparts,
+    consistent with previous research indicating that the multiplicity rate is
+    high in bright sources discovered in single-dish sub-mm or FIR surveys.
+    The ALMA counterparts to our {\it Herschel} targets are located
+    significantly closer to each other than ALMA counterparts to sources found
+    in the LABOCA ECDFS Submillimeter Survey.  Theoretical models underpredict
+    the excess number of sources with small separations seen in our ALMA
+    sample.  The high multiplicity rate and low projected separations between
+    sources seen in our sample argue in favor of interactions and mergers
+    plausibly driving both the prodigious emission from the brightest DSFGs as
+    well as the sharp downturn above $S_{880} = 8\,$mJy.
 
@@
 SPIRE flux densities measured in this way represent our ``fiducial'' flux
-densities and are presented in Table~\ref{tab:positions}.  Interested readers
+densities and are presented in Table~\ref{tab:position}.  Interested readers
 may refer to Table~\ref{tab:photometry} for a comparison of the fiducial,
@@
 strongly lensed sources are removed from the sample, the median intrinsic flux
-density is 1.3 times lower than the median apparent flux density.  If we only
-consider examples of weak lensing (i.e., removing the unlensed sources), the
-factor rises back to 1.6.  These factors will be significant sources of error
-if they are incorrectly ignored.  When discussing the intrinsic properties of
-bright sources \citep[including their luminosity functions,
-e.g.][]{Wyithe:2011rm} discovered in wide-field FIR or mm surveys, it is
-critical to consider the effects of lensing.
+density is 1.3 times lower than the median apparent flux density.  Removing the
+unlensed sources from consideration pushes this factor back to 1.6.  At these
+levels, failing to correct for amplification due to gravitational lensing will
+be a significant source of error, since the absolute calibration uncertainty is
+typically of order 5-10\%.  When discussing the intrinsic properties of bright
+sources \citep[including their luminosity functions, e.g.][]{Wyithe:2011rm}
+discovered in wide-field FIR or mm surveys, it is critical to consider the
+effects of lensing.
 
@@
 
-Finally, the brightest single source in the {\it Herschel}-ALMA sample is
-HADFS11.0, with an intrinsic flux density of $S_{870} = 17.5 \pm
-0.4\,$mJy.  However, there are also two objects with multiple sources that
-have separations smaller than 1$\arcsec$, which have summed flux densities
-comparable to this; namely HADFS02 (16.8$\,$mJy) and HECDFS13 (15.3$\,$mJy).  This is
-approaching the values found in the most extreme systems, such as GN20
+Finally, the brightest source in the {\it Herschel}-ALMA sample is
+HADFS11.0, with an intrinsic flux density of $S_{870} = 17.5 \pm 0.4\,$mJy.
+However, there are also two objects with multiple sources that have separations
+smaller than 1$\arcsec$, which have summed flux densities comparable to this;
+namely HADFS02 (16.8$\,$mJy) and HECDFS13 (15.3$\,$mJy).  This is approaching
+the values found in the most extreme systems, such as GN20
 \citep[20.6$\,$mJy,][]{2006MNRAS.370.1185P} and HFLS3
@@
 870$\,\mu$m flux density, $S_{\rm component}$.  Figure~\ref{fig:componentflux}
-shows these values for our {\it Herschel}-ALMA sample and compares to ALESS.  Lensing has a
-significant impact on the apparent flux densities of many objects in our ALMA
-sample, so we are careful to show only intrinsic flux densities in this
-diagram.  This diagram reflects the known result that the multipicity rate in
-ALESS rises and the average fractional contribution per component decreases
+shows these values for our {\it Herschel}-ALMA sample and compares to ALESS.
+Lensing has a significant impact on the apparent flux densities of many objects
+in our ALMA sample, so we are careful to show only intrinsic flux densities in
+this diagram.  This diagram reflects the known result that the multipicity rate
+in ALESS rises and the average fractional contribution per component decreases
 with increasing $S_{\rm total}$ \citep{Hodge:2013qy}.  A simple extrapolation
-of this phenomenon to the flux density regime probed by our {\it Herschel}-ALMA sample would
-have suggested a very high multiplicity rate and a very low average fractional
-contribution per component.  The multiplicity rate in our sample is indeed
-higher, but we find that the average fractional contribution per component
-hovers around 0.4 for essentially the full range in our sample.  This is a
-reflection of the fact that the brightest {\it Herschel} DSFGs comprise 1-3
-ALMA components, not 5-10 ALMA components as might have been expected from a
-naive extrapolation of the ALESS results.
+of this phenomenon to the flux density regime probed by our {\it Herschel}-ALMA
+sample would have suggested a very high multiplicity rate and a very low
+average fractional contribution per component.  The multiplicity rate in our
+sample is indeed higher, but we find that the average fractional contribution
+per component hovers around 0.4 for essentially the full range in our sample.
+This is a reflection of the fact that the brightest {\it Herschel} DSFGs
+comprise 1-3 ALMA components, not 5-10 ALMA components as might have been
+expected from a naive extrapolation of the ALESS results.
 
@@
 counterparts found in our {\it Herschel}-ALMA sample (green squares), in ALESS
-(pink diamonds), and in mock catalogs from \citet{HB13} (color scale).  Sources
-identified in our {\it Herschel}-ALMA sample lie much closer to each other than
-they do in either ALESS or the \citet{HB13} simulations.  {\it Right}: Number
-of ALMA sources per annular area as a function of angular separation from the
-ALMA centroid.  Results are shown for our ALMA sample (thick green line), ALESS
-(thick pink line), the \citet{HB13} simulations (thick blue line), and our {\it
-Herschel}-ALMA sample as would have been seen with ALESS resolution and
-sensitivity (thick orange line).  We also show the range of separations that
-would be seen if sources were randomly distributed within the ALMA field of
-view (green hatched region with solid and dashed green lines).  The DSFGs in
-our {\it Herschel}-ALMA sample show a much stronger excess on angular
-separation scales $<2\arcsec$ compared to ALESS and the \citet{HB13}
-simulations, even when taking into account the difference in sensitivity and
-spatial resolution between our ALMA observations and those of ALESS.  }
+(pink diamonds) and mock catalogs from \citet{HB13} and \citet{Cowley:2015lr}
+(blue plus signs and orange crosses, respectively).  Sources identified in our
+{\it Herschel}-ALMA sample lie much closer to each other than they do in either
+ALESS or the \citet{HB13} simulations.  {\it Right}: Number of ALMA sources per
+annular area as a function of angular separation from the ALMA centroid.
+Symbols and colors are as in left panel.  We also show how our {\it
+Herschel}-ALMA sample would appear if it had been observed with ALESS
+resolution and sensitivity (light green squares).  The range of separations
+that would be seen if sources were randomly distributed within the ALMA field
+of view is also shown (dark dashed line and hatched region).  The {\it
+Herschel}-ALMA DSFGs show a significantly stronger excess on angular separation
+scales $<2\arcsec$ compared to both ALESS and the \citet{HB13} simulations,
+even when taking into account the difference in sensitivity and spatial
+resolution between our ALMA observations and those of ALESS.  The simulations
+from \citet{Cowley:2015lr} show better agreement with the data, likely due to
+the more sophisticated treatment of blending compared to \citet{HB13}.}
 \label{fig:dNdA}
@@
 to investigate these possibilities further, we make use of mock catalogs of
-DSFGs that are based on numerical simulations and presented by \citet{HB13}.
-We summarize the methodology used to generate $dN/dA$ values from the mock
-catalogs here and refer the reader to \citet{HB13} for full details.
+DSFGs that are based on numerical simulations and presented by \citet{HB13} and
+\citet{Cowley:2015lr}.
+
+We begin with the \citet{HB13} simulations, summarizing the methodology used to
+generate the mock catalogs here and refering the reader to \citet{HB13} for
+full details.
 
@@
 a projected angular distance $d_{\rm neighbor}$.  To obtain a direct comparison
-with our {\it Herschel}-ALMA sample, we use $S_{\rm thresh} = 1.0\,$mJy (corresponding to the
-5$\sigma$ limit of the ALMA data) and $d_{\rm neighbor} = 40\arcsec$
-(reflecting the size of the {\it Herschel} beam at 500$\,\mu$m).  We use the
-known positions in the mock catalogs for all blended sources and compute
-centroid and separations for every blended source using the same methodology as
-we applied to our {\it Herschel}-ALMA sample and to ALESS.
-
-The $dN/dA$ values found in the mock catalogs are shown by the
-thick blue line in Figure \ref{fig:dNdA}.  There is a significant increase in
+with our {\it Herschel}-ALMA sample, we use $S_{\rm thresh} = 1.0\,$mJy
+(corresponding to the 5$\sigma$ limit of the ALMA data) and $d_{\rm neighbor} =
+40\arcsec$ (reflecting the size of the {\it Herschel} beam at 500$\,\mu$m).  We
+use the known positions in the mock catalogs for all blended sources and
+compute centroid and separations for every blended source using the same
+methodology as we applied to our {\it Herschel}-ALMA sample and to ALESS.
+
+The $dN/dA$ values found in the mock catalogs are shown by the thick blue line
+and plus signs in Figure \ref{fig:dNdA}.  There is a significant increase in
 $dN/dA$ on separations smaller than $\approx 0\farcs5$, but the amplitude of
@@
 limitation). To explore whether interaction-induced starbursts are the origin
-of the excess at small angular separations observed in our {\it Herschel}-ALMA sample, we
-modified the \citet{HB13} model to include a crude treatment of
+of the excess at small angular separations observed in our {\it Herschel}-ALMA
+sample, we modified the \citet{HB13} model to include a crude treatment of
 interaction-induced SFR enhancement. Mock galaxies with one or more neighbors
@@
 smaller than 1$\,$kpc, the imposed increase was a factor of ten.  Because these
-SFR enhancements are greater than suggested by simulations \citep[e.g.][]{Cox08,
-H11, H14, Torrey12} or observations of local galaxy pairs
+SFR enhancements are greater than suggested by simulations
+\citep[e.g.][]{Cox08, H11, H14, Torrey12} or observations of local galaxy pairs
 \citep[e.g.][]{Scudder12, Patton13}, we consider this test to provide an upper
@@
 sophisticated treatment of blending is necessary.
+
+To explore this possibility, we investigate mock catalogs based on the
+methodology presented in \citet{Cowley:2015lr}.  Here, we give a brief summary
+and refer the interested reader to \citet{Cowley:2015lr} for full details. An
+updated version of the {\sc galform} \citep[e.g.][Lacey et al. in
+preparation]{Cole:2000fk} semi-analytic galaxy formation model is used to
+populate halo merger trees \citep[e.g.][]{Parkinson:2008qy, Jiang:2014lr}
+derived from a Millennium style $N$-body dark matter only simulation
+\citep{Springel:2005lr, Guo:2013lr} with WMAP7 cosmology
+\citep{Komatsu:2011fk}.  Submm flux is calculated using a model based on the
+radiative transfer.  Dust is assumed to exist in two components,  dense
+molecular clouds and a diffuse ISM.  Energy absorbed from starlight by each
+dust component is calculated self-consistently.  The dust is then assumed to
+emit radiation as a modified blackbody, assuming thermal equilibrium.
+
+Three randomly orientated 20 deg$^2$ lightcone catalogues are generated using
+the method described in \citet{Merson:2013lr}.  We choose as the lower flux
+limit for inclusion of simulated galaxies into our lightcone catalogue
+$S_{500\mu\rm{m}}>0.1$ mJy, as this is the limit at which we recover 90 per
+cent of the extragalactic background light (EBL) as predicted by our model (122
+Jy~deg$^{-2}$). This is in excellent agreement with observations from the
+\emph{COBE} satellite \citep[e.g.,][]{Puget:1996lr}. This ensures we have a
+realistic 500 $\mu$m  background in our mock images.
+
+Mock imaging is created by binning the lightcone galaxies onto a pixelated grid
+which is then convolved with a 36$\arcsec$ FWHM Gaussian (corresponding to the
+\emph{Herschel} SPIRE beam at 500$\,\mu$m).  The image is then constrained to
+have a zero mean by the subtraction of a uniform background.  No instrumental
+noise is added, nor are any further filtering procedures applied to the mock
+image.  This procedure is repeated at 350$\,\mu$m and 250$\,\mu$m in order to
+provide simulated \emph{Herschel} photometry, adjusting the FWHM of the
+Gaussian PSF appropriately and changing the lower limit of inclusion into our
+lightcone to ensure 90 per cent of the predicted EBL is recovered at each
+wavelength.
+
+Source positions are selected as maxima in the mock 250$\,\mu$m image, with the
+position and flux of the source being determined by the maximal pixel.  To
+simulate `deblended' \emph{Herschel} photometry we record the value of the
+pixel located at the position of the 250$\,\mu$m maxima in the 350$\,\mu$m and
+500$\,\mu$m images. We select all \emph{Herschel} sources satisfying
+$S_{500\,\mu\rm{m}}>50\,$mJy and $z > 1$ to identify galaxies from our
+lightcone catalogs within a 9$\arcsec$ radius of the source position, modelling
+the ALMA primary beam profile as a Gaussian with an 18$\arcsec$ FWHM and a
+maximum sensitivity of 1$\,$mJy.
+
+The $dN/dA$ values derived from the \citet{Cowley:2015lr} mock catalogs are
+shown by the thick orange line and crosses in Figure \ref{fig:dNdA}.  Here, the
+amplitude of the increase in $dN/dA$ on separations smaller than $\approx
+2\arcsec$ mimics the trend seen in the data.  However, there is a deficit of
+multiple systems with separations of $0\farcs5$ or less compared to the {\it
+Herschel}-ALMA sample.  This result suggests that a sophisticated treatment of
+blending yields better agreement between simulations and observations but the
+simulations still under-predict the number of multiple systems with small
+separations.
+
+Future work on the theoretical side should seek to determine if the application
+of the \citet{Cowley:2015lr} blending algorithm to the \citet{HB13} simulations
+yields similarly better agreement with the data.  On the observational side, it
+is critical to establish whether {\it Herschel} sources with multiple ALMA
+counterparts are physically related by measuring spectroscopic redshifts to
+individual counterparts.  Fortunately, this is a viable project today with the
+VLA and ALMA.
 
@@
 density, $S_{\rm trans}$, occurs --- i.e., where $P(\mu>\mu_{870}$ > 2).  In
-the data, the logistic regression fit yields $S_{\rm trans} = 24\,$mJy,
+the data, the logistic regression fit yields $S_{\rm trans} = 24\pm3\,$mJy
+(error accounts only for statistical uncertainty in $S_{870}$ and $\mu_{870}$),
 whereas the models based on the ALESS and COSMOS luminosity functions yield
@@
 \citep[e.g.,][]{Weis:2009ly}.  This suggests that very luminous galaxies such
-as GN20 and HFLS3 may be much more rare than previously thought.
+as GN20 and HFLS3 may be more rare than previously thought.
 
@@
     \item 36/62 ALMA sources experience significant amplification from a nearby
-        foreground galaxy ($\mu_{870} > 1.1$).  The median amplification in the
-        sample is $\mu_{870} = 1.6$.  Only 6 sources show morphology typical of
-        strong gravitational lensing and could be identified as lenses from the
-        ALMA imaging alone.  A multi-wavelength approach is critical to
-        identifying structure along the line of sight and determining an
-        unbiased measurement of the flux densities in our sample.
+        foreground galaxy that is comparable to or greater than the absolute
+        calibration uncertainty (i.e., $\mu_{870} > 1.1$).  The median
+        amplification in the subset that experiences lensing is $\mu_{870} =
+        1.6$.  Only 6 sources show morphology typical of strong gravitational
+        lensing and could be identified as lenses from the ALMA imaging alone.
+        A multi-wavelength approach is critical to identifying structure along
+        the line of sight and determining an unbiased measurement of the flux
+        densities in our sample.
 
@@
         counterparts to ALESS sources as well as simulated sources from
-        \citet{HB13}.  This conclusion remains true even when we degrade our
+        \citet{HB13} and \citet{Cowley:2015lr}, although the improved
+        treatment of blending by the latter yields superior agreement with the
+        data.  This conclusion remains true even when we degrade our
         ALMA observations to match the spatial resolution, sensitivity, and
@@
 what fraction of {\it Herschel} sources are actually physically associated with
-each other (and not just a result of projection effects along the line of
+each other (and not simply a result of projection effects along the line of
 sight).  %Molecular spectroscopy will also provide critical information about
@@
 
-\clearpage
+%\clearpage
 \input{table_photometry}

### 2015-04-15 Code/addsourceid.py

@@ -1,0 +1,27 @@
+"""
+
+Add a source ID column to the Cowley mock catalog.
+
+"""
+
+from astropy.io import ascii
+
+
+dataloc = '../Data/SPIRE_ALMA_Cat_v4.txt'
+data = ascii.read(dataloc)
+
+nrows = len(data)
+
+sourcevector = [0]
+sourceID = 0
+sourceRAprevious = data['SourceX'][0]
+for i in range(1, nrows):
+    sourceRA = data['SourceX'][i]
+    if sourceRA != sourceRAprevious:
+        sourceID += 1
+    sourcevector.append(sourceID)
+    sourceRAprevious = sourceRA
+
+data['sourceID'] = sourcevector
+
+data.write('SPIRE_ALMA_Cat_v4_sourceID.txt', format='ascii')

### 2015-04-15 Code/allpositions.py

@@ -11,6 +11,7 @@ and radius 2.
 """
 
 from astropy.table import Table
+from astropy.io import ascii
 import matplotlib
 import matplotlib.pyplot as plt
 from pylab import savefig
@@ -19,6 +20,8 @@ import sep_util
 from scipy.io import readsav
 
 
+model = 'Hayward'
+
 # set font properties
 font = {'family' : 'Arial',
         'weight' : 'normal',
@@ -26,7 +29,7 @@ font = {'family' : 'Arial',
 matplotlib.rc('font', **font)
 matplotlib.rcParams['axes.linewidth'] = 1.2
 
-fig = plt.figure(figsize=(5.8, 4.5))
+fig = plt.figure(figsize=(4.5, 4.5))
 plt.clf()
 
 # Plotting parameters
@@ -79,17 +82,46 @@ dec_alma = numpy.array(sep_alma[3]) * 3600
 plt.plot(ra_alma, dec_alma, afmt, alpha=0.8, color=acolor, ms=ams, 
         label='Herschel-ALMA')
 
+#if model == 'Hayward':
 # add Hayward et al. simulated galaxies
-h13 = readsav('../Data/shane_data.sav')
+h13 = readsav('../Data/100_brightest_shane_data.sav')
 flux_h13 = h13['s850']
 #hithresh = flux_h13 > 2
-flux_h13 = h13['s850']#[hithresh]
-ra_h13 = h13['dra']#[hithresh]
-dec_h13 = h13['ddec']#[hithresh]
+flux_h13 = h13['bright_s850']#[hithresh]
+ra_h13 = h13['bright_dra']#[hithresh]
+dec_h13 = h13['bright_ddec']#[hithresh]
+smod = 'HB13'
+#else:
+c15 = ascii.read('../Data/SPIRE_ALMA_Cat_v4.txt')
+s500_c15 = c15['SourceS500']
+zc = c15['z']
+hithresh = (s500_c15 > 50) & (zc > 1)
+c15 = c15[hithresh]
+c15 = sep_util.rmSingles(c15, targetstring='SurveyID')
+nmultiples = len(c15)
 
-plt.hexbin(ra_h13, dec_h13, cmap='rainbow')
-cbar = plt.colorbar()
-cbar.set_label(r'$N_{\rm HB13}$')
[…]

### 2015-04-15 Code/componentflux.py

@@ -115,9 +115,9 @@ yyyerrbarger = fluxcomponent['S850'] / 10.
 # **********
 
 # Plotting parameters
-bargcolor = 'Black'
-bargms = 4
-bargfmt = '.'
+bargcolor = 'orange'
+bargms = 6
+bargfmt = 'x'
 
 # Load the data
 #fluxcomponent_file = '../Data/barger2012.dat'
@@ -302,8 +302,8 @@ ax1.plot(xxxhodge, yyyhodge, hodgefmt, ms=hodgems, mfc=hodgecolor,
 #        capsize=0)
 #ax1.plot(xxxbarger, yyybarger, bargfmt, ms=bargms, color=bargcolor, label='Barger+12')
 
-ax1.plot(xxxbarger, yyybarger, bargfmt, ms=bargms, color=bargcolor,
-        label='Cowley+2014 SAM')
+#ax1.plot(xxxbarger, yyybarger, bargfmt, ms=bargms, color=bargcolor,
+#        label='C15 Simulation', mew=1.2)
 #ax1.plot(xxxbarger, yyybarger, bargfmt, ms=bargms, color=bargcolor,
 #        mec='none', label='Cowley+2014')
 

### 2015-04-15 Code/dnda.py

@@ -11,6 +11,7 @@ and radius 2.
 """
 
 from astropy.table import Table
+from astropy.io import ascii
 import matplotlib
 import matplotlib.pyplot as plt
 from pylab import savefig
@@ -40,9 +41,9 @@ bin_edges = numpy.arange(0, nbins + 1, binwidth)
 # Herschel source and each LESS source.  So far, the factor of 3 was meant to
 # reproduce the median S500 flux density ratio, but S870 will be more accurate.
 
-simcolor = 'orange'
+simcolor = 'MediumSpringGreen'
 simms = 4
-simfmt = 's'
+simfmt = 's-'
 
 fluxcomponent_file = '../Data/table_ALESSsim.dat'
 fluxcomponent = Table.read(fluxcomponent_file, format='ascii')
@@ -59,16 +60,44 @@ simalma = sep_util.getSeparation(fluxcomponent, rastring='ra_alma', \
 avgsep_simalma, wmeansep_simalma, ra_simalma, dec_simalma = simalma
 
 sep_util.histArea(avgsep_simalma, nbins, color=simcolor, fmt=simfmt, ms=simms,
-        norm=nmultiples)
+        norm=nmultiples, label='Herschel-ALMA ALESS-Sim')
 
 #sep_util.simArea(fluxcomponent, nsim, bin_edges, fluxstring='S_870_observed',
 #        edgecolor=asimcolor, facecolor='none', hatch='\\', norm=nmultiples)
+
+# *********
+# Cowley simulation
+# *********
+
+c15color = 'Orange'
+c15ms = 6
+c15fmt = 'x-'
+c15mew = 1.5
+
+c15 = ascii.read('../Data/SPIRE_ALMA_Cat_v4.txt')
+s500_c15 = c15['SourceS500']
+zc = c15['z']
+hithresh = (s500_c15 > 50) & (zc > 1)
+c15 = c15[hithresh]
+c15 = sep_util.rmSingles(c15, targetstring='SurveyID')
+nmultiples = len(c15)
+
+simc15 = sep_util.getSeparation(c15, degrees=True, rastring='GalaxyX', \
+        decstring='GalaxyY', fluxstring='GalaxyS850', targetstring='SurveyID')
+avgsep_c15, wmeansep_c15, ra_c15, dec_c15 = simc15
+sep_util.histArea(avgsep_c15, nbins, color=c15color, fmt=c15fmt,
[…]

### 2015-04-15 Code/mag-flux.py

@@ -200,17 +200,18 @@ def Pmu_model(modloc, linestyle='solid', lf='Powerlaw', fill=False,
         #plt.plot(xx, yy, color=color, linestyle=linestyle, linewidth=1.5)
         #print(key, xx[find_nearest(yy, 0.5)])
         if fill:
-            pass
-            #sigmadata = Table.read('../Data/Sig_1p1_30powerlaw.txt',
-            #        format='ascii')
-            #y1 = fractiondata['karim'] - sigmadata['karim']
-            #y2 = fractiondata['karim'] + sigmadata['karim']
+            #pass
+            sigmadata = Table.read('../Data/Sig_2_30powerlaw.txt',
+                    format='ascii')
+            sigmadata = sigmadata[ok]
+            y1 = fractiondata['karim'] - sigmadata['karim']
+            y2 = fractiondata['karim'] + sigmadata['karim']
             #plt.fill_between(xx, y1, y2, facecolor=color, zorder=-4, alpha=0.3)
-            #plt.fill_between(xx, y1, y2, facecolor='none', zorder=-4,
-            #        edgecolor=color, hatch='\\\\')
+            plt.fill_between(xx, y1, y2, facecolor='none', zorder=-4,
+                    edgecolor=color, hatch='\\\\')
         if addlabel:
             plt.plot(xx, yy, color=color, linestyle=linestyle, 
-                    label='Karim+ 2013', linewidth=1.5)
+                    label='ALESS', linewidth=1.5)
 
         # predicted P(mu) for Steep LF
         key = 'break15'
@@ -223,16 +224,17 @@ def Pmu_model(modloc, linestyle='solid', lf='Powerlaw', fill=False,
         print(key, xx[find_nearest(yy, 0.5)])
         if addlabel:
             plt.plot(xx, yy, color=color, linestyle=linestyle, 
-                    label=r'$S_\star = 15\,$mJy', linewidth=1.5)
+                    label='COSMOS', linewidth=1.5)
 
         if fill:
-            pass
-            #sigmadata = Table.read('../Data/Sig_1p1_30powerlaw.txt',
-            #        format='ascii')
-            #y1 = fractiondata['break15'] - sigmadata['break15']
-            #y2 = fractiondata['break15'] + sigmadata['break15']
-            #plt.fill_between(xx, y1, y2, facecolor=color, zorder=-5)
[…]

### 2015-04-15 Code/sep_util.py

@@ -56,7 +56,7 @@ def setThresh(fluxcomponent, thresh, fluxstring='f880'):
 
 
 def getSeparation(fluxcomponent, rastring='offra', decstring='offdec',
-        targetstring='target', fluxstring='f880'):
+        targetstring='target', fluxstring='f880', degrees=False):
 
     nindiv = len(fluxcomponent)
 
@@ -73,12 +73,16 @@ def getSeparation(fluxcomponent, rastring='offra', decstring='offdec',
         fluxs = fluxcomponent[fluxstring][match]
         nmatch = fluxcomponent[fluxstring][match].size
         try:
-            avgra = ras.mean() / 3600
-            avgdec = decs.mean() / 3600
-            ra = fluxcomponent[rastring][icomp] / 3600
-            dec = fluxcomponent[decstring][icomp] / 3600
-            newra = ras / 3600
-            newdec = decs / 3600
+            if degrees:
+                factor = 1.
+            else:
+                factor = 3600.
+            avgra = ras.mean() / factor
+            avgdec = decs.mean() / factor
+            ra = fluxcomponent[rastring][icomp] / factor
+            dec = fluxcomponent[decstring][icomp] / factor
+            newra = ras / factor
+            newdec = decs / factor
         except:
             newra = numpy.zeros(nmatch)
             newdec = numpy.zeros(nmatch)
@@ -182,7 +186,7 @@ def simPosition(fluxcomponent, distance=8.5, rastring='offra',
             randomra = uniform(low=lowra, high=highra)
             randomdec = uniform(low=lowdec, high=highdec)
         #print(randomra, randomdec)
-        c = SkyCoord(ra=randomra * u.degree, dec=randomdec * u.degree)
+        #c = SkyCoord(ra=randomra * u.degree, dec=randomdec * u.degree)
 
         fluxcomponent[rastring][icomp] = randomra
         fluxcomponent[decstring][icomp] = randomdec
@@ -193,7 +197,7 @@ def simPosition(fluxcomponent, distance=8.5, rastring='offra',
 
 def simArea(fluxcomponent, nsim, bin_edges, targetstring='target', 
         edgecolor='black', facecolor='none', hatch='', fluxstring='f880',
-        norm=1.0):
+        norm=1.0, label=''):
[…]

### 2015-04-15 LaTeX/ms.tex
Added units to Table 5

@@
 A.~J.~Smith\altaffilmark{3},
+J.~D.~Vieira\altaffilmark{7},
 L.~Wang\altaffilmark{3},

### 2015-04-20 LaTeX/Bussmann14_text_WCv1p0.tex
Text from Cowley

@@
-We also compare our results to mock catalogues based on the methodology presented in \cite{Cowley14}, for full details we refer the reader to Cowley et al.
-but summarise it briefly here.
-An updated version of the \galform \citep[e.g.][Lacey et al.
-in preparation]{Cole00} semi-analytic galaxy formation model is used to populate halo merger trees \citep[e.g.][]{PCH08,Jiang14} derived from a Millennium style $N$-body dark matter only simulation \citep{Springel05,Guo13} with WMAP7 cosmology \citep{Komatsu11}.
-Submm flux is calculated using a model based on the radiative transfer.
-Dust is assumed to exist in two components,  dense molecular clouds and a diffuse ISM.
-Energy absorbed from starlight by each dust component is calculated self-consistently.
-The dust is then assumed to emit radiation as a modified blackbody, assuming thermal equilibrium.
+We also compare our results to mock catalogues based on the methodology
+presented in \cite{Cowley14}, for full details we refer the reader to Cowley et
+al. but summarise it briefly here. An updated version of the \galform
+\citep[e.g.][Lacey et al. in preparation]{Cole00} semi-analytic galaxy
+formation model is used to populate halo merger trees
+\citep[e.g.][]{PCH08,Jiang14} derived from a Millennium style $N$-body dark
+matter only simulation \citep{Springel05,Guo13} with WMAP7 cosmology
+\citep{Komatsu11}.  Submm flux is calculated using a model based on the
+radiative transfer.  Dust is assumed to exist in two components,  dense
+molecular clouds and a diffuse ISM.  Energy absorbed from starlight by each
+dust component is calculated self-consistently. The dust is then assumed to
+emit radiation as a modified blackbody, assuming thermal equilibrium.
 
-Three randomly orientated 20 deg$^2$ lightcone catalogues are generated using the method described in \cite{Merson13}.
-We choose as the lower flux limit for inclusion of simulated galaxies into our lightcone catalogue $S_{500\mu\rm{m}}>0.1$ mJy, as this is the limit at which we recover 90 per cent of the extragalactic background light (EBL) as predicted by our model (122 Jy deg$^{-2}$).
-This is in excellent agreement with observations from the \emph{COBE} satellite \citep[e.g.][]{Puget96,Fixsen98}.
-This ensures we have a realistic 500 $\mu$m  background in our mock images.
+Three randomly orientated 20 deg$^2$ lightcone catalogues are generated using
+the method described in \cite{Merson13}.  We choose as the lower flux limit for
+inclusion of simulated galaxies into our lightcone catalogue
+$S_{500\mu\rm{m}}>0.1$ mJy, as this is the limit at which we recover 90 per
+cent of the extragalactic background light (EBL) as predicted by our model (122
+Jy deg$^{-2}$). This is in excellent agreement with observations from the
+\emph{COBE} satellite \citep[e.g.][]{Puget96,Fixsen98}. This ensures we have a
+realistic 500 $\mu$m  background in our mock images.
 
-Mock imaging is created by binning the lightcone galaxies onto a pixelated grid which is then convolved with a  36 arcsec FWHM Gaussian ($\sim$ \emph{Herschel} SPIRE beam at 500 $\mu$m).
-The image is then constrained to have a zero mean by the subtraction of a uniform background.
-For simplicity we do not attempt to add any instrumental noise, nor perform any further filtering of the mock image.
+Mock imaging is created by binning the lightcone galaxies onto a pixelated grid
+which is then convolved with a  36 arcsec FWHM Gaussian ($\sim$ \emph{Herschel}
+SPIRE beam at 500 $\mu$m).  The image is then constrained to have a zero mean
+by the subtraction of a uniform background.  For simplicity we do not attempt
+to add any instrumental noise, nor perform any further filtering of the mock
+image.
 
-This procedure is repeated at 350 and 250 $\mu$m in order to provide simulated \emph{Herschel} photometry.
-We adjust the FWHM of the Gaussian PSF to 25 (18) arcsec at 350 (250) $\mu$m, and change the lower limit of inclusion into our lightcone to ensure 90 per cent of the predicted EBL is recovered at each wavelength.
+This procedure is repeated at 350 and 250 $\mu$m in order to provide simulated
+\emph{Herschel} photometry.  We adjust the FWHM of the Gaussian PSF to 25 (18)
+arcsec at 350 (250) $\mu$m, and change the lower limit of inclusion into our
+lightcone to ensure 90 per cent of the predicted EBL is recovered at each
+wavelength.
 
-Source positions are then selected as maxima in the mock 250 $\mu$m image, with the position and flux of the source being recorded as the center and value of the maximal pixel.
-To simulate `deblended' \emph{Herschel} photometry we simply read off the value of the pixel located at the position of the $250$ $\mu$m maxima in the 350 and 500 $\mu$m images.
-For all \emph{Herschel} sources with $S_{500\mu\rm{m}}>50$ mJy we then identify galaxies from our lightcone catalogues within a 9 arcsec radius ($\sim$ ALMA primary beam) of the source position, modelling the ALMA primary beam profile as a Gaussian with an 18 arcsec FWHM and a maximum sensitivity of 1 mJy.
+Source positions are then selected as maxima in the mock 250 $\mu$m image, with
+the position and flux of the source being recorded as the center and value of
+the maximal pixel.  To simulate `deblended' \emph{Herschel} photometry we
+simply read off the value of the pixel located at the position of the $250$
+$\mu$m maxima in the 350 and 500 $\mu$m images. For all \emph{Herschel} sources
+with $S_{500\mu\rm{m}}>50$ mJy we then identify galaxies from our lightcone
+catalogues within a 9 arcsec radius ($\sim$ ALMA primary beam) of the source
+position, modelling the ALMA primary beam profile as a Gaussian with an 18
+arcsec FWHM and a maximum sensitivity of 1 mJy.

### 2015-04-20 LaTeX/ms.tex
Fix author list.

--- 2015-04-15 LaTeX/ms.tex
@@
 A.~Fialkov\altaffilmark{2},
-J.~Scudders\altaffilmark{3},
+J.~M.~Scudder\altaffilmark{3},
 C.~Hayward\altaffilmark{4,5},
@@
 F.~De Bernardis\altaffilmark{9},
-Hai~Fu\altaffilmark{11},
-R.~Gavazzi\altaffilmark{12},
-R.~Hopwood\altaffilmark{13},
-R.~J.~Ivison\altaffilmark{14,15},
-M.~Jarvis\altaffilmark{16},
+D.~Farrah\altaffilmark{11},
+Hai~Fu\altaffilmark{12},
+R.~Gavazzi\altaffilmark{13},
+R.~Hopwood\altaffilmark{14},
+R.~J.~Ivison\altaffilmark{15,16},
+M.~Jarvis\altaffilmark{17},
 C.~Lacey\altaffilmark{6},
@@
 S.~J.~Oliver\altaffilmark{3},
-I.~P{\'e}rez-Fournon\altaffilmark{17,18},
-D.~Rigopoulou\altaffilmark{19,20},
-I.~G.~Roseboom\altaffilmark{3,15},
-Douglas~Scott\altaffilmark{21},
+I.~P{\'e}rez-Fournon\altaffilmark{18,19},
+D.~Rigopoulou\altaffilmark{20,21},
+I.~G.~Roseboom\altaffilmark{3,16},
+Douglas~Scott\altaffilmark{22},
 A.~J.~Smith\altaffilmark{3},
+J.~D.~Vieira\altaffilmark{23},
 L.~Wang\altaffilmark{3},
-J.~Wardlow\altaffilmark{22}}
+J.~Wardlow\altaffilmark{24}}
 \altaffiltext{$\dagger$}{Herschel is an ESA space observatory with science
@@
 \altaffiltext{10}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}
-\altaffiltext{11}{Department of Physics and Astronomy, The University of Iowa, 203 Van Allen Hall, Iowa City, IA 52242}
-\altaffiltext{12}{Institut d'Astrophysique de Paris, UMR 7095, CNRS, UPMC Univ. Paris 06, 98bis boulevard Arago, F-75014 Paris, France}
-\altaffiltext{13}{Astrophysics Group, Imperial College London, Blackett Laboratory, Prince Consort Road, London SW7 2AZ, UK}
-\altaffiltext{14}{UK Astronomy Technology Centre, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
-\altaffiltext{15}{Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
-\altaffiltext{16}{Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Hertfordshire AL10 9AB, UK}
-\altaffiltext{17}{Instituto de Astrof{\'\i}sica de Canarias (IAC), E-38200 La Laguna, Tenerife, Spain}
-\altaffiltext{18}{Departamento de Astrof{\'\i}sica, Universidad de La Laguna (ULL), E-38205 La Laguna, Tenerife, Spain}
-\altaffiltext{19}{RAL Space, Rutherford Appleton Laboratory, Chilton, Didcot, Oxfordshire OX11 0QX, UK}
-\altaffiltext{20}{Department of Astrophysics, Denys Wilkinson Building, University of Oxford, Keble Road, Oxford OX1 3RH, UK}
-\altaffiltext{21}{Department of Physics \& Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T~1Z1, Canada}
-\altaffiltext{22}{Dark Cosmology Centre, Niels Bohr Institute, University of
-Copenhagen, Juliane Maries Vej 30, 2100 Copenhagen, Denmark}
+\altaffiltext{11}{Department of Physics, Virginia Tech, Blacksburg, VA 24061}
+\altaffiltext{12}{Department of Physics and Astronomy, The University of Iowa, 203 Van Allen Hall, Iowa City, IA 52242}
+\altaffiltext{13}{Institut d'Astrophysique de Paris, UMR 7095, CNRS, UPMC Univ. Paris 06, 98bis boulevard Arago, F-75014 Paris, France}
+\altaffiltext{14}{Astrophysics Group, Imperial College London, Blackett Laboratory, Prince Consort Road, London SW7 2AZ, UK}
+\altaffiltext{15}{UK Astronomy Technology Centre, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
+\altaffiltext{16}{Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
+\altaffiltext{17}{Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Hertfordshire AL10 9AB, UK}
+\altaffiltext{18}{Instituto de Astrof{\'\i}sica de Canarias (IAC), E-38200 La Laguna, Tenerife, Spain}
+\altaffiltext{19}{Departamento de Astrof{\'\i}sica, Universidad de La Laguna (ULL), E-38205 La Laguna, Tenerife, Spain}
+\altaffiltext{20}{RAL Space, Rutherford Appleton Laboratory, Chilton, Didcot, Oxfordshire OX11 0QX, UK}
+\altaffiltext{21}{Department of Astrophysics, Denys Wilkinson Building, University of Oxford, Keble Road, Oxford OX1 3RH, UK}
+\altaffiltext{22}{Department of Physics \& Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T~1Z1, Canada}
+\altaffiltext{23}{Department of Astronomy and Department of Physics, University of Illinois, 1002 West Green Street, Urbana, IL 61801}
+\altaffiltext{24}{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 Copenhagen, Denmark}
 

### 2015-04-20 LaTeX/ms.tex
Moved figures
Figures must be in same directory as latex file for ApJ submission.

@@
 %\epsscale{1.00} 
-\includegraphics[width=\linewidth]{../Figures/spirecolflux.pdf}
+\includegraphics[width=\linewidth]{spirecolflux.pdf}
 
@@
 %\includegraphics[width=\textwidth]{cutouts_dec17.png}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HELAISS02_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM02_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM31_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM29_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM07_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM20_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM01_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM04_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM09_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM03_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM11_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM23_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HELAISS02_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HXMM02_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HXMM31_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HXMM29_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HXMM07_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HXMM20_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HXMM01_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HXMM04_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HXMM09_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HXMM03_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HXMM11_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HXMM23_870_250.pdf}
 \end{centering}
@@
 %\includegraphics[width=\textwidth]{cutouts_dec17.png}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM22_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM05_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM30_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HXMM12_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HECDFS12_870_500.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HECDFS04_870_500.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HECDFS13_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS04_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS02_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS11_870_500.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS10_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS01_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HXMM22_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HXMM05_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HXMM30_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HXMM12_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HECDFS12_870_500.pdf}
+\includegraphics[width=0.331\textwidth]{HECDFS04_870_500.pdf}
+\includegraphics[width=0.331\textwidth]{HECDFS13_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HADFS04_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HADFS02_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HADFS11_870_500.pdf}
+\includegraphics[width=0.331\textwidth]{HADFS10_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HADFS01_870_250.pdf}
 \end{centering}
@@
     \begin{centering}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS09_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS08_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HADFS03_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HCOSMOS02_870_250.pdf}
-\includegraphics[width=0.331\textwidth]{../Figures/overlays/HCOSMOS01_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HADFS09_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HADFS08_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HADFS03_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HCOSMOS02_870_250.pdf}
+\includegraphics[width=0.331\textwidth]{HCOSMOS01_870_250.pdf}
 %\epsscale{1.00} 
@@
 %\includegraphics[width=\textwidth]{cutouts_dec17.png}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM02_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM02_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM02_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM31_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM31_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM31_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM29_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM29_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM29_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM07_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM07_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM07_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM20_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM20_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM20_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM01_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM01_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM01_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM04_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM04_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM04_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM09_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM09_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM09_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM03_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM03_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM03_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM11_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM11_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM11_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM23_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM23_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM23_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM22_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM22_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM22_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM05_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM05_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM05_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM30_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM30_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM30_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM12_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM12_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HXMM12_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HELAISS02_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HELAISS02_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HELAISS02_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM02_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM02_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM02_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM31_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM31_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM31_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM29_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM29_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM29_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM07_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM07_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM07_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM20_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM20_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM20_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM01_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM01_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM01_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM04_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM04_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM04_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM09_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM09_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM09_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM03_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM03_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM03_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM11_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM11_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM11_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM23_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM23_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM23_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM22_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM22_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM22_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM05_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM05_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM05_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM30_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM30_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM30_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM12_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM12_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HXMM12_residual_bestfit.pdf}
 \end{centering}
@@
     \begin{centering}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS04_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS04_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS04_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS02_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS02_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS02_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS11_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS11_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS11_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS10_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS10_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS10_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS01_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS01_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS01_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS09_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS09_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS09_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS08_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS08_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS08_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS03_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS03_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS03_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS02_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS02_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS02_residual_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS01_optical_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS01_model_bestfit.pdf}
-\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS01_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HECDFS12_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HECDFS12_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HECDFS12_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HECDFS04_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HECDFS04_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HECDFS04_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HECDFS13_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HECDFS13_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HECDFS13_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HADFS04_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HADFS04_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HADFS04_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HADFS02_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HADFS02_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HADFS02_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HADFS11_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HADFS11_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HADFS11_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HADFS10_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HADFS10_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HADFS10_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HADFS01_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HADFS01_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HADFS01_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HADFS09_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HADFS09_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HADFS09_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HADFS08_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HADFS08_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HADFS08_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HADFS03_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HADFS03_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HADFS03_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HCOSMOS02_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HCOSMOS02_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HCOSMOS02_residual_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HCOSMOS01_optical_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HCOSMOS01_model_bestfit.pdf}
+\includegraphics[width=0.162\textwidth]{HCOSMOS01_residual_bestfit.pdf}
 \end{centering}
@@
 %\includegraphics[width=\textwidth]{cutouts_dec17.png}
-\includegraphics[width=0.195\textwidth]{../Figures/HECDFS04_rgb.pdf}
-\includegraphics[width=0.195\textwidth]{../Figures/HCOSMOS02_rgb.pdf}
-\includegraphics[width=0.195\textwidth]{../Figures/HELAISS02_rgb.pdf}
-\includegraphics[width=0.195\textwidth]{../Figures/HXMM11_rgb.pdf}
-\includegraphics[width=0.195\textwidth]{../Figures/HXMM20_rgb.pdf}
+\includegraphics[width=0.195\textwidth]{HECDFS04_rgb.pdf}
+\includegraphics[width=0.195\textwidth]{HCOSMOS02_rgb.pdf}
+\includegraphics[width=0.195\textwidth]{HELAISS02_rgb.pdf}
+\includegraphics[width=0.195\textwidth]{HXMM11_rgb.pdf}
+\includegraphics[width=0.195\textwidth]{HXMM20_rgb.pdf}
 \end{centering}
@@
 %\epsscale{1.00} 
-\includegraphics[width=\linewidth]{../Figures/f870_delens.pdf}
+\includegraphics[width=\linewidth]{f870_delens.pdf}
 %\includegraphics[width=0.24\linewidth]{../Figures/reff_delens.pdf}
@@
 %\epsscale{1.00} 
-\includegraphics[width=\linewidth]{../Figures/fluxtotalcomponent.pdf}
+\includegraphics[width=\linewidth]{fluxtotalcomponent.pdf}
 
@@
 %\epsscale{1.00} 
-\includegraphics[height=3in]{../Figures/AllPositions.pdf}
-\includegraphics[height=3in]{../Figures/dNdA.pdf}
+\includegraphics[height=3in]{AllPositions.pdf}
+\includegraphics[height=3in]{dNdA.pdf}
 
@@
 %\epsscale{1.00} 
-\includegraphics[width=0.335\textwidth]{../Figures/DifferentialNumberCounts.pdf}
-\includegraphics[width=0.335\textwidth]{../Figures/s870_mu_z1p5.pdf}
-\includegraphics[width=0.335\textwidth]{../Figures/Pmu_S870_z1p5.pdf}
+\includegraphics[width=0.335\textwidth]{DifferentialNumberCounts.pdf}
+\includegraphics[width=0.335\textwidth]{s870_mu_z1p5.pdf}
+\includegraphics[width=0.335\textwidth]{Pmu_S870_z1p5.pdf}
 

### 2015-04-20 LaTeX/ms.tex
Hayward final comments

--- 2015-04-20 LaTeX/ms.tex
@@
 J.~M.~Scudder\altaffilmark{3},
-C.~Hayward\altaffilmark{4,5},
+C.~C.~Hayward\altaffilmark{4,5},
 W.~Cowley\altaffilmark{6},
@@
 cosmological simulation \citep{Klypin11} using the {\sc rockstar} halo finder
-\citep{Behroozi13a,Behroozi13b}.  Catalogs of subhalos are created from eight
+\citep{Behroozi13a, Behroozi13b}.  Catalogs of subhalos are created from eight
 randomly chosen lightcones, each with an area of 1.4$^\circ \times 1.4^\circ$.
@@
 of the excess at small angular separations observed in our {\it Herschel}-ALMA
-sample, we modified the \citet{HB13} model to include a crude treatment of
-interaction-induced SFR enhancement. Mock galaxies with one or more neighbors
-within a physical distance of 5$\,$kpc and with a stellar mass between
-one-third and three times that of the galaxy under consideration (i.e.  a
-`major merger') had their SFRs increased by a factor of two. For distances
-smaller than 1$\,$kpc, the imposed increase was a factor of ten.  Because these
-SFR enhancements are greater than suggested by simulations
-\citep[e.g.][]{Cox08, H11, H14, Torrey12} or observations of local galaxy pairs
-\citep[e.g.][]{Scudder12, Patton13}, we consider this test to provide an upper
-limit on the possible effect of interactions on blended sources in the
-\citet{HB13} model.  We find an insignificant effect on the values of $dN/dA$
-when using the merger-induced model as described above.  The main reason for
-this is that only two sources had their SFRs boosted by a factor of ten, and
-$\approx150$ experienced a factor of two increase. In the \citet{HB13} model, a
-factor of two increase in SFR corresponds to only a ~30\% increase in
-$S_{870}$, so it is perhaps unsurprising that the weak boosts in SFR cause
-little change in $dN/dA$.
+sample, we analyzed modified versions of the \citet{HB13} model that include a
+crude treatment of interaction-induced SFR enhancements \citep{Miller:2015lr}.
+Mock galaxies with one or more neighbors within a physical distance of 5$\,$kpc
+and with a stellar mass between one-third and three times that of the galaxy
+under consideration (i.e.  a `major merger') had their SFRs increased by a
+factor of two. For distances smaller than 1$\,$kpc, the imposed increase was a
+factor of ten.  Because these SFR enhancements are greater than suggested by
+simulations \citep[e.g.][]{Cox08, H11, H14, Torrey12} or observations of local
+galaxy pairs \citep[e.g.][]{Scudder12, Patton13}, we consider this test to
+provide an upper limit on the possible effect of interactions on blended
+sources in the \citet{HB13} model, although the incompleteness of the
+\citet{Behroozi13b} catalogs for mergers with small separations could cause
+some interacting systems to be missed.  We find an insignificant effect on the
+values of $dN/dA$ when using the merger-induced model as described above.  The
+main reason for this is that only two sources had their SFRs boosted by a
+factor of ten, and $\approx150$ experienced a factor of two increase. In the
+\citet{HB13} model, a factor of two increase in SFR corresponds to only a ~30\%
+increase in $S_{870}$, so it is perhaps unsurprising that the weak boosts in
+SFR cause little change in $dN/dA$.
 
@@
 R.J.I. acknowledges support from European Research Council Advanced
-Investigator Grant, Cosmicism, 321302.
+Investigator Grant, Cosmicism, 321302. C.C.H. is grateful to the Gordon and
+Betty Moore Foundation for financial support.
 

### 2015-04-20 LaTeX/ms.tex
Fialkov comments.

@@
 A.~Fialkov\altaffilmark{2},
-J.~M.~Scudder\altaffilmark{3},
+J.~Scudders\altaffilmark{3},
 C.~C.~Hayward\altaffilmark{4,5},
@@
 \altaffiltext{1}{Department of Astronomy, Space Science Building, Cornell University, Ithaca, NY, 14853-6801}
-\altaffiltext{2}{Departement de Physique, Ecole Normale Sup erieure, CNRS, 24 rue Lhomond, Paris, 75005 France}
+\altaffiltext{2}{Departement de Physique, Ecole Normale Superieure, CNRS, 24 rue Lhomond, 75005 Paris, France}
 \altaffiltext{3}{Astronomy Centre, Dept. of Physics \& Astronomy, University of Sussex, Brighton BN1 9QH, UK}
@@
 \altaffiltext{23}{Department of Astronomy and Department of Physics, University of Illinois, 1002 West Green Street, Urbana, IL 61801}
-\altaffiltext{24}{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 Copenhagen, Denmark}
+\altaffiltext{24}{Dark Cosmology Centre, Niels Bohr Institute, University of
+Copenhagen, Juliane Maries Vej 30, 2100 Copenhagen, Denmark}
 
@@
 as well as with the {\it Herschel}-SMA sample in \citet{Bussmann:2013lr}.  A
-further eght appear in the ``Supplementary sample'' of \citet{Wardlow:2013lr}.
+further eight appear in the ``Supplementary sample'' of \citet{Wardlow:2013lr}.
 The remainder have $S_{500} < 80\,$mJy and thus do not appear in
@@
 \citep{Navarro:1997ys} that is truncated at the virial radius.  The NFW profile
-describes the outskirts of dark matter halos better, while the SIS profile is
-preferred on smaller scales because it correctly fits the observed flat
-rotational curves in galaxies.  We make sure that the resulting probability
-density of lensing, $P\,(\mu)$, is normalized to unity.  To describe $n_{\rm
-lens}\,(M, \, z)$, we generate the abundance of halos at each mass and redshift
-using the \citet{Sheth:1999kx} formalism.  To describe $dN_{\rm source}/dz$, we
-adopt the following redshift distribution which is based on photometric
-redshifts of optical counterparts to ALMA sources identified in ALESS
-\citep{Simpson:2014lr}:
+describes the outskirts of dark matter halos better \citep{Mandelbaum:2005lr},
+while the SIS profile is preferred on smaller scales because it correctly fits
+the observed flat rotational curves in galaxies \citep{Kochanek:1994fk}.  We
+make sure that the resulting probability density of lensing, $P\,(\mu)$, is
+normalized to unity.  To describe $n_{\rm lens}\,(M, \, z)$, we generate the
+abundance of halos at each mass and redshift using the \citet{Sheth:1999kx}
+formalism.  To describe $dN_{\rm source}/dz$, we adopt the following redshift
+distribution which is based on photometric redshifts of optical counterparts to
+ALMA sources identified in ALESS \citep{Simpson:2014lr}:
 
@@
 PdBI \citep{Miettinen:2015lr}.  These interferometric observations have shown
-show that all of the sources in their surveys are either unlensed or lensed by
+that all of the sources in their surveys are either unlensed or lensed by
 magnification factors $<2$.  This is why the ALESS and COSMOS luminosity
@@
 However, there are significant differences in where this transition flux
-density, $S_{\rm trans}$, occurs --- i.e., where $P(\mu>\mu_{870}$ > 2).  In
+density, $S_{\rm trans}$, occurs --- i.e., where $P(\mu>\mu_{870}) > 2$.  In
 the data, the logistic regression fit yields $S_{\rm trans} = 24\pm3\,$mJy
@@
 $S_{\rm trans} = 37\,$mJy $S_{\rm trans} = 69\,$mJy, respectively.
-
-Note caveats.
 

### 2015-04-20 LaTeX/ms.tex
Cowley final comments.

@@
 C.~C.~Hayward\altaffilmark{4,5},
-W.~Cowley\altaffilmark{6},
+W.~I.~Cowley\altaffilmark{6},
 J.~Bock\altaffilmark{7,8},
@@
 J.~D.~Vieira\altaffilmark{23},
-L.~Wang\altaffilmark{3},
+L.~Wang\altaffilmark{6},
 J.~Wardlow\altaffilmark{24}}
@@
     {\it Herschel} sources, the lens models presented here tentatively favor
-    intrinsic luminosity functions for DSFGs with a break near 8$\,$mJy at
+    intrinsic number counts for DSFGs with a break near 8$\,$mJy at
     880$\,\mu$m and a steep fall off at higher flux densities.  Nearly 70\% of
@@
 {\it Herschel} DSFG of a given $S_{500}$ \citep{Bussmann:2013lr}.  This could
-indicate herald new insights in our understanding of the bright end of the
-intrinsic DSFG luminosity function or in the nature of the deflectors.
+herald new insights in our understanding of the bright end of the
+intrinsic DSFG number counts or in the nature of the deflectors.
 
@@
 Three aspects of our dataset make it uniquely suited to improving our
-understanding of the bright end of the intrinsic DSFG luminosity function.
+understanding of the bright end of the intrinsic DSFG number counts.
 First, the sample occupies a distinct regime in flux density between the
@@
 $\mu_{870}$ as a function of $S_{870}$ and discuss implications for the bright
-end of the DSFG luminosity function in Section~\ref{sec:discuss}.  Finally, we
+end of the DSFG number counts in Section~\ref{sec:discuss}.  Finally, we
 present our conclusions in Section~\ref{sec:conclusions}.
@@
 Herschel}-ALMA sample opens a new window of discovery space on the bright end
-of the DSFG luminosity function.
+of the DSFG number counts.
 
@@
 typically of order 5-10\%.  When discussing the intrinsic properties of bright
-sources \citep[including their luminosity functions, e.g.][]{Wyithe:2011rm}
+sources \citep[including their number counts, e.g.][]{Wyithe:2011rm}
 discovered in wide-field FIR or mm surveys, it is critical to consider the
@@
 that the sources are merely unrelated galaxies that appear blended due to
-projection effects \citep{HB13}.  Spatially resolved spectroscopy is necessary
-to answer this question definitively, but is not currently available.  Instead,
-to investigate these possibilities further, we make use of mock catalogs of
-DSFGs that are based on numerical simulations and presented by \citet{HB13} and
-\citet{Cowley:2015lr}.
+projection effects \citep{HB13, Cowley:2015lr, Munoz-Arancibia:2015qy}.
+Spatially resolved spectroscopy is necessary to answer this question
+definitively, but is not currently available.  Instead, to investigate these
+possibilities further, we make use of mock catalogs of DSFGs that are based on
+numerical simulations and presented by \citet{HB13} and \citet{Cowley:2015lr}.
 
@@
 methodology presented in \citet{Cowley:2015lr}.  Here, we give a brief summary
-and refer the interested reader to \citet{Cowley:2015lr} for full details. An
-updated version of the {\sc galform} \citep[e.g.][Lacey et al. in
-preparation]{Cole:2000fk} semi-analytic galaxy formation model is used to
-populate halo merger trees \citep[e.g.][]{Parkinson:2008qy, Jiang:2014lr}
-derived from a Millennium style $N$-body dark matter only simulation
-\citep{Springel:2005lr, Guo:2013lr} with WMAP7 cosmology
-\citep{Komatsu:2011fk}.  Submm flux is calculated using a model based on the
-radiative transfer.  Dust is assumed to exist in two components,  dense
-molecular clouds and a diffuse ISM.  Energy absorbed from starlight by each
-dust component is calculated self-consistently.  The dust is then assumed to
-emit radiation as a modified blackbody, assuming thermal equilibrium.
+and refer the interested reader to \citet{Cowley:2015lr} for full details. A
+new version of the {\sc galform} \citep[e.g.][Lacey et al. in
+preparation]{Cole:2000fk} semi-analytic model of hierarchical galaxy formation
+is used to populate halo merger trees \citep[e.g.][]{Parkinson:2008qy,
+Jiang:2014lr} derived from a Millennium style $N$-body dark matter only
+simulation \citep{Springel:2005lr, Guo:2013lr} with WMAP7 cosmology
+\citep{Komatsu:2011fk}.  A sub-mm flux for each galaxy is calculated using a
+self-consistent model based on radiative transfer and energy balance arguments.
+Dust is assumed to exist in two components,  dense molecular clouds and a
+diffuse ISM.  Energy absorbed from stellar radiation by each dust component is
+calculated by solving the equations of radiative transfer in an assumed dust
+geometry.  The dust is then assumed to emit radiation as a modified blackbody.
 
@@
 limit for inclusion of simulated galaxies into our lightcone catalogue
-$S_{500\mu\rm{m}}>0.1$ mJy, as this is the limit at which we recover 90 per
-cent of the extragalactic background light (EBL) as predicted by our model (122
+$S_{500\mu\rm{m}}>0.1$ mJy, as this is the limit at which we recover 90\% of
+the extragalactic background light (EBL) as predicted by the model (122
 Jy~deg$^{-2}$). This is in excellent agreement with observations from the
-\emph{COBE} satellite \citep[e.g.,][]{Puget:1996lr}. This ensures we have a
-realistic 500 $\mu$m  background in our mock images.
+\emph{COBE} satellite \citep[e.g.,][]{Puget:1996lr}, and thus ensures a
+realistic 500 $\mu$m  background in the mock images.
 
@@
 which is then convolved with a 36$\arcsec$ FWHM Gaussian (corresponding to the
-\emph{Herschel} SPIRE beam at 500$\,\mu$m).  The image is then constrained to
+\emph{Herschel}/SPIRE beam at 500$\,\mu$m).  The image is then constrained to
 have a zero mean by the subtraction of a uniform background.  No instrumental
 noise is added, nor are any further filtering procedures applied to the mock
-image.  This procedure is repeated at 350$\,\mu$m and 250$\,\mu$m in order to
-provide simulated \emph{Herschel} photometry, adjusting the FWHM of the
-Gaussian PSF appropriately and changing the lower limit of inclusion into our
-lightcone to ensure 90 per cent of the predicted EBL is recovered at each
-wavelength.
+image.  For the purposes of source identification, this procedure is repeated
+at 250$\,\mu$m.  For this, we adjust the FWHM of the Gaussian PSF to
+18$\arcsec$ and change the lower flux limit of inclusion into our lightcone to
+ensure 90\% of the predicted EBL is recovered at this wavelength.
 
 Source positions are selected as maxima in the mock 250$\,\mu$m image, with the
-position and flux of the source being determined by the maximal pixel.  To
-simulate `deblended' \emph{Herschel} photometry we record the value of the
-pixel located at the position of the 250$\,\mu$m maxima in the 350$\,\mu$m and
+position of the source being recorded as the center the maximal pixel for
+simplicity.  To mimic `deblended' \emph{Herschel} photometry we record the
+value of the pixel located at the position of the 250$\,\mu$m maxima in the
 500$\,\mu$m images. We select all \emph{Herschel} sources satisfying
@@
 surveys with the brightest apparent flux densities are highly sensitive to the
-shape of the intrinsic luminosity function at the bright end.  In this section,
+shape of the intrinsic number counts at the bright end.  In this section,
 we combine our ALMA and SMA measurements of magnification factors to investigate
@@
 redshift, $n_{\rm lens}\,(M, \, z),$ the redshift distribution of the sources,
-$dN_{\rm source}/dz$, and the intrinsic luminosity function of the sources,
+$dN_{\rm source}/dz$, and the intrinsic number counts of the sources,
 $dn_{\rm source}/dS_{870}^\prime$.  The latter component is the least certain
@@
 function.  For these reasons, we fix all components of the model except the
-shape of the intrinsic luminosity function.  Our goal is to take luminosity
+shape of the intrinsic number counts.  Our goal is to take luminosity
 functions that can successfully fit observed faint DSFG number counts
@@
 
-We explore two intrinsic luminosity functions that are intended to bracket the
+We explore two intrinsic number counts that are intended to bracket the
 plausible range of values for DSFGs based on two interferometric surveys.  One
-is the luminosity function measured in ALESS \citep{Karim:2013lr}, and the
+is the number counts measured in ALESS \citep{Karim:2013lr}, and the
 other is from interferometric follow-up of the first AzTEC survey in COSMOS
@@
 magnification factors $<2$.  This is why the ALESS and COSMOS luminosity
-functions represent a plausible range of intrinsic luminosity functions for
-DSFGs.  These luminosity functions are shown in the left panel of
+functions represent a plausible range of intrinsic number counts for
+DSFGs.  These number counts are shown in the left panel of
 Figure~\ref{fig:lensstats}.  Interferometric follow-up data in COSMOS
@@
 Table~\ref{tab:models} provides values for the parameters of the broken
-power-law for the ALESS and COSMOS luminosity functions.  The data and
-corresponding luminosity functions are shown in the left panel of
+power-law for the ALESS and COSMOS number counts.  The data and
+corresponding number counts are shown in the left panel of
 Figure~\ref{fig:lensstats}.
@@
 
-\noindent Here $ dn/dS_{870}$ is the observed luminosity function and
-$dn/dS_{870}^\prime$ is the intrinsic luminosity function.
+\noindent Here $ dn/dS_{870}$ is the observed number counts and
+$dn/dS_{870}^\prime$ is the intrinsic number counts.
 
@@
 as a function of $S_{870}$, $\langle\mu_{870}\rangle$, assuming the two
-intrinsic luminosity functions for DSFGs described in Table~\ref{tab:models}.
+intrinsic number counts for DSFGs described in Table~\ref{tab:models}.
 
@@
 
-\caption{ {\it Left}: Observed luminosity functions from interferometer
+\caption{ {\it Left}: Observed number counts from interferometer
 follow-up of mm sources in COSMOS \citep[black circles;][]{Younger:2007fk,
@@
 diamonds;][]{Karim:2013lr}.  The magneta and blue lines represent the range of
-plausible intrinsic luminosity functions for DSFGs given these two datasets.
+plausible intrinsic number counts for DSFGs given these two datasets.
 {\it Middle}: Magnification factors at 870$\,\mu$m as a function of apparent
@@
 the average magnification factor, $\langle\mu_{870}\rangle$, predicted by our
-models for the two intrinsic luminosity functions shown on the left.  The model
-luminosity functions predict higher $\langle\mu_{870}\rangle$ than are seen in
+models for the two intrinsic number counts shown on the left.  The model
+number counts predict higher $\langle\mu_{870}\rangle$ than are seen in
 the data.  {\it Right}: Probability that a source with a given $S_{870}$
@@
 the 1$\sigma$ uncertainty).  Colored lines are the same as in the middle and
-left panels.  The intrinsic luminosity function that provides a good fit to the
-COSMOS data predicts too many unlensed or weakly lensed sources with intrinsic
+left panels.  The intrinsic number counts that provide a good fit to the
+COSMOS data predict too many unlensed or weakly lensed sources with intrinsic
 flux densities of $S_{870}^\prime \sim 50\,$mJy.} \label{fig:lensstats}
@@
 by factors of 5-10.  However, the dispersion in the predicted
-$\langle\mu_{870}\rangle$ values for both intrinsic luminosity functions rises
+$\langle\mu_{870}\rangle$ values for both intrinsic number counts rises
 smoothly from $\sigma_\mu \approx 2$ at $S_{870} = 15\,$mJy to $\sigma_\mu
@@
 
-A related but distinct test of the intrinsic luminosity functions for DSFGs
+A related but distinct test of the intrinsic number counts for DSFGs
 comes from the probability of a given source experiencing a magnification above
@@
 (error accounts only for statistical uncertainty in $S_{870}$ and $\mu_{870}$),
-whereas the models based on the ALESS and COSMOS luminosity functions yield
+whereas the models based on the ALESS and COSMOS number counts yield
 $S_{\rm trans} = 37\,$mJy $S_{\rm trans} = 69\,$mJy, respectively.
@@
 are over-predicted and lensed sources with $S_{870} < 50\,$mJy are
-under-predicted.  If the ALESS luminosity function continues to be supported by
+under-predicted.  If the ALESS number counts continue to be supported by
 the evidence as additional data are obtained, the implications are significant.
@@
 
-    \item An intrinsic luminosity function for DSFGs with a form that matches
-        observations in COSMOS \citep{Miettinen:2015lr} under-predicts the
-        number of lensed sources with apparent $S_{870} > 10\,$mJy.  A
-        luminosity function based on ALESS observations provides a better match
+    \item Intrinsic number counts for DSFGs with a form that matches
+        observations in COSMOS \citep{Miettinen:2015lr} under-predict the
+        number of lensed sources with apparent $S_{870} > 10\,$mJy.  Number
+        counts based on ALESS observations provide a better match
         to our magnification measurements.  The interpretation of these results
@@
         goal is to draw attention to this analysis method as a means to test
-        luminosity functions of DSFGs using wide-field {\it Herschel} data.
+        number counts of DSFGs using wide-field {\it Herschel} data.
 
@@
 
-If the ALESS luminosity function continues to provide the best predicted
+If the ALESS number counts continue to provide the best predicted
 magnification factors in larger samples with weaker biases, this suggests that

### 2015-04-20 LaTeX/ms.tex
Wardlow final comments.

@@
 Our sample includes 29 DSFGs drawn from five independent, confusion-limited
-fields in HerMES with declinations $> 2 ^\circ$ and totaling $55\,$deg$^2$.
+fields in HerMES with declinations $< 2 ^\circ$ and totaling $55\,$deg$^2$.
 
@@
 significant overlap in $S_{870}$ between our sample and ALESS is evidence that
-the DSFGs in our sample have higher $S_{500}/S_{870}$ ratios than the DSFGs in
-ALESS (recall Figure~\ref{fig:sample}, which shows that ALESS sources have much
-lower $S_{500}$ than our targets).  This difference is likely due to
-differences in dust temperature and/or redshift distributions of the two
-samples and probably arises from selection effects.
+the DSFGs in our sample have higher $S_{500}/S_{870}$ ratios (even when the
+effect of lensing in our sample is taken into account) than the DSFGs in ALESS
+(recall Figure~\ref{fig:sample}, which shows that ALESS sources have much lower
+$S_{500}$ than our targets).  This difference is likely due to differences in
+dust temperature and/or redshift distributions of the two samples and probably
+arises from selection effects.
 
@@
 
-Finally, the brightest source in the {\it Herschel}-ALMA sample is
-HADFS11.0, with an intrinsic flux density of $S_{870} = 17.5 \pm 0.4\,$mJy.
-However, there are also two objects with multiple sources that have separations
-smaller than 1$\arcsec$, which have summed flux densities comparable to this;
-namely HADFS02 (16.8$\,$mJy) and HECDFS13 (15.3$\,$mJy).  This is approaching
-the values found in the most extreme systems, such as GN20
+Finally, the brightest source in the {\it Herschel}-ALMA sample is HADFS11.0,
+with an intrinsic flux density of $S_{870} = 17.5 \pm 0.4\,$mJy.  However,
+there are also two objects with multiple sources that have separations smaller
+than 1$\arcsec$, which have summed flux densities comparable to this; namely
+HADFS02 (16.8$\,$mJy) and HECDFS13 (15.3$\,$mJy).  This is approaching the
+values found in the most extreme systems, such as GN20
 \citep[20.6$\,$mJy,][]{2006MNRAS.370.1185P} and HFLS3
@@
 \citep[e.g.,][]{Narayanan:2010lr}.  One possibility is that the objects with
-multiple sources represent blends of physically unassociated systems.  Testing
-this possibility requires redshift determinations of each source and is beyond
-the scope of this paper.
+multiple sources represent blends of physically unassociated systems.  We
+explore this possibility via comparison to theoretical models in
+Section~\ref{sec:spatialdist}, but a direct empirical test requires redshift
+determinations of each source and is beyond the scope of this paper.
 

### 2015-04-20 LaTeX/ms.tex
Wang final comments.

@@
 J.~D.~Vieira\altaffilmark{23},
-L.~Wang\altaffilmark{6},
-J.~Wardlow\altaffilmark{24}}
+L.~Wang\altaffilmark{6,24},
+J.~Wardlow\altaffilmark{25}}
 \altaffiltext{$\dagger$}{Herschel is an ESA space observatory with science
@@
 \altaffiltext{23}{Department of Astronomy and Department of Physics, University of Illinois, 1002 West Green Street, Urbana, IL 61801}
-\altaffiltext{24}{Dark Cosmology Centre, Niels Bohr Institute, University of
+\altaffiltext{24}{SRON Netherlands Institute for Space Research, Landleven 12, 9747 AD, Groningen, The Netherlands}
+\altaffiltext{25}{Dark Cosmology Centre, Niels Bohr Institute, University of
 Copenhagen, Juliane Maries Vej 30, 2100 Copenhagen, Denmark}
@@
 ALMA-accesible HerMES fields, and was constructed from the SUSSEXtractor
-catalogs, which were available prior to the ALMA Cycle~0 deadline.
-Subsequently, improved efforts to deblend SPIRE photometry at 500$\,\mu$m using
-StarFinder \citep{Wang:2014lr} were introduced that formed the basis of the
-lens selection criteria used in \citet{Wardlow:2013lr}.  As a result of the
-improved deblending algorithms in the StarFinder catalogues and
+catalogs \citep{Smith:2012uq}, which were available prior to the ALMA Cycle~0
+deadline.  Subsequently, improved efforts to deblend SPIRE photometry at
+500$\,\mu$m using StarFinder \citep{Wang:2014lr} were introduced that formed
+the basis of the lens selection criteria used in \citet{Wardlow:2013lr}.  As a
+result of the improved deblending algorithms in the StarFinder catalogues and
 \citet{Wardlow:2013lr} a number of objects in our sample have significantly

### 2015-04-20 LaTeX/ms.tex
Fix Scudder's name.

@@
 
-%./authors_list hermes_authors_data_dr1_20121108.txt apj rsb dr fialkov scudders hayward cowley almalens
+%./authors_list hermes_authors_data_dr1_20121108.txt apj rsb dr fialkov scudder hayward cowley almalens
 \author{R.~S.~Bussmann\altaffilmark{1},
@@
 A.~Fialkov\altaffilmark{2},
-J.~Scudders\altaffilmark{3},
+J.~Scudder\altaffilmark{3},
 C.~C.~Hayward\altaffilmark{4,5},
@@
 
-\input{table_lf}
-
 The product of the model is the lensing optical depth for a given lensing
@@
 the total probability distribution function.
+
+\input{table_lf}
 

### 2015-04-20 LaTeX/ms.tex
Use bbl directly in manuscript.

--- 2015-04-20 LaTeX/ms.tex
@@
 
-\bibliographystyle{apj}
-
-\bibliography{rbussman}
+%\bibliographystyle{apj}
+
+%\bibliography{rbussman}
+\begin{thebibliography}{106}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Aravena} {et~al.}(2010){Aravena}, {Bertoldi}, {Carilli},
+  {Schinnerer}, {McCracken}, {Salvato}, {Riechers}, {Sheth}, {Sm{\v
+  o}lci{\'c}}, {Capak}, {Koekemoer}, \& {Menten}}]{Aravena:2010fr}
+{Aravena}, M., {Bertoldi}, F., {Carilli}, C., {Schinnerer}, E., {McCracken},
+  H.~J., {Salvato}, M., {Riechers}, D., {Sheth}, K., {Sm{\v o}lci{\'c}}, V.,
+  {Capak}, P., {Koekemoer}, A.~M., \& {Menten}, K.~M. 2010, \apjl, 708, L36
+
+\bibitem[{{Barger} {et~al.}(2012){Barger}, {Wang}, {Cowie}, {Owen}, {Chen}, \&
+  {Williams}}]{Barger:2012yg}
+{Barger}, A.~J., {Wang}, W.-H., {Cowie}, L.~L., {Owen}, F.~N., {Chen}, C.-C.,
+  \& {Williams}, J.~P. 2012, \apj, 761, 89
+
+\bibitem[{{Behroozi} {et~al.}(2013{\natexlab{a}}){Behroozi}, {Wechsler}, \&
+  {Conroy}}]{Behroozi13c}
+{Behroozi}, P.~S., {Wechsler}, R.~H., \& {Conroy}, C. 2013{\natexlab{a}}, \apj,
+  770, 57
+
+\bibitem[{{Behroozi} {et~al.}(2013{\natexlab{b}}){Behroozi}, {Wechsler}, \&
+  {Wu}}]{Behroozi13a}
+{Behroozi}, P.~S., {Wechsler}, R.~H., \& {Wu}, H.-Y. 2013{\natexlab{b}}, \apj,
+  762, 109
+
+\bibitem[{{Behroozi} {et~al.}(2013{\natexlab{c}}){Behroozi}, {Wechsler}, {Wu},
+  {Busha}, {Klypin}, \& {Primack}}]{Behroozi13b}
+{Behroozi}, P.~S., {Wechsler}, R.~H., {Wu}, H.-Y., {Busha}, M.~T., {Klypin},
+  A.~A., \& {Primack}, J.~R. 2013{\natexlab{c}}, \apj, 763, 18
+
+\bibitem[{{Blain}(1996)}]{1996MNRAS.283.1340B}
+{Blain}, A.~W. 1996, \mnras, 283, 1340
+
+\bibitem[{{Bothwell} {et~al.}(2013){Bothwell}, {Smail}, {Chapman}, {Genzel},
+  {Ivison}, {Tacconi}, {Alaghband-Zadeh}, {Bertoldi}, {Blain}, {Casey}, {Cox},
+  {Greve}, {Lutz}, {Neri}, {Omont}, \& {Swinbank}}]{Bothwell:2013lr}
+{Bothwell}, M.~S., {Smail}, I., {Chapman}, S.~C., {Genzel}, R., {Ivison},
+  R.~J., {Tacconi}, L.~J., {Alaghband-Zadeh}, S., {Bertoldi}, F., {Blain},
+  A.~W., {Casey}, C.~M., {Cox}, P., {Greve}, T.~R., {Lutz}, D., {Neri}, R.,
+  {Omont}, A., \& {Swinbank}, A.~M. 2013, \mnras, 429, 3047
+
+\bibitem[{{Bussmann} {et~al.}(2012){Bussmann}, {Gurwell}, {Fu}, {Smith}, {Dye},
+  {Auld}, {Baes}, {Baker}, {Bonfield}, {Cava}, {Clements}, {Cooray}, {Coppin},
+  {Dannerbauer}, {Dariush}, {De Zotti}, {Dunne}, {Eales}, {Fritz}, {Hopwood},
+  {Ibar}, {Ivison}, {Jarvis}, {Kim}, {Leeuw}, {Maddox}, {Micha{\l}owski},
+  {Negrello}, {Pascale}, {Pohlen}, {Riechers}, {Rigby}, {Scott}, {Temi}, {Van
+  der Werf}, {Wardlow}, {Wilner}, \& {Verma}}]{Bussmann:2012lr}
+{Bussmann}, R.~S., {Gurwell}, M.~A., {Fu}, H., {Smith}, D.~J.~B., {Dye}, S.,
+  {Auld}, R., {Baes}, M., {Baker}, A.~J., {Bonfield}, D., {Cava}, A.,
+  {Clements}, D.~L., {Cooray}, A., {Coppin}, K., {Dannerbauer}, H., {Dariush},
+  A., {De Zotti}, G., {Dunne}, L., {Eales}, S., {Fritz}, J., {Hopwood}, R.,
+  {Ibar}, E., {Ivison}, R.~J., {Jarvis}, M.~J., {Kim}, S., {Leeuw}, L.~L.,
+  {Maddox}, S., {Micha{\l}owski}, M.~J., {Negrello}, M., {Pascale}, E.,
+  {Pohlen}, M., {Riechers}, D.~A., {Rigby}, E., {Scott}, D., {Temi}, P., {Van
+  der Werf}, P.~P., {Wardlow}, J., {Wilner}, D., \& {Verma}, A. 2012, \apj, 756
+
+\bibitem[{{Bussmann} {et~al.}(2013){Bussmann}, {P{\'e}rez-Fournon}, {Amber},
+  {Calanog}, {Gurwell}, {Dannerbauer}, {De Bernardis}, {Fu}, {Harris}, {Krips},
+  {Lapi}, {Maiolino}, {Omont}, {Riechers}, {Wardlow}, {Baker}, {Birkinshaw},
+  {Bock}, {Bourne}, {Clements}, {Cooray}, {De Zotti}, {Dunne}, {Dye}, {Eales},
+  {Farrah}, {Gavazzi}, {Gonz{\'a}lez Nuevo}, {Hopwood}, {Ibar}, {Ivison},
+  {Laporte}, {Maddox}, {Mart{\'{\i}}nez-Navajas}, {Michalowski}, {Negrello},
+  {Oliver}, {Roseboom}, {Scott}, {Serjeant}, {Smith}, {Smith}, {Streblyanska},
+  {Valiante}, {van der Werf}, {Verma}, {Vieira}, {Wang}, \&
+  {Wilner}}]{Bussmann:2013lr}
+{Bussmann}, R.~S., {P{\'e}rez-Fournon}, I., {Amber}, S., {Calanog}, J.,
+  {Gurwell}, M.~A., {Dannerbauer}, H., {De Bernardis}, F., {Fu}, H., {Harris},
+  A.~I., {Krips}, M., {Lapi}, A., {Maiolino}, R., {Omont}, A., {Riechers}, D.,
+  {Wardlow}, J., {Baker}, A.~J., {Birkinshaw}, M., {Bock}, J., {Bourne}, N.,
+  {Clements}, D.~L., {Cooray}, A., {De Zotti}, G., {Dunne}, L., {Dye}, S.,
+  {Eales}, S., {Farrah}, D., {Gavazzi}, R., {Gonz{\'a}lez Nuevo}, J.,
+  {Hopwood}, R., {Ibar}, E., {Ivison}, R.~J., {Laporte}, N., {Maddox}, S.,
+  {Mart{\'{\i}}nez-Navajas}, P., {Michalowski}, M., {Negrello}, M., {Oliver},
+  S.~J., {Roseboom}, I.~G., {Scott}, D., {Serjeant}, S., {Smith}, A.~J.,
+  {Smith}, M., {Streblyanska}, A., {Valiante}, E., {van der Werf}, P., {Verma},
+  A., {Vieira}, J.~D., {Wang}, L., \& {Wilner}, D. 2013, \apj, 779, 25
+
+\bibitem[{{Calanog} {et~al.}(2014){Calanog}, {Fu}, {Cooray}, {Wardlow}, {Ma},
+  {Amber}, {Baes}, {Bock}, {Bourne}, {Bussmann}, {Casey}, {Chapman},
+  {Clements}, {Conley}, {Dannerbauer}, {DeZotti}, {Dunne}, {Dye}, {Eales},
+  {Farrah}, {Furlanetto}, {Harris}, {Ivison}, {Maddox}, {Magdis},
+  {Michalowski}, {Negrello}, {Nightingale}, {O'Bryan}, {Oliver}, {Riechers},
+  {Scott}, {Serjeant}, {Simpson}, {Smith}, {Timmons}, {Thacker}, {Valiante}, \&
+  {Vieira}}]{Calanog:2014lr}
+{Calanog}, J.~A., {Fu}, H., {Cooray}, A., {Wardlow}, J., {Ma}, B., {Amber}, S.,
+  {Baes}, M., {Bock}, J., {Bourne}, N., {Bussmann}, R.~S., {Casey}, C.~M.,
+  {Chapman}, S.~C., {Clements}, D.~L., {Conley}, A., {Dannerbauer}, H.,
+  {DeZotti}, G., {Dunne}, L., {Dye}, S., {Eales}, S., {Farrah}, D.,
+  {Furlanetto}, C., {Harris}, A.~I., {Ivison}, R.~J., {Maddox}, S.~J.,
+  {Magdis}, G., {Michalowski}, M.~J., {Negrello}, M., {Nightingale}, J.,
+  {O'Bryan}, J.~M., {Oliver}, S.~J., {Riechers}, D., {Scott}, D., {Serjeant},
+  S., {Simpson}, J., {Smith}, M., {Timmons}, N., {Thacker}, C., {Valiante}, E.,
+  \& {Vieira}, J.~D. 2014, ArXiv e-prints
+
+\bibitem[{{Capak} {et~al.}(2011){Capak}, {Riechers}, {Scoville}, {Carilli},
+  {Cox}, {Neri}, {Robertson}, {Salvato}, {Schinnerer}, {Yan}, {Wilson}, {Yun},
+  {Civano}, {Elvis}, {Karim}, {Mobasher}, \& {Staguhn}}]{Capak:2011qy}
+{Capak}, P.~L., {Riechers}, D., {Scoville}, N.~Z., {Carilli}, C., {Cox}, P.,
+  {Neri}, R., {Robertson}, B., {Salvato}, M., {Schinnerer}, E., {Yan}, L.,
+  {Wilson}, G.~W., {Yun}, M., {Civano}, F., {Elvis}, M., {Karim}, A.,
+  {Mobasher}, B., \& {Staguhn}, J.~G. 2011, \nat, 470, 233
+
+\bibitem[{{Carlstrom} {et~al.}(2011)}]{Carlstrom:2011qy}
+{Carlstrom}, J.~E. {et~al.} 2011, \pasp, 123, 568
+
+\bibitem[{{Casey} {et~al.}(2012{\natexlab{a}}){Casey}, {Berta},
+  {B{\'e}thermin}, {Bock}, {Bridge}, {Budynkiewicz}, {Burgarella}, {Chapin},
+  {Chapman}, {Clements}, {Conley}, {Conselice}, {Cooray}, {Farrah},
+  {Hatziminaoglou}, {Ivison}, {le Floc'h}, {Lutz}, {Magdis}, {Magnelli},
+  {Oliver}, {Page}, {Pozzi}, {Rigopoulou}, {Riguccini}, {Roseboom}, {Sanders},
+  {Scott}, {Seymour}, {Valtchanov}, {Vieira}, {Viero}, \&
+  {Wardlow}}]{Casey:2012qy}
+{Casey}, C.~M., {Berta}, S., {B{\'e}thermin}, M., {Bock}, J., {Bridge}, C.,
+  {Budynkiewicz}, J., {Burgarella}, D., {Chapin}, E., {Chapman}, S.~C.,
+  {Clements}, D.~L., {Conley}, A., {Conselice}, C.~J., {Cooray}, A., {Farrah},
+  D., {Hatziminaoglou}, E., {Ivison}, R.~J., {le Floc'h}, E., {Lutz}, D.,
+  {Magdis}, G., {Magnelli}, B., {Oliver}, S.~J., {Page}, M.~J., {Pozzi}, F.,
+  {Rigopoulou}, D., {Riguccini}, L., {Roseboom}, I.~G., {Sanders}, D.~B.,
+  {Scott}, D., {Seymour}, N., {Valtchanov}, I., {Vieira}, J.~D., {Viero}, M.,
+  \& {Wardlow}, J. 2012{\natexlab{a}}, \apj, 761, 140
+
+\bibitem[{{Casey} {et~al.}(2012{\natexlab{b}}){Casey}, {Berta},
+  {B{\'e}thermin}, {Bock}, {Bridge}, {Burgarella}, {Chapin}, {Chapman},
+  {Clements}, {Conley}, {Conselice}, {Cooray}, {Farrah}, {Hatziminaoglou},
+  {Ivison}, {le Floc'h}, {Lutz}, {Magdis}, {Magnelli}, {Oliver}, {Page},
+  {Pozzi}, {Rigopoulou}, {Riguccini}, {Roseboom}, {Sanders}, {Scott},
+  {Seymour}, {Valtchanov}, {Vieira}, {Viero}, \& {Wardlow}}]{Casey:2012uq}
+{Casey}, C.~M., {Berta}, S., {B{\'e}thermin}, M., {Bock}, J., {Bridge}, C.,
+  {Burgarella}, D., {Chapin}, E., {Chapman}, S.~C., {Clements}, D.~L.,
+  {Conley}, A., {Conselice}, C.~J., {Cooray}, A., {Farrah}, D.,
+  {Hatziminaoglou}, E., {Ivison}, R.~J., {le Floc'h}, E., {Lutz}, D., {Magdis},
+  G., {Magnelli}, B., {Oliver}, S.~J., {Page}, M.~J., {Pozzi}, F.,
+  {Rigopoulou}, D., {Riguccini}, L., {Roseboom}, I.~G., {Sanders}, D.~B.,
+  {Scott}, D., {Seymour}, N., {Valtchanov}, I., {Vieira}, J.~D., {Viero}, M.,
+  \& {Wardlow}, J. 2012{\natexlab{b}}, \apj, 761, 139
+
+\bibitem[{{Casey} {et~al.}(2014){Casey}, {Narayanan}, \&
+  {Cooray}}]{Casey:2014lr}
+{Casey}, C.~M., {Narayanan}, D., \& {Cooray}, A. 2014, \physrep, 541, 45
+
+\bibitem[{{Chapman} {et~al.}(2005){Chapman}, {Blain}, {Smail}, \&
+  {Ivison}}]{2005ApJ...622..772C}
+{Chapman}, S.~C., {Blain}, A.~W., {Smail}, I., \& {Ivison}, R.~J. 2005, \apj,
+  622, 772
+
+\bibitem[{{Cole} {et~al.}(2000){Cole}, {Lacey}, {Baugh}, \&
+  {Frenk}}]{Cole:2000fk}
+{Cole}, S., {Lacey}, C.~G., {Baugh}, C.~M., \& {Frenk}, C.~S. 2000, \mnras,
+  319, 168
+
+\bibitem[{{Condon} {et~al.}(1998){Condon}, {Cotton}, {Greisen}, {Yin},
+  {Perley}, {Taylor}, \& {Broderick}}]{Condon:1998uq}
+{Condon}, J.~J., {Cotton}, W.~D., {Greisen}, E.~W., {Yin}, Q.~F., {Perley},
+  R.~A., {Taylor}, G.~B., \& {Broderick}, J.~J. 1998, \aj, 115, 1693
+
+\bibitem[{{Conley} {et~al.}(2011)}]{Conley:2011lr}
+{Conley}, A. {et~al.} 2011, \apjl, 732, L35
+
+\bibitem[{{Cooray} {et~al.}(2014){Cooray}, {Calanog}, {Wardlow}, {Bock},
+  {Bridge}, {Burgarella}, {Bussmann}, {Casey}, {Clements}, {Conley}, {Farrah},
+  {Fu}, {Gavazzi}, {Ivison}, {La Porte}, {Lo Faro}, {Ma}, {Magdis}, {Oliver},
+  {Osage}, {P{\'e}rez-Fournon}, {Riechers}, {Rigopoulou}, {Scott}, {Viero}, \&
+  {Watson}}]{Cooray:2014rm}
+{Cooray}, A., {Calanog}, J., {Wardlow}, J.~L., {Bock}, J., {Bridge}, C.,
+  {Burgarella}, D., {Bussmann}, R.~S., {Casey}, C.~M., {Clements}, D.,
+  {Conley}, A., {Farrah}, D., {Fu}, H., {Gavazzi}, R., {Ivison}, R.~J., {La
+  Porte}, N., {Lo Faro}, B., {Ma}, B., {Magdis}, G., {Oliver}, S.~J., {Osage},
+  W.~A., {P{\'e}rez-Fournon}, I., {Riechers}, D., {Rigopoulou}, D., {Scott},
+  D., {Viero}, M., \& {Watson}, D. 2014, \apj, 790, 40
+
+\bibitem[{{Cowley} {et~al.}(2015){Cowley}, {Lacey}, {Baugh}, \&
+  {Cole}}]{Cowley:2015lr}
+{Cowley}, W.~I., {Lacey}, C.~G., {Baugh}, C.~M., \& {Cole}, S. 2015, \mnras,
+  446, 1784
+
+\bibitem[{{Cox} {et~al.}(2008){Cox}, {Jonsson}, {Somerville}, {Primack}, \&
+  {Dekel}}]{Cox08}
+{Cox}, T.~J., {Jonsson}, P., {Somerville}, R.~S., {Primack}, J.~R., \& {Dekel},
+  A. 2008, \mnras, 384, 386
+
+\bibitem[{{Daddi} {et~al.}(2009)}]{Daddi:2009qy}
+{Daddi}, E. {et~al.} 2009, \apj, 694, 1517
+
+\bibitem[{{Dye} {et~al.}(2015){Dye}, {Furlanetto}, {Swinbank}, {Vlahakis},
+  {Nightingale}, {Dunne}, {Eales}, {Smail}, {Oteo-Gomez}, {Hunter}, {Negrello},
+  {Dannerbauer}, {Ivison}, {Gavazzi}, {Cooray}, \& {van der Werf}}]{Dye:2015fp}
+{Dye}, S., {Furlanetto}, C., {Swinbank}, A.~M., {Vlahakis}, C., {Nightingale},
+  J.~W., {Dunne}, L., {Eales}, S.~A., {Smail}, I., {Oteo-Gomez}, I., {Hunter},
+  T., {Negrello}, M., {Dannerbauer}, H., {Ivison}, R.~J., {Gavazzi}, R.,
+  {Cooray}, A., \& {van der Werf}, P. 2015, ArXiv e-prints
+
+\bibitem[{{Eales} {et~al.}(2010)}]{2010PASP..122..499E}
+{Eales}, S. {et~al.} 2010, \pasp, 122, 499
+
+\bibitem[{{Engel} {et~al.}(2010){Engel}, {Tacconi}, {Davies}, {Neri}, {Smail},
+  {Chapman}, {Genzel}, {Cox}, {Greve}, {Ivison}, {Blain}, {Bertoldi}, \&
+  {Omont}}]{2010ApJ...724..233E}
+{Engel}, H., {Tacconi}, L.~J., {Davies}, R.~I., {Neri}, R., {Smail}, I.,
+  {Chapman}, S.~C., {Genzel}, R., {Cox}, P., {Greve}, T.~R., {Ivison}, R.~J.,
+  {Blain}, A., {Bertoldi}, F., \& {Omont}, A. 2010, \apj, 724, 233
+
+\bibitem[{{Fialkov} \& {Loeb}(2015)}]{Fialkov:2015eu}
+{Fialkov}, A. \& {Loeb}, A. 2015, ArXiv e-prints
+
+\bibitem[{{Foreman-Mackey} {et~al.}(2013){Foreman-Mackey}, {Hogg}, {Lang}, \&
+  {Goodman}}]{Foreman-Mackey:2013yq}
+{Foreman-Mackey}, D., {Hogg}, D.~W., {Lang}, D., \& {Goodman}, J. 2013, \pasp,
+  125, 306
+
+\bibitem[{{Fu} {et~al.}(2013)}]{Fu:2013lr}
+{Fu}, H. {et~al.} 2013, \nat, 498, 338
+
+\bibitem[{{Gavazzi} {et~al.}(2011)}]{Gavazzi:2011lr}
+{Gavazzi}, R. {et~al.} 2011, \apj, 738, 125
+
+\bibitem[{{Goodman} \& {Weare}(2010)}]{goodmanweare}
+{Goodman}, J. \& {Weare}, J. 2010, Communications in Applied Mathematics and
+  Computational Science, 5, 65
+
+\bibitem[{{Griffin} {et~al.}(2010)}]{2010A&A...518L...3G}
+{Griffin}, M.~J. {et~al.} 2010, \aap, 518, L3+
+
+\bibitem[{{Guo} {et~al.}(2013){Guo}, {White}, {Angulo}, {Henriques}, {Lemson},
+  {Boylan-Kolchin}, {Thomas}, \& {Short}}]{Guo:2013lr}
+{Guo}, Q., {White}, S., {Angulo}, R.~E., {Henriques}, B., {Lemson}, G.,
+  {Boylan-Kolchin}, M., {Thomas}, P., \& {Short}, C. 2013, \mnras, 428, 1351
+
+\bibitem[{{Hayward} {et~al.}(2013{\natexlab{a}}){Hayward}, {Behroozi},
+  {Somerville}, {Primack}, {Moreno}, \& {Wechsler}}]{HB13}
+{Hayward}, C.~C., {Behroozi}, P.~S., {Somerville}, R.~S., {Primack}, J.~R.,
+  {Moreno}, J., \& {Wechsler}, R.~H. 2013{\natexlab{a}}, \mnras
+
+\bibitem[{{Hayward} {et~al.}(2012{\natexlab{a}}){Hayward}, {Jonsson}, {Kere{\v
+  s}}, {Magnelli}, {Hernquist}, \& {Cox}}]{Hayward:2012lr}
+{Hayward}, C.~C., {Jonsson}, P., {Kere{\v s}}, D., {Magnelli}, B., {Hernquist},
+  L., \& {Cox}, T.~J. 2012{\natexlab{a}}, \mnras, 424, 951
+
+\bibitem[{{Hayward} {et~al.}(2012{\natexlab{b}}){Hayward}, {Jonsson}, {Kere{\v
+  s}}, {Magnelli}, {Hernquist}, \& {Cox}}]{H12}
+---. 2012{\natexlab{b}}, \mnras, 424, 951
+
+\bibitem[{{Hayward} {et~al.}(2011){Hayward}, {Kere{\v s}}, {Jonsson},
+  {Narayanan}, {Cox}, \& {Hernquist}}]{H11}
+{Hayward}, C.~C., {Kere{\v s}}, D., {Jonsson}, P., {Narayanan}, D., {Cox},
+  T.~J., \& {Hernquist}, L. 2011, \apj, 743, 159
+
+\bibitem[{{Hayward} {et~al.}(2013{\natexlab{b}}){Hayward}, {Narayanan},
+  {Kere{\v s}}, {Jonsson}, {Hopkins}, {Cox}, \& {Hernquist}}]{HN13}
+{Hayward}, C.~C., {Narayanan}, D., {Kere{\v s}}, D., {Jonsson}, P., {Hopkins},
+  P.~F., {Cox}, T.~J., \& {Hernquist}, L. 2013{\natexlab{b}}, \mnras, 428, 2529
+
+\bibitem[{{Hayward} {et~al.}(2014){Hayward}, {Torrey}, {Springel}, {Hernquist},
+  \& {Vogelsberger}}]{H14}
+{Hayward}, C.~C., {Torrey}, P., {Springel}, V., {Hernquist}, L., \&
+  {Vogelsberger}, M. 2014, \mnras, 442, 1992
+
+\bibitem[{{Hezaveh} {et~al.}(2013)}]{Hezaveh:2013fk}
+{Hezaveh}, Y.~D. {et~al.} 2013, \apj, 767, 132
+
+\bibitem[{{Hinshaw} {et~al.}(2013){Hinshaw}, {Larson}, {Komatsu}, {Spergel},
+  {Bennett}, {Dunkley}, {Nolta}, {Halpern}, {Hill}, {Odegard}, {Page}, {Smith},
+  {Weiland}, {Gold}, {Jarosik}, {Kogut}, {Limon}, {Meyer}, {Tucker}, {Wollack},
+  \& {Wright}}]{Hinshaw:2013ty}
+{Hinshaw}, G., {Larson}, D., {Komatsu}, E., {Spergel}, D.~N., {Bennett}, C.~L.,
+  {Dunkley}, J., {Nolta}, M.~R., {Halpern}, M., {Hill}, R.~S., {Odegard}, N.,
+  {Page}, L., {Smith}, K.~M., {Weiland}, J.~L., {Gold}, B., {Jarosik}, N.,
+  {Kogut}, A., {Limon}, M., {Meyer}, S.~S., {Tucker}, G.~S., {Wollack}, E., \&
+  {Wright}, E.~L. 2013, \apjs, 208, 19
+
+\bibitem[{{Ho} {et~al.}(2004){Ho}, {Moran}, \& {Lo}}]{Ho:2004lr}
+{Ho}, P.~T.~P., {Moran}, J.~M., \& {Lo}, K.~Y. 2004, \apjl, 616, L1
+
+\bibitem[{{Hodge} {et~al.}(2013)}]{Hodge:2013qy}
+{Hodge}, J.~A. {et~al.} 2013, \apj, 768, 91
+
+\bibitem[{{Hook} {et~al.}(2004){Hook}, {J{\o}rgensen}, {Allington-Smith},
+  {Davies}, {Metcalfe}, {Murowinski}, \& {Crampton}}]{Hook:2004qy}
+{Hook}, I.~M., {J{\o}rgensen}, I., {Allington-Smith}, J.~R., {Davies}, R.~L.,
+  {Metcalfe}, N., {Murowinski}, R.~G., \& {Crampton}, D. 2004, \pasp, 116, 425
+
+\bibitem[{{Ikarashi} {et~al.}(2014){Ikarashi}, {Ivison}, {Caputi}, {Aretxaga},
+  {Dunlop}, {Hatsukade}, {Hughes}, {Iono}, {Izumi}, {Kawabe}, {Kohno}, {Lagos},
+  {Motohara}, {Nakanishi}, {Ohta}, {Tamura}, {Umehata}, {Wilson}, {Yabe}, \&
+  {Yun}}]{Ikarashi:2014nr}
+{Ikarashi}, S., {Ivison}, R.~J., {Caputi}, K.~I., {Aretxaga}, I., {Dunlop},
+  J.~S., {Hatsukade}, B., {Hughes}, D., {Iono}, D., {Izumi}, T., {Kawabe}, R.,
+  {Kohno}, K., {Lagos}, C.~P., {Motohara}, K., {Nakanishi}, K., {Ohta}, K.,
+  {Tamura}, Y., {Umehata}, H., {Wilson}, G., {Yabe}, K., \& {Yun}, M.~S. 2014,
+  ArXiv e-prints
+
+\bibitem[{{Ikarashi} {et~al.}(2011)}]{Ikarashi:2011qy}
+{Ikarashi}, S. {et~al.} 2011, \mnras, 415, 3081
+
+\bibitem[{{Ivison} {et~al.}(2007){Ivison}, {Greve}, {Dunlop}, {Peacock},
+  {Egami}, {Smail}, {Ibar}, {van Kampen}, {Aretxaga}, {Babbedge}, {Biggs},
+  {Blain}, {Chapman}, {Clements}, {Coppin}, {Farrah}, {Halpern}, {Hughes},
+  {Jarvis}, {Jenness}, {Jones}, {Mortier}, {Oliver}, {Papovich},
+  {P{\'e}rez-Gonz{\'a}lez}, {Pope}, {Rawlings}, {Rieke}, {Rowan-Robinson},
+  {Savage}, {Scott}, {Seigar}, {Serjeant}, {Simpson}, {Stevens}, {Vaccari},
+  {Wagg}, \& {Willott}}]{Ivison:2007qv}
+{Ivison}, R.~J., {Greve}, T.~R., {Dunlop}, J.~S., {Peacock}, J.~A., {Egami},
+  E., {Smail}, I., {Ibar}, E., {van Kampen}, E., {Aretxaga}, I., {Babbedge},
+  T., {Biggs}, A.~D., {Blain}, A.~W., {Chapman}, S.~C., {Clements}, D.~L.,
+  {Coppin}, K., {Farrah}, D., {Halpern}, M., {Hughes}, D.~H., {Jarvis}, M.~J.,
+  {Jenness}, T., {Jones}, J.~R., {Mortier}, A.~M.~J., {Oliver}, S., {Papovich},
+  C., {P{\'e}rez-Gonz{\'a}lez}, P.~G., {Pope}, A., {Rawlings}, S., {Rieke},
+  G.~H., {Rowan-Robinson}, M., {Savage}, R.~S., {Scott}, D., {Seigar}, M.,
+  {Serjeant}, S., {Simpson}, C., {Stevens}, J.~A., {Vaccari}, M., {Wagg}, J.,
+  \& {Willott}, C.~J. 2007, \mnras, 380, 199
+
+\bibitem[{{Ivison} {et~al.}(2011){Ivison}, {Papadopoulos}, {Smail}, {Greve},
+  {Thomson}, {Xilouris}, \& {Chapman}}]{2011MNRAS.412.1913I}
+{Ivison}, R.~J., {Papadopoulos}, P.~P., {Smail}, I., {Greve}, T.~R., {Thomson},
+  A.~P., {Xilouris}, E.~M., \& {Chapman}, S.~C. 2011, \mnras, 412, 1913
+
+\bibitem[{{Ivison} {et~al.}(2013)}]{Ivison:2013fk}
+{Ivison}, R.~J. {et~al.} 2013, \apj, 772, 137
+
+\bibitem[{{Jiang} {et~al.}(2014){Jiang}, {Helly}, {Cole}, \&
+  {Frenk}}]{Jiang:2014lr}
+{Jiang}, L., {Helly}, J.~C., {Cole}, S., \& {Frenk}, C.~S. 2014, \mnras, 440,
+  2115
+
+\bibitem[{{Karim} {et~al.}(2013)}]{Karim:2013lr}
+{Karim}, A. {et~al.} 2013, \mnras, 432, 2
+
+\bibitem[{{Keeton}(2001)}]{Keeton:2001lr}
+{Keeton}, C.~R. 2001, ArXiv Astrophysics e-prints
+
+\bibitem[{{Klypin} {et~al.}(2011){Klypin}, {Trujillo-Gomez}, \&
+  {Primack}}]{Klypin11}
+{Klypin}, A.~A., {Trujillo-Gomez}, S., \& {Primack}, J. 2011, \apj, 740, 102
+
+\bibitem[{{Kochanek}(1994)}]{Kochanek:1994fk}
+{Kochanek}, C.~S. 1994, \apj, 436, 56
+
+\bibitem[{{Komatsu} {et~al.}(2011){Komatsu}, {Smith}, {Dunkley}, {Bennett},
+  {Gold}, {Hinshaw}, {Jarosik}, {Larson}, {Nolta}, {Page}, {Spergel},
+  {Halpern}, {Hill}, {Kogut}, {Limon}, {Meyer}, {Odegard}, {Tucker}, {Weiland},
+  {Wollack}, \& {Wright}}]{Komatsu:2011fk}
+{Komatsu}, E., {Smith}, K.~M., {Dunkley}, J., {Bennett}, C.~L., {Gold}, B.,
+  {Hinshaw}, G., {Jarosik}, N., {Larson}, D., {Nolta}, M.~R., {Page}, L.,
+  {Spergel}, D.~N., {Halpern}, M., {Hill}, R.~S., {Kogut}, A., {Limon}, M.,
+  {Meyer}, S.~S., {Odegard}, N., {Tucker}, G.~S., {Weiland}, J.~L., {Wollack},
+  E., \& {Wright}, E.~L. 2011, \apjs, 192, 18
+
+\bibitem[{{Lilly} {et~al.}(1996){Lilly}, {Le Fevre}, {Hammer}, \&
+  {Crampton}}]{Lilly:1996uq}
+{Lilly}, S.~J., {Le Fevre}, O., {Hammer}, F., \& {Crampton}, D. 1996, \apjl,
+  460, L1
+
+\bibitem[{{Lima} {et~al.}(2010){Lima}, {Jain}, \& {Devlin}}]{Lima:2010fk}
+{Lima}, M., {Jain}, B., \& {Devlin}, M. 2010, \mnras, 406, 2352
+
+\bibitem[{{Madau} {et~al.}(1996){Madau}, {Ferguson}, {Dickinson}, {Giavalisco},
+  {Steidel}, \& {Fruchter}}]{1996MNRAS.283.1388M}
+{Madau}, P., {Ferguson}, H.~C., {Dickinson}, M.~E., {Giavalisco}, M.,
+  {Steidel}, C.~C., \& {Fruchter}, A. 1996, \mnras, 283, 1388
+
+\bibitem[{{Magnelli} {et~al.}(2011){Magnelli}, {Elbaz}, {Chary}, {Dickinson},
+  {Le Borgne}, {Frayer}, \& {Willmer}}]{Magnelli:2011ul}
+{Magnelli}, B., {Elbaz}, D., {Chary}, R.~R., {Dickinson}, M., {Le Borgne}, D.,
+  {Frayer}, D.~T., \& {Willmer}, C.~N.~A. 2011, \aap, 528, A35+
+
+\bibitem[{{Mandelbaum} {et~al.}(2005){Mandelbaum}, {Tasitsiomi}, {Seljak},
+  {Kravtsov}, \& {Wechsler}}]{Mandelbaum:2005lr}
+{Mandelbaum}, R., {Tasitsiomi}, A., {Seljak}, U., {Kravtsov}, A.~V., \&
+  {Wechsler}, R.~H. 2005, \mnras, 362, 1451
+
+\bibitem[{{Merson} {et~al.}(2013){Merson}, {Baugh}, {Helly}, {Gonzalez-Perez},
+  {Cole}, {Bielby}, {Norberg}, {Frenk}, {Benson}, {Bower}, {Lacey}, \&
+  {Lagos}}]{Merson:2013lr}
+{Merson}, A.~I., {Baugh}, C.~M., {Helly}, J.~C., {Gonzalez-Perez}, V., {Cole},
+  S., {Bielby}, R., {Norberg}, P., {Frenk}, C.~S., {Benson}, A.~J., {Bower},
+  R.~G., {Lacey}, C.~G., \& {Lagos}, C.~d.~P. 2013, \mnras, 429, 556
+
+\bibitem[{{Messias} {et~al.}(2014){Messias}, {Dye}, {Nagar}, {Orellana},
+  {Bussmann}, {Calanog}, {Dannerbauer}, {Fu}, {Ibar}, {Inohara}, {Ivison},
+  {Negrello}, {Riechers}, {Sheen}, {Aguirre}, {Amber}, {Birkinshaw}, {Bourne},
+  {Bradford}, {Clements}, {Cooray}, {De Zotti}, {Demarco}, {Dunne}, {Eales},
+  {Fleuren}, {Kamenetzky}, {Lupu}, {Maddox}, {Marrone}, {Micha{\l}owski},
+  {Murphy}, {Nguyen}, {Omont}, {Rowlands}, {Smith}, {Smith}, {Valiante}, \&
+  {Vieira}}]{Messias:2014fk}
+{Messias}, H., {Dye}, S., {Nagar}, N., {Orellana}, G., {Bussmann}, R.~S.,
+  {Calanog}, J., {Dannerbauer}, H., {Fu}, H., {Ibar}, E., {Inohara}, A.,
+  {Ivison}, R.~J., {Negrello}, M., {Riechers}, D.~A., {Sheen}, Y.-K.,
+  {Aguirre}, J.~E., {Amber}, S., {Birkinshaw}, M., {Bourne}, N., {Bradford},
+  C.~M., {Clements}, D.~L., {Cooray}, A., {De Zotti}, G., {Demarco}, R.,
+  {Dunne}, L., {Eales}, S., {Fleuren}, S., {Kamenetzky}, J., {Lupu}, R.~E.,
+  {Maddox}, S.~J., {Marrone}, D.~P., {Micha{\l}owski}, M.~J., {Murphy}, E.~J.,
+  {Nguyen}, H.~T., {Omont}, A., {Rowlands}, K., {Smith}, D., {Smith}, M.,
+  {Valiante}, E., \& {Vieira}, J.~D. 2014, \aap, 568, A92
+
+\bibitem[{{Miettinen} {et~al.}(2015){Miettinen}, {Smol{\v c}i{\'c}}, {Novak},
+  {Aravena}, {Karim}, {Masters}, {Riechers}, {Bussmann}, {McCracken}, {Ilbert},
+  {Bertoldi}, {Capak}, {Feruglio}, {Halliday}, {Kartaltepe}, {Navarrete},
+  {Salvato}, {Sanders}, {Schinnerer}, \& {Sheth}}]{Miettinen:2015lr}
+{Miettinen}, O., {Smol{\v c}i{\'c}}, V., {Novak}, M., {Aravena}, M., {Karim},
+  A., {Masters}, D., {Riechers}, D.~A., {Bussmann}, R.~S., {McCracken}, H.~J.,
+  {Ilbert}, O., {Bertoldi}, F., {Capak}, P., {Feruglio}, C., {Halliday}, C.,
+  {Kartaltepe}, J.~S., {Navarrete}, F., {Salvato}, M., {Sanders}, D.,
+  {Schinnerer}, E., \& {Sheth}, K. 2015, ArXiv e-prints
+
+\bibitem[{{Miller} {et~al.}(2015){Miller}, {Hayward}, {Chapman}, \&
+  {Behroozi}}]{Miller:2015lr}
+{Miller}, T.~B., {Hayward}, C.~C., {Chapman}, S.~C., \& {Behroozi}, P.~S. 2015,
+  ArXiv e-prints
+
+\bibitem[{{Mu{\~n}oz Arancibia} {et~al.}(2015){Mu{\~n}oz Arancibia},
+  {Navarrete}, {Padilla}, {Cora}, {Gawiser}, {Kurczynski}, \&
+  {Ruiz}}]{Munoz-Arancibia:2015qy}
+{Mu{\~n}oz Arancibia}, A.~M., {Navarrete}, F.~P., {Padilla}, N.~D., {Cora},
+  S.~A., {Gawiser}, E., {Kurczynski}, P., \& {Ruiz}, A.~N. 2015, \mnras, 446,
+  2291
+
+\bibitem[{{Narayanan} {et~al.}(2010){Narayanan}, {Hayward}, {Cox}, {Hernquist},
+  {Jonsson}, {Younger}, \& {Groves}}]{Narayanan:2010lr}
+{Narayanan}, D., {Hayward}, C.~C., {Cox}, T.~J., {Hernquist}, L., {Jonsson},
+  P., {Younger}, J.~D., \& {Groves}, B. 2010, \mnras, 401, 1613
+
+\bibitem[{{Navarro} {et~al.}(1997){Navarro}, {Frenk}, \&
+  {White}}]{Navarro:1997ys}
+{Navarro}, J.~F., {Frenk}, C.~S., \& {White}, S.~D.~M. 1997, \apj, 490, 493
+
+\bibitem[{{Negrello} {et~al.}(2007){Negrello}, {Perrotta},
+  {Gonz{\'a}lez-Nuevo}, {Silva}, {de Zotti}, {Granato}, {Baccigalupi}, \&
+  {Danese}}]{2007MNRAS.377.1557N}
+{Negrello}, M., {Perrotta}, F., {Gonz{\'a}lez-Nuevo}, J., {Silva}, L., {de
+  Zotti}, G., {Granato}, G.~L., {Baccigalupi}, C., \& {Danese}, L. 2007,
+  \mnras, 377, 1557
+
+\bibitem[{{Negrello} {et~al.}(2010)}]{Negrello:2010fk}
+{Negrello}, M. {et~al.} 2010, Science, 330, 800
+
+\bibitem[{{Nguyen} {et~al.}(2010)}]{Nguyen:2010fk}
+{Nguyen}, H.~T. {et~al.} 2010, \aap, 518, L5
+
+\bibitem[{{Oliver} {et~al.}(2012)}]{Oliver:2012lr}
+{Oliver}, S.~J. {et~al.} 2012, \mnras, 424, 1614
+
+\bibitem[{{Parkinson} {et~al.}(2008){Parkinson}, {Cole}, \&
+  {Helly}}]{Parkinson:2008qy}
+{Parkinson}, H., {Cole}, S., \& {Helly}, J. 2008, \mnras, 383, 557
+
+\bibitem[{{Patton} {et~al.}(2013){Patton}, {Torrey}, {Ellison}, {Mendel}, \&
+  {Scudder}}]{Patton13}
+{Patton}, D.~R., {Torrey}, P., {Ellison}, S.~L., {Mendel}, J.~T., \& {Scudder},
+  J.~M. 2013, \mnras, 433, L59
+
+\bibitem[{{Pedregosa} {et~al.}(2011)}]{scikitlearn}
+{Pedregosa}, F. {et~al.} 2011, {Journal of Machine Learning Research}, 12, 2825
+
+\bibitem[{{Pilbratt} {et~al.}(2010)}]{Pilbratt:2010fk}
+{Pilbratt}, G.~L. {et~al.} 2010, \aap, 518, L1
+
+\bibitem[{{Pope} {et~al.}(2006)}]{2006MNRAS.370.1185P}
+{Pope}, A. {et~al.} 2006, \mnras, 370, 1185
+
+\bibitem[{{Puget} {et~al.}(1996){Puget}, {Abergel}, {Bernard}, {Boulanger},
+  {Burton}, {Desert}, \& {Hartmann}}]{Puget:1996lr}
+{Puget}, J.-L., {Abergel}, A., {Bernard}, J.-P., {Boulanger}, F., {Burton},
+  W.~B., {Desert}, F.-X., \& {Hartmann}, D. 1996, \aap, 308, L5
+
+\bibitem[{{Riechers} {et~al.}(2011{\natexlab{a}})}]{Riechers:2011uq}
+{Riechers}, D.~A. {et~al.} 2011{\natexlab{a}}, \apjl, 733, L12
+
+\bibitem[{{Riechers} {et~al.}(2011{\natexlab{b}})}]{2011ApJ...733L..11R}
+---. 2011{\natexlab{b}}, \apjl, 733, L11+
+
+\bibitem[{{Riechers} {et~al.}(2013)}]{Riechers:2013lr}
+---. 2013, \nat, 496, 329
+
+\bibitem[{{Rieke} {et~al.}(2004)}]{2004ApJS..154...25R}
+{Rieke}, G.~H. {et~al.} 2004, \apjs, 154, 25
+
+\bibitem[{{Robson} {et~al.}(2014){Robson}, {Ivison}, {Smail}, {Holland},
+  {Geach}, {Gibb}, {Riechers}, {Ade}, {Bintley}, {Bock}, {Chapin}, {Chapman},
+  {Clements}, {Conley}, {Cooray}, {Dunlop}, {Farrah}, {Fich}, {Fu}, {Jenness},
+  {Laporte}, {Oliver}, {Omont}, {P{\'e}rez-Fournon}, {Scott}, {Swinbank}, \&
+  {Wardlow}}]{Robson:2014xy}
+{Robson}, E.~I., {Ivison}, R.~J., {Smail}, I., {Holland}, W.~S., {Geach},
+  J.~E., {Gibb}, A.~G., {Riechers}, D., {Ade}, P.~A.~R., {Bintley}, D., {Bock},
+  J., {Chapin}, E.~L., {Chapman}, S.~C., {Clements}, D.~L., {Conley}, A.,
+  {Cooray}, A., {Dunlop}, J.~S., {Farrah}, D., {Fich}, M., {Fu}, H., {Jenness},
+  T., {Laporte}, N., {Oliver}, S.~J., {Omont}, A., {P{\'e}rez-Fournon}, I.,
+  {Scott}, D., {Swinbank}, A.~M., \& {Wardlow}, J. 2014, \apj, 793, 11
+
+\bibitem[{{Rybak} {et~al.}(2015){Rybak}, {McKean}, {Vegetti}, {Andreani}, \&
+  {White}}]{Rybak:2015fk}
+{Rybak}, M., {McKean}, J.~P., {Vegetti}, S., {Andreani}, P., \& {White},
+  S.~D.~M. 2015, ArXiv e-prints
+
+\bibitem[{{Savage} \& {Oliver}(2007)}]{Savage:2007sf}
+{Savage}, R.~S. \& {Oliver}, S. 2007, \apj, 661, 1339
+
+\bibitem[{{Scott} {et~al.}(2008){Scott}, {Austermann}, {Perera}, {Wilson},
+  {Aretxaga}, {Bock}, {Hughes}, {Kang}, {Kim}, {Mauskopf}, {Sanders},
+  {Scoville}, \& {Yun}}]{Scott:2008qy}
+{Scott}, K.~S., {Austermann}, J.~E., {Perera}, T.~A., {Wilson}, G.~W.,
+  {Aretxaga}, I., {Bock}, J.~J., {Hughes}, D.~H., {Kang}, Y., {Kim}, S.,
+  {Mauskopf}, P.~D., {Sanders}, D.~B., {Scoville}, N., \& {Yun}, M.~S. 2008,
+  \mnras, 385, 2225
+
+\bibitem[{{Scudder} {et~al.}(2012){Scudder}, {Ellison}, {Torrey}, {Patton}, \&
+  {Mendel}}]{Scudder12}
+{Scudder}, J.~M., {Ellison}, S.~L., {Torrey}, P., {Patton}, D.~R., \& {Mendel},
+  J.~T. 2012, \mnras, 426, 549
+
+\bibitem[{{Sersic}(1968)}]{1968adga.book.....S}
+{Sersic}, J.~L. 1968, {Atlas de galaxias australes} (Cordoba, Argentina:
+  Observatorio Astronomico, 1968)
+
+\bibitem[{{Sheth} \& {Tormen}(1999)}]{Sheth:1999kx}
+{Sheth}, R.~K. \& {Tormen}, G. 1999, \mnras, 308, 119
+
+\bibitem[{{Simpson} {et~al.}(2015){Simpson}, {Smail}, {Swinbank}, {Almaini},
+  {Blain}, {Bremer}, {Chapman}, {Chen}, {Conselice}, {Coppin}, {Danielson},
+  {Dunlop}, {Edge}, {Farrah}, {Geach}, {Hartley}, {Ivison}, {Karim}, {Lani},
+  {Ma}, {Meijerink}, {Micha{\l}owski}, {Mortlock}, {Scott}, {Simpson},
+  {Spaans}, {Thomson}, {van Kampen}, \& {van der Werf}}]{Simpson:2015ty}
+{Simpson}, J.~M., {Smail}, I., {Swinbank}, A.~M., {Almaini}, O., {Blain},
+  A.~W., {Bremer}, M.~N., {Chapman}, S.~C., {Chen}, C.-C., {Conselice}, C.,
+  {Coppin}, K.~E.~K., {Danielson}, A.~L.~R., {Dunlop}, J.~S., {Edge}, A.~C.,
+  {Farrah}, D., {Geach}, J.~E., {Hartley}, W.~G., {Ivison}, R.~J., {Karim}, A.,
+  {Lani}, C., {Ma}, C.-J., {Meijerink}, R., {Micha{\l}owski}, M.~J.,
+  {Mortlock}, A., {Scott}, D., {Simpson}, C.~J., {Spaans}, M., {Thomson},
+  A.~P., {van Kampen}, E., \& {van der Werf}, P.~P. 2015, \apj, 799, 81
+
+\bibitem[{{Simpson} {et~al.}(2014){Simpson}, {Swinbank}, {Smail}, {Alexander},
+  {Brandt}, {Bertoldi}, {de Breuck}, {Chapman}, {Coppin}, {da Cunha},
+  {Danielson}, {Dannerbauer}, {Greve}, {Hodge}, {Ivison}, {Karim}, {Knudsen},
+  {Poggianti}, {Schinnerer}, {Thomson}, {Walter}, {Wardlow}, {Wei{\ss}}, \&
+  {van der Werf}}]{Simpson:2014lr}
+{Simpson}, J.~M., {Swinbank}, A.~M., {Smail}, I., {Alexander}, D.~M., {Brandt},
+  W.~N., {Bertoldi}, F., {de Breuck}, C., {Chapman}, S.~C., {Coppin}, K.~E.~K.,
+  {da Cunha}, E., {Danielson}, A.~L.~R., {Dannerbauer}, H., {Greve}, T.~R.,
+  {Hodge}, J.~A., {Ivison}, R.~J., {Karim}, A., {Knudsen}, K.~K., {Poggianti},
+  B.~M., {Schinnerer}, E., {Thomson}, A.~P., {Walter}, F., {Wardlow}, J.~L.,
+  {Wei{\ss}}, A., \& {van der Werf}, P.~P. 2014, \apj, 788, 125
+
+\bibitem[{{Smith} {et~al.}(2012){Smith}, {Wang}, {Oliver}, {Auld}, {Bock},
+  {Brisbin}, {Burgarella}, {Chanial}, {Chapin}, {Clements}, {Conversi},
+  {Cooray}, {Dowell}, {Eales}, {Farrah}, {Franceschini}, {Glenn}, {Griffin},
+  {Ivison}, {Mortier}, {Page}, {Papageorgiou}, {Pearson}, {P{\'e}rez-Fournon},
+  {Pohlen}, {Rawlings}, {Raymond}, {Rodighiero}, {Roseboom}, {Rowan-Robinson},
+  {Savage}, {Scott}, {Seymour}, {Symeonidis}, {Tugwell}, {Vaccari},
+  {Valtchanov}, {Vigroux}, {Ward}, {Wright}, \& {Zemcov}}]{Smith:2012uq}
+{Smith}, A.~J., {Wang}, L., {Oliver}, S.~J., {Auld}, R., {Bock}, J., {Brisbin},
+  D., {Burgarella}, D., {Chanial}, P., {Chapin}, E., {Clements}, D.~L.,
+  {Conversi}, L., {Cooray}, A., {Dowell}, C.~D., {Eales}, S., {Farrah}, D.,
+  {Franceschini}, A., {Glenn}, J., {Griffin}, M., {Ivison}, R.~J., {Mortier},
+  A.~M.~J., {Page}, M.~J., {Papageorgiou}, A., {Pearson}, C.~P.,
+  {P{\'e}rez-Fournon}, I., {Pohlen}, M., {Rawlings}, J.~I., {Raymond}, G.,
+  {Rodighiero}, G., {Roseboom}, I.~G., {Rowan-Robinson}, M., {Savage}, R.,
+  {Scott}, D., {Seymour}, N., {Symeonidis}, M., {Tugwell}, K.~E., {Vaccari},
+  M., {Valtchanov}, I., {Vigroux}, L., {Ward}, R., {Wright}, G., \& {Zemcov},
+  M. 2012, \mnras, 419, 377
+
+\bibitem[{{Smol{\v c}i{\'c}} {et~al.}(2012){Smol{\v c}i{\'c}}, {Aravena},
+  {Navarrete}, {Schinnerer}, {Riechers}, {Bertoldi}, {Feruglio}, {Finoguenov},
+  {Salvato}, {Sargent}, {McCracken}, {Albrecht}, {Karim}, {Capak}, {Carilli},
+  {Cappelluti}, {Elvis}, {Ilbert}, {Kartaltepe}, {Lilly}, {Sanders}, {Sheth},
+  {Scoville}, \& {Taniguchi}}]{Smolcic:2012zl}
+{Smol{\v c}i{\'c}}, V., {Aravena}, M., {Navarrete}, F., {Schinnerer}, E.,
+  {Riechers}, D.~A., {Bertoldi}, F., {Feruglio}, C., {Finoguenov}, A.,
+  {Salvato}, M., {Sargent}, M., {McCracken}, H.~J., {Albrecht}, M., {Karim},
+  A., {Capak}, P., {Carilli}, C.~L., {Cappelluti}, N., {Elvis}, M., {Ilbert},
+  O., {Kartaltepe}, J., {Lilly}, S., {Sanders}, D., {Sheth}, K., {Scoville},
+  N.~Z., \& {Taniguchi}, Y. 2012, \aap, 548, A4
+
+\bibitem[{{Springel} {et~al.}(2005){Springel}, {White}, {Jenkins}, {Frenk},
+  {Yoshida}, {Gao}, {Navarro}, {Thacker}, {Croton}, {Helly}, {Peacock}, {Cole},
+  {Thomas}, {Couchman}, {Evrard}, {Colberg}, \& {Pearce}}]{Springel:2005lr}
+{Springel}, V., {White}, S.~D.~M., {Jenkins}, A., {Frenk}, C.~S., {Yoshida},
+  N., {Gao}, L., {Navarro}, J., {Thacker}, R., {Croton}, D., {Helly}, J.,
+  {Peacock}, J.~A., {Cole}, S., {Thomas}, P., {Couchman}, H., {Evrard}, A.,
+  {Colberg}, J., \& {Pearce}, F. 2005, \nat, 435, 629
+
+\bibitem[{{Swetz} {et~al.}(2011)}]{Swetz:2011qy}
+{Swetz}, D.~S. {et~al.} 2011, \apjs, 194, 41
+
+\bibitem[{{Tacconi} {et~al.}(2008)}]{2008ApJ...680..246T}
+{Tacconi}, L.~J. {et~al.} 2008, \apj, 680, 246
+
+\bibitem[{{Tamura} {et~al.}(2015){Tamura}, {Oguri}, {Iono}, {Hatsukade},
+  {Matsuda}, \& {Hayashi}}]{Tamura:2015lq}
+{Tamura}, Y., {Oguri}, M., {Iono}, D., {Hatsukade}, B., {Matsuda}, Y., \&
+  {Hayashi}, M. 2015, ArXiv e-prints
+
+\bibitem[{{Torrey} {et~al.}(2012){Torrey}, {Cox}, {Kewley}, \&
+  {Hernquist}}]{Torrey12}
+{Torrey}, P., {Cox}, T.~J., {Kewley}, L., \& {Hernquist}, L. 2012, \apj, 746,
+  108
+
+\bibitem[{{Treu}(2010)}]{Treu:2010fk}
+{Treu}, T. 2010, \araa, 48, 87
+
+\bibitem[{{Vieira} {et~al.}(2013)}]{Vieira:2013fk}
+{Vieira}, J.~D. {et~al.} 2013, \nat, 495, 344
+
+\bibitem[{{Wang} {et~al.}(2014){Wang}, {Viero}, {Clarke}, {Bock}, {Buat},
+  {Conley}, {Farrah}, {Guo}, {Heinis}, {Magdis}, {Marchetti}, {Marsden},
+  {Norberg}, {Oliver}, {Page}, {Roehlly}, {Roseboom}, {Schulz}, {Smith},
+  {Vaccari}, \& {Zemcov}}]{Wang:2014lr}
+{Wang}, L., {Viero}, M., {Clarke}, C., {Bock}, J., {Buat}, V., {Conley}, A.,
+  {Farrah}, D., {Guo}, K., {Heinis}, S., {Magdis}, G., {Marchetti}, L.,
+  {Marsden}, G., {Norberg}, P., {Oliver}, S.~J., {Page}, M.~J., {Roehlly}, Y.,
+  {Roseboom}, I.~G., {Schulz}, B., {Smith}, A.~J., {Vaccari}, M., \& {Zemcov},
+  M. 2014, \mnras, 444, 2870
+
+\bibitem[{{Wardlow} {et~al.}(2013)}]{Wardlow:2013lr}
+{Wardlow}, J.~L. {et~al.} 2013, \apj, 762, 59
+
+\bibitem[{{Wei{\ss}} {et~al.}(2009){Wei{\ss}}, {Kov{\'a}cs}, {Coppin}, {Greve},
+  {Walter}, {Smail}, {Dunlop}, {Knudsen}, {Alexander}, {Bertoldi}, {Brandt},
+  {Chapman}, {Cox}, {Dannerbauer}, {De Breuck}, {Gawiser}, {Ivison}, {Lutz},
+  {Menten}, {Koekemoer}, {Kreysa}, {Kurczynski}, {Rix}, {Schinnerer}, \& {van
+  der Werf}}]{Weis:2009ly}
+{Wei{\ss}}, A., {Kov{\'a}cs}, A., {Coppin}, K., {Greve}, T.~R., {Walter}, F.,
+  {Smail}, I., {Dunlop}, J.~S., {Knudsen}, K.~K., {Alexander}, D.~M.,
+  {Bertoldi}, F., {Brandt}, W.~N., {Chapman}, S.~C., {Cox}, P., {Dannerbauer},
+  H., {De Breuck}, C., {Gawiser}, E., {Ivison}, R.~J., {Lutz}, D., {Menten},
+  K.~M., {Koekemoer}, A.~M., {Kreysa}, E., {Kurczynski}, P., {Rix}, H.-W.,
+  {Schinnerer}, E., \& {van der Werf}, P.~P. 2009, \apj, 707, 1201
+
+\bibitem[{{Wyithe} {et~al.}(2011){Wyithe}, {Yan}, {Windhorst}, \&
+  {Mao}}]{Wyithe:2011rm}
+{Wyithe}, J.~S.~B., {Yan}, H., {Windhorst}, R.~A., \& {Mao}, S. 2011, \nat,
+  469, 181
+
+\bibitem[{{Younger} {et~al.}(2007){Younger}, {Fazio}, {Huang}, {Yun}, {Wilson},
+  {Ashby}, {Gurwell}, {Lai}, {Peck}, {Petitpas}, {Wilner}, {Iono}, {Kohno},
+  {Kawabe}, {Hughes}, {Aretxaga}, {Webb}, {Mart{\'{\i}}nez-Sansigre}, {Kim},
+  {Scott}, {Austermann}, {Perera}, {Lowenthal}, {Schinnerer}, \& {Smol{\v
+  c}i{\'c}}}]{Younger:2007fk}
+{Younger}, J.~D., {Fazio}, G.~G., {Huang}, J.-S., {Yun}, M.~S., {Wilson},
+  G.~W., {Ashby}, M.~L.~N., {Gurwell}, M.~A., {Lai}, K., {Peck}, A.~B.,
+  {Petitpas}, G.~R., {Wilner}, D.~J., {Iono}, D., {Kohno}, K., {Kawabe}, R.,
+  {Hughes}, D.~H., {Aretxaga}, I., {Webb}, T., {Mart{\'{\i}}nez-Sansigre}, A.,
+  {Kim}, S., {Scott}, K.~S., {Austermann}, J., {Perera}, T., {Lowenthal},
+  J.~D., {Schinnerer}, E., \& {Smol{\v c}i{\'c}}, V. 2007, \apj, 671, 1531
+
+\bibitem[{{Younger} {et~al.}(2009){Younger}, {Fazio}, {Huang}, {Yun}, {Wilson},
+  {Ashby}, {Gurwell}, {Peck}, {Petitpas}, {Wilner}, {Hughes}, {Aretxaga},
+  {Kim}, {Scott}, {Austermann}, {Perera}, \& {Lowenthal}}]{Younger:2009lr}
+{Younger}, J.~D., {Fazio}, G.~G., {Huang}, J.-S., {Yun}, M.~S., {Wilson},
+  G.~W., {Ashby}, M.~L.~N., {Gurwell}, M.~A., {Peck}, A.~B., {Petitpas}, G.~R.,
+  {Wilner}, D.~J., {Hughes}, D.~H., {Aretxaga}, I., {Kim}, S., {Scott}, K.~S.,
+  {Austermann}, J., {Perera}, T., \& {Lowenthal}, J.~D. 2009, \apj, 704, 803
+
+\bibitem[{{Zavala} {et~al.}(2014){Zavala}, {Aretxaga}, \&
+  {Hughes}}]{Zavala:2014lr}
+{Zavala}, J.~A., {Aretxaga}, I., \& {Hughes}, D.~H. 2014, \mnras, 443, 2384
+
+\end{thebibliography}
 

### 2015-04-22 LaTeX/ms.tex
Deleted unnecessary figures.

@@
 
-    The {\it Herschel} Multi-tiered Extragalactic Survey (HerMES) has
-    identified large numbers of dusty star-forming galaxies (DSFGs) over a wide
-    range in redshift.  A detailed understanding of these DSFGs is hampered by
-    the poor spatial resolution of {\it Herschel}.  We present 870$\,\mu$m
-    0$\farcs$45 imaging obtained in Cycle~0 with the Atacama Large
-    Millimeter/submillimeter Array (ALMA) of a sample of 29 HerMES DSFGs.  The
-    ALMA imaging reveals that these DSFGs comprise a total of 62 sources (down
-    to the $5\sigma$ limit in our ALMA sample; $\sigma \approx 0.2\,$mJy).
-    Optical or near-infrared imaging indicates that 36 of the ALMA sources
-    experience a significant flux boost from gravitational lensing ($\mu >
-    1.1$), but only 6 are strongly lensed and show multiple images.  We
-    introduce and make use of {\sc uvmcmcfit}, a general purpose and publicly
-    available Markov chain Monte Carlo visibility plane analysis tool to
-    analyze the source properties.  Combined with our previous work on brighter
-    {\it Herschel} sources, the lens models presented here tentatively favor
-    intrinsic number counts for DSFGs with a break near 8$\,$mJy at
-    880$\,\mu$m and a steep fall off at higher flux densities.  Nearly 70\% of
-    the {\it Herschel} sources break down into multiple ALMA counterparts,
-    consistent with previous research indicating that the multiplicity rate is
-    high in bright sources discovered in single-dish sub-mm or FIR surveys.
-    The ALMA counterparts to our {\it Herschel} targets are located
-    significantly closer to each other than ALMA counterparts to sources found
-    in the LABOCA ECDFS Submillimeter Survey.  Theoretical models underpredict
-    the excess number of sources with small separations seen in our ALMA
-    sample.  The high multiplicity rate and low projected separations between
-    sources seen in our sample argue in favor of interactions and mergers
-    plausibly driving both the prodigious emission from the brightest DSFGs as
-    well as the sharp downturn above $S_{880} = 8\,$mJy.
+The {\it Herschel} Multi-tiered Extragalactic Survey (HerMES) has identified large numbers of dusty star-forming galaxies (DSFGs) over a wide range in redshift.
+A detailed understanding of these DSFGs is hampered by the poor spatial resolution of {\it Herschel}.
+We present 870$\,\mu$m 0$\farcs$45 imaging obtained in Cycle~0 with the Atacama Large Millimeter/submillimeter Array (ALMA) of a sample of 29 HerMES DSFGs.
+The ALMA imaging reveals that these DSFGs comprise a total of 62 sources (down to the $5\sigma$ limit in our ALMA sample; $\sigma \approx 0.2\,$mJy).
+Optical or near-infrared imaging indicates that 36 of the ALMA sources experience a significant flux boost from gravitational lensing ($\mu > 1.1$), but only 6 are strongly lensed and show multiple images.
+We introduce and make use of {\sc uvmcmcfit}, a general purpose and publicly available Markov chain Monte Carlo visibility plane analysis tool to analyze the source properties.
+Combined with our previous work on brighter {\it Herschel} sources, the lens models presented here tentatively favor intrinsic number counts for DSFGs with a break near 8$\,$mJy at 880$\,\mu$m and a steep fall off at higher flux densities.
+Nearly 70\% of the {\it Herschel} sources break down into multiple ALMA counterparts, consistent with previous research indicating that the multiplicity rate is high in bright sources discovered in single-dish sub-mm or FIR surveys.
+The ALMA counterparts to our {\it Herschel} targets are located significantly closer to each other than ALMA counterparts to sources found in the LABOCA ECDFS Submillimeter Survey.
+Theoretical models underpredict the excess number of sources with small separations seen in our ALMA sample.
+The high multiplicity rate and low projected separations between sources seen in our sample argue in favor of interactions and mergers plausibly driving both the prodigious emission from the brightest DSFGs as well as the sharp downturn above $S_{880} = 8\,$mJy.
 
@@
 for each of the 250$\, \mu$m, 350$\,\mu$m, and 500$\,\mu$m {\it Herschel}
-Spectral and Photometric Imaging REceiver \citep[SPIRE;][]{2010A&A...518L...3G}
+Spectral and Photometric Imaging REceiver \citep[SPIRE;][]{Griffin:2010lr}
 channels using the SUSSEXtractor peak finder algorithm \citep{Savage:2007sf}.
@@
 
-\bibitem[{{Griffin} {et~al.}(2010)}]{2010A&A...518L...3G}
+\bibitem[{{Griffin} {et~al.}(2010)}]{Griffin:2010lr}
 {Griffin}, M.~J. {et~al.} 2010, \aap, 518, L3+

### 2015-05-04 LaTeX/ms.tex
Bug fix in table 1 and 3
Plus other minor changes.

@@
 
-\slugcomment{To be submitted to the ApJ}
+\slugcomment{Submitted to the ApJ}
 
@@
 R.~J.~Ivison\altaffilmark{15,16},
-M.~Jarvis\altaffilmark{17},
+M.~Jarvis\altaffilmark{17,18},
 C.~Lacey\altaffilmark{6},
@@
 S.~J.~Oliver\altaffilmark{3},
-I.~P{\'e}rez-Fournon\altaffilmark{18,19},
-D.~Rigopoulou\altaffilmark{20,21},
+I.~P{\'e}rez-Fournon\altaffilmark{19,20},
+D.~Rigopoulou\altaffilmark{21,17},
 I.~G.~Roseboom\altaffilmark{3,16},
@@
 \altaffiltext{16}{Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
-\altaffiltext{17}{Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Hertfordshire AL10 9AB, UK}
-\altaffiltext{18}{Instituto de Astrof{\'\i}sica de Canarias (IAC), E-38200 La Laguna, Tenerife, Spain}
-\altaffiltext{19}{Departamento de Astrof{\'\i}sica, Universidad de La Laguna (ULL), E-38205 La Laguna, Tenerife, Spain}
-\altaffiltext{20}{RAL Space, Rutherford Appleton Laboratory, Chilton, Didcot, Oxfordshire OX11 0QX, UK}
-\altaffiltext{21}{Department of Astrophysics, Denys Wilkinson Building, University of Oxford, Keble Road, Oxford OX1 3RH, UK}
+\altaffiltext{17}{Department of Astrophysics, Denys Wilkinson Building, University of Oxford, Keble Road, Oxford OX1 3RH, UK}
+\altaffiltext{18}{Astrophysics Group, Physics Department, University of the Western Cape, Private Bag X17, 7535, Bellville, Cape Town, South Africa}
+\altaffiltext{19}{Instituto de Astrof{\'\i}sica de Canarias (IAC), E-38200 La Laguna, Tenerife, Spain}
+\altaffiltext{20}{Departamento de Astrof{\'\i}sica, Universidad de La Laguna (ULL), E-38205 La Laguna, Tenerife, Spain}
+\altaffiltext{21}{RAL Space, Rutherford Appleton Laboratory, Chilton, Didcot, Oxfordshire OX11 0QX, UK}
 \altaffiltext{22}{Department of Physics \& Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T~1Z1, Canada}
@@
 slope of $\alpha = -0.24$ and is consistent with non-thermal emission from the
-lens.
+lens.  For this target, we show VIDEO $K_{\rm s}$ imaging
+\citep{Jarvis:2013lr}.
 
@@
 
-The National Radio Astronomy Observatory is a facility of the National Science
-Foundation operated under cooperative agreement by Associated Universities,
-Inc.  The Dark Cosmology Centre is funded by the Danish National Research
-Foundation.
+The VIDEO imaging data are based on data products from observations
+made with ESO Telescopes at the La Silla or Paranal Observatories under ESO
+programme ID 179.A-2006.
 
@@
 
-R.J.I. acknowledges support from European Research Council Advanced
+The National Radio Astronomy Observatory is a facility of the National Science
+Foundation operated under cooperative agreement by Associated Universities,
+Inc.  The Dark Cosmology Centre is funded by the Danish National Research
+Foundation. R.J.I. acknowledges support from European Research Council Advanced
 Investigator Grant, Cosmicism, 321302. C.C.H. is grateful to the Gordon and
@@
 %\bibliography{rbussman}
-\begin{thebibliography}{106}
+\begin{thebibliography}{107}
 \expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
@@
 
+\bibitem[{{Jarvis} {et~al.}(2013){Jarvis}, {Bonfield}, {Bruce}, {Geach},
+  {McAlpine}, {McLure}, {Gonz{\'a}lez-Solares}, {Irwin}, {Lewis}, {Yoldas},
+  {Andreon}, {Cross}, {Emerson}, {Dalton}, {Dunlop}, {Hodgkin}, {Le},
+  {Karouzos}, {Meisenheimer}, {Oliver}, {Rawlings}, {Simpson}, {Smail},
+  {Smith}, {Sullivan}, {Sutherland}, {White}, \& {Zwart}}]{Jarvis:2013lr}
+{Jarvis}, M.~J., {Bonfield}, D.~G., {Bruce}, V.~A., {Geach}, J.~E., {McAlpine},
+  K., {McLure}, R.~J., {Gonz{\'a}lez-Solares}, E., {Irwin}, M., {Lewis}, J.,
+  {Yoldas}, A.~K., {Andreon}, S., {Cross}, N.~J.~G., {Emerson}, J.~P.,
+  {Dalton}, G., {Dunlop}, J.~S., {Hodgkin}, S.~T., {Le}, F.~O., {Karouzos}, M.,
+  {Meisenheimer}, K., {Oliver}, S., {Rawlings}, S., {Simpson}, C., {Smail}, I.,
+  {Smith}, D.~J.~B., {Sullivan}, M., {Sutherland}, W., {White}, S.~V., \&
+  {Zwart}, J.~T.~L. 2013, \mnras, 428, 1281
+
 \bibitem[{{Jiang} {et~al.}(2014){Jiang}, {Helly}, {Cole}, \&

### 2015-05-04 Code/cosmos_lumfunc.py

@@ -230,9 +230,9 @@ dndS[high] = dndS2[high]
 line3, = plt.plot(Svector, dndS, color='blue', lw=1.5,
         label=r'PL, $S_\star = 15\,{\rm mJy}$')
 
-data1, = plt.plot(bin_centers, diff890, 'o', label='COSMOS', color='black')
+data1, = plt.plot(bin_centers, diff890, 'o', label='COSMOS', color='#A9D0F5')
 plt.errorbar(bin_centers, diff890, yerr=e_diff890, fmt='o',
-        ecolor='gray', capsize=0, color='black')
+        ecolor='gray', capsize=0, color='#A9D0F5')
 data2, = plt.plot(alessfluxes, alesscounts, 'D', label='ALESS', color='pink')
 plt.errorbar(alessfluxes, alesscounts, yerr=e_alesscounts, fmt='D',
         ecolor='gray', capsize=0, color='pink')

### 2015-05-04 Code/maketable_source.py

@@ -23,6 +23,7 @@ mu_estimate = False
 cwd = os.getcwd()
 
 observed = ascii.read('../Data/table_observed.dat')
+#observed.sort('target')
 
 # read in the sample targets
 anloc = '../../../../ModelFits/'
@@ -62,7 +63,7 @@ for itarg in range(0, ntarg):
     e500 = dataphot['e500'][itarg]
     strfmt = '{0:12} ${1:4.0f} \pm {2:2.0f}$ & ${3:4.0f} \pm {4:2.0f}$ & ' \
             + '${5:4.0f} \pm {6:2.0f}$'
-    print(strfmt.format(objname, s250, e250, s350, e350, s500, e500))
+    #print(strfmt.format(objname, s250, e250, s350, e350, s500, e500))
     fitdir = anloc + dataname[itarg] + '/' + goodfit + '/'
     os.chdir(fitdir)
 
@@ -354,6 +355,8 @@ for itarg in range(0, ntarg):
             #msgfmt = msg.format(mu_indiv, e_mu_indiv)            
             #print(msgfmt)
 
+        #if nsource > 1:
+        #    print(' ')
         for isource in range(nsource):
 
             pbcorr = observed['pbcorr'][sourcecounter]
@@ -386,7 +389,7 @@ for itarg in range(0, ntarg):
             if tag2 in fitresults.keys():
                 if fitresultsgood[tag2].mean() == 100:
                     continue
-                observedflux = fluxdist / pbcorr * fitresultsgood[tag2] / remu
+                observedflux = fluxdist / pbcorr * fitresultsgood[tag2]# / remu
                 mu_indiv = remu#fitresultsgood[tag2].mean()
                 e_mu_indiv = e_remu#fitresultsgood[tag2].std()
             else:
@@ -473,7 +476,7 @@ for itarg in range(0, ntarg):
                     numpy.cos(decdeg_centroid) / 3600
             decdeg = decdeg_centroid + (ddecdeg_source) / 3600
             c = SkyCoord(ra=radeg*u.degree, dec=decdeg*u.degree)
-            #fullRADec = c.to_string('hmsdms', sep=':')
+            fullRADec = c.to_string('hmsdms', sep=':')
 
             # Effective Radius
[…]
